### 2020-10-25 Week3/Code/TAutoCorr.tex
CMEECourseWork

\documentclass[12pt]{paper}

\title{Autocorrelation of Annual Temperature in Key West, Florida for the 20th Century}

\author{Cong Liu}

\date{Oct, 2020}

\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage[colorlinks]{hyperref}

\begin{document}
  \maketitle
  \tableofcontents
  \begin{abstract}
    This paper concerns whether temperatures of years are autocorrelated. Temperatures
    in Key West, Florida for 20th century were used. Lag 1 autocorrelation was tested, and 
    \textit{p}-value was estimated using a simulation approach. The results showed a weak but significant
    correlation between temperature of one year and its successive year.

  \end{abstract}

  \section{Introduction}
  Autocorrelation refers to correlation between current values of a variable and its past values.
  If autocorrelation is found between values that are \textit{k} time periods apart, it is called
  a lag \textit{k} autocorrelation. In this paper, autocorrelation in temperatures of Key West, 
  Florida in 20th century was tested and \textit{p}-value was estimated, showing a weak but significant
  lag 1 autocorrelation.

  \section{Materials \& Methods}

    \subsection{Data of Temperatures}
    The raw data file of temperatures is named as KeyWestAnnualMeanTemperature.Rdata, 
    which is accessible in 
    \newline
    \href{https://github.com/mhasoba/TheMulQuaBio/tree/master/content/data}{https://github.com/mhasoba/TheMulQuaBio/tree/master/content/data}.
    It was plotted by a R script.

    \subsection{Autocorrelation Test}
    A R script was used to calculate Pearson's correlation coefficient between temperatures that
    are 1 year apart.

    \subsection{Estimation of \textit{p}-value}
    A R script is used to estimate \textit{p}-value. To begin with, values of temperature were
    rearranged randomly, and Pearson's correlation coefficient of lag 1 autocorrelation was calculated.
    This process was repeated 10,000 times, and the fraction of correlation coefficients whose absolute 
    values are larger than that from raw data is approximate \textit{p}-value.

  \section{Results}

    \subsection{Plot of Raw Data}
    Figure 1 illustrates temperatures in Key West, Florida for 20th century.

    \begin{figure}[H]
        \centering
        \includegraphics[width=0.7\textwidth]{TAutoCorr_Figure1.pdf}
        \caption{Temperature in Key West, Florida}
        \label{Fig. 2}    
    \end{figure}

    \subsection{Test of Autocorrelation}
    The correlation coefficient of temperatures 1 year apart is 0.3262, and approximate 
    \textit{p}-value was 0.0013.

  \section{Discussion}
  Correlation coefficient measures the extent that two variables are linearly correlated.
  A positive correlation coefficient means positive correlation between two variables. If 
  the correlation coefficient is negative, then there is a negative correlation. The closer
  the absolute value of correlation coefficient to 1, the stronger the correlation is. Here, the
  correlation coefficient between one-year-apart temperatures is 0.3262, showing that there is a weak 
  positive correlation between the temperatures of one year and its successive year.
  \newline
  The statistical significance is measured by \textit{p}-value. It is defined as the probability that
  null hypothesis is rejected while it is true, namely, the false positive probability. A 
  small \textit{p}-value means high significance. Here, the 
  estimated \textit{p}-value was 0.0013, indicating the correlation is significant.

  \section{Conclusion}
  Overall, a weak but significant lag 1 autocorrelation was found in temperatures of Key West, Florida 
  for 20th century.

  \section{Supplement}
  All codes are wraped in TAutoCorr.R, which is accessible in 
\end{document}

### 2020-10-25 Week3/Code/DataWrang.R

@@ -1,0 +1,68 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: DataWrang.R
+#Work Path: CMEECourseWork/Week3
+#Dependency: tidyverse
+#Input:
+#Function: Data wrangling.R
+#Output:
+#Usage:
+#Date: Oct, 2020
+
+################################################################
+################## Wrangling the Pound Hill Dataset ############
+################################################################
+setwd("CMEECourseWork/Week3")
+############# Load the dataset ###############
+# header = false because the raw data don't have real headers
+MyData <- as.matrix(read.csv("Data/PoundHillData.csv", header = FALSE))
+
+# header = true because we do have metadata headers
+MyMetaData <- read.csv("Data/PoundHillMetaData.csv", header = TRUE, sep = ";")
+
+############# Inspect the dataset ###############
+head(MyData)
+dim(MyData)
+str(MyData)
+fix(MyData) #you can also do this
+fix(MyMetaData)
+
+############# Transpose ###############
+# To get those species into columns and treatments into rows 
+MyData <- t(MyData) 
+head(MyData)
+dim(MyData)
+
+############# Replace species absences with zeros ###############
+MyData[MyData == ""] = 0
+
+############# Convert raw matrix to data frame ###############
+
+TempData <- as.data.frame(MyData[-1,],stringsAsFactors = F) #stringsAsFactors = F is important!
+colnames(TempData) <- MyData[1,] # assign column names from original data
+
+############# Convert from wide to long format  ###############
+require(reshape2) # load the reshape2 package
+
+?melt #check out the melt function
+
+MyWrangledData <- melt(TempData, id=c("Cultivation", "Block", "Plot", "Quadrat"), variable.name = "Species", value.name = "Count")
+
+MyWrangledData[, "Cultivation"] <- as.factor(MyWrangledData[, "Cultivation"])
+MyWrangledData[, "Block"] <- as.factor(MyWrangledData[, "Block"])
+MyWrangledData[, "Plot"] <- as.factor(MyWrangledData[, "Plot"])
+MyWrangledData[, "Quadrat"] <- as.factor(MyWrangledData[, "Quadrat"])
+MyWrangledData[, "Count"] <- as.integer(MyWrangledData[, "Count"])
+
+str(MyWrangledData)
+head(MyWrangledData)
+dim(MyWrangledData)
+
[…]

### 2020-10-25 Week3/Code/MyBars.R

@@ -1,0 +1,63 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: MyBars.R
+#Work Path: CMEECourseWork/Week3
+#Dependency: ggplot2
+#Input: Data/Results.txt
+#Function: Exemplify annotating a plot
+#Output: Results/MyBars.pdf
+#Usage: Rscript MyBars.R
+#Date: Oct, 2020
+
+library("ggplot2")
+a <- read.table("Data/Results.txt", header = TRUE)
+head(a)
+
+a$ymin <- rep(0, dim(a)[1]) # append a column of zeros
+
+pdf("Results/MyBars.pdf")
+
+# Print the first linerange
+p <- ggplot(a)
+p <- p + geom_linerange(data = a, aes(
+  x = x,
+  ymin = ymin,
+  ymax = y1,
+  size = (0.5)
+),
+colour = "#E69F00",
+alpha = 1/2, show.legend = FALSE)
+
+# Print the second linerange
+p <- p + geom_linerange(data = a, aes(
+  x = x,
+  ymin = ymin,
+  ymax = y2,
+  size = (0.5)
+),
+colour = "#56B4E9",
+alpha = 1/2, show.legend = FALSE)
+
+# Print the third linerange:
+p <- p + geom_linerange(data = a, aes(
+  x = x,
+  ymin = ymin,
+  ymax = y3,
+  size = (0.5)
+),
+colour = "#D55E00",
+alpha = 1/2, show.legend = FALSE)
+
+# Annotate the plot with labels:
+p <- p + geom_text(data = a, aes(x = x, y = -500, label = Label))
+
+# now set the axis labels, remove the legend, and prepare for bw printing
+p <- p + scale_x_continuous("My x axis",
+                            breaks = seq(3, 5, by = 0.05)) + 
+  scale_y_continuous("My y axis") + 
+  theme_bw() + 
+  theme(legend.position = "none") 
+p
+
+
+dev.off()

### 2020-10-25 Week3/Code/R_conditionals.R

@@ -1,0 +1,48 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: R_conditionals.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Examples of functions with conditionals
+#Output:
+#Usage: Rscript R_conditionals.R
+#Date: Oct, 2020
+
+# Checks if an integer is even
+is.even <- function(n = 2){
+  if (n %% 2 == 0)
+  {
+    return(paste(n,'is even!'))
+  } 
+  return(paste(n,'is odd!'))
+}
+
+is.even(6)
+
+# Checks if a number is a power of 2
+is.power2 <- function(n = 2){
+  if (log2(n) %% 1==0)
+  {
+    return(paste(n, 'is a power of 2!'))
+  } 
+  return(paste(n,'is not a power of 2!'))
+}
+
+is.power2(4)
+
+# Checks if a number is prime
+is.prime <- function(n){
+  if (n==0){
+    return(paste(n,'is a zero!'))
+  }
+  if (n==1){
+    return(paste(n,'is just a unit!'))
+  }
+  ints <- 2:(n-1)
+  if (all(n%%ints!=0)){
+    return(paste(n,'is a prime!'))
+  } 
+  return(paste(n,'is a composite!'))
+}
+
+is.prime(3)

### 2020-10-25 Week3/Code/Ricker.R

@@ -1,0 +1,26 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: Ricker.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Illustrate Ricker model of population growth
+#Output: A figure shows population growth of Ricker model
+#Usage: Rscript Ricker.R
+#Date: Oct, 2020
+
+Ricker <- function(N0=1, r=1, K=10, generations=50)
+{
+  # Runs a simulation of the Ricker model
+  # Returns a vector of length generations
+  
+  N <- rep(NA, generations)    # Creates a vector of NA
+  
+  N[1] <- N0
+  for (t in 2:generations)
+  {
+    N[t] <- N[t-1] * exp(r*(1.0-(N[t-1]/K)))
+  }
+  return (N)
+}
+
+plot(Ricker(generations=10), type="l")

### 2020-10-25 Week3/Code/SQLinR.R

@@ -1,0 +1,74 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: SQLinR.R
+#Work Path: CMEECourseWork/Week3
+#Dependency:
+#Input:
+#Function: Build, manipulate and access database using SQLite
+#Output:
+#Usage:
+#Date: Oct, 2020
+
+#install the sqlite package
+install.packages('sqldf')
+
+# To load the packages
+library(sqldf)
+
+# The command below opens a connection to the database.
+#If the database does not yet exist, one is created in the working directory of R.
+db <- dbConnect(SQLite(), dbname='Test.sqlite')
+
+# Now let's enter some data to the table
+# Using the db connection to our database, the data are entered using SQL queries
+# The next command just create the table
+dbSendQuery(conn = db,
+            "CREATE TABLE Consumer
+       (OriginalID TEXT,
+        ConKingdom TEXT,
+        ConPhylum TEXT,
+        ConSpecies TEXT)")
+
+# Once the table is created, we can enter the data.
+#INSERT specifies where the data is entered (here the School table).
+#VALUES contains the data
+
+ dbSendQuery(conn = db,
+         "INSERT INTO Consumer
+         VALUES (1, 'Animalia', 'Arthropoda', 'Chaoborus trivittatus')")
+ dbSendQuery(conn = db,
+         "INSERT INTO Consumer
+         VALUES (2, 'Animalia', 'Arthropoda', 'Chaoborus americanus')")
+ dbSendQuery(conn = db,
+         "INSERT INTO Consumer
+         VALUES (3, 'Animalia', 'Chordata', 'Stizostedion vitreum')")
+
+
+# Once we have our table, we can query the results using:
+
+dbGetQuery(db, "SELECT * FROM Consumer")
+dbGetQuery(db, "SELECT * FROM Consumer WHERE ConPhylum='Chordata'")
+
+
+# Tables can be also imported from csv files.
+# As example, let's use the Biotraits dataset.
+# The easiest way is to read the csv files into R as data frames.
+# Then the data frames are imported into the database.
+
+Resource <- read.csv("Data/Resource.csv")  # Read csv files into R
+
+# Import data frames into database
+ dbWriteTable(conn = db, name = "Resource", value = Resource, row.names = FALSE)
+
+# Check that the data have been correctly imported into the School table.
+ dbListTables(db)                 # The tables in the database
+ dbListFields(db,"Resource")       # The columns in a table
[…]

### 2020-10-25 Week3/Code/TAutoCorr.R

@@ -1,0 +1,48 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: TAutoCorr.R
+#Work Directory: CMEECourseWork/Week3
+#Dependency: ggplot2
+#Input: Data/KeyWestAnnualMeanTemperature.RData
+#Function: Test autocorrelation of each year's temperature 
+#Output: 
+#Usage:
+#Date: Oct, 2020
+
+setwd("CMEECourseWork/Week3")
+load("Data/KeyWestAnnualMeanTemperature.RData") #Import data
+
+library(ggplot2)
+
+pdf("TAutoCorr_Figure1.pdf")
+p0 = ggplot(data = ats, aes(x = Year, y = Temp)) + #Plot temperatures 
+  geom_point(size = 0.5) + #Adjust point size
+  labs(x = "Year",
+       y = "Temperature") + #Set titles for the plot, x axis and y axis
+  theme(plot.title  = element_text(size = 10, hjust = 0.5), #Adjust word size of title and put it in the center
+        axis.title.x = element_text(size = 10), #Adjust word size of x axis title
+        axis.title.y = element_text(size = 10)) #Adjust word size of y axis title
+p0
+dev.off()
+
+yr0 = ats$Temp[1:99]
+yr1 = ats$Temp[2:100]
+autoco = cor(yr0,yr1)
+autoco
+
+corrs = rep(NA, 10000)
+for (i in 1:10000) {
+  yr = sample(ats$Temp, size = 100, replace = F)
+  yr0 = yr[1:99]
+  yr1 = yr[2:100]
+  corrs[i] = cor(yr0, yr1)
+}
+corrs
+
+j = 0
+for (corr in corrs) {
+  if (abs(corr) > abs(autoco)) {
+    j = j + 1
+  }
+}
+j/10000

### 2020-10-25 Week3/Code/TreeHeight.R

@@ -1,0 +1,45 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: boilerplate.R
+#Work Path: CMEECourseWork/Week3
+#Input: Data/trees.csv
+#Function: Calculate heights of trees given distance of each tree 
+#          from its base and angle to its top, using  the trigonometric formula 
+#Output: Results/TreeHts.csv
+#Usage: Rscript TreeHeight.R
+#Date: Oct, 2020
+
+# Calculate heights of trees
+# height = distance * tan(radians)
+# ARGUMENTS
+# degrees: The angle of elevation of tree
+# distance: The distance from base of tree (e.g., meters)
+# OUTPUT
+# The heights of the tree, same units as "distance"
+TreeHeight <- function(degrees, distance){
+  radians <- degrees * pi / 180
+  height <- distance * tan(radians)
+  print(paste("Tree height is:", height))
+  
+  return (height)
+}
+
+
+getwd()
+setwd("CMEECourseWork/Week3")
+data = read.csv("Data/trees.csv", header = T)
+a = nrow(data)
+head(data)
+
+Tree.Height.m = c()
+for ( i in 1:a ){
+  distance = as.numeric(data$Distance.m[i])
+  degree = as.numeric(data$Angle.degrees[i])
+  height = TreeHeight(degree, distance)
+  Tree.Height.m[i] = height 
+}
+
+data_more = data.frame(data, Tree.Height.m)
+head(data_more)
+write.csv(data_more, "Results/TreeHts.csv", row.names = F)
+

### 2020-10-25 Week3/Code/Vectorize1.R

@@ -1,0 +1,28 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: Vectoriza1.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Exemplify vectorization's effect in computing efficiency and low speed of loops
+#Output:
+#Usage: Rscript Vectorize1.R
+#Date: Oct, 2020
+
+M <- matrix(runif(1000000),1000,1000)
+
+SumAllElements <- function(M){
+  Dimensions <- dim(M)
+  Tot <- 0
+  for (i in 1:Dimensions[1]){
+    for (j in 1:Dimensions[2]){
+      Tot <- Tot + M[i,j]
+    }
+  }
+  return (Tot)
+}
+
+print("Using loops, the time taken is:")
+print(system.time(SumAllElements(M)))
+
+print("Using the in-built vectorized function, the time taken is:")
+print(system.time(sum(M)))

### 2020-10-25 Week3/Code/Vectorize2.R

@@ -1,0 +1,57 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: Vectorize.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Simulate stochastic Ricker model in vectorized and un-victorized way,
+#          and compare their efficiency
+#Output:
+#Usage: Rscript Vectorize2.R
+#Date: Oct, 2020
+
+# Runs the stochastic Ricker equation with gaussian fluctuations
+
+rm(list=ls())
+
+stochrick<-function(p0=runif(1000,.5,1.5),r=1.2,K=1,sigma=0.2,numyears=100)
+{
+  #initialize
+  N<-matrix(NA,numyears,length(p0))
+  N[1,]<-p0
+  
+  for (pop in 1:length(p0)){#loop through the populations
+    
+    for (yr in 2:numyears){ #for each pop, loop through the years
+
+      N[yr,pop] <- N[yr-1,pop] * exp(r * (1 - N[yr - 1,pop] / K) + rnorm(1,0,sigma))
+    
+    }
+  
+  }
+ return(N)
+
+}
+
+# Now write another function called stochrickvect that vectorizes the above 
+# to the extent possible, with improved performance: 
+stochrickvect<-function(p0=runif(1000,.5,1.5),r=1.2,K=1,sigma=0.2,numyears=100)
+{
+  #initialize
+  N<-matrix(NA, nrow = 100, ncol = 1000)
+  N[1,]<-p0
+  
+  for (yr in 2:numyears){ #for each pop, loop through the years
+      
+      N[yr,] = N[yr-1,] * exp(r * (1 - N[yr - 1,] / K) + rnorm(1,0,sigma))
+      
+    }
+    
+  
+  return(N)
+}  
+
+print("Un-vectorized Stochastic Ricker takes:")
+print(system.time(res2<-stochrick()))
+
+print("Vectorized Stochastic Ricker takes:")
+print(system.time(res2<-stochrickvect()))

### 2020-10-25 Week3/Code/apply1.R

@@ -1,0 +1,24 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: apply1.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Exemplify the usage of *apply functions
+#Output:
+#Usage: Rscript apply1.R
+#Date: Oct, 2020
+
+## Build a random matrix
+M <- matrix(rnorm(100), 10, 10)
+
+## Take the mean of each row
+RowMeans <- apply(M, 1, mean)
+print (RowMeans)
+
+## Now the variance
+RowVars <- apply(M, 1, var)
+print (RowVars)
+
+## By column
+ColMeans <- apply(M, 2, mean)
+print (ColMeans)

### 2020-10-25 Week3/Code/apply2.R

@@ -1,0 +1,19 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: apply2.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Exemplify the usage of *apply functions
+#Output:
+#Usage: Rscript apply2.R
+#Date: Oct, 2020
+
+SomeOperation <- function(v){
+  if (sum(v) > 0){
+    return (v * 100)
+  }
+  return (v)
+}
+
+M <- matrix(rnorm(100), 10, 10)
+print (apply(M, 1, SomeOperation))

### 2020-10-25 Week3/Code/basic_io.R

@@ -1,0 +1,19 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: basic_io.R
+#Work Path: CMEECourseWork/Week3
+#Input: Data/trees.csv
+#Function: Illustrate R input-output 
+#Output: Results/MyData.csv
+#Usage: Rscript basic_io.R
+#Date: Oct, 2020
+
+MyData <- read.csv("Data/trees.csv", header = TRUE) # import with headers
+
+write.csv(MyData, "Results/MyData.csv") #write it out as a new file
+
+write.table(MyData[1,], file = "Results/MyData.csv",append=TRUE) # Append to it
+
+write.csv(MyData, "Results/MyData.csv", row.names=TRUE) # write row names
+
+write.table(MyData, "Results/MyData.csv", col.names=FALSE) # ignore column names

### 2020-10-25 Week3/Code/boilerplate.R

@@ -1,0 +1,24 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: boilerplate.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Illustrate skipping to next iteration of a loop
+#Output:
+#Usage: Rscript boilerplate.R
+#Date: Oct, 2020
+
+MyFunction <- function(Arg1, Arg2){
+  
+  # Statements involving Arg1, Arg2:
+  print(paste("Argument", as.character(Arg1), "is a", class(Arg1))) # print Arg1's type
+  print(paste("Argument", as.character(Arg2), "is a", class(Arg2))) # print Arg2's type
+  
+  return (c(Arg1, Arg2)) #this is optional, but very useful
+}
+
+MyFunction(1,2) #test the function
+MyFunction("Riki","Tiki") #A different test
+
+ls()
+class(MyFunction)

### 2020-10-25 Week3/Code/break.R

@@ -1,0 +1,20 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: break.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Illustrate breaking out of loops 
+#Output:
+#Usage: Rscript break.R
+#Date: Oct, 2020
+
+i <- 0 #Initialize i
+while(i < Inf) {
+  if (i == 10) {
+    break 
+  } # Break out of the while loop! 
+  else { 
+    cat("i equals " , i , " \n")
+    i <- i + 1 # Update i
+  }
+}

### 2020-10-25 Week3/Code/browse.R

@@ -1,0 +1,25 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: browse.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: An exemple of debugging
+#Output:
+#Usage:
+#Date: Oct, 2020
+
+Exponential <- function(N0 = 1, r = 1, generations = 10){
+  # Runs a simulation of exponential growth
+  # Returns a vector of length generations
+  
+  N <- rep(NA, generations)    # Creates a vector of NA
+  
+  N[1] <- N0
+  for (t in 2:generations){
+    N[t] <- N[t-1] * exp(r)
+#    browser()
+  }
+  return (N)
+}
+
+plot(Exponential(), type="l", main="Exponential growth")

### 2020-10-25 Week3/Code/control_flow.R

@@ -1,0 +1,47 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: control_flow.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Illustrate R control flow tools 
+#Output:
+#Usage: Rscript control_flow.R
+#Date: Oct, 2020
+
+a <- TRUE
+if (a == TRUE){
+  print ("a is TRUE")
+} else {
+  print ("a is FALSE")
+}
+
+z <- runif(1) ## Generate a uniformly distributed random number
+if (z <= 0.5) {print ("Less than a half")}
+
+z <- runif(1)
+if (z <= 0.5) {
+  print ("Less than a half")
+}
+
+for (i in 1:10){
+  j <- i * i
+  print(paste(i, " squared is", j ))
+}
+
+for(species in c('Heliodoxa rubinoides', 
+                 'Boissonneaua jardini', 
+                 'Sula nebouxii')){
+  print(paste('The species is', species))
+}
+
+v1 <- c("a","bc","def")
+for (i in v1){
+  print(i)
+}
+
+i <- 0
+while (i < 10){
+  i <- i+1
+  print(i^2)
+}
+

### 2020-10-25 Week3/Code/next.R

@@ -1,0 +1,15 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: next.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Illustrate skipping to next iteration of a loop
+#Output:
+#Usage: Rscript next.R
+#Date: Oct, 2020
+
+for (i in 1:10) {
+  if ((i %% 2) == 0) # check if the number is odd
+    next # pass to next iteration of loop 
+  print(i)
+}

### 2020-10-25 Week3/Code/sample.R

@@ -1,0 +1,78 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: sample.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Exemplify vectorization
+#Output:
+#Usage: Rscript sample.R
+#Date: Oct, 2020
+
+######### Functions ##########
+
+## A function to take a sample of size n from a population "popn" and return its mean
+myexperiment <- function(popn,n){
+  pop_sample <- sample(popn, n, replace = FALSE)
+  return(mean(pop_sample))
+}
+
+## Calculate means using a for loop without preallocation:
+loopy_sample1 <- function(popn, n, num){
+  result1 <- vector() #Initialize empty vector of size 1 
+  for(i in 1:num){
+    result1 <- c(result1, myexperiment(popn, n))
+  }
+  return(result1)
+}
+
+## To run "num" iterations of the experiment using a for loop on a vector with preallocation:
+loopy_sample2 <- function(popn, n, num){
+  result2 <- vector(,num) #Preallocate expected size
+  for(i in 1:num){
+    result2[i] <- myexperiment(popn, n)
+  }
+  return(result2)
+}
+
+## To run "num" iterations of the experiment using a for loop on a list with preallocation:
+loopy_sample3 <- function(popn, n, num){
+  result3 <- vector("list", num) #Preallocate expected size
+  for(i in 1:num){
+    result3[[i]] <- myexperiment(popn, n)
+  }
+  return(result3)
+}
+
+
+## To run "num" iterations of the experiment using vectorization with lapply:
+lapply_sample <- function(popn, n, num){
+  result4 <- lapply(1:num, function(i) myexperiment(popn, n))
+  return(result4)
+}
+
+## To run "num" iterations of the experiment using vectorization with lapply:
+sapply_sample <- function(popn, n, num){
+  result5 <- sapply(1:num, function(i) myexperiment(popn, n))
+  return(result5)
+}
+
+popn <- rnorm(1000) # Generate the population
+hist(popn)
+
+n <- 20 # sample size for each experiment
+num <- 1000 # Number of times to rerun the experiment
+
+print("The loopy, non-preallocation approach takes:" )
+print(system.time(loopy_sample1(popn, n, num)))
+
+print("The loopy, but with preallocation approach takes:" )
+print(system.time(loopy_sample2(popn, n, num)))
+
[…]

### 2020-10-25 Week3/Code/try.R

@@ -1,0 +1,36 @@
+#Language: R
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: try.R
+#Work Path: CMEECourseWork/Week3
+#Input:
+#Function: Exemplify the usage of try()
+#Output:
+#Usage:
+#Date: Oct, 2020
+
+doit <- function(x){
+  temp_x <- sample(x, replace = TRUE)
+  if(length(unique(temp_x)) > 30) {#only take mean if sample was sufficient
+    print(paste("Mean of this sample was:", as.character(mean(temp_x))))
+  } 
+  else {
+    stop("Couldn't calculate mean: too few unique values!")
+  }
+}
+
+popn <- rnorm(50)
+hist(popn)
+
+lapply(1:15, function(i) try(doit(popn)))
+
+result <- lapply(1:15, function(i) try(doit(popn), FALSE))
+
+class(result)
+
+result
+
+result <- vector("list", 15) #Preallocate/Initialize
+for(i in 1:15) {
+  result[[i]] <- try(doit(popn), FALSE)
+}
+

### 2020-10-25 Week3/Code/TAutoCorr.tex
CMEECourseWork

@@
-\documentclass[12pt]{paper}
+\documentclass[12pt]{article}
 
@@
 
-\author{Cong Liu}
+\author{Cong Liu (cong.liu20@imperial.ac.uk)}
 
@@
 \usepackage[colorlinks]{hyperref}
+\usepackage{hyperref}
 
@@
   \begin{abstract}
-    This paper concerns whether temperatures of years are autocorrelated. Temperatures
+    This study concerns whether temperatures of years are autocorrelated. Temperatures
     in Key West, Florida for 20th century were used. Lag 1 autocorrelation was tested, and 
@@
 
-    \subsection{Estimation of \textit{p}-value}
+    \subsection{Estimation of \texorpdfstring{$\mathit{p}$}{}-value}
     A R script is used to estimate \textit{p}-value. To begin with, values of temperature were
@@
   All codes are wraped in TAutoCorr.R, which is accessible in 
+  \newline
+  \href{https://github.com/CongLiu37/CMEECourseWork/tree/main/Week3/Code}{https://github.com/CongLiu37/CMEECourseWork/tree/main/Week3/Code}
 \end{document}

### 2020-10-30 Week3/Code/TAutoCorr.R
CMEECourseWork

@@ -10,11 +10,9 @@
 #Date: Oct, 2020
 
 load("Data/KeyWestAnnualMeanTemperature.RData") #Import data
-setwd("Code")
 
 library(ggplot2)
 
-pdf("TAutoCorr_Figure1.pdf")
 p0 = ggplot(data = ats, aes(x = Year, y = Temp)) + #Plot temperatures 
   geom_point(size = 0.5) + #Adjust point size
   labs(x = "Year",
@@ -23,7 +21,7 @@ p0 = ggplot(data = ats, aes(x = Year, y = Temp)) + #Plot temperatures
         axis.title.x = element_text(size = 10), #Adjust word size of x axis title
         axis.title.y = element_text(size = 10)) #Adjust word size of y axis title
 p0
-dev.off()
+
 
 yr0 = ats$Temp[1:99]
 yr1 = ats$Temp[2:100]
@@ -47,4 +45,5 @@ for (corr in corrs) {
     j = j + 1
   }
 }
-j/10000
+ap-p = j/10000
+ap-p

### 2020-12-07 MiniProject/Code/Report.tex
CMEECourseWork

%Language: LaTeX
%Author: Cong Liu (cong.liu20@imperial.ac.uk)
%Script: Report.tex
%Work directory: CMEECourseWork/Week3/Code
%Description: Report of the miniproject in thermal performance curves.

%Word Count

\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage[justification=centering]{caption}

\title{Model Selection to Find a Most Sufficient Model Fitting to Thermal Performance of Metabolic Traits\footnotemark[1]}

\author{Cong Liu\footnotemark[2]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{Word Count: 2611}
\footnotetext[2]{Department of Life Sciences (Silwood Park), Imperial College of Science, Technology and Medicine}

\date{Nov, 2020}

\linespread{1.5}
\begin{document}
  \maketitle
  \newpage

  \linenumbers
  \begin{abstract}
    Determining thermal dependence of biological traits provides better understanding in distribution patterns of species 
    and is helpful in assessing the impact of climate change on biological systems. Here, I fitted quadratic polynomial 
    model, cubic polynomial model, Briere model and Ratkowsky model to observed data of metabolic traits under different 
    temperatures to calculate thermal performance curves. Model averaging and selection by either AIC or BIC were 
    conducted to find one most sufficient model fitting to empirical data of each curve. 
    In most curves, AIC and BIC give support to 
    the same model and Ratkowsky model has the highest frequency of being the most suitable model 
    under two selection criteria. However, for some thermal performance curves in the dataset, even the best model 
    selected here fail in describing thermal dependence of metabolic traits, indicating that the four plausible models 
    are not suitable and more models need to be involved. Overall, the results show that Ratkowsky model is sufficient 
    for most thermal performance curves involved in this study.

  \end{abstract}

  \section{Introduction}

  Temperature is an important abiotic factor that influences the functioning of organisms, especially 
  for ectotherms whose body temperatures reflect that of their environments to different extent. It affects 
  the rates of biochemical reactions and consequently has profound influence on different biological 
  activities like metabolism, growth, development and reproduction \cite{sinclair2016can}. And this can 
  lead to further consequences in abundance and distribution of organisms \cite{schulte2011thermal}. 
  Besides, interactions among species are also affected by thermal environment \cite{grigaltchik2012thermal}.  
  \newline
  Thermal performance curve describes the dependence of performance (usually, the rate of a physiological 
  activities or fitness) on temperature quantitatively \cite{sinclair2016can}. Generally, organisms response 
  to temperature fluctuation in a similar manner. The value of performance peaks at some temperature point, 
  and decreases when temperature deviates from the maximum point, while extremely high or low temperatures are lethal 
  \cite{sinclair2016can,krenek2011thermal}. 
  The mathematical modelling of thermal performance curve provides a framework for the estimation of 
  physiological characters like the optimum temperature at which performance peaks, upper and lower 
  thermal limit thermal performance, and thermal tolerance range \cite{krenek2011thermal}. 
  Besides, it is also helpful in predicting 
  performance of organisms when temperature fluctuates. Thus, thermal performance curve is helpful in better 
  understanding distribution patterns of species. There is evidence that 
  the thermal tolerance range of a species is often corresponded 
  to the temperature fluctuation of its habitat, indicating the 
  importance of temperature as a selective force in shaping distribution pattern \cite{sunday2011global, clusella2011climatic}. 
  There is also evidence showing 
  that thermal sensitivity plays a role in the dynamics of biodiversity \cite{allen2002global}. Furthermore, 
  investigations in thermal performance curve help better predict the impact of current climate change on 
  biological process \cite{krenek2011thermal, sears2011introduction}.  
  \newline
  Currently, there are numerous mathematical models with different properties  
  that are used to illustrate thermal performance curves of different clades 
  \cite{krenek2011thermal,angilletta2006estimating}. Which model, or models are sufficient in describing thermal dependence 
  of performance is the main concern of this study. 
  Using a dataset of observed data from 841 thermal performance curves, 
  I calculated these curves by fitting 
  four plausible models to them. 
  Then I conducted model averaging and selection to find one model that is most sufficient to describe the observed data.
   Akaike information criterion (AIC) or 
  Bayesian information criterion (BIC) was used as model selection criterion \cite{johnson2004model}. 
  Besides, whether metabolic trait or habitat type is corresponded to models that get most support from 
  empirical data was assessed.

  \section{Materials and Methods}
    \subsection{Original Data}
    The original dataset used here is named as ThermRespData.csv and its field names are defined in another 
    file called BiotraitsTemplateDescription.pdf. Both files are accessible in 
    \newline 
    \href{https://github.com/mhasoba/TheMulQuaBio/tree/master/content/data}{https://github.com/mhasoba/TheMulQuaBio/tree/master/content/data}. 
    \newline 
    The main fields of interest are OriginalTraitValue (trait values) and ConTemp (the temperatures 
    in Celsius scale). Each thermal performance curve is corresponded to a unique ID from 1 to 903. 
    Among them 62 curves contain negative trait values and were removed. 
    So a total of 841 thermal performance curves was used in following analysis.

  \subsection{Plausible Models} 
    Denote by \textit{B} the trait value and \textit{T} the temperature. The function that describes 
    the relationship between temperature and trait value is  
    \begin{equation} 
      B = B(T) 
    \end{equation} 
    Plausible models are: (1) quadratic polynomial model with constants  
    $B_0$, $B_1$ and $B_2$: 
    \begin{equation} 
    B(T) = B_0 + B_1 T + B_2 T^2 
    \end{equation} 
    (2) cubic polynomial model with constants  
    $B_0$, $B_1$, $B_2$ and $B_3$: 
    \begin{equation} 
    B(T) = B_0 + B_1 T + B_2 T^2 + B_3 T^3 
    \end{equation} 
    (3) Briere model with constants  
    $B_0$, $T_0$ and $T_m$ 
    \cite{briere1999novel}: 
    \begin{equation}\label{equ:Briere} 
    B(T) = B_0 T (T - T_0) \sqrt{T_m - T} 
    \end{equation} 
    $T_0$ and $T_m$ are lower and upper thermal limit thermal performance. 
    \newline 
    (4) Ratkowsky model with constants  
    $T_0$, $T_m$, $a$ and $b$  
    \cite{ratkowsky1983model}: 
    \begin{equation} 
    B(T) = \{a (T-T_0) (1-e^{b(T-T_m)})\}^2 
    \end{equation} 
    $T_0$ and $T_m$ are lower and higher thermal limit thermal performance. 
  \subsection{Model Fitting} 
    To conduct model fitting, least square method was used, and non-linear models were fitted using Levenberg-Marquardt  
    algorithm \cite{ranganathan2004levenberg, lourakis2005brief}. Maximum iteration number was 200.  
    \newline 
    For fitting of Briere model, start values of $T_0$ and $T_m$ were the lowest and highest sampled temperatures 
    of each curve and they are denoted by $T_{0st}$ and $T_{mst}$ respectively. From Eq. (\ref{equ:Briere}), 
    \begin{equation}\label{lalala} 
    B_0 = \frac{B(T)}{T (T - T_0) \sqrt{T_m - T}} 
    \end{equation} 
    For each curve, remove samples with lowest and highest temperatures and denote the rest as  
    $\{(T_i, B_i), i = 1,2,\cdots,n-2\}$, where $n$ is sample size.  
    So from Eq. (\ref{lalala}), a rough estimation of $B_0$, denoted by $B_{0est}$ can be given by  
    \begin{equation}\label{esti} 
    B_{0est} = \frac{\sum_{i=1}^{n-2}\frac{B_i}{T_i (T_i - T_{0st}) \sqrt{T_{mst} - T_i}}}{n-2} 
    \end{equation} 
    The start values of $B_0$ was taken from a uniform distribution between $0$ and $2B_{0est}$. 
    Each curve was fitted 100 times with different start values of $B_0$. 
    \newline 
    As for fitting of Ratkowsky model, start values of $T_0$ and $T_m$ were the lowest and highest sampled temperatures 
    of each curve. Start values of $a$ and $b$ were taken from set  
    $\{10^i: i = -5,-4,-3,-2,-1,0,1,2,3,4\}$. So for each curve, there are ten start values of $a$ and $b$,  
    and 100 combinations of them. Hence, each curve was fitted 100 times with different start values.

  \subsection{Model Selection}
  After model fitting, AIC and BIC of all models  
  were calculated using  
  following equations \cite{johnson2004model}: 
  \begin{equation} 
  AIC = -2L + 2k 
  \end{equation} 
  \begin{equation} 
  BIC = -2L + klnn 
  \end{equation} 
  where $n$ is sample size, $k$ is number of parameters in the model, and $L$ is maximized log-likelihood value of the model. 
  $L$ is given by the following equation \cite{johnson2004model}: 
  \begin{equation} 
  L = -\frac{n}{2}ln\frac{RSS}{n} 
  \end{equation} 
  where $RSS$ is residual sum of squares of the model.

  \subsection{Model Averaging}
  In non-linear model fitting, dataset for each thermal performance curve was fitted 100 times and multiple solutions 
  with similar AIC or BIC could 
  be obtained. To find one most sufficient model supported by observed data, I conducted model averaging. 
  Among all solutions obtained through dataset of one thermal performance curve, those with lowest AIC or BIC values 
  were selected and averaged. 
  For one thermal performance curve, denote by $l$ the number of optimal solutions with lowest AIC or BIC among all solutions 
  obtained 
  by non-linear model fitting, and $\theta_i$ the $i$th solution, then the parameters of averaged model, denoted by $\theta$, 
  is given by following equation \cite{johnson2004model, buckland1997model}:
  \begin{equation}
    \theta = \sum_{i=1}^{l}\omega_i\theta_i
  \end{equation}
  The weight $\omega_i$ is given by smoothed AIC or BIC method \cite{buckland1997model}:
  \begin{equation}
    \omega_i = \frac{e^{-xIC_i/2}}{\sum_{i=1}^{l}e^{-xIC_i/2}}
  \end{equation}   
  where $xIC_i$ is the AIC or BIC of $i$th solution. Here, model averaging was conducted to solutions with equal AIC 
  or BIC values, 
  so 
  \begin{equation}
    \omega_i = \frac{1}{l}
  \end{equation}
  Then I calculated AIC and BIC of the averaged model and conducted model selection among linear and non-linear models.

  \subsection{Computating Tools}
  Most scripts are written in R 4.0.3, taking advantage of its powerful packages in model fitting 
  and visualization, and of in-built functions for form processing. R package minpack.lm was used for model 
  fitting, while visualization was conducted by R packages ggplot2, gridExtra and cowplot. 
  The report was written using LaTeX because it is efficient in typesetting. 
  A bash script was used to compile LaTeX source code. 
  Finally, a python3 script was written to run all scripts using os module.

  \section{Results}
    \subsection{Model Fitting and Selection}
    For each curve, models with lowest AIC or BIC were selected and they are either quadratic, 
    cubic, of Briere or of Ratkowsky. No curve has multiple models equally supported by AIC or BIC. 
    Among 841 thermal performance curves, 639 (76.0\%) of them can be fitted by Briere model, and 649 (77.2\%) of them can 
    be fitted by Ratkowsky model. After model fitting, Briere or Ratkowsky models with lowest AIC or BIC 
    values among all solutions 
    were selected and averaged before further model selection. 
    Figure. 1 provides examples of models that were used in selection among linear and non-linear models, and Figure 2 
    illustrates the distributions of AIC and BIC for each curve.
    \begin{figure}[H]
      \centering
      \includegraphics[width=\textwidth]{../Results/Fig1.pdf}
      \caption{Examples of models used for model selection. Criterion of selection within non-linear models is AIC for 
      subfigure \textbf{a}, \textbf{b} and \textbf{c}; and BIC for subfigure \textbf{d}, \textbf{e} and \textbf{f}. 
      The IDs of thermal performance curves 
      are: 148 (\textbf{a}), 204 (\textbf{b}), 322 (\textbf{c}), 138 (\textbf{d}), 237 (\textbf{e}),
      519 (\textbf{f}).}
    \end{figure}

    \begin{figure}[H]
      \centering
      \includegraphics[width=\textwidth]{../Results/a.pdf}
      \caption{The distribution of AIC and BIC. The lateral axis represents the IDs of curves, and the vertical 
      axis represents values of AIC (\textbf{a}) or BIC (\textbf{b}). The colours of lines represent different 
      plausible models.}
    \end{figure}
    When AIC is used as criterion for model selection, 57 (6.78\%) curves are  
    fitted by quadratic polynomial function and 160 (19.02\%) curves for cubic polynomial function. As for non-linear 
    models, 190 (22.59\%) curves are fitted by Briere model, and the rest 434 (51.61\%) curves are fitted by Ratkowsky 
    model. When BIC is used for model selection, 218 (25.92\%) curves are fitted by linear models (55 quadratic 
    polynomial model and 163 cubic polynomial model). 191 (22.71\%) curves are fitted by Briere model, while the 
    rest 432 (51.37\%) curves are fitted by Ratkowsky model. 18 curves are sufficiently 
    fitted by different models under different criteria for model selection as shown in Table 1.
    \begin{table}[H]
      \centering
      \caption{Curves That AIC and BIC Support Different Models}
      \begin{tabular}{@{}cccc@{}}
        \toprule
        ID  & AIC-supported   & BIC-supported \\ \midrule
        99  & Briere    & Ratkowsky \\
        105 & Ratkowsky & cubic     \\
        232 & Ratkowsky & Briere              \\
        318 & Ratkowsky & Briere            \\
        330 & Briere    & Ratkowsky           \\
        351 & Briere    & Ratkowsky           \\
        426 & Ratkowsky & Briere             \\
        496 & Briere    & Ratkowsky          \\
        569 & Ratkowsky & Briere             \\
        635 & quadratic & cubic               \\
        644 & quadratic & cubic               \\
        669 & Ratkowsky & Briere             \\
        681 & Ratkowsky & Briere             \\
        737 & Briere    & Ratkowsky           \\
        745 & Ratkowsky & Briere             \\
        765 & Briere    & Ratkowsky           \\
        827 & Ratkowsky & Briere              \\
        879 & Briere    & Ratkowsky           \\ \bottomrule
        \end{tabular}
        \end{table}

        \subsection{Assess Best Models for Curves of Different Metabolic or Habitat Types}
        To assess preferred models for thermal performance curves of differnet metabolic traits or species living in different 
        habitat types, 18 curves were removed because AIC and BIC supported different models. So a total of 823 
        curves were involved.
        \newline  
        In the original dataset, the metabolic trait of each curve is defined in the field of StandardisedTraitName 
        (trait name for comparison), 
        which contains three categories: gross photosynthesis rate, net photosynthesis rate and respiration rate. Another field 
        relevant to 
        trait name is OriginalTraitName (trait name as it found in source). It should be noted there are four curves 
        have no StandardisedTraitName, while their OriginalTraitName are oxygen evolution 
        rate in thylakoid membranes (IDs: 698, 699) and cell specific photosynthesis rate (IDs: 441, 442). They were not 
        involved in assessing which model is suitable for different metabolic traits.
        As for habit type of each curve, it is defined in another field (Habitat), which is composed of four types: aquatic, 
        freshwater, freshwater/terrestrial, marine and terrestrial. Here I assessed which model is suitable for determining 
        thermal performance of species living in terrestrial or non-terrestrial (aquatic, 
        freshwater, freshwater/terrestrial and marine) habitats.
        \newline  
        Table 2 illustrates the sufficient models for thermal performance curves of different metabolic traits. 
        A total of 819 thermal performance curves of three metabolic traits are involved. 
        For models of each metabolic trait, non-linear  
        model occupies a larger proportion 
        (75.0\% of gross photosynthesis rate, 78.8\% of net photosynthesis rate, and 66.2\% of respiration rate) than linear 
        models. Besides, Ratkowsky model takes a bigger amount than Briere model in all metabolic traits except gross 
        photosynthesis rate.
        \newline
        Then I classified thermal performance curves according to whether the species studied is specific in terrestrial 
        habitats (Table 3). Non-linear model 
        takes the biggest amount of sufficient models for both two kinds of habitat type 
        (82.1\% for terrestrial habitat and 55.2\% of non-terrestrial habitat), and Ratkowsky model occupies biggest proportion 
        among four models. 
        \begin{table}[H]
          \centering
          \caption{Selected Models for Thermal Performance Curves of Different Metabolic Traits}
          \begin{tabular}{@{}ccccc@{}}
          \toprule
          Model     & Gross photosynthesis rate & Net photosynthesis rate & Respiration rate  & Total \\ \midrule
          Quadratic & 0   & 19  & 36  & 55    \\
          Cubic     & 9   & 80  & 71  & 160   \\
          Briere    & 16  & 73  & 94  & 183   \\
          Ratkowsky & 11  & 294 & 116 & 421   \\
          Total     & 36  & 466 & 317 & 819   \\ \bottomrule
          \end{tabular}
          \end{table}

          \begin{table}[H]
            \centering
            \caption{Selected Models for Thermal Performance Curves from Species in Different Habitat Types}
            \begin{tabular}{@{}cccc@{}}
            \toprule
            Model     & Terrestrial & Non-terrestrial & Total \\ \midrule
            Quadratic & 21          & 34              & 55    \\
            Cubic     & 81          & 79              & 160   \\
            Briere    & 134         & 49              & 183   \\
            Ratkowsky & 335         & 90              & 425   \\
            Total     & 571         & 252             & 823   \\ \bottomrule
            \end{tabular}
            \end{table}

    \subsection{Preferred Models May not Describe the Observed Data Well}
    Through model selection, I selected one model for each curve and it is the most sufficient one in terms of describing 
    the thermal performance curve among four plausible models. However, the preferred models of some curves still 
    fail in describing thermal performance throughout the temperature 
    range between lower and upper thermal limits of performance. As the growth of temperature in this range, 
    performance is supposed to increases, peaks at some point, and then drops \cite{sinclair2016can,krenek2011thermal}. 
    The preferred models of some curves are 
    not bell-shaped (Figure. 3). Furthermore, ecologically unrealistic estimations 
    of thermal limits of performance are also given by some selected models (Figure 4).

    \begin{figure}[H]
      \centering
      \includegraphics[width=\textwidth]{../Results/Fig2.pdf}
      \caption{Examples of preferred models that are not bell-shaped curves. IDs of thermal performance curves 
      are: 456 (\textbf{a}), 
      841 (\textbf{b}), 455 (\textbf{c}), 600 (\textbf{d}). Mathematical expression of each model is given at 
      the bottom of each subfigure. For these datasets, AIC and BIC support the same models with equal parameters.} 
    \end{figure}

    \begin{figure}[H]
      \centering
      \includegraphics[width=\textwidth]{../Results/b.pdf}
      \caption{Examples of preferred models that give unrealistic estimations of thermal limits of performance. 
      IDs of thermal performance curves are: 81 (\textbf{a}), 
      215 (\textbf{b}), 46 (\textbf{c}), 254 (\textbf{d}). Criterion of model selection is AIC, and estimations of lower 
      and upper thermal limits of performance, denoted as $T_0$ and $T_m$, are given at the bottom of each subfigure.}
    \end{figure}

  \section{Discussion}
  Investigations in how organisms response to temperature fulctuation are helpful in better understanding 
  the impact of recent and future climate change on biological systems \cite{kingsolver2013heat, vasseur2014increased}. 
  In assessment of thermal performance, it is important to choose an appropriate mathematical model that 
  is best supported by empirical data and is able to provide relatively precise estimations of controlled variable, 
  given values of independent variable. Currently, there are plenty of mathematical models used in fitting thermal 
  performance curves, and model selection criteria can be used to explicate how sufficient a model is in describing 
  thermal performance curves \cite{krenek2011thermal, angilletta2006estimating, johnson2004model}. 
  In order to find which model is best supported by observed data of thermal performance, 
  I fitted four plausible models to a dataset composed of 841 thermal performance curves 
  and conducted model averaging and selection using either AIC or BIC as criterion. 
  In most cases, AIC and BIC prefer the same model.
  The results also showed that under both selection criteria, 
  Ratkowsky model is sufficient in quantifying thermal performance for about 51\% of curves in the dataset. 
  \newline
  In model selection, a set of plausible models are ranked by some criterion and the most appropriate one is selected. 
  AIC and BIC are two criterion for model selection. 
  They take 
  both fit and model complexity into consideration to balance under- and over-fitting to observed data 
  \cite{johnson2004model, zucchini2000introduction}. Although AIC and BIC are quite similar 
  in forms, they are divergent in theoretical motivations. BIC is based on Bayesian statistical analysis and is an 
  approximation reflecting the probability that each plausible model is the true model that generated the empirical 
  data \cite{kuha2004aic}. Minimized BIC is corresponded to maximized posterior 
  probability among all plausibilities and can be thought as a criterion for model selection \cite{wit2012all}. However, 
  the existence of "true model" is problematic \cite{box1979all}, and the theoretical basis of BIC is 
  controversial \cite{kuha2004aic}. As for AIC, it measures the predictive performance of 
  each candidate model by estimating Kullback-Leible information loss \cite{kuha2004aic,deleeuw1992akaike, 
   burnham2004multimodel}, 
  and is thus well-founded in information theory.  
  Here, I conducted model selection using AIC and BIC as criterion respectively. 
  In most cases, they prefer the same model. However, I tend to use AIC as model selection criterion because of its solid 
  theoretical foundation.
  \newline
  In non-linear model fitting, an iterative algorithm is employed to gain a numerical local optimal solution, 
  which is sensitive to start values 
  \cite{ranganathan2004levenberg, lourakis2005brief}. 
  Here, 
  I fitted each non-linear model 100 times with different start values before model selection, attempting to 
  find the global optimal solution. For one thermal 
  performance dataset, multiple solutions can be obtained by different start values while they have equal and 
  lowest AIC or BIC. This is because of limited accuracy in numerical calculation of AIC and BIC 
  by R scripts. To deal with this, I conducted model averaging using smoothed AIC or BIC method. 
  When multiple plausible models get nearly equivalent support from observed data (\textit{e.g.} similar AIC or BIC values), 
  model averaging is a good method 
  to give estimations of model parameters or predict values of response variables \cite{johnson2004model}.
  \newline
  Generally, thermal performance curve is supposed to be a bell-shaped curve with ecologically realistic 
  lower and upper thermal limits of performance \cite{sinclair2016can,krenek2011thermal}. 
  However, some models supported by AIC or BIC are not bell-shaped curves, 
  as exemplified in Figure 3. Others may give estimations of thermal limits of performance that are too low or too high to 
  be realistic, as exemplified in Figure 4. Such models may fit to the observed data well (Figure 3d and Figure 4a), but 
  fail in describing the whole thermal performance curve. A possible reason is that there are not enough sampes from a wide 
  enough temperature range to allow the models to capture the change of performance over temperature in different ranges. 
  For example, curve 215 
  only contains samples of relatively low temperature (\textit{i.e.} temperatures of all samples are no greater 
  than the optimum 
  temperature  
  where performance peaks) as it is shown in Figure 4b. An alternative explanation is that none of the four plausible models 
  are suitable for describing the observed data. 
  AIC and BIC can only explicate the relative goodness of each model in a given set of models \cite{johnson2004model, 
  buckland1997model, zucchini2000introduction}
   and it 
  is possible that no model in the given set can fit to the observed data sufficiently. Under these circumstances, more 
  models are needed to be used in fitting and selection.

  Overall, I conducted model fitting, averaging and selection using observed data of 841 thermal performance curves. 
  Plausible models include quadratic polynomial model, cubic polynomial model, Briere model and Ratkowsky model. AIC and 
  BIC were used as model selection criterion. For most curves, AIC and BIC give support to the same model. The results shows 
  that for more than a half of thermal performance curves involved here, Ratkowsky model is the most sufficient one among 
  four plausibilities. When curves are classified according to metabolic trait or habitat type of species, Ratkowsky model is 
  most sufficient one for a majority of curves in most categories. However, some selected models cannot describe the whole 
  thermal performance curves or contain unrealistic parameters, indicating that none of the four models is suitable for 
  fitting to the observed data.

  \newpage

  \bibliographystyle{unsrt}
  \bibliography{References}

\end{document}

### 2020-12-07 HPC2020-master/model code/CongLiu37/CongLiu37_HPC_2020_main.R

@@ -1,0 +1,240 @@
+# CMEE 2020 HPC excercises R code main proforma
+# you don't HAVE to use this but it will be very helpful.  If you opt to write everything yourself from scratch please ensure you use EXACTLY the same function and parameter names and beware that you may loose marks if it doesn't work properly because of not using the proforma.
+
+name <- "Cong Liu"
+preferred_name <- "Cong"
+email <- "cong.liu20@imperial.ac.uk"
+username <- "CongLiu37"
+
+# please remember *not* to clear the workspace here, or 
+#anywhere in this file. If you do, it'll wipe out your username information 
+#that you entered just above, and when you 
+#use this file as a 'toolbox' as intended it'll 
+#also wipe away everything you're doing outside of the toolbox.  
+#For example, it would wipe away any automarking code 
+#that may be running and that would be annoying!
+
+# Question 1
+species_richness <- function(community){
+  return(length(unique(community)))
+}
+
+# Question 2
+init_community_max <- function(size){
+  return(seq(size))
+}
+
+# Question 3
+init_community_min <- function(size){
+  return(rep(1,size))
+}
+
+# Question 4
+choose_two <- function(max_value){
+  return(sample(seq(1:max_value), size = 2, replace = F))
+}
+
+# Question 5
+neutral_step <- function(community){
+  a = choose_two(length(community))
+  community[a[1]] = community[a[2]]
+  return(community)
+}
+
+# Question 6
+neutral_generation <- function(community){
+  
+}
+
+# Question 7
+neutral_time_series <- function(community,duration)  {
+  
+}
+
+# Question 8
+question_8 <- function() {
+  # clear any existing graphs and plot your graph within the R window
+  return("type your written answer here")
+}
+
+# Question 9
+neutral_step_speciation <- function(community,speciation_rate)  {
+  
+}
+
+# Question 10
+neutral_generation_speciation <- function(community,speciation_rate)  {
+  
+}
+
+# Question 11
+neutral_time_series_speciation <- function(community,speciation_rate,duration)  {
+  
+}
+
+# Question 12
+question_12 <- function()  {
+  # clear any existing graphs and plot your graph within the R window
+  
+  return("type your written answer here")
+}
+
+# Question 13
+species_abundance <- function(community)  {
+  
+}
+
+# Question 14
+octaves <- function(abundance_vector) {
+  
+}
+
+# Question 15
+sum_vect <- function(x, y) {
+  
+}
+
+# Question 16 
[…]

### 2020-12-07 HPC2020-master/model code/my test file HPC 2020.R

@@ -1,0 +1,31 @@
+# CMEE 2020 HPC excercises R code HPC run code proforma
+
+rm(list=ls()) # good practice in this instance
+source("CongLiu37/CongLiu37_HPC_2020_main.R")
+# it should take a faction of a second to source your file
+# if it takes longer you're using the main file to do actual simulations
+# it should be used only for defining functions that will be useful for your cluster run and which will be marked automatically
+
+# do what you like here to test your functions (this won't be marked)
+# for example
+species_richness(c(1,4,4,5,1,6,1))
+# should return 4 when you've written the function correctly for question 1
+
+# you may also like to use this file for playing around and debugging
+# but please make sure it's all tidied up by the time it's made its way into the main.R file or other files.
+
+init_community_max(7)
+#should return a vector {1 2 3 4 5 6 7}
+
+init_community_min(4)
+#should return a vector {1 1 1 1}
+
+#Test
+species_richness(init_community_min(100))
+species_richness(init_community_max(100))
+
+choose_two(4)
+#should return one of the following vectors:
+#{1 2}, {1 3}, {1 4}, {2 1}, {2 3}, {2 4}, {3 1}, {3 2}, {3 4}, {4 1}, {4 2}, {4 3}
+
+neutral_step(c(10,5,13))

### 2020-12-07 MiniProject/Code/CompileLaTeX.sh

@@ -1,0 +1,30 @@
+#!/bin/bash
+#Auther: Cong liu (cong.liu20@imperial.ac.uk)
+#Script: CompileLaTeX.sh
+#Work Path: CMEECourseWork/MiniProject/Code
+#Input: .tex and .bib files in Code/
+#Function: Run LaTeX, save .pdf file in Results/ and remove other files
+#Output: .pdf file in Results/
+#Usage: bash Code/CompileLaTeX.sh [Base name of .tex]
+#Date: Oct 2020
+
+pdflatex $1.tex
+pdflatex $1.tex
+bibtex $1
+pdflatex $1.tex
+pdflatex $1.tex
+
+rm *~
+rm *.aux
+rm *.dvi
+rm *.log
+rm *.nav
+rm *.out
+rm *.snm
+rm *.toc
+rm *.bbl
+rm *.blg
+rm *fdb_latexmk
+rm *fls
+
+mv *.pdf ../Results

### 2020-12-07 MiniProject/Code/FiguresInReport.R

@@ -1,14 +1,58 @@
-
+#Language: R 4.0.3
+#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
+#Script: FIguresInReport.R
+#Work Path: CMEECourseWork/MiniProject/Code
+#Dependency: ggplot2, gridExtra, cowplot 
+#Input:  ../Results/bestAIC_quadratic.csv
+#        ../Results/bestBIC_quadratic.csv
+#        ../Results/bestAIC_cubic.csv
+#        ../Results/bestBIC_cubic.csv
+#        ../Results/bestAIC_Briere.csv
+#        ../Results/bestBIC_Briere.csv
+#        ../Results/bestAIC_Ratkowsky.csv
+#        ../Results/bestBIC_Ratkowsky.csv
+#        ../Results/filtered_data.csv
+#        ../Results/move_curves.csv
+#        ../Results/quadratic_valid.csv
+#        ../Results/cubic_valid.csv
+#        ../Results/Briere_AIC.csv
+#        ../Results/Briere_BIC.csv
+#        ../Results/Ratkowsky_AIC.csv
+#        ../Results/Ratkowsky_BIC.csv
+#Function: Plot figures in report.
+#Date: Nov, 2020
 
 rm(list = ls())
 library(ggplot2)
 library(gridExtra)
+library(cowplot)
 
 rescale = read.csv("../Results/move_curves.csv", header = T)
 IDs = subset(rescale, minus == 0)$ID
 
 data = read.csv("../Results/filtered_data.csv", header = T)
 
+Q = subset(read.csv("../Results/quadratic_valid.csv", header = T),
+           ID %in% IDs)
+C = subset(read.csv("../Results/cubic_valid.csv", header = T),
+           ID %in% IDs)
+B_AIC = subset(read.csv("../Results/Briere_AIC.csv", header = T),
+           ID %in% IDs)
+B_BIC = subset(read.csv("../Results/Briere_BIC.csv", header = T),
+           ID %in% IDs)
+R_AIC = subset(read.csv("../Results/Ratkowsky_AIC.csv", header = T),
+           ID %in% IDs)
+R_BIC = subset(read.csv("../Results/Ratkowsky_BIC.csv", header = T),
+           ID %in% IDs)
+
+q_AIC = subset(read.csv("../Results/bestAIC_quadratic.csv", header = T),
+               ID %in% IDs)
[…]

### 2020-12-07 MiniProject/Code/ModelQC.R

@@ -8,14 +8,12 @@
 #       ../Results/Briere_model.csv
 #       ../Results/Ratkowsky_model.csv
 #Function: (1) For each curve, select combinations of parameters of Briere model
-#              that lead to lowest AIC or BIC.
+#              that lead to lowest AIC or BIC and average them.
 #          (2) For each curve, select combinations of parameters of Ratkowsky model
-#              that lead to lowest AIC or BIC.
+#              that lead to lowest AIC or BIC and average them.
 #          (3) Extract parameter values of all models.
 #Output: ../Results/quadratic_valid.csv
 #        ../Results/cubic_valid.csv
-#        ../Results/Briere_valid.csv
-#        ../Results/Ratkowsky_valid.csv
 #        ../Results/Briere_AIC.csv
 #        ../Results/Briere_BIC.csv
 #        ../Results/Ratkowsky_AIC.csv
@@ -24,6 +22,7 @@
 #Date: Nov, 2020
 
 rm(list = ls())
+data = read.csv("../Results/filtered_data.csv")
 
 Q = read.csv("../Results/quadratic_polynomial_model.csv", header = T)
 colnames(Q) = Q[1,]
@@ -45,15 +44,6 @@ B = read.csv("../Results/Briere_model.csv")
 colnames(B) = B[1,]
 B = B[-1,]
 B1 = B
-#B1 = subset(B, as.numeric(B$B0) > 0)
-#B1 = subset(B1, as.numeric(B1$T0) > -30)
-#B1 = subset(B1, as.numeric(B1$Tm) < 100)
-#B1 = subset(B1,as.numeric(B1$T0) < as.numeric(B1$Tm))
-
-#v2 = paste(length(table(B1$ID)),"of 903 curves can be fitted by Briere models with realistic parameters")
-#print(v2)
-
-#write.csv(B1, "../Results/Briere_valid.csv",row.names = F)
 
 ID_B = names(table(B1$ID))
 B_AIC = data.frame()
@@ -72,31 +62,55 @@ B_AIC_parameters = data.frame(ID = B_AIC$ID,
[…]

### 2020-12-07 MiniProject/Code/PlotBestModels.R

@@ -43,28 +43,37 @@ for (i in 1:903){
   temp = seq(min(d$ConTemp), max(d$ConTemp), 0.1)
   
   p = ggplot(d, aes(x = ConTemp, y = OriginalTraitValue)) + geom_point() +
-    labs(title = as.character(i)) +
+    labs(title = paste("ID:", as.character(i))) +
     xlab("Temperature") +
-    ylab("Trait Value")
-  if (nrow(modq) != 0){
-  pre1 = modq$B0 + modq$B1*temp + modq$B2*temp^2
-  p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre1),
-                    aes(x = ConTemp, y = OriginalTraitValue, colour = "Quadratic"))}
-  if (nrow(modc) != 0){
-  pre2 = modc$B0 + modc$B1*temp + modc$B2*temp^2 + modc$B3*temp^3
-  p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre2),
-                    aes(x = ConTemp, y = OriginalTraitValue, colour = "Cubic"))}
+    ylab("Trait Value") +
+    theme(plot.title = element_text(hjust = 0.5))
   
+  pre1 = data.frame()
+  if (nrow(modq) != 0){
+    pre1 = modq$B0 + modq$B1*temp + modq$B2*temp^2
+    pre1 = data.frame(Model = rep("Quadratic", length(temp)),
+                      ConTemp = temp,
+                      OriginalTraitValue = pre1)}
+  pre2 = data.frame()
+  if (nrow(modc) != 0){
+    pre2 = modc$B0 + modc$B1*temp + modc$B2*temp^2 + modc$B3*temp^3
+    pre2 = data.frame(Model = rep("Cubic", length(temp)),
+                      ConTemp = temp,
+                      OriginalTraitValue = pre2)}
+  pre3 = data.frame()
   if (nrow(modb) != 0){
-    for (j in 1:nrow(modb)){
-      pre = as.numeric(modb$B0[j]) * temp * (temp-as.numeric(modb$T0[j])) * (as.numeric(modb$Tm[j])-temp)^0.5
-      p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre),
-                        aes(x = ConTemp, y = OriginalTraitValue, colour = "Briere"))}}
[…]

### 2020-12-07 MiniProject/Code/PlotValidModels.R

@@ -39,30 +39,36 @@ for (i in 1:903){
   temp = seq(min(d$ConTemp), max(d$ConTemp), 0.1)
   
   p = ggplot(d, aes(x = ConTemp, y = OriginalTraitValue)) + geom_point() +
-    labs(title = as.character(i)) +
+    labs(title = paste("ID:", as.character(i))) +
     xlab("Temperature") +
-    ylab("Trait Value")
-  
+    ylab("Trait Value") +
+    theme(plot.title = element_text(hjust = 0.5))
+  pre1 = data.frame()
   if (nrow(modq) != 0){
   pre1 = modq$B0 + modq$B1*temp + modq$B2*temp^2
-  p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre1),
-                    aes(x = ConTemp, y = OriginalTraitValue, colour = "Quadratic"))}
-  
+  pre1 = data.frame(Model = rep("Quadratic", length(temp)),
+                    ConTemp = temp,
+                    OriginalTraitValue = pre1)}
+  pre2 = data.frame()
   if (nrow(modc) != 0){
-  pre2 = modc$B0 + modc$B1*temp + modc$B2*temp^2 + modc$B3*temp^3
-  p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre2),
-                    aes(x = ConTemp, y = OriginalTraitValue, colour = "Cubic"))}
-
+    pre2 = modc$B0 + modc$B1*temp + modc$B2*temp^2 + modc$B3*temp^3
+  pre2 = data.frame(Model = rep("Cubic", length(temp)),
+                    ConTemp = temp,
+                    OriginalTraitValue = pre2)}
+  pre3 = data.frame()
   if (nrow(modb) != 0){
-  for (j in 1:nrow(modb)){
-    pre = as.numeric(modb$B0[j]) * temp * (temp-as.numeric(modb$T0[j])) * (as.numeric(modb$Tm[j])-temp)^0.5
-    p = p + geom_line(data = data.frame(ConTemp = temp, OriginalTraitValue = pre),
-                      aes(x = ConTemp, y = OriginalTraitValue, colour = "Briere"))}}
+    pre3 = as.numeric(modb$B0) * temp * (temp-as.numeric(modb$T0)) * (abs(as.numeric(modb$Tm)-temp))^0.5
+  pre3 = data.frame(Model = rep("Briere", length(pre3)),
[…]

### 2020-12-07 MiniProject/Code/StatisticsResults.R

@@ -107,15 +107,18 @@ for (i in IDs){
   if (i %in% r_BIC$ID){mod[i,3] = "Ratkowsky"}
 }
 
-
+data = read.csv("../Data/ThermRespData.csv")
 a = subset(mod, bestAIC != bestBIC)
+
 p12 = paste(nrow(a), "curves are best fitted by different functions when different criterion",
             "of model selection is used")
 print(p12)
 print(a)
+write.csv(a, "../Results/a.csv", row.names = F)
 
-data = read.csv("../Data/ThermRespData.csv")
-table(data$Habitat)
+
+
+
 Metabolic = rep(NA, 903)
 Hab =  rep(NA, 903)
 for (i in 1:903){
@@ -136,7 +139,7 @@ table(subset(mod, Metabolic == "net photosynthesis rate")$bestAIC)
 print("For respiration rate")
 table(subset(mod, Metabolic == "respiration rate")$bestAIC)
 
-print("For species living in non-terrestrial habitat")
+print("For species living in terrestrial habitat")
 table(subset(mod,Habitat == "terrestrial")$bestAIC)
 print("For species living in non-terrestrial habitat")
 table(subset(mod,Habitat != "terrestrial")$bestAIC)

### 2021-01-13 Week3/Code/DataWrang.R
CMEECourseWork

@@ -2,10 +2,10 @@
 #Auther: Cong Liu (cong.liu20@imperial.ac.uk)
 #Script: DataWrang.R
 #Work Path: CMEECourseWork/Week3/Code
-#Dependency: reshape2
+#Dependency: reshape2, tidyverse
 #Input: Data/PoundHillData.csv
 #       Data/PoundHillMetaData.csv
-#Function: Data wrangling usin reshape2 packae
+#Function: Data wrangling using reshape2 packae
 #Output:
 #Usage: Rscript DataWrang.R
 #Date: Oct, 2020

### 2021-01-13 Week3/Code/GPDD_Data.R

@@ -28,6 +28,7 @@ mp1<-mp + geom_point(aes(x=visit.x,
                    size = 0.1) +
   scale_size(range=c(1,1))
 mp1
+
 #The locations from which there is data are distributed unevenly among the world.
 #Most locations are in Europe and North America, especially in United Kingdom
 #and western coastal line of America and Canada. There is only one

### 2021-01-13 Week3/Code/PP_Dists.R

@@ -157,6 +157,7 @@ hist(subset(TempData,
      main = "predacious/piscivorous")
 dev.off()
 
+#Calculate means and variances
 ty = names(table(TempData$data.Type.of.feeding.interaction))
 insec = subset(TempData,
                TempData$data.Type.of.feeding.interaction == 

### 2021-01-13 Week3/Code/PP_Regress.R

@@ -5,7 +5,7 @@
 #Dependency: ggplot2, scales, broom
 #Input: Data/EcolArchives-E089-51-D1.csv
 #Function: Regress prey mass and predator mass for each 
-#          Feeding Type × Predator life Stage combination and
+#          Feeding Type+Predator life Stage combination and
 #          save results in Results/PP_Regress_Results.csv.
 #          For each combination, if it has only two sample poits or 
 #          there is no correlation (R-square = 0), it will not be saved in csv file.
@@ -20,6 +20,7 @@ rm(list = ls())
 #Import data
 data = read.csv("../Data/EcolArchives-E089-51-D1.csv")
 
+#Convert unit of mass
 for (i in 1:nrow(data)){
   if (data$Prey.mass.unit[i] == "mg"){
     data$Prey.mass.unit[i] = "g"
@@ -32,6 +33,7 @@ PredatorStage = names(table(data$Predator.lifestage))
 
 RegTitle = c("slope", "intercept", "R^2","adjusted-R^2", 
              "F-statistic", "p-value")
+
 library(broom)
 #Summary of linear model
 lmSum = function(a,b){
@@ -46,10 +48,11 @@ lmSum = function(a,b){
   c[6] = unname(glance(mol)$p.value)
   return(c)
 }
-data$Prey.mass.unit
+
 Reg = data.frame(RegTitle)
 n = names(Reg)
 k = 2
+#Regression
 for (i in FeedType){
   for (j in PredatorStage){
     d = subset(data,

### 2021-01-13 Week3/Code/TAutoCorr.R

@@ -4,11 +4,10 @@
 #Work Directory: CMEECourseWork/Week3/Code
 #Dependency: ggplot2
 #Input: Data/KeyWestAnnualMeanTemperature.RData
-#Function: Test autocorrelation of each year's temperature 
-#Output: TAutoCorr_Figure1.pdf
-#Usage:
+#Function: Test autocorrelation of each year's temperature and estimate p-value
+#Usage: Rscript TAutoCorr.R
 #Date: Oct, 2020
-
+rm(list = ls())
 load("../Data/KeyWestAnnualMeanTemperature.RData") #Import data
 
 library(ggplot2)
@@ -45,5 +44,5 @@ for (corr in corrs) {
     j = j + 1
   }
 }
-ap-p = j/10000
-ap-p
+ap_p = j/10000
+ap_p

### 2021-01-13 Week3/Code/Vectorize1.R

@@ -10,7 +10,7 @@
 #Date: Oct, 2020
 
 M <- matrix(runif(1000000),1000,1000)
-dim(M)
+# Calculate sum of a matrix by loop
 SumAllElements <- function(M){
   Dimensions <- dim(M)
   Tot <- 0

### 2021-01-13 Week3/Code/boilerplate.R

@@ -1,9 +1,9 @@
 #Language: R
 #Auther: Cong Liu (cong.liu20@imperial.ac.uk)
 #Script: boilerplate.R
-#Work Path: CMEECourseWork/Week3/COde
+#Work Path: CMEECourseWork/Week3/Code
 #Input:
-#Function: Illustrate skipping to next iteration of a loop
+#Function: An exemple of R function
 #Output:
 #Usage: Rscript boilerplate.R
 #Date: Oct, 2020

### 2021-01-13 Week3/Code/preallocate.R

@@ -16,7 +16,7 @@ NoPreallocFun <- function(x){
     print(object.size(a))
   }
 }
-
+#Run-time without preallocation
 system.time(NoPreallocFun(10))
 
 
@@ -28,5 +28,5 @@ PreallocFun <- function(x){
     print(object.size(a))
   }
 }
-
+#Run-time with preallocation
 system.time(PreallocFun(10))

### 2021-01-13 Week3/Code/try.R

@@ -8,6 +8,7 @@
 #Usage:
 #Date: Oct, 2020
 
+#Sampling and calculating mean
 doit <- function(x){
   temp_x <- sample(x, replace = TRUE)
   if(length(unique(temp_x)) > 30) {#only take mean if sample was sufficient

### 2021-01-19 MiniProject/Code/Report.tex
CMEECourseWork

@@
 
-\title{Model Selection to Find a Most Sufficient Model Fitting to Thermal Performance of Metabolic Traits\footnotemark[1]}
+\title{Model Selection to Find a Sufficient Model Fitting to Thermal Performance of Metabolic Traits\footnotemark[1]}
 
@@
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\footnotetext[1]{Word Count: 2611}
+\footnotetext[1]{Word Count: 2597}
 \footnotetext[2]{Department of Life Sciences (Silwood Park), Imperial College of Science, Technology and Medicine}
@@
   \begin{abstract}
-    Determining thermal dependence of biological traits provides better understanding in distribution patterns of species 
-    and is helpful in assessing the impact of climate change on biological systems. Here, I fitted quadratic polynomial 
-    model, cubic polynomial model, Briere model and Ratkowsky model to observed data of metabolic traits under different 
-    temperatures to calculate thermal performance curves. Model averaging and selection by either AIC or BIC were 
+    Determining thermal dependence of biological traits provides understanding in distribution patterns of species 
+    and is helpful in assessing the impact of climate change on biological systems. Here, I fitted 
+    four plausibe models to observed data of metabolic traits under different 
+    temperatures to calculate thermal performance curves. Model selection by either AIC or BIC were 
     conducted to find one most sufficient model fitting to empirical data of each curve. 
     In most curves, AIC and BIC give support to 
-    the same model and Ratkowsky model has the highest frequency of being the most suitable model 
-    under two selection criteria. However, for some thermal performance curves in the dataset, even the best model 
-    selected here fail in describing thermal dependence of metabolic traits, indicating that the four plausible models 
+    the same model and Ratkowsky model has the highest frequency of being selected. 
+    However, for some thermal performance curves in the dataset, the selected model 
+    fails in describing thermal dependence of metabolic traits, indicating that the four plausible models 
     are not suitable and more models need to be involved. Overall, the results show that Ratkowsky model is sufficient 
@@
   activities or fitness) on temperature quantitatively \cite{sinclair2016can}. Generally, organisms response 
-  to temperature fluctuation in a similar manner. The value of performance peaks at some temperature point, 
+  to temperature fluctuation in a similar manner. The value of performance peaks at some temperature point 
   and decreases when temperature deviates from the maximum point, while extremely high or low temperatures are lethal 
@@
   physiological characters like the optimum temperature at which performance peaks, upper and lower 
-  thermal limit thermal performance, and thermal tolerance range \cite{krenek2011thermal}. 
+  thermal limits of performance, and thermal tolerance range \cite{krenek2011thermal}. 
   Besides, it is also helpful in predicting 
@@
   of performance is the main concern of this study. 
-  Using a dataset of observed data from 841 thermal performance curves, 
+  Using a dataset of observed data from 841 thermal performance curves of different metabolic traits, 
   I calculated these curves by fitting 
   four plausible models to them. 
-  Then I conducted model averaging and selection to find one model that is most sufficient to describe the observed data.
+  Then I conducted model selection to find one model that is most sufficient to describe the observed data. 
   Akaike information criterion (AIC) or 
@@
     \newline 
-    The main fields of interest are OriginalTraitValue (trait values) and ConTemp (the temperatures 
+    The main fields of interest are OriginalTraitValue (trait values) and ConTemp (temperatures 
     in Celsius scale). Each thermal performance curve is corresponded to a unique ID from 1 to 903. 
@@
     \end{equation} 
-    $T_0$ and $T_m$ are lower and upper thermal limit thermal performance. 
+    $T_0$ and $T_m$ are lower and upper thermal limits of performance. 
     \newline 
@@
     \end{equation} 
-    $T_0$ and $T_m$ are lower and higher thermal limit thermal performance. 
+    $T_0$ and $T_m$ are lower and higher thermal limits of performance. 
   \subsection{Model Fitting} 
@@
     of each curve. Start values of $a$ and $b$ were taken from set  
-    $\{10^i: i = -5,-4,-3,-2,-1,0,1,2,3,4\}$. So for each curve, there are ten start values of $a$ and $b$,  
+    $\{10^i: i = -5,-4,-3,-2,-1,0,1,2,3,4\}$ iteratively. So for each curve, there are ten start values of $a$ and $b$,  
     and 100 combinations of them. Hence, each curve was fitted 100 times with different start values.
@@
 
-        \subsection{Assess Best Models for Curves of Different Metabolic or Habitat Types}
+        \subsection{Selected Models for Curves of Different Metabolic or Habitat Types}
         To assess preferred models for thermal performance curves of differnet metabolic traits or species living in different 
@@
         model occupies a larger proportion 
-        (75.0\% of gross photosynthesis rate, 78.8\% of net photosynthesis rate, and 66.2\% of respiration rate) than linear 
+        (75.0\% in gross photosynthesis rate, 78.8\% in net photosynthesis rate, and 66.2\% in respiration rate) than linear 
         models. Besides, Ratkowsky model takes a bigger amount than Briere model in all metabolic traits except gross 
@@
         (82.1\% for terrestrial habitat and 55.2\% of non-terrestrial habitat), and Ratkowsky model occupies biggest proportion 
-        among four models. 
+        among four plausible models. 
         \begin{table}[H]
@@
 
-    \subsection{Preferred Models May not Describe the Observed Data Well}
+    \subsection{Preferred Models May not Describe the Observed Data Sufficiently}
     Through model selection, I selected one model for each curve and it is the most sufficient one in terms of describing 
@@
   In assessment of thermal performance, it is important to choose an appropriate mathematical model that 
-  is best supported by empirical data and is able to provide relatively precise estimations of controlled variable, 
+  is best supported by empirical data and is able to provide relatively precise estimations of dependent variable using 
   given values of independent variable. Currently, there are plenty of mathematical models used in fitting thermal 
@@
   in forms, they are divergent in theoretical motivations. BIC is based on Bayesian statistical analysis and is an 
-  approximation reflecting the probability that each plausible model is the true model that generated the empirical 
+  approximation reflecting the probability that the plausible model is the true model that generated the empirical 
   data \cite{kuha2004aic}. Minimized BIC is corresponded to maximized posterior 
   probability among all plausibilities and can be thought as a criterion for model selection \cite{wit2012all}. However, 
-  the existence of "true model" is problematic \cite{box1979all}, and the theoretical basis of BIC is 
-  controversial \cite{kuha2004aic}. As for AIC, it measures the predictive performance of 
+  whether there is such a "true model" is controversial \cite{box1979all}, and the theoretical basis of BIC is 
+  disputed \cite{kuha2004aic}. As for AIC, it measures the predictive performance of 
   each candidate model by estimating Kullback-Leible information loss \cite{kuha2004aic,deleeuw1992akaike, 
@@
   as exemplified in Figure 3. Others may give estimations of thermal limits of performance that are too low or too high to 
-  be realistic, as exemplified in Figure 4. Such models may fit to the observed data well (Figure 3d and Figure 4a), but 
+  be realistic, as exemplified in Figure 4. Such models may fit to the observed data well (\textit{e.g.} Figure 3d and Figure 4a), but 
   fail in describing the whole thermal performance curve. A possible reason is that there are not enough sampes from a wide 

### 2021-01-19 MiniProject/Code/BestModel.R

@@ -1,6 +1,5 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: BestModel.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency: 
 #Input: ../Results/quadratic_valid.csv
@@ -12,19 +11,19 @@
 #Function: For each curve, select best-fitting models from 
 #          quadratic, cubic, Briere and Ratkowsky models, 
 #          using either AIC or BIC as criteria.
-#Output: ../Results/bestAIC_quadratic.csv
-#        ../Results/bestBIC_quadratic.csv
-#        ../Results/bestAIC_cubic.csv
-#        ../Results/bestBIC_cubic.csv
-#        ../Results/bestAIC_Briere.csv
-#        ../Results/bestBIC_Briere.csv
-#        ../Results/bestAIC_Ratkowsky.csv
-#        ../Results/bestBIC_Ratkowsky.csv
+#Output: ../Results/bestAIC_quadratic.csv (AIC, quadratic winner)
+#        ../Results/bestBIC_quadratic.csv (BIC, quadratic winner)
+#        ../Results/bestAIC_cubic.csv (AIC, cubic winner)
+#        ../Results/bestBIC_cubic.csv (BIC, cubic winner)
+#        ../Results/bestAIC_Briere.csv (AIC, Briere winner)
+#        ../Results/bestBIC_Briere.csv (BIC, Briere winner)
+#        ../Results/bestAIC_Ratkowsky.csv (AIC, Ratkowsky winner)
+#        ../Results/bestBIC_Ratkowsky.csv (BIC, Ratkowsky winner)
 #Usage: Rscript BestModel.R
 #Date: Nov, 2020
 
 rm(list = ls())
-
+#Import data
 Qua = read.csv("../Results/quadratic_valid.csv", header = T)
 Cub = read.csv("../Results/cubic_valid.csv", header = T)
 
@@ -43,7 +42,7 @@ BICbestQ = data.frame()
 BICbestC = data.frame()
 BICbestB = data.frame()
 BICbestR = data.frame()
-
+#Model selection
 for (i in 1:903){
   q = subset(Qua, ID == i)
   c = subset(Cub, ID == i)
@@ -105,6 +104,7 @@ for (i in 1:903){
     }
 }
 
+#Output
[…]

### 2021-01-19 MiniProject/Code/Briere_model.R

@@ -1,13 +1,12 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: Briere_model.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency: minpack.lm
 #Input: ../Results/filtered_data.csv
-#Function: Fit each thermal performace curve with Ratkowsky model:
+#Function: Fit each thermal performace curve with Briere model:
 #          B(T) = B0*T*(T-T0)*(Tm-T)^0.5 
 #          where B(T) is trait value under temperature T. 
-#          T0, Tm, B0 are constants
+#          T0, Tm, B0 are constants. AIC and BIC are calculated.
 #Output: ../Results/Briere_model.csv
 #Usage: Rscript Briere_model.R
 #Date: Oct, 2020
@@ -26,21 +25,24 @@ name = c("SampleSize","AIC","BIC",
 
 Bri = data.frame(Value_name = name)
 
+#Briere model
 Bri_fun = function(t, B0, T0, Tm){
   return(B0*t*(t-T0)*(abs(Tm-t))^0.5)
 }
 
+
 for (i in 1:903){
   d = subset(data, ID == i)
-  
+  #Start values of T0 and Tm
   T0_start = min(d$ConTemp)
   Tm_start = max(d$ConTemp)
-  
+  #Start values of B0
   B0est = d$OriginalTraitValue/(d$ConTemp*(d$ConTemp-T0_start)*(Tm_start-d$ConTemp)^0.5)
   B0est = B0est[!is.infinite(B0est)]
   B0est = mean(B0est)
   B0_starts = runif(100, 0, 2*B0est)
   
+  #Model fitting with different start values of B0
   for (B0_start in B0_starts){
       mol = try(
         nlsLM(data = d,
@@ -48,7 +50,7 @@ for (i in 1:903){
               start = list(B0 = B0_start, T0 = T0_start, Tm = Tm_start),
               control = list(maxiter = 200)),
         silent = T)
-      if (as.vector(summary(mol))[2] != "try-error"){
+      if (as.vector(summary(mol))[2] != "try-error"){ #If convergence
         report = rep(NA,19)
         #Sample size
         report[1] = nrow(d)

### 2021-01-19 MiniProject/Code/CompileLaTeX.sh

@@ -1,30 +1,21 @@
-#!/bin/bash
 #Auther: Cong liu (cong.liu20@imperial.ac.uk)
-#Script: CompileLaTeX.sh
 #Work Path: CMEECourseWork/MiniProject/Code
 #Input: .tex and .bib files in Code/
-#Function: Run LaTeX, save .pdf file in Results/ and remove other files
-#Output: .pdf file in Results/
-#Usage: bash Code/CompileLaTeX.sh [Base name of .tex]
-#Date: Oct 2020
-
+#Function: Compile LaTeX, save .pdf file in Results/ and remove other files
+#Output: .pdf file in ../Writeup
+#Usage: bash CompileLaTeX.sh [Base name of .tex]
+#Date: Nov 2020
 pdflatex $1.tex
 pdflatex $1.tex
 bibtex $1
 pdflatex $1.tex
 pdflatex $1.tex
 
-rm *~
 rm *.aux
-rm *.dvi
 rm *.log
-rm *.nav
 rm *.out
-rm *.snm
-rm *.toc
 rm *.bbl
 rm *.blg
-rm *fdb_latexmk
-rm *fls
 
-mv *.pdf ../Results
+
+mv *.pdf ../Writeup

### 2021-01-19 MiniProject/Code/ModelQC.R

@@ -1,6 +1,5 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: ModelQC.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency: 
 #Input: ../Results/quadratic_polynomial_model.csv
@@ -8,10 +7,13 @@
 #       ../Results/Briere_model.csv
 #       ../Results/Ratkowsky_model.csv
 #Function: (1) For each curve, select combinations of parameters of Briere model
-#              that lead to lowest AIC or BIC and average them.
+#              that lead to lowest AIC or BIC and conduct model averaging, 
+#              saving as ../Results/Briere_AIC.csv and ../Results/Briere_BIC.csv.
 #          (2) For each curve, select combinations of parameters of Ratkowsky model
-#              that lead to lowest AIC or BIC and average them.
-#          (3) Extract parameter values of all models.
+#              that lead to lowest AIC or BIC and conduct model averaging,
+#              saving as ../Results/Ratkowsky_AIC.csv and ../Results/Ratkowsky_BIC.csv
+#          (3) Extract parameter values of all linear models, saving as 
+#              ../Results/quadratic_valid.csv and ../Results/cubic_valid.csv.
 #Output: ../Results/quadratic_valid.csv
 #        ../Results/cubic_valid.csv
 #        ../Results/Briere_AIC.csv
@@ -24,22 +26,22 @@
 rm(list = ls())
 data = read.csv("../Results/filtered_data.csv")
 
+#Extract parameters of quadratic model
 Q = read.csv("../Results/quadratic_polynomial_model.csv", header = T)
 colnames(Q) = Q[1,]
 Q = Q[-1,]
 Q = data.frame(lapply(Q, as.numeric))
-
 Q_parameter = data.frame(ID=Q$ID,AIC=Q$AIC,BIC=Q$BIC,B0=Q$B0,B1=Q$B1,B2=Q$B2)
 write.csv(Q_parameter,"../Results/quadratic_valid.csv", row.names = F)
-
+#Extract parameters of cubic model
[…]

### 2021-01-19 MiniProject/Code/PlotBestModels.R

@@ -1,6 +1,5 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: PlotBestModels.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency: ggplot2 
 #Input:  ../Results/bestAIC_quadratic.csv
@@ -12,15 +11,15 @@
 #        ../Results/bestAIC_Ratkowsky.csv
 #        ../Results/bestBIC_Ratkowsky.csv
 #        ../Results/filtered_data.csv
-#Function: Plot best model of each curve when AIC or BIC is used for
-#          model selection.
-#Output: ../Results/AIC_bestmodels.pdf
-#        ../Results/BIC_bestmodels.pdf
+#Function: Plot best model of each curve under either AIC or BIC.
+#Output: ../Results/AIC_bestmodels.pdf (AIC-selected)
+#        ../Results/BIC_bestmodels.pdf (BIC-selected)
 #Usage: Rscript PlotBestModels.R
 #Date: Nov, 2020
-
 rm(list = ls())
 library(ggplot2)
+
+#Import models
 q_AIC = read.csv("../Results/bestAIC_quadratic.csv", header = T)
 c_AIC = read.csv("../Results/bestAIC_cubic.csv", header = T)
 b_AIC = read.csv("../Results/bestAIC_Briere.csv", header = T)
@@ -33,6 +32,7 @@ r_BIC = read.csv("../Results/bestBIC_Ratkowsky.csv", header = T)
 
 data = read.csv("../Results/filtered_data.csv", header = T)
 
+#Plotting
 pdf("../Results/AIC_bestmodels.pdf")
 for (i in 1:903){
   modq = subset(q_AIC, ID == i)

### 2021-01-19 MiniProject/Code/PlotValidModels.R

@@ -1,6 +1,5 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: PlotValidModels.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency: ggplot2
 #Input: ../Results/quadratic_valid.csv
@@ -10,7 +9,9 @@
 #       ../Results/Ratkowsky_AIC.csv
 #       ../Results/Ratkowsky_BIC.csv
 #       ../Results/filtered_data.csv
-#Function: Visualize models of all curves
+#Function: Visualize four plausible models of each curve.
+#          If selection and averaging of non-linear model is based on AIC, plots save in ../Results/AIC_models.pdf.
+#          If selection and averaging of non-linear model is based on BIC, plots save in ../Results/BIC_models.pdf.
 #Output: ../Results/AIC_models.pdf
 #        ../Results/BIC_models.pdf
 #Usage: Rscript PlotValidModels.R
@@ -21,6 +22,7 @@ rm(list = ls())
 
 library(ggplot2)
 
+#Import models
 q = read.csv("../Results/quadratic_valid.csv", header = T)
 c = read.csv("../Results/cubic_valid.csv", header = T)
 b_AIC = read.csv("../Results/Briere_AIC.csv", header = T)
@@ -29,6 +31,7 @@ b_BIC = read.csv("../Results/Briere_BIC.csv", header = T)
 r_BIC = read.csv("../Results/Ratkowsky_BIC.csv", header = T)
 data = read.csv("../Results/filtered_data.csv", header = T)
 
+#Plotting ../Results/AIC_models.pdf
 pdf("../Results/AIC_models.pdf")
 for (i in 1:903){
   modq = subset(q, ID == i)
@@ -37,42 +40,49 @@ for (i in 1:903){
   modr = subset(r_AIC, ID == i)
   d = subset(data, ID == i)
   temp = seq(min(d$ConTemp), max(d$ConTemp), 0.1)
-  
+  #Plot points
   p = ggplot(d, aes(x = ConTemp, y = OriginalTraitValue)) + geom_point() +
     labs(title = paste("ID:", as.character(i))) +
     xlab("Temperature") +
     ylab("Trait Value") +
     theme(plot.title = element_text(hjust = 0.5))
+  #Calculate curve of quadratic model
   pre1 = data.frame()
[…]

### 2021-01-19 MiniProject/Code/Ratkowsky_model.R

@@ -1,13 +1,12 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: Ratkowsky_model.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Depemdency: minpack.lm
 #Input: ../Results/filtered_data.csv
 #Function: Fit each thermal performace curve with Ratkowsky model:
 #          B(T)^0.5 = a * (t - T0) * (1 - exp(b * (t - Tm)))
 #          where B(T) is trait value under temperature T. 
-#          T0, Tm, a, b are constants.
+#          T0, Tm, a, b are constants. AIC and BIC are calculated.
 #Output: ../Results/Ratkowsky_model.csv
 #Usage: Rscript Ratkowsky_model.R
 #Date: Oct, 2020
@@ -27,20 +26,24 @@ name = c("SampleSize","AIC","BIC",
 
 Rat = data.frame(Value_name = name)
 
+#Ratkowsky model
 Rat_fun = function(t, T0, Tm, a, b){
   return(a * (t - T0) * (1 - exp(b * (t - Tm))))
 }
 
+#Start values of a and b
 a_starts = 10^seq(-5,4)
 b_starts = 10^seq(-5,4)
+
 for (i in 1:903){
   d = subset(data, ID == i)
-  
+  #Start values of T0 and Tm
   T0_start = min(d$ConTemp)
   Tm_start = max(d$ConTemp)
   
   for (a0 in a_starts){
     for (b0 in b_starts){
+      #Model fitting
       mol = try(
         nlsLM(data = d,
               sqrt(d$OriginalTraitValue) ~ Rat_fun(ConTemp,T0, Tm, a, b),
@@ -51,7 +54,6 @@ for (i in 1:903){
         report = rep(NA,24)
         #Sample size
         report[1] = nrow(d)
-        
         #T0
         report[4] = coef(summary(mol))["T0",1]
         report[5] = coef(summary(mol))["T0",2]
@@ -78,11 +80,10 @@ for (i in 1:903){
         report[23] = b0
         #ID
         report[24] = i
-        
+        #AIC, BIC
         pre = (Rat_fun(d$ConTemp, report[4], report[9], report[14],report[19]))^2
         RSS = sum((d$OriginalTraitValue - pre)^2)
[…]

### 2021-01-19 MiniProject/Code/StatisticsResults.R

@@ -23,21 +23,23 @@ rm(list = ls())
 
 rescale = read.csv("../Results/move_curves.csv", header = T)
 
+#How many curves are not rescaled
 p1 = paste(nrow(subset(rescale, minus == 0)), "curves have no negative trait value")
 print(p1)
 
 IDs = subset(rescale, minus == 0)$ID
 
+#How many times Briere model is fitted
 briere = read.csv("../Results/Briere_model.csv", header = T)
 briere_positive = subset(briere, briere$X %in% IDs)
 p2 = paste(length(table(briere_positive$X)), "of 841 curves can be fitted by Briere function")
 print(p2)
-
+#How many times Ratkowsky model is fitted
 ratkowsky = read.csv("../Results/Ratkowsky_model.csv", header = T)
 ratkowsky_positive = subset(ratkowsky, X %in% IDs)
 p3 = paste(length(table(ratkowsky_positive$X)), "of 841 curves can be fitted by Ratkowsky function")
 print(p3)
-
+#Under AIC selection, how many times each model wins
 print("When AIC is used for model selection:")
 q_AIC = subset(read.csv("../Results/bestAIC_quadratic.csv", header = T),
                ID %in% IDs)
@@ -55,7 +57,7 @@ p6 = paste(length(table(b_AIC$ID)), "curves are best fitted by Briere function")
 print(p6)
 p7 = paste(length(table(r_AIC$ID)), "curves are best fitted by Ratkowsky function")
 print(p7)
-
+#Under BIC selection, how many times each model wins
 print("When BIC is used for model selection:")
 q_BIC = subset(read.csv("../Results/bestBIC_quadratic.csv", header = T),
                ID %in% IDs)
@@ -73,7 +75,7 @@ p10 = paste(length(table(b_BIC$ID)), "curves are best fitted by Briere function"
 print(p10)
 p11 = paste(length(table(r_BIC$ID)), "curves are best fitted by Ratkowsky function")
 print(p11)
-
+#Is there curve has best models from multiple categories of functions when AIC is used as criterion
 if(length(intersect(q_AIC$ID,b_AIC$ID)) == 0 &
    length(intersect(q_AIC$ID,c_AIC$ID)) == 0 &
    length(intersect(q_AIC$ID,r_AIC$ID)) == 0 &
@@ -82,7 +84,7 @@ if(length(intersect(q_AIC$ID,b_AIC$ID)) == 0 &
[…]

### 2021-01-19 MiniProject/Code/cubic_polynomial_model.R

@@ -7,7 +7,7 @@
 #Function: Fit each thermal performance curve with cubic model:
 #          B(T) = B0 + B1*T + B2*T^2 + B3*T^3
 #          where B(T) is trait value under temperature T. 
-#          B0, B1, B2, B3 are constants.
+#          B0, B1, B2, B3 are constants. AIC and BIC are calculated.
 #Output: ../Results/cubic_polynomial_model.csv
 #Usage: Rscript cubic_polynomial_model.R
 #Date: Oct, 2020
@@ -25,6 +25,7 @@ name = c("SampleSize","AIC","BIC",
 
 cub = data.frame(Value_name = name)
 
+#Model fitting
 for (i in 1:903){
   d = subset(data, ID == i)
   
@@ -41,17 +42,17 @@ for (i in 1:903){
   report[5] = coef(summary(mol))["(Intercept)",2]
   report[6] = coef(summary(mol))["(Intercept)",3]
   report[7] = coef(summary(mol))["(Intercept)",4] #H0: B0 = 0
-  #Tm
+  #B1
   report[8] = coef(summary(mol))["poly(ConTemp, 3, raw = T)1",1]
   report[9] = coef(summary(mol))["poly(ConTemp, 3, raw = T)1",2]
   report[10] = coef(summary(mol))["poly(ConTemp, 3, raw = T)1",3]
   report[11] = coef(summary(mol))["poly(ConTemp, 3, raw = T)1",4] #H0: B1 = 0
-  #a
+  #B2
   report[12] = coef(summary(mol))["poly(ConTemp, 3, raw = T)2",1]
   report[13] = coef(summary(mol))["poly(ConTemp, 3, raw = T)2",2]
   report[14] = coef(summary(mol))["poly(ConTemp, 3, raw = T)2",3]
   report[15] = coef(summary(mol))["poly(ConTemp, 3, raw = T)2",4] #H0: B2 = 0
-  
+  #B3
   report[16] = coef(summary(mol))["poly(ConTemp, 3, raw = T)3",1]
   report[17] = coef(summary(mol))["poly(ConTemp, 3, raw = T)3",2]
   report[18] = coef(summary(mol))["poly(ConTemp, 3, raw = T)3",3]

### 2021-01-19 MiniProject/Code/data_filter.R

@@ -1,13 +1,13 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: data_filter.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency:
 #Input: ../Data/ThermRespData.csv
 #Function: Rescale curves with negative trait values to make performance positive.
 #          These rescaled curves will be used in model fitting and selection, to make 
 #          IDs of curves are consecutive integers. They will be removed in further 
-#          analysis.
+#          analysis. Rescaled data saves in ../Results/filtered_data.csv. Whether a curve is 
+#          rescaled saves in ../Results/move_curves.csv (minus=0 means no rescaling)
 #Output: ../Results/filtered_data.csv
 #        ../Results/move_curves.csv
 #Usage: Rscript data_filter.R
@@ -20,6 +20,7 @@ data = read.csv("../Data/ThermRespData.csv")
 tempData = data.frame()
 move = rep(NA,903)
 
+#Rescaling
 for (i in 1:903){
   d = subset(data, ID == i)
   a = min(d$OriginalTraitValue)

### 2021-01-19 MiniProject/Code/quadratic_polynomial_model.R

@@ -1,13 +1,12 @@
 #Language: R 4.0.3
-#Auther: Cong Liu (cong.liu20@imperial.ac.uk)
-#Script: quadratic_polynomial_model.R
+#Author: Cong Liu (cong.liu20@imperial.ac.uk)
 #Work Path: CMEECourseWork/MiniProject/Code
 #Dependency:
 #Input: ../Results/filtered_data.csv
 #Function: Fit each thermal performance curve with quadratic model:
 #          B(T) = B0 + B1*T + B2*T^2 
 #          where B(T) is trait value under temperature T, 
-#          B0, B1, B2 are constants.
+#          B0, B1, B2 are constants. AIC and BIC are calculated.
 #Output: ../Results/quadratic_polynomial_model.csv
 #Usage: Rscript quadratic_polynomial_model.R
 #Date: Oct, 2020
@@ -24,6 +23,7 @@ name = c("SampleSize","AIC","BIC",
 
 qua = data.frame(Value_name = name)
 
+#Model fitting
 for (i in 1:903){
   d = subset(data, ID == i)
   
@@ -40,12 +40,12 @@ for (i in 1:903){
   report[5] = coef(summary(mol))["(Intercept)",2]
   report[6] = coef(summary(mol))["(Intercept)",3]
   report[7] = coef(summary(mol))["(Intercept)",4] #H0: B0 = 0
-  #Tm
+  #B1
   report[8] = coef(summary(mol))["poly(ConTemp, 2, raw = T)1",1]
   report[9] = coef(summary(mol))["poly(ConTemp, 2, raw = T)1",2]
   report[10] = coef(summary(mol))["poly(ConTemp, 2, raw = T)1",3]
   report[11] = coef(summary(mol))["poly(ConTemp, 2, raw = T)1",4] #H0: B1 = 0
-  #a
+  #B2
   report[12] = coef(summary(mol))["poly(ConTemp, 2, raw = T)2",1]
   report[13] = coef(summary(mol))["poly(ConTemp, 2, raw = T)2",2]
   report[14] = coef(summary(mol))["poly(ConTemp, 2, raw = T)2",3]
@@ -55,6 +55,7 @@ for (i in 1:903){
         
   qua = cbind(qua,report)
 }
+
 
 labels = c("ID",qua[16,][-1])
 colnames(qua) = labels

### 2021-08-19 MResProject/Latex/Draft.tex
Added README file.

\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=red,citecolor=black]{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{floatrow}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{natbibspacing}
\usepackage[toc,page]{appendix}

\title{Metagenomic DNA discoveries after sequencing everything (bacteria, parasites, food, gut) inside a bee}
\author{Cong Liu}
\date{2021.8}

\linespread{1.5}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}

\begin{document}

\bibliographystyle{plainnat}
\setcitestyle{round}

  \maketitle
  \vspace*{\fill}
  \begin{center}
    A thesis submitted in partial fulfilment of the requirements for the degree of Master
of Science/Research at Imperial College London
\newline
Submitted for the MRes/MSc in Computational Methods in Ecology and Evolution
  \end{center}

  \newpage
  Declaration:
  \newline

  \newpage
  \linenumbers
  \begin{abstract}
    Bee-associated microbiome plays a crucial role in host health and relevant investigations have been boosted by shotgun metagenomics. 
    However, bioinformatics for metagenomic data analysis is complex, and the results may be compromised by insufficient sequencing. 
    Here, an integrated pipeline combining assembly-dependent and -independent methods was introduced for taxonomic and functional profiling of shotgun metagenomic data. 
    It was used for profiling metagenomic datasets ($2 \times 150 bp$ read pairs) from honey bees, bumble bees and flower surface. 
    Rarefaction and model fitting was conducted to compute expected species/function diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to determine minimal sequencing depth capable of estimating diversity sufficiently. 
    As a result, functional profiling was demanding about sequencing effort. 
    None of datasets involved was sufficient for providing almost complete coverage of function diversity. 
    As for species diversity, the average minimal sequencing depth for reliable estimation of Hill number of order 0, 1 and 2 for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; and for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million. 
    For flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
    These results are helpful for cost-effective utilization of shotgun metagenomics in investigations of pollination system. 
    The integrated pipeline and the framework for rarefaction analysis can also be applied for researches on other environments. 
  \end{abstract}

  \section{Introduction}
  The health of bees is a crucial issue that has received increasing concern \citep{amiri2020using}. 
  As pollinators of numerous plants, bees play an important role in the stability of natural and agricultural systems \citep{hristov2020significance,foldesi2021larger,bansch2021crop,khalifa2021overview}. 
  However, diverse pathogens and environmental factors impose threaten on bee health. 
  The trend of bee decline has been widely observed at a global scale and attributed to multiple factors including pesticide exposure, invasive species, habitat loss, disease prevalence and climate change \citep{brown2009conservation,hristov2020factors,cheng2021ecology,zattara2021worldwide}.
  \newline
  Bees are associated with a community of microorganisms influencing host health \citep{engel2016bee,raymann2018role}. 
  Bee-associated microbiome plays a role in food digestion and carbohydrate metabolism by mediating processes including breaking down 
  % plant-produced polysaccharide including 
  plant-produced pectin and hemicellulose \citep{zheng2019division}; hydrolysis of sucrose \citep{engel2012functional,lee2015saccharide}, a predominant component of nectar \citep{nicolson2007nectar} and metabolism of mannose \citep{engel2012functional,lee2015saccharide} which presents in nectar 
  % of \textit{Tilia} 
  \citep{adler2000ecological} and is poisonous to honey bees \citep{de1986mechanism}. 
  Besides, it is also involved in immunity against pathogens, providing protection against pathogens including \textit{Crithidia}, 
  % a protozoan genus exclusively parasitising arthropods 
  \citep{koch2011socially,cariveau2014variation}, \textit{Paenibacillus larvae}, 
  % a bacteria causing lethal American foulbrood in honey bees 
  \citep{ebeling2016biology,forsgren2010novel} and \textit{Nosema} 
  % a genus of fungal pathogens 
  \citep{cariveau2014variation,maes2016diet}.
  \newline
  Host-associated microbiome plays an important role in host homeostasis and metagenomics boosted by high throughput sequencing provides powerful tools for understanding its composition, function and dynamics. 
  For example, amplicon sequencing is a powerful tool and has revealed incredible understanding in microbiome \citep{eckburg2005diversity,galloway2020tools,new2020metagenomics}. 
  However, it only focuses on a small part of the whole microbiome. 
  Shotgun sequencing of microbiome, or metagenomics, unselectively captures DNA in a sample and is capable of providing comprehensive inventories of taxa and functional gene clusters (FGCs) with high resolution \citep{quince2017shotgun,new2020metagenomics}.
  \newline
  However, utilization of shotgun metagenomics is hindered by challenges in bioinformatics. 
  Typical goal of metagenomics is to provide taxonomic and functional profile of the community, and there is not a golden standard for bioinformatics of metagenome. 
  Generaly, one of the first steps in metagenomic analysis is assembling short reads into long contigs, which can help improve accuracy of metagenomic annotation \citep{tran2020assembling} and is necessary for 
  % tasks including recovery of uncultured genomes \citep{garza2015cultured,chen2020accurate} and 
  discovery of novel taxa and genes \citep{culligan2014metagenomics,youngblut2020large}. 
  However, metagenome assembly is complex, compromised by fragmental assembly, chimeras \citep{mikheenko2016metaquast} and loss of taxon/function diversity due to unassembled reads \citep{vollmers2017comparing,ayling2020new}. 
  Probably because of these shortcomings, assembly is skipped in some researches and short reads are directly proceeded for annotation \citep{tringe2005comparative,huson2007megan,abubucker2012metabolic,vermote2018amplicon,bovo2018shotgun}, although the accuracy may be compromised due to low information load of short reads \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling}. 
  A combination of both assembly-dependent and -free method might be helpful for overcoming the complexity of metagenomic assembly and inaccuracy of short read annotation \citep{becker2020modular}. 
  \newline
  Another challenge of metagenomics is the determination of sequencing depth. 
  It is recommended to retrieve as many reads as possible \citep{quince2017shotgun}, since insufficient sequencing causes imprecise estimation of taxon/FGC diversity \citep{cattonaro2018you,zaheer2018impact,pereira2019impact,gweon2019impact}. 
  However, deep sequencing is expensive, which hinders its utilization, especially in large-scale projects. 
  Currently, there is hardly any published guideline for the sufficient sequencing depth of a given environment or study type in order to reach a trade-off between sequencing effort and reliable output. 
  \newline
  The determination of sequencing depth can be conducted by rarefaction analysis, a method originated from traditional ecology \citep{sanders1968marine,hurlbert1971nonconcept,heck1975explicit,moreno2000assessing,hortal2005ed,gomez2014using,hughes2021sampling}. 
  In field based surveys, a random sample of individuals is drawn from a community and assigned to species. 
  Then a rarefaction curve illustrating expected biodiversity represented by given sampling effort (often measured by number of captured individuals) is generated by random subsampling the original sample without replacement, and quantified by model fitting \citep{hughes2005application,gotelli2011estimating}. 
  The slope of the rarefaction curve represents the expected rise of the curve if one more individual is captured. 
  The sample is nearly complete if and only if the final slope is small, and the point at which the slope of rarefaction curve falls to a cut-off value represents the minimal sampling effort required for assessment of biodiversity \citep{heck1975explicit,moreno2000assessing,hortal2004butterfly,hortal2005ed,chao2012coverage,gomez2014using,roswell2021conceptual}. 
  This framework for determination of sampling effort can be used in shotgun metagenomics, since a metagenomic dataset can be viewed as a random sample of an assemblage of genomic sequences, and 
  profiling is the process by which reads are assigned to taxa or FGCs. 
  The concept corresponding to sampling effort is sequencing depth in metagenomics, which is measured by read number.
  \newline 
  In macroecology, comprehensive analytical frameworks are available for computing expected biodiversity returned by given sample sizes using a reference sample \citep{heck1975explicit,chao2012coverage,chao2014rarefaction}. 
  % However, analytical approaches derived for computing rarefaction curve in macroecology \citep{heck1975explicit,chao2012coverage,chao2014rarefaction} 
  However, they are not suitable for metagenomics because 
  % they are based on 
  of the assumptions that every captured individual can be assuredly assigned to a species, and the present of rare species is as reliable as that of abundant species. 
  In shotgun metagenomics, reads may be unannotated or annotated incorrectly due to low sequencing quality, host contamination, similar structures in genomes of different species, non-coding regions in genomes and limited sensitivity of profiling pipeline. 
  As a result, taxa or FGCs of low relative abundance are more likely to be false positive than that of high abundance.
  \newline
  In this project, I aimed to (1) construct an integrated pipeline combining assembly-dependent and -independent methods for metagenomic profiling and (2) estimate minimal sequencing depth sufficient for covering species and FGC diversity of metagenome from three environmental types: honey bees, bumble bees and surface of flowers. 
  In the integrated pipeline (Figure \ref{Pipeline}), assembly-dependent taxon profiling is conducted after quality filtering and removing host contamination. 
  To address high negative rate of assembly-dependent search, a reference database of genomes from species present in the assembly is constructed and used for filtering non-host reads. 
  Reads not recruited by the reference database are subjected to assembly-free taxonomic search. 
  This integrated pipeline was used to profile metagenomic datasets from honey bees, bumble bees and environmental DNA (eDNA) washed from a flower (\textit{Erigeron annuus}). 
  It was shown that the construction of reference database and assembly-free search helped identified species not represented by the assembly. 
  Then I simulated different sequencing depth by rarefaction and profiled subsampled datasets using the integrated pipeline, generating inventories of species and Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}. 
  Each KO represents one FGC, \textit{i.e.} an aggregate of genes with same function. 
  Diversity of species and KOs was measured by Hill numbers of order 0, 1 and 2. 
  Sequencing depth was measured by number of clean read pairs (150 bp read length). 
  % The higher the order is, the more sensitive to relative abundances Hill number is. 
  The relationship between Hill numbers and sequencing depth (number of 150 bp pair-end reads) was quantified by fitting and averaging asymptotic species accumulation models, and estimation of minimal sequencing depth was given by the point where the slope of rarefaction curve drops to cut-off values. 
  Sample would be excluded from estimation of minimal sequencing depth if the original dataset was not sufficient for providing an almost complete inventory of species or KOs, which was characterized by small final slope of rarefaction curve for species or KO richness (Hill number of order 0). 
  As a result, when measuring species diversity by Hill number of order 0, 1 and 2, the average minimal sequencing depth for honey bee samples are 40.33 million, 18.57 million and 17.45 million; for bumble bee samples, the averages are 42.49 million, 40.33 million and 24.77 million; and for flower surface, 0.88 million sequencing depth is not sufficient for providing an almost complete inventory of species, indicating higher sequencing depth is needed. 
  As for functional diversity, no datasets involved in this project is big enough for providing an almost complete inventory of KOs, indicating the sequencing depth need to be higher than the maximum of each sample type, \textit{i.e.} 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../Figures/FigurePipeline.pdf}
    \caption{An overview of the integrated pipeline. 
    The pipeline is separated into 5 modules, indicated by blue boxes. 
    Green boxes indicate dataset of reads, while yellow boxes indicate database of genomes. 
    Black arrows indicate the input and output of each step and the numbers on them indicate the order that each step is utilized.}
    \label{Pipeline}
  \end{figure}

  \section{Materials and Methods}
    \subsection{Samples, DNA extraction and sequencing}

    \subsection{Metagenomic profiling using integrated pipeline}
      \subsubsection{Integrated pipeline}
      The integrated pipeline was designed for shotgun metagenomic profiling (assigning reads to taxa or FGCs). 
      It is separated into five modules (Figure \ref{Pipeline}).
      \newline
      In the module of quality control and host removing, sequencing data quality is checked using FastQC v.0.11.5 \citep{andrews2010fastqc} and quality control is conducted by Trimmomatic v.0.39 \citep{bolger2014trimmomatic}. 
      Then clean reads are mapped to host genome using Bowtie2 v.2.4.2 \citep{langmead2012fast} and non-host reads are extracted by SAMtools v.1.11 \citep{li2009sequence}. 
      \newline
      The non-host reads are subject to the module of assembly-dependent species identification. 
      \textit{De novo} assembly is conducted by SPAdes v.3.15.2 \citep{prjibelski2020using}. 
      Assembled contigs are aligned to NCBI non-redundant (nr) database by DIAMOND v.2.0.7.145 \citep{buchfink2015fast}, and assigned to taxa by MEGAN6 \citep{huson2007megan}. 
      \newline
      Then fragment recruitment is conducted. 
      A reference database comprising reference genome dataset, \textit{i.e.} genomic sequences in FASTA format and corresponding genome annotation in general feature format (gff), was constructed. 
      For each species represented by assembly, its reference genome dataset, if available, is downloaded from NCBI using its \textit{datasets} command-line tool and added to the reference database. 
      Then non-host reads are mapped to the reference database by Bowtie2, and unmapped reads are extracted by SAMtools. 
      \newline
      Reads not recruited by the reference database are subjected to assembly-independent species identification. 
      They are aligned to NCBI nr database through DIAMOND and assigned to taxa by MEGAN6.
      \newline
      Finally, functional annotation is conducted by EggNOG-mapper v.2.1.2 \citep{huerta2017fast}. 
      It takes coding sequences (CDSs) of genomes in the reference database and reads subject to assembly-independent species identification as input and assigns them to KOs.
      \newline
      The integrated pipeline was used for analyzing metagenomic datasets involved in this study and details in parameter settings of each module are described in Supplementary \ref{ParameterSetting}.

      \subsubsection{Taxon/function quantification and metabolic pathway reconstruction}
      After profiling, identified species and KOs were quantified by calculating relative sequence abundance, \textit{i.e.} proportion of reads assigned to a species/KO in all reads annotated. 
      For species without available reference genomes, their abundances were calculated using reads assigned to them in assembly-independent search. 
      As for taxa with available reference genomes, they may be identified in both assembly-dependent and -independent search due to strain-specific genomic structures that are not present in reference genomes. 
      Their abundances were calculated by summating number of reads that (1) mapped to coding sequences (CDSs) of reference genomes and (2) assigned to them in assembly-independent search. 
      Reads mapped to non-coding regions were not taken into consideration in order to avoid overestimation since the assembly-independent search was based on aligning reads to nr database, which is composed of proteins. 
      As for KO quantification, CDSs with zero-coverage were excluded. 
      Abundances of KOs were calculated by summating number of reads that (1) mapped to CDSs assigned to KOs and (2) assigned to KOs directly. 
      Extraction of CDSs and calculation of their coverage were conducted by BEDtools v.2.30.0 \citep{quinlan2010bedtools}.
      % \newline
      % In order to investigate metabolic potentialities of metagenome, CDSs with non-zero coverage from reference genomes and reads subject to assembly-independent search were functionally annotated using EggNOG-mapper v.2.1.2 \citep{huerta2017fast}. 
      % It searches query sequences  
      % Identified functional categories were quantified by proportion of reads assigned to a category in all reads annotated (relative sequence abundance). 
      % The number of reads assigned to a functional category equals the sum of reads (1) assigned to the category directly and (2) mapped to CDSs assigned to the category.
      \newline
      Metabolic pathways were inferred based on KOs. 
      Reads assigned to plants and arthropods were not included since they were unlikely to represent living organisms. 
      MinPath v.1.6 was used for pathway inference \citep{ye2009parsimony}. 
      It finds a minimal set of KEGG pathways that can explain all KOs provided as input.

    \subsection{Estimation of minimal sequencing depth required for metagenomic profiling}
    The impact of sequencing depth on taxon/function diversity of metagenome was simulated by rarefaction. 
    Diversity was measured by Hill numbers, which are calculated from inventory of relative abundances. 
    For taxon diversity, the inventory was generated by assigning reads to species; while for function diversity, it was obtained by assigning reads to KOs. 
    Then the rarefaction curve plotting Hill number against sequencing depth was computed, and minimal sequencing depth required for reliable extimation of diversity were given by the point where the slope of rarefaction curve drops to a cut-off value.

      \subsubsection{Simulating different sequencing depth by subsampling and measuring diversity by Hill numbers}
      Species/KO inventories obtained from different sequencing depth was simulated by rarefaction. 
      % \textit{i.e.} randomly taking a proportion of the original dataset without replacement. 
      Since the ratio between numbers of raw and clean reads is dependent on sequencing process and is not influenced by sample type, sequencing depth here refers to number of clean read pairs to exclude variance caused by different proportion of low quality reads in samples of same type. 
      Besides, the expected ratio between host and non-host reads in a metagenomic dataset is dependent on the DNA sample and not impacted significantly by sequencing depth. 
      Thus the proportion of non-host reads in each simulation is expected to be the same with that in the original dataset. 
      \newline
      Based on these considerations, I randomly subsampled non-host dataset of each sample, taking 10\%-100\% of read pairs at interval of 10\% by \textit{reformat.sh} script of BBmap v.38.90 \citep{bushnell2014bbmap}, and profiled subsampled datasets by the integrated pipeline (Figure \ref{Pipeline}). 
      The sequencing depth of each subsampled dataset equals number of subsampled non-host read pairs divided by ratio between non-host and clean read pairs. 
      Thus, each subsampled dataset of non-host reads is corresponded to an imaginary dataset of clean reads, whose proportion of non-host reads is the same with that of the original metagenomic dataset. 
      \newline
      After profiling subsampled datasets, species/KO diversity was measured by Hill numbers of order $q$, defined as Equation \ref{HillNumbers} \citep{hill1973diversity}.
      \begin{equation}
        D^{(q)} = (\sum_{i}(p_i)^q)^{\frac{1}{1-q}}
        \label{HillNumbers}
      \end{equation}
      $p_i$ represents the relative abundance of $i$th species/KO, and $q$ determines sensitivity to relative abundances. 
      When $q = 0$, abundances are not taken into consideration and $D^{(0)}$ equals species/KO richness. 
      When $q = 1$, Hill number is defined as the limit of Equation \ref{HillNumbers} as $q$ tends to 1 (\ref{HillShannon}) and emphasis is given to species/KOs with general abundances.
      \begin{equation}
        D^{(1)} = e^{-\sum_{i}p_ilogp_i}
        \label{HillShannon}
      \end{equation}
      When $q = 2$, high leverage is provided to abundant species/KOs and Hill number equals the inverse of Simpson index (Equation \ref{HillSimpson}).
      \begin{equation}
        D^{(2)} = \frac{1}{\sum_{i}(p_i)^2}
        \label{HillSimpson}
      \end{equation}

      \subsubsection{Quantification of relationship between sequencing depth and Hill numbers by fitting rarefaction curves}
      Hill number of order $q$ (Equation \ref{HillNumbers}) measures diversity of an inventory as the number of equally abundant categories in an imaginary inventory with the same diversity \citep{chao2014unifying,roswell2021conceptual}. 
      Order $q$ determines leverage given to abundant categories. 
      All Hill numbers behave in the following way: if a proportion of categories in an inventory was removed randomly, all Hill numbers would decrease by that proportion \citep{roswell2021conceptual}. 
      Thus, it can be hypothesized that as sequencing depth (number of clean read pairs) increases, the detection of novel species/KOs leads to increase of Hill numbers, and when sequencing depth is so big that all species/KOs present in the metagenomic DNA sample have been detected, Hill numbers level off. 
      Such a relationship can be fitted by asymptotic species accumulation models.
      \newline
      Let Hill number of order $q$ (Equation \ref{HillNumbers}) be a function of sequencing depth $x$, which takes million read pairs as the unit. 
      This function was fitted using a multimodel inference method. 
      First, a total of five candidate models (Table \ref{candidate_models}) were fitted to rarefaction curves which plots Hill numbers against sequencing depth. 
      R package \textit{minpack.lm} v.1.2.1, which employs Levenberg-Marquardt nonlinear least-square algorithm, was used for model fitting. 
      Then small sample unbiased Akaike information criterion (AICc) \citep{anderson2007model} of each candidate model was calculated (Equation \ref{AICc}):
      \begin{equation}
        AICc = -2L+2k+\frac{2k(k+1)}{(n-k-1)}
        \label{AICc}
      \end{equation}
      where $n$ is number of observed data points ($n = 10$ in this study), $k$ is the number of fitted coefficients, and $L$ is maximized log-likelihood, given by Equation \ref{likelihood}.
      \begin{equation}
        L = -0.5nlog(\frac{Rss}{n})
        \label{likelihood}
      \end{equation}
      $Rss$ represents residual sum of squares.
      \newline
      Then model averaging was conducted. First, differences of AICc scores between $i$th candidate models and the model with lowest AICc value were calculated using Equation \ref{Delta}.
      \begin{equation}
        \Delta_i = AICc_i-AICc_{min}
        \label{Delta}
      \end{equation}
      $AICc_i$ is the AICc score of $i$th plausible model and $AICc_{min}$ is the lowest AICc score among all candidate models. 
      The Akaike weight of $i$th model is given by Equation \ref{weight} \citep{anderson2007model}.
      \begin{equation}
        w_i = \frac{e^{(-0.5\Delta_i)}}{\sum_{i}e^{(-0.5\Delta_i)}}
        \label{weight}
      \end{equation}
      Denote $i$th candidate model by $D^{(q)}_i = D^{(q)}_i(x)$, the averaged model is given by Equation \ref{average}.
      \begin{equation}
        D^{(q)}(x) = \sum_{i}w_iD^{(q)}_i(x)
        \label{average}
      \end{equation}
      The slope of rarefaction curve was calculated by first derivative of averaged model (Equation \ref{average_derivation}). 
      It reflects the increase rate of the curve.
      \begin{equation}
        \frac{dD^{q}}{dx} = \sum_{i}w_i\frac{dD^{(q)}_i}{dx}
        \label{average_derivation}
      \end{equation}
      The asymptote of rarefaction curve as sequencing depth tends to infinity is given by Equation \ref{asymptote}. 
      It provides an estimation of the total diversity and is comparable among metagenomic DNA samples with different sequencing depth \citep{lamas1991preliminary,soberonm1993use,hortal2004butterfly,jimenez2005determining,hortal2006evaluating}. 
      However, the accuracy of asymptotic estimators is controversial in macroecology \citep{soberonm1993use,colwell1994estimating,chazdon1998statistical,jimenez2006comparing,hortal2006evaluating}, and their performance in shotgun metagenomics is seldom evaluated.
      \begin{equation}
        \lim_{x \to +\infty}D^{(q)}(x) = \sum_{i}w_i\lim_{x \to +\infty}D^{(q)}_i(x)
        \label{asymptote}
      \end{equation}

      \subsubsection{Estimating minimal sequencing depth using rarefaction curves} 
      Minimal sequencing depth is defined as the point at which diversity starts to level off as sequencing depth increases, and its precise estimation via rarefaction is based on the assumption that the original dataset is sufficient for detection of almost all species/KOs present. 
      % providing a reliable inventory of species/KOs present, \textit{i.e.} almost all species/KOs present in the DNA sample are detected. 
      This assumption can be verified by looking at the rarefaction curve that plots species/KO richness (Hill number of order 0) against sequencing depth. 
      The original dataset is sufficient for providing a reliable inventory if and only if the rarefaction curve of richness is characterized by a small final slope \citep{heck1975explicit,moreno2000assessing,hortal2004butterfly,hortal2005ed,gomez2014using}. 
      Then an estimation of minimal sequencing depth is provided by the point at which the slope of rarefaction curve decreases to a given cut-off value \citep{hortal2005ed}. 
      % \newline 
      % This method is on the analogy of that used in macroecology to determine whether more sampling effort is needed to illustrate biodiversity of a community. 
      % In macroecological researches, rarefaction curve plots detected biodiversity against sampling effort, which is often measured by number of captured individuals. 
      % Precise quantification of the relationship between biodiversity and sampling effort via rarefaction assumes the original sample is nearly complete \citep{heck1975explicit,gotelli2011estimating}. 
      % This assumption can be verified by looking at the slope of rarefaction curve, which is the expected rise of the curve if one more individual is captured. 
      % The sample is nearly complete if and only if the final slope is small\citep{heck1975explicit,chao2012coverage,roswell2021conceptual}. 
      % The point at which the slope of rarefaction curve falls to a cut-off value represents the minimal sampling effort required for assessment of biodiversity \citep{hortal2005ed}. 
      % The concept corresponding to sampling effort is sequencing depth in metagenomics, which is measured by number of read pairs. 
      % Thus, the insights provided by rarefaction analysis in macroecology is transferrable to metagenomics.
      % \newline 
      % However, analytical approaches derived for computing rarefaction curve in macroecology \citep{chao2012coverage,chao2014rarefaction} are not suitable for metagenomics because they are based on the assumption that every captured individual can be assuredly assigned to a species, which is unreasonable for shotgun metagenomics. 
      % In shotgun metagenomics, reads may not be assigned to any species or function category for multiple reasons, including sequencing error, limited sensitivity of homology search, similar structures in genomes of different species and the present non-coding regions.

  \section{Results}

    \subsection{Sequence reads and pipeline evaluation}
    Eight samples (four honey bees, three bumble bees and one flower eDNA) were sequenced. 
    The quality reports of raw reads showed low-quality 3'-end (Figure \ref{QC}a), uneven base content in 5'-end (Figure \ref{QC}b) and the present of adaptors (Figure \ref{QC}c). 
    The quality control procedure covered these aspects and improved data quality (Figure \ref{QC}d, \ref{QC}e and \ref{QC}f).
    \newline
    After quality control, read pairs aligned to host genome were removed. 
    Table \ref{data_statistics} reports numbers of raw, clean and non-host read pairs. 
    Honey bee sample \textit{Bee\_Amellifera\_13\_1} was dropped for further analysis since its raw read pair number (1.10 million) is significantly lower than three other samples (about 59 million). 
    After quality control, 62.08\%-76.52\% of raw read pairs were retained for these three honey bee samples. 
    Then a different proportion of non-host read pairs (29.52\%-86.19\%) were retained. 
    As for bumble bee samples, about 58 million raw read pairs were obtained for each sample and 82.1\%-83.8\% were retained after quality control. 
    After host removing, 7.35\%-10.08\% of clean reads were retained.  
    For flower eDNA sample, 1.44 million raw read pairs were obtained and 61.15\% of them were retained. 
    \newline
    In integrated pipeline (Figure \ref{Pipeline}), clean non-host reads are first assembled to into contigs and assigned to taxa. 
    To address false negative results in assembly-dependent taxon search \citep{sharon2015accurate,vollmers2017comparing}, a reference database composed of genomes of species represented by contigs is constructed. 
    Reads not aligned to the reference database are subjected to assembly-independent taxon search. 
    The reference database and assembly-independent search helped improve species identification in all three sample types, especially in simulations of low sequencing depth (Figure \ref{CompareSensitivity}).

      \begin{figure}[H]
        \begin{subfigure}
          \centering
          \textbf{a}
        \end{subfigure}
        \hspace{0.32\linewidth}
        \begin{subfigure}
          \centering
          \textbf{b}
        \end{subfigure}
        \hspace{0.32\linewidth}
        \begin{subfigure}
          \centering
          \textbf{c}
        \end{subfigure}
        \newline
        \hfill
        \begin{subfigure}
          \centering
          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Honey.pdf}
        \end{subfigure}
        \hfill
        \begin{subfigure}
          \centering
          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Bumble.pdf}
        \end{subfigure}
        \hfill
        \begin{subfigure}
          \centering
          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Flower.pdf}
        \end{subfigure}
        \caption{Integrated pipeline improves the detection of species richness. 
        The horizonal axis represents sequencing depth, and the vertical axis represents the ratio between number of species only detected by assembly-independent search and number of species detected by assembly-dependent search. 
        Sample type is shown in the top left of each subfigure.}
        \label{CompareSensitivity}
        \end{figure}

    \subsection{Characterization of species composition}
    All seven samples were dominated by bacterial and/or arthropod species (Figure \ref{GroupAbundance}b). 
    Honey bee samples \textit{Bee\_Amellifers\_hv13\_2} and \textit{Bee\_Amellifera\_wild\_1} were dominated by bacteria (approximate 90\% relative abundance), while in \textit{Bee\_Amellifera\_hv15\_1}, arthropods, bacteria and viruses accounted for most annotated reads. 
    As for bumble bee samples, they were all dominated by bacteria and arthropods. 
    For the flower eDNA sample, arthropods were the most dominant and bacteria were the second.

      \begin{figure}[H]
        \centering
        \begin{subfigure}
          \centering
          \textbf{a}
        \end{subfigure}
        \newline
        \begin{subfigure}
          \centering
          \includegraphics[width=0.5\textwidth]{../Figures/NonHostRatio.pdf}
        \end{subfigure}
        \vfill
        \newline
        \begin{subfigure}
          \centering
          \textbf{b}
        \end{subfigure}
        \newline
        \begin{subfigure}
          \centering
          \includegraphics[width=0.5\textwidth]{../Figures/1_species_RelAbundance_GroupAbundance.pdf}
        \end{subfigure}
        \vfill
        \caption{a. The number of host and non-host reads in each sample. 
        b. The relative abundance of species under six taxonomic groups: superkingdom Viruses, superkingdom Bacteria, kingdom Viridiplantae (plants), kingdom Fungi, phylum Arthropoda and others (species that are not in the other five groups).}
        \label{GroupAbundance}
        \end{figure}

    Figure \ref{BacteriaHeatmap} illustrates composition of bacteria, most of which are common bee-associated species within \textit{Bifidobacterium}, \textit{Frischella}, \textit{Gilliamella}, \textit{Snodgrassella} and \textit{Lactobacillus} \citep{koch2011bacterial,moran2015genomics,kwong2017dynamic}. 
    \textit{Apilactobacillus} and \textit{Bombilactobacillus} are genera separated from \textit{Lactobacillus} recently \citep{zheng2020taxonomic}. 
    \textit{Fructobacillus} is often found in fructose-rich environments like flowers \citep{endo2014genus}. 
    \textit{Bartonella apis} is related to animal pathogens \citep{kevsnerova2016bartonella} and is widespread in honey bee workers \citep{raymann2018role}. 
    % \textit{Bombiscardovia coagulans} is a member of Bifidobacteriaceae isolated from \textit{Bombus lapidarius} \citep{killer2010bombiscardovia}. 
    % \textit{Candidatus Schmidhempelia bombi} is an uncultured symbiont of \textit{Bombus impatiens} \citep{martinson2014genomic}. 
    % It should be noted that some typical bee-associated bacteria were found on the flower, including \textit{Bartonella apis}, \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}.
    % \newline
    % Different sample types are different in abundance distribution of bacteria (Figure \ref{BacteriaHeatmap}). 
    % For honey bee samples, bacterial community in \textit{Bee\_Amellifera\_hv13\_2} is dominated by \textit{Fructobacillus fructosus} (approximate 70\% relative abundance), while the other two honey bee samples share a similar bacteria abundance distribution with almost no species with relative sequence abundance $> 20\%$. 
    % As for bumble bee samples, \textit{Bifidobacterium commune} is the most abundant bacterial species in all three samples (about $20\%$ in \textit{Bee\_Bimpatiens\_hv3\_1} and about $40\%$ in the other two samples). 
    % Two bumble bees from the same hive (\textit{Bee\_Bimpatiens\_hv4\_1} and 
    % \textit{Bee\_Bimpatiens\_hv4\_1}) share similarity in bacterial abundance distribution. 
    % In the flower eDNA sample, some bee-associated bacteria were identified, including \textit{Bartonella apis}, \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}.
    \newline
    Figure \ref{ArthropodHeatmap} shows composition of arthropods, and most of them are pollinators within \textit{Apis} and \textit{Bombus}. 
    However, some of them might be considered as false positive. 
    For example, \textit{Apis cerana}, \textit{Apis dorsata} and \textit{Apis florea} are mainly found in Asia and unlikely to present in the area where samples were collected. 
    These might derive by similarity between genomes of \textit{Apis mellifera} and other \textit{Apis} species. 
    % It should be noted that host contamination was removed before profiling. 
    % As a result, in honey bee samples, \textit{Apis} species were rare and \textit{Bombus} species were abundant, while in bumble bee samples, \textit{Bombus} species were rare and \textit{Apis} species are abundant. 
    \newline
    Figure \ref{PlantHeatmap} illustrates plant species, indicating foraging area of bees. 
    Most samples were dominanted by one or two plant species, except \textit{Bee\_Amellifera\_hv13\_2}. 
    Some crops were identified, including \textit{Brassica napus} (rape), \textit{Brassica oleracea}, \textit{Cicer arietinum} (chickpea), \textit{Glycine max} (soybean), \textit{Helianthus annuus} (sunflower), \textit{Nicotiana sylvestris} (flowering tabacco) and \textit{Raphanus sativus} (radish).
    \newline
    Figure \ref{FungusHeatmap} shows compositions of fungal species. 
    \textit{Nosema ceranae}, a widespread bee pathogen, was the dominant fungal species in most samples including the flower eDNA. 
    Three yeast species (\textit{Clavispora lusitaniae}, \textit{Saprochaete ingens} and \textit{Wickerhamiella sorbophila}) were found in bees. 
    % Other fungal species include three yeasts (\textit{Clavispora lusitaniae}, \textit{Saprochaete ingens} and \textit{Wickerhamiella sorbophila}) 
    % and one opportunistic pathogen (\textit{Malassezia restricta}). 
    \newline
    Figure \ref{ViruseHeatmap} illustrates viruses identified. 
    Several phages were identified, including \textit{Bifidobacterium phage BitterVaud1} that infects bee-commensal bacterium \textit{Bifidobacterium asteroides} \citep{bonilla2020honey}, \textit{Bacteriophage sp.} that infects \textit{Pseudomonas aeruginosa} \citep{essoh2015investigation}, an opportunistic pathogen that might contaminate bees \citep{bailey1968honey,papadopoulou1992experimental,papadopoulou1993haemocyte}, and species in Myoviridae and Siphoviridae. 
    % family Myoviridae and Siphoviridae
    Most of the others are arthropod-associated viruses. 
    \textit{Apis mellifera filamentous virus} and \textit{Bombus cryptarum densovirus} are bee-infecting viruses \citep{clark1978filamentous,bailey1981properties,schoonvaere2018study}. 
    Several arthropod-infecting parvoviruses were found, including \textit{Blattodean pefuambidensovirus 1}, \textit{Hemipteran scindoambidensovirus 1}, \textit{Hymenopteran scindoambidensovirus 1} and \textit{Orthopteran scindoambidensovirus 1} \citep{penzes2020reorganizing}.

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Bacteria.pdf}
        \caption{Heatmaps for bacterial species abundance distribution in all samples. 
        The relative abundance takes reads assigned to bacterial species as background. 
        Species with relative abundance smaller than 1\% in all samples are collapsed as "others".}
        \label{BacteriaHeatmap}
        \end{figure}

    \subsection{Characterization of functional profiling}
    In order to illustrate metabolic potentially of metagenomic samples, KEGG pathways were inferred using a parsimony approach. 
    Reads assigned to plant and arthropod species were not involved in pathway inference. 
    The coverage of a pathway was calculated by the ratio between number of annotated KOs and total number of KOs involved in that pathway. 
    \newline
    Here concern is given to metabolism pathways of carbonhydrates and amino acids, which are crucial for bee health. 
    Inferred pathways indicate potential capability of metabolism of sugars including fructose, sucrose, mannose and galactose (Figure \ref{Carbohydrate}), and all essential amino acids for honey bees (Figure \ref{AminoAcid})\citep{groot1953protein}.

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\textwidth]{../Figures/PathwayCov_AminoAcid.pdf}
        \caption{Heatmaps for pathways of amino acid metabolism.}
        \label{AminoAcid}
        \end{figure}

    \subsection{Minimal sequencing depth required for detection of species and function diversity}
    In order to estimate minimal sequencing depth for combinations of sample type (honey bee, bumble bee and flower eDNA) and study type (species profiling and function profiling), shallow sequencing was simulated by rarefaction. 
    The relationship between sequencing depth (clean read pairs) and species/KO diversity (Hill numbers of order 0, 1, 2) was quantified by fitting and averaging asymptotic species accumulation models. 
    The asymptote of the model provides an estimation of total diversity and its slope reflects the increase rate of diversity. 
    Minimal sequencing depth was estimated by the point at wich the slope of the rarefaction curve drops to a cut-off value.
    \newline
    Rarefaction assumes that the original dataset provides an almost complete inventory, which can be verified by final slope of rarefaction curve for Hill number of order 0 (richness). 
    Figure \ref{RichnessAccumulation} shows rarefaction curves for species/KO richness and Table \ref{RichnessModelSlope} summarizes their final slopes. 
    For species diversity rarefaction, all bumble bee samples are sufficient, with final slopes $< 0.1$ and completeness (ratio between final richness and asymptote) $> 0.98$. 
    % Their rarefaction curves for species richness almost level off, with final slopes $< 0.1$ and completeness (ratio between final richness and asymptote) $> 98\%$. 
    As for honey bees, {Bee\_Amellifera\_hv15\_1} and \textit{Bee\_Amellifera\_wild\_1} are sufficient, while \textit{Bee\_Amellifera\_hv13\_2} is insufficient, with final slope $> 1$ and completeness $< 0.8$. 
    % As for species diversity rarefaction of honey bee samples, the final slopes of \textit{Bee\_Amellifera\_hv15\_1} and \textit{Bee\_Amellifera\_wild\_1} are smaller than 0.1 and their completeness are higher than 99\%, indicating almost all species present in them were detected. 
    % The final slope of \textit{Bee\_Amellifera\_hv13\_2} is 1.0958 and its completeness is 79.31\%, indicating insufficient sequencing. 
    For the flower eDNA sample, the final slope of species richness rarefaction curve is 10.8380 and its completeness is 1.32\%, indicating more sequencing effort is needed for species profiling. 
    As for function diversity rarefaction, the final slopes of all KO richness rarefaction curves are higher than 15, indicating no dataset can providing an almost complete inventory of KOs. 
    Thus, estimation of minimal sequencing depth was conducted for the combinations of two sample types (honey bee and bumble bee) and one study type (species profiling), based on five datasets (two honey bees and three bumble bees).
    \begin{figure}[H]
      \begin{subfigure}
        \centering
        \textbf{a}
      \end{subfigure}
      \hspace{0.32\linewidth}
      \begin{subfigure}
        \centering
        \textbf{b}
      \end{subfigure}
      \hspace{0.32\linewidth}
      \begin{subfigure}
        \centering
        \textbf{c}
      \end{subfigure}
      \newline
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_TaxonHill_0.pdf}
      \end{subfigure}
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_TaxonHill_0.pdf}
      \end{subfigure}
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_TaxonHill_0.pdf}
      \end{subfigure}
      \newline
      \begin{subfigure}
        \centering
        \textbf{d}
      \end{subfigure}
      \hspace{0.32\linewidth}
      \begin{subfigure}
        \centering
        \textbf{e}
      \end{subfigure}
      \hspace{0.32\linewidth}
      \begin{subfigure}
        \centering
        \textbf{f}
      \end{subfigure}
      \newline
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_FunctionHill_0.pdf}
      \end{subfigure}
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_FunctionHill_0.pdf}
      \end{subfigure}
      \hfill
      \begin{subfigure}
        \centering
        \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_FunctionHill_0.pdf}
      \end{subfigure}
      \caption{Rarefaction curves for species (a, b, c) or KO (d, e, f) richness (Hill number of order 0). 
      The horizonal axis represents sequencing depth, and the vertical axis represents richness. 
      Sample type is shown in the top left of each subfigure. 
      Note that the scale of horizonal axis in subfigure c and f is much smaller than that in other subfigures.}
      \label{RichnessAccumulation}
      \end{figure}

      \begin{table}[H]
        \centering
        \caption{Summary of final point of rarefaction curve for species/KO richness (Hill number of order 0). 
      Type: indicates whether this row reports rarefaction curve for species or KO richness. 
      Depth: sequencing depth taking million read pairs as unit. 
      OR: observed species/KO richness. 
      ER: expected species/KO richness predicted by modeling rarefaction curve. 
      FS: final slope of rarefaction curve. 
      Asym: asymptote calculated by modeling rarefaction curve. 
      Comp: completeness, represented by ratio between ER and Asym.}
      \label{RichnessModelSlope}
      \resizebox{\textwidth}{!}{%
      \begin{tabular}{cccccccc} %ccccccc
      \toprule
Sample                           &Type   &Depth &OR  & ER          & FS      & Asym    & Comp \\ \midrule
\textit{Bee\_Amellifera\_hv13\_2}&species&35.28 &144 & 146.69      & 1.0958  & 184.94  & 0.7931 \\
\textit{Bee\_Amellifera\_hv15\_1}&species&45.05 &97  & 88.53       & 0.0344  & 88.84   & 0.9966 \\
\textit{Bee\_Amellifera\_wild\_1}&species&44.46 &179 & 175.89      & 0.0991  & 176.84  & 0.9946 \\
\textit{Bee\_Bimpatiens\_hv3\_1} &species&53.61 &96  & 89.00       & 0.0897  & 90.79   & 0.9803 \\
\textit{Bee\_Bimpatiens\_hv4\_1} &species&48.42 &63  & 62.06       & 0.0626  & 62.92   & 0.9862 \\
\textit{Bee\_Bimpatiens\_hv4\_2} &species&45.80 &87  & 85.59       & 0.0146  & 85.69   & 0.9988 \\
\textit{Flower\_eDNA}            &species&0.88  &43  & 40.04       & 10.8380 & 3034.88 & 0.0132 \\
\textit{Bee\_Amellifera\_hv13\_2}&KO     &35.28 &9289& 9284.45     & 38.6844 & 10641.27& 0.8725 \\
\textit{Bee\_Amellifera\_hv15\_1}&KO     &45.05 &9046& 9102.78     & 43.8717 & 10453.98& 0.8707 \\
\textit{Bee\_Amellifera\_wild\_1}&KO     &44.46 &7216& 7151.72     & 21.4368 & 14779.89& 0.4839 \\
\textit{Bee\_Bimpatiens\_hv3\_1} &KO     &53.61 &6872& 6769.80     & 21.1588 & 28111.79& 0.2408 \\
\textit{Bee\_Bimpatiens\_hv4\_1} &KO     &48.42 &5427& 5410.71     & 19.6932 & 7665.58 & 0.7058 \\
\textit{Bee\_Bimpatiens\_hv4\_2} &KO     &45.8  &7288& 7259.56     & 15.6309 & 7873.64 & 0.9220 \\
\textit{Flower\_eDNA}            &KO     &0.88  &3732& 3544.54     & 60.4367 & 3571.11 & 0.9926 \\
      \bottomrule
      \end{tabular}%
      }
      \end{table}

    % \begin{figure}[H]
    %   \begin{subfigure}
    %     \centering
    %     \textbf{a}
    %   \end{subfigure}
    %   \hspace{0.32\linewidth}
    %   \begin{subfigure}
    %     \centering
    %     \textbf{b}
    %   \end{subfigure}
    %   \hspace{0.32\linewidth}
    %   \begin{subfigure}
    %     \centering
    %     \textbf{c}
    %   \end{subfigure}
    %   \newline
    %   \hfill
    %   \begin{subfigure}
    %     \centering
    %     \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_TaxonHill_0.pdf}
    %   \end{subfigure}
    %   \hfill
    %   \begin{subfigure}
    %     \centering
    %     \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_TaxonHill_0.pdf}
    %   \end{subfigure}
    %   \hfill
    %   \begin{subfigure}
    %     \centering
    %     \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_TaxonHill_0.pdf}
    %   \end{subfigure}
      % \newline
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \textbf{d}
      % \end{subfigure}
      % \hspace{0.32\linewidth}
      % \begin{subfigure}
      %   \centering
      %   \textbf{e}
      % \end{subfigure}
      % \hspace{0.32\linewidth}
      % \begin{subfigure}
      %   \centering
      %   \textbf{f}
      % \end{subfigure}
      % \newline
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_TaxonHill_1.pdf}
      % \end{subfigure}
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_TaxonHill_1.pdf}
      % \end{subfigure}
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_TaxonHill_1.pdf}
      % \end{subfigure}
      % \newline
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \textbf{g}
      % \end{subfigure}
      % \hspace{0.32\linewidth}
      % \begin{subfigure}
      %   \centering
      %   \textbf{h}
      % \end{subfigure}
      % \hspace{0.32\linewidth}
      % \begin{subfigure}
      %   \centering
      %   \textbf{i}
      % \end{subfigure}
      % \newline
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_TaxonHill_2.pdf}
      % \end{subfigure}
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_TaxonHill_2.pdf}
      % \end{subfigure}
      % \hfill
      % \begin{subfigure}
      %   \centering
      %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_TaxonHill_2.pdf}
      % \end{subfigure}
      % \caption{Rarefaction curves for species richness (Hill number of order 0). 
      % The horizonal axis represents sequencing depth, and the vertical axis represents species richness. 
      % Sample type is shown in the top left of each subfigure.}
      % \label{SpeciesAccumulation}
      % \end{figure}

%     \begin{table}[H]
%       \centering
%       \caption{Summary of final point of rarefaction curve for species richness (Hill number of order 0). 
%       Depth: sequencing depth taking million read pairs as unit. 
%       OR: observed species richness. 
%       ER: expected species richness predicted by modeling rarefaction curve. 
%       FS: final slope of rarefaction curve. 
%       Asym: asymptote calculated by modeling rarefaction curve. 
%       Comp: completeness, represented by ratio between ER and Asym.}
%       \label{SpeciesRichnessModel}
%       \resizebox{\textwidth}{!}{%
%       \begin{tabular}{ccccccc} %ccccccc
%       \toprule
% Sample                   & Depth   & OR  & ER          & FS      & Asym    & Comp \\ \midrule
% \textit{Bee\_Amellifera\_hv13\_2} & 35.28   & 144 & 146.69      & 1.0958  & 184.94  & 0.7931 \\
% \textit{Bee\_Amellifera\_hv15\_1} & 45.05   & 97  & 88.53       & 0.0344  & 88.84   & 0.9966 \\
% \textit{Bee\_Amellifera\_wild\_1} & 44.46   & 179 & 175.89      & 0.0991  & 176.84  & 0.9946 \\
% \textit{Bee\_Bimpatiens\_hv3\_1}  & 53.61   & 96  & 89.00       & 0.0897  & 90.79   & 0.9803 \\
% \textit{Bee\_Bimpatiens\_hv4\_1}  & 48.42   & 63  & 62.06       & 0.0626  & 62.92   & 0.9862 \\
% \textit{Bee\_Bimpatiens\_hv4\_2}  & 45.80   & 87  & 85.59       & 0.0146  & 85.69   & 0.9988 \\
% \textit{Flower\_eDNA}             & 0.88    & 43  & 40.04       & 10.8380 & 3034.88 & 0.0132 \\
%       \bottomrule
%       \end{tabular}
%       }
%       \end{table}

      % \begin{figure}[H]
        % \begin{subfigure}
        %   \centering
        %   \textbf{a}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{b}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{c}
        % \end{subfigure}
        % \newline
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_FunctionHill_0.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_FunctionHill_0.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_FunctionHill_0.pdf}
        % \end{subfigure}
        % \newline
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \textbf{d}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{e}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{f}
        % \end{subfigure}
        % \newline
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_FunctionHill_1.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_FunctionHill_1.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_FunctionHill_1.pdf}
        % \end{subfigure}
        % \newline
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \textbf{g}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{h}
        % \end{subfigure}
        % \hspace{0.32\linewidth}
        % \begin{subfigure}
        %   \centering
        %   \textbf{i}
        % \end{subfigure}
        % \newline
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Honey_FunctionHill_2.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Bumble_FunctionHill_2.pdf}
        % \end{subfigure}
        % \hfill
        % \begin{subfigure}
        %   \centering
        %   \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Flower_FunctionHill_2.pdf}
        % \end{subfigure}
        % \caption{Rarefaction curves for KO richness (Hill number of order 0). 
        % The horizonal axis represents sequencing depth, and the vertical axis represents KO richness. 
        % Sample type is shown in the top left of each subfigure.}
        % \label{FunctionAccumulation}
        % \end{figure}

%       \begin{table}[H]
%         \centering
%         \caption{Summary of final point of rarefaction curve for KO richness (Hill number of order 0). 
%         Depth: sequencing depth taking million read pairs as unit. 
%         OR: observed KO richness. 
%         ER: expected KO richness predicted by modeling rarefaction curve. 
%         FS: final slope of rarefaction curve. 
%         Asym: asymptote calculated by modeling rarefaction curve. 
%         Comp: completeness, represented by ratio between ER and Asym.}
%         \label{FunctionRichnessModel}
%         \resizebox{\textwidth}{!}{%
%         \begin{tabular}{ccccccc}
%         \toprule
% Sample                           &Depth  & OR    & ER        & FS       & Asym    & Comp   \\ \midrule
% \textit{Flower\_eDNA}            &0.88   & 3732  & 3544.54   & 60.4367  & 3571.11 & 0.9926 \\
% \textit{Bee\_Bimpatiens\_hv3\_1} &53.61  & 6872  & 6769.80   & 21.1588  & 28111.79& 0.2408 \\
% \textit{Bee\_Bimpatiens\_hv4\_1} &48.42  & 5427  & 5410.71   & 19.6932  & 7665.58 & 0.7058 \\
% \textit{Bee\_Bimpatiens\_hv4\_2} &45.8   & 7288  & 7259.56   & 15.6309  & 7873.64 & 0.9220 \\
% % \textit{Bee\_Amellifera\_hv13\_1}&0.84   & 3341  & 3322.97   & 909.4389 & 6975.56 & 0.4764 \\
% \textit{Bee\_Amellifera\_hv13\_2}&35.28  & 9289  & 9284.45   & 38.6844  & 10641.27& 0.8725 \\
% \textit{Bee\_Amellifera\_hv15\_1}&45.05  & 9046  & 9102.78   & 43.8717  & 10453.98& 0.8707 \\
% \textit{Bee\_Amellifera\_wild\_1}&44.46  & 7216  & 7151.72   & 21.4368  & 14779.89& 0.4839 \\
%         \bottomrule
%         \end{tabular}%
%         }
%         \end{table}

    Minimal sequencing depth is estimated by the point at which the slope of rarefaction curve drops to a cut-off value. 
    Table \ref{MinDepth} summarizes estimations of minimal sequencing depth for detection of species diversity, using 0.5, 0.1, 0.05 and 0.01 as cut-off values.  
    When order $q$ of Hill number equals 0, \textit{i.e.} species abundances are not considered, cut-off value of 0.1 for slope of rarefaction curve is sufficient for providing completeness $> 97\%$ in all samples. 
    The average minimal sequencing depth are 40.33 million for honey bees and 42.49 million for bumble bees. 
    When species abundances are considered (order $q$ equals 1 or 2), cut-off value of 0.01 can provide completeness $> 95\%$ in most pairs of sample and $q$ value. 
    For honey bees, the average minimal sequencing depth are 18.57 million ($q = 1$) and 17.45 million ($q = 2$). 
    For bumble bee samples, the average minimal sequencing depth are 40.33 million ($q = 1$) and 24.77 million ($q = 2$). 
      \begin{table}[H]
        \centering
        \caption{Summary of minimal sequencing depth estimated from different cut-off values of slope. 
        Minimal sequencing depth was estimated by the point at which the slope of rarefaction curve drops to a cut-off value (0.5, 0.1, 0.05 or 0.01), which is indicated in names of columns. 
        For example, MinD\_0.5 represents estimated minimal sequencing depth taking 0.5 as cut-off value, and ED\_0.5 is expected Hill number from MinD\_0.5. Comp\_0.5 is the ratio between OptDiv\_0.5 and the asymptote (represented by Asym). 
        Unit of sequencing depth is million read pairs. 
        $q$ refers to order of Hill number determining sensitivity to species abundance distribution.}
        \label{MinDepth}
        \resizebox{\textwidth}{!}{%
        \begin{tabular}{ccccccccccccccc} % lllllllllllllll
        \toprule
Sample&$q$&Asym  &MinD\_0.5&ED\_0.5&Comp\_0.5  &MinD\_0.1&ED\_0.1&Comp\_0.1  &MinD\_0.05&ED\_0.05&Comp\_0.05  &MinD\_0.01&ED\_0.01&Comp\_0.01 \\ \midrule
% \textit{Bee\_Amellifera\_hv13\_1}&0&4262.21 &1373.18&4022.37&0.9437 &2142.41&4213.53&0.9886 &2473.90&4237.44&0.9942 &3244.93&4256.60&0.9987\\
% \textit{Bee\_Amellifera\_hv13\_2}&0&184.94  &59.87&165.10&0.8927  &120.88&179.94&0.9730  &149.83&182.02&0.9842&226.97&183.88&0.9942\\
\textit{Bee\_Amellifera\_hv15\_1}&0&88.84  &23.54&84.85 &0.9551  &36.27&87.99 &0.9905  &41.95&88.40 &0.9951  &55.75&88.74 &0.9989\\
\textit{Bee\_Amellifera\_wild\_1}&0&176.84 &30.53&172.46&0.9752  &44.39&175.88&0.9946  &50.57&176.33&0.9971  &65.86&176.70&0.9992\\

% \textit{Bee\_Amellifera\_hv13\_1}&1&7.06  &0.06&6.56&0.9296  &0.63&6.66&0.9434  &1.30&6.71&0.9501  &3.41&6.76&0.9571\\
% \textit{Bee\_Amellifera\_hv13\_2}&1&16.01 &5.55&15.03&0.9385 &8.70&15.81&0.9872 &10.08&15.91&0.9934  &13.34&15.99&0.9984\\
\textit{Bee\_Amellifera\_hv15\_1}&1&12.28  &3.18 &10.67 &0.8699  &5.83 &11.33 &0.9224  &7.21 &11.43 &0.9304  &15.21&11.58 &0.9429\\
\textit{Bee\_Amellifera\_wild\_1}&1&14.77  &0.69 &13.49 &0.9137  &3.30 &14.03 &0.9498  &6.20 &14.23 &0.9635  &21.93&14.58 &0.9868\\

% \textit{Bee\_Amellifera\_hv13\_1}&2&4.85   &0.02 &4.26  &0.8789  &0.20 &4.29 &0.8848  &0.94&4.34 &0.8950  &4.27 &4.42 &0.9115\\
% \textit{Bee\_Amellifera\_hv13\_2}&2&11.00  &4.47 &10.15 &0.9232  &7.20 &10.83&0.9845  &8.38&10.91&0.9922  &11.14&10.98&0.9984\\
\textit{Bee\_Amellifera\_hv15\_1}&2&8.40   &3.10 &6.35  &0.7561  &8.17 &7.49  &0.8909  &11.97&7.75  &0.9229  &27.99&8.11 &0.9655\\
\textit{Bee\_Amellifera\_wild\_1}&2&9.88   &0.18 &9.49  &0.9602  &0.90 &9.63  &0.9747  &1.73 &9.69  &0.9805  &6.91 &9.80  &0.9916\\

\textit{Bee\_Bimpatiens\_hv3\_1}&0&90.79  &30.80&83.69&0.9218  &52.03&88.85&0.9786  &62.56&89.61&0.9870  &92.35&90.32&0.9948\\
\textit{Bee\_Bimpatiens\_hv4\_1}&0&62.92  &24.83&57.22&0.9093  &42.76&61.61&0.9791  &51.24&62.22&0.9887  &73.55&62.76&0.9973\\
\textit{Bee\_Bimpatiens\_hv4\_2}&0&85.69  &21.75&82.30&0.9604  &32.67&85.01&0.9920  &37.39&85.35&0.9960  &48.40&85.62&0.9992\\

\textit{Bee\_Bimpatiens\_hv3\_1}&1&21.59  &3.63 &10.50&0.4862  &9.47 &11.76&0.5449  &15.37&12.18&0.5639  &58.09&13.04&0.6040\\
\textit{Bee\_Bimpatiens\_hv4\_1}&1&11.85  &3.80 &9.45 &0.7973  &10.15&10.87&0.9174  &14.68&11.19&0.9445  &31.22&11.57&0.9766\\
\textit{Bee\_Bimpatiens\_hv4\_2}&1&12.66  &4.17 &10.24&0.8087  &10.47&11.67&0.9213  &14.85&11.98&0.9458  &31.68&12.36&0.9760\\

\textit{Bee\_Bimpatiens\_hv3\_1}&2&8.73   &2.20 &6.16 &0.7051  &6.28 &7.06 &0.8088  &9.45 &7.28 &0.8344  &23.89&7.60 &0.8708\\
\textit{Bee\_Bimpatiens\_hv4\_1}&2&8.33   &3.12 &6.28 &0.7540  &8.52 &7.50 &0.9002  &12.30&7.76 &0.9323  &26.68&8.09 &0.9718\\
\textit{Bee\_Bimpatiens\_hv4\_2}&2&7.12   &2.90 &5.34 &0.7493  &7.47 &6.38 &0.8961  &10.58&6.60 &0.9270  &23.73&6.90 &0.9683\\

% \textit{Flower\_eDNA}&0&3034.88 &922.36&2870.43&0.9458  &1428.16&2996.00&0.9872  &1648.07&3011.86&0.9924  &2173.39&3024.82& 0.9967\\
% \textit{Flower\_eDNA}&1&6.46    &0.74  &5.59   &0.8656  &2.89   &6.07   &0.9399  &4.50   &6.19   &0.9575  &11.30  &6.34   & 0.9810\\
% \textit{Flower\_eDNA}&2&4.40    &0.55  &3.50   &0.7940  &2.47   &3.92   &0.8910  &3.93   &4.03   &0.9145  &10.24  &4.17   & 0.9463\\
        \bottomrule
        \end{tabular}%
        }
        \end{table}

\section{Discussion}
Shotgun metagenomics provides powerful tools for microbiome investigations, yet its utilization is hindered by bioinformatical challenges and high cost of deep sequencing. 
Here, I constructed an integrated pipeline, which combines assembly-dependent and -independent profiling methods to help detect species richness and profiled real metagenomic datasets from honey bees, bumble bees and flower surface.  
Then I simulated the relationship between species/KO diversity measured by Hill numbers (order $q = 0, 1, 2$) and sequencing depth measured by clean read pair ($2 \times 150$ bp) number. 
It is showed that to detect species diversity, the average minimal sequencing depth for honey bee samples are 40.33 million ($q = 0$), 18.57 million ($q = 1$) and 17.45 million ($q = 2$); for bumble bee samples, the averages are 42.49 million ($q = 0$), 40.33 million ($q = 1$) and 24.77 million ($q = 2$); and for flower surface, more than 0.88 million sequencing depth is needed. 
As for function diversity, no datasets in this project is sufficient for providing an almost complete inventory of KOs, indicating deeper sequencing is needed, \textit{i.e.} sequencing depth need to be higher than 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface. 
Additionally, bee symbionts and pathogens were found on the flower eDNA sample, and pathway inference indicates that bee-associated microbiome may have capability of metabolizing amino acids that are essential for host.
\newline
% High throughput sequencing provides approaches including amplicon sequencing and shotgun metagenomics for investigations of bee-associated microbiome, which imposes significant impact on bee health \citep{engel2016bee,raymann2018role,bonilla2018functional}. 
% a crucial issue receiving increasing concern \citep{breeze2011pollination,hristov2020significance}. 
Shotgun metagenomics provides unique advantages over amplicon sequencing, which is vastly used in bee microbiome investigations (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}). 
In amplicon sequencing, a species-specific barcode region is amplified and sequenced \citep{abdelfattah2018metabarcoding}. 
Since it captures a small region of the whole genome, amplicon sequencing dataset is relatively small in size, which makes it low-cost both economically and computationally. 
Besides, comprehensive and streamlined softwares for amplicon sequencing analysis are available, including QIIME \citep{bolyen2019reproducible}, Mothur \citep{schloss2020reintroducing} and VSEARCH \citep{rognes2016vsearch}. 
However, a single amplicon sequencing dataset does not represent all taxa in the community since different barcode region is used for identification of different taxonomic group, \textit{e.g.} 
16S ribosomal RNA (rRNA) for bacteria \citep{hayashi2002phylogenetic,eckburg2005diversity}, 
internal transcribed spacer (ITS) for fungi \citep{nilsson2008intraspecific}, 
cytochrome c oxidase subunit I (COI) for Animalia \citep{hebert2003barcoding} 
and plastid genes for plants \citep{group2009dna}. 
Besides, it does not provide information on FGCs. 
Metabolic capacity of microbiome need to be inferred based on reference genomes \Citep{asshauer2015tax4fun,douglas2018predicting}. 
Shotgun metagenomics provides an alternative to overcome these drawbacks by capturing and sequencing DNA in a sample unselectively. 
It is capable of representing all taxonomic groups and providing information on FGC composition. 
\newline
The advantages of shotgun metagenomics over amplicon sequencing are valuable for investigations in bee-associated microbiome for two reasons. 
First, bees vist numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including plants, arthropods, bacteria and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}. 
These materials represent a diverse assemblage which is difficult to be profiled comprehensively via amplicon sequencing. 
Besides, bee bacterial symbionts are diversified at strain level \citep{engel2012functional,powell2016strain,ellegaard2020vast}. 
Bacterial strains are often highly variable in gene content \citep{cordero2014explaining,brockhurst2019ecology}, and thus different in metabolic capacity. 
However, resolving strain-level diversity by species-specific region is difficult \citep{rodriguez2018much,ciufo2018using,olm2020consistent}, and no information on gene content is provided by amplicon sequencing. 
Based on these considerations, shotgun metagenomics provides valuable tools for bee microbiome investigations. 
However, utilization of shotgun metagenomics is hindered by unique challenges. 
First, there is not a golden standard for bioinformatics of metagenomic annotation pipeline to provide abundances of taxa and FGCs. 
Second, shotgun metagenomics is often associated with high cost since it captures a big proportion of microbial genomes. 
\newline
The integrated pipeline for taxonomic and functional profiling of metagenomic dataset provides several advantages. 
First, through combination with assembly-free taxon search, it helps solve high false negative rate associated with assembly-dependent species identification, which is caused by reads left unassembled. 
This was shown by analyzing real metagenomic datasets from pollination system and simulating different sequencing depth by rarefaction (Figure \ref{CompareSensitivity}). 
Second, the modularity of integrated pipeline provides flexibility for incorporation of alternative tools. 
For example, BWA aligner \citep{li2009fast} serves as an alternative for Bowtie2, and SPAdes can be replaced by other metagenomic assemblers such as Megahit \citep{li2015megahit} and IDBA-UD \citep{peng2012idba}. 
Third, the output files generated by each step are recorded and can be inspected easily, which is important for troubleshooting. 
\newline
Determination of sequencing depth is important for shotgun metagenomics since insufficient sequencing causes underestimation of taxonomic/functional diversity \citep{cattonaro2018you,zaheer2018impact,gweon2019impact,pereira2019impact}, while deep sequencing is of high cost. 
Here, expected species/KO diversity provided by given sequencing depth was estimated by rarefaction and model fitting, using datasets from honey bees, bumble bees and flower surface. 
It was shown that increasing sequencing depth boosted identification of species/KO (Figure \ref{RichnessAccumulation}, Table \ref{RichnessModelSlope}), highlighting value of deep metagenomic sequencing. 
For function profiling, no dataset involved here is big enough to provide an almost complete inventory of KOs (Table \ref{RichnessModelSlope}) even though most samples were deeply sequenced (Table \ref{QC}), indicating such task is demanding about sequencing depth. 
Therefore, when dealing with function potentiality of microbiome associated with bees or flowers, retrieving as many reads as possible would be recommended. 
As for species profiling, although deep sequencing is still valuable, optimization of sequencing depth can be made when the budget is limited (Table \ref{MinDepth}). 
For honey bees, approximate 40 million sequencing depth can be sufficient for representing species richness. 
When assessing biodiversity by Hill numbers of order 1 (Equation \ref{HillShannon}) or 2 (Equation \ref{HillSimpson}), 17-19 million sequencing depth can provide robust estimation. 
As for bumble bees, about 40-43 million sequencing depth can provide reliable estimation for Hill numbers of order 0 (richness) or 1, and about 25 million sequencing depth can be sufficient for representing biodiversity measured by Hill number of order 2.  
\newline
Additionally, the results of metagenomic profiling indicate overlap between microbiome of bees and flowers, and provide evidence on potentiality of bee microbiome in metabolism of carbonhydrates and amino acids.
In the flower eDNA sample, bee-associated microorganisms were identified, including both pathogens (\textit{e.g.} \textit{Nosema ceranae} and \textit{Apis mellifera filamentous virus}) and typical bee symbionts (\textit{e.g.} \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}) (Figure \ref{BacteriaHeatmap}, \ref{FungusHeatmap} and \ref{ViruseHeatmap}). 
Shared microbiome between bees and flowers is revealed by growing evidence, although its role in pollination system remains an open question \citep{keller2020more,vannette2020floral}. 
As for function profiling, it is indicated that bee-associated microbiome is capable of metabolizing carbohydrates such as glucose, fructose, sucrose and mannose (Figure \ref{Carbohydrate}). 
Carbohydrates are main component of bee diet and microbiome-mediated carbohydrate-processing have been vastly investigated \citep{engel2012functional,lee2015saccharide,lee2018differential,taylor2019effect}. 
Besides, pathways for metabolism of all ten essential amino acids for honey bees (arginine, histidine, isoleucine, leucine, lysine, methionine, phenylalanine, threonine, tryptophan and valine) \citep{groot1953protein} were inferred (Figure \ref{AminoAcid}). 
Essential amino acids are crucial for bee health \citep{simcock2014single,paoli2014dietary,stabler2015nutrient,hendriksma2019effects} and influence feeding preference due to their potential deficiency in single pollen source \citep{cook2003honey,hendriksma2014amino,hendriksma2016honey}. 
Whether bee-associated microbiome influences host health by providing amino acids need to be further investigated. 
% deficiency of arginine in dandelion \citep{herbert1970brood} and histidine in corn \citep{hocherl2012evaluation}.
\newline
There are several limitations of this project. 
First, the integrated pipeline need to be evaluated more comprehensively. 
Mock metagenomic datasets of different diversity can be used to evaluate sensitivity and accuracy of integrated pipeline and its performance need to be compared with other profiling methods. 
Second, the efficacy of estimation of minimal sequencing depth required for different environmental types is reduced by limited number of samples. 
Here, honey bee and bumble bee associated microbiome was represented by only three samples, and there was only one sample of flower eDNA. 
However, microbiomes of pollination system are highly dynamic and variable in diversity. 
To generate reliable guideline for sufficient sequencing depth, more samples need to be evolved. 
Third, there is a lack of repeat in sequencing depth subsampling. 
Repeated subsampling boosts precise computation of rarefaction curve and increases accuracy of estimation of minimal sequencing depth. 
\newline
Oerall, I constructed an integrated pipeline, combining assembly-dependent and -free methods for metagenomic profiling. 
The pipeline was used for profiling metagenomic datasets ($2 \times 150 bp$ read pairs) from pollination system. 
Then I conducted rarefaction analysis, computing expected species/KO diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to determine minimal sequencing depth capable of reliably estimating diversity. 
It was shown that functional profiling is demanding about sequencing effort. 
Sequencing depth of 45.06 million (13.52 Gbp) for honey bees, 53.61 million (16.08 Gbp) for bumble bees and 0.88 million (0.26 Gbp) for flower surface were not sufficient for providing almost complete inventories of KOs. 
For species diversity of order 0, 1 and 2, the average minimal sequencing depth for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million. 
As for species profiling of flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
These results are helpful for applying shotgun metagenomics to pollination system investigations in an cost-effective way. 
The integrated pipeline and the framework for rarefaction analysis can be used for researches on other environments.

% bee importance {gallai2009economic,gill2016protecting,ferrier2018economic,cooley2021buzz}, 
% bee decline {cappa2021analysis,frizzera2021interaction,hemberger2021historical}

\section{Data and Code Availability}

% \appendix
% \appendixpage
% \addappheadtotoc
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }
\section{Supplementary}
  \beginsupplement
  \subsection{Parameter settings of integrated pipeline}
  \label{ParameterSetting}
    \subsubsection{Quality control and host removing}
    \label{HostRemove}
    Quality control was conducted to reduce compromise from low quality reads.
    Data quality was checked using FastQC v.0.11.5 \citep{andrews2010fastqc} before filtering. 
    FastQC reports of raw reads showed the following aspects need to be covered in quality control: (1) low base quality in 3'-end (Figure \ref{QC}a); (2) uneven base content in 5'-end (Figure \ref{QC}c) and (3) the present of Nextera adaptors (Figure \ref{QC}e). 
    Therefore, quality control was conducted using Trimmomatic v.0.39 \citep{bolger2014trimmomatic}, which (1) trimmed adaptors; (2) cutted 15 bases from the 5'-ends of reads; (3) cutted bases off from 3'-ends of reads if Phred-33 quality is below 20; (4) dropped reads shorter than 50 bp; (5) dropped reads if average Phred-33 quality is below 20. 
    Then unpaired reads were removed and quality of clean data was checked using FastQC (Figure \ref{QC}d, \ref{QC}e, \ref{QC}f).
    \newline  
    After quality control, host read pairs were removed. 
    First, clean read pairs were mapped to host genome (GCA\_003254395.2 for \textit{Apis mellifera} and GCA\_000188095 for \textit{Bombus impatiens}, downloaded from NCBI) using Bowtie2 v.2.4.2 \citep{langmead2012fast} with flags \textit{--end-to-end} and \textit{--sensitive}. 
    With flag \textit{--end-to-end}, Bowtie2 requires the read aligned without any clipping from neither end, and \textit{--sensitive} maintains a trade-off between speed and sensitivity. 
    SAM files generated by Bowtie2 were converted to BAM format using SAMtools v.1.11 \citep{li2009sequence}. 
    Then non-host read pairs were extracted from BAM files by SAMtools according to the present of SAM flag 12 (neither forward nor reverse read in a pair of reads is mapped).

    \subsubsection{Assembly-dependent species identification}
    \label{AssemblyDependent}
    In order to identify taxa of metagenome, \textit{de novo} assembly was conducted. 
    Non-host read pairs were assembled using SPAdes v.3.15.2 \citep{prjibelski2020using}. 
    Values of k-mer ranged from 21 to 101 at interval of 10. 
    Flags \textit{--only-assembler} and \textit{--meta} were used. 
    Through flag \textit{--meta}, SPAdes runs metaSPAdes which is developed for metagenomic assembly \citep{nurk2017metaspades}. 
    The \textit{--only-assembler} flag skips read error correction and runs assembly only. 
    Its utilization is justified by the following facts. 
    First, when \textit{--only-assembler} is not used, SPAdes conducts error correction before assembly. 
    It is conducted by BayesHamme, which is optimized for single cell sequencing instead of shotgun metagenomics \citep{nikolenko2013bayeshammer}. 
    Besides, reads used for \textit{de novo} assembly had been filtered to ensure their quality.
    \newline
    After assembly, taxon identification was conducted using DIAMOND v.2.0.7.145 \citep{buchfink2015fast} and MEGAN6 \citep{huson2007megan}. 
    Assembled contigs with a length above 500 bp were aligned to nr database using DIAMOND v.2.0.7.145 with \textit{--long-reads} flag. 
    This flag triggers frame-shift aware alignment mode, which is optimized for long sequence alignment. 
    Therefore, short contigs (length $<$ 500 bp) were not retained. 
    Besides, alignments with an E-value $< 1e-5$ or identity $< 50\%$ were removed, and for each contig, only alignments above 10\% of the best local bit score were retained. 
    The output of DIAMOND was analysized by the \textit{blast2rma} tool of MEGAN6 with \textit{-lg} flag, which runs lowest-common-ancestor (LCA)-based algorithm developed for long contigs and assigns each contig to a taxon \citep{huson2018megan}. 
    The parameter \textit{-supp} was 0, which means the present of a taxon would be identified as long as at least one contig was assigned. 
    This value was used because a contig is assembled from multiple short reads and represents a strong signal for the present of a taxon.

    \subsubsection{Fragment recruitment}
    To integrate individual genomic data of species identified by assembly-dependent search, a reference database comprising reference genome dataset, \textit{i.e.} genomic sequences in FASTA format and corresponding gff file, was constructed. 
    For each species represented by assembly, its reference genome dataset, if available, was downloaded from NCBI using its \textit{datasets} command-line tool and added to the reference database. 
    \newline
    Then fragment recruitment was conducted. 
    The non-host read pairs were mapped to genomic sequences in the reference database using Bowtie2. 
    Read pairs that were not recruited were extracted using SAMtools. 
    Settings for Bowtie2 and SAMtools were the same as that described in \ref{HostRemove}. 
    Read pairs recruited by the reference database were assigned to corresponding species, while the others were subjected to assembly-independent search.

    \subsubsection{Assembly-independent species identification}
    In order to detect species not represented by assembly \citep{sharon2015accurate,vollmers2017comparing}, assembly-independent search was conducted, taking read pairs not recruited by the reference database as input. 
    These reads were aligned to nr database through DIAMOND without using \textit{--long-reads} flag, which triggers computing alignments for short metagenomic reads. 
    Other settings were the same as described in \ref{AssemblyDependent}. 
    Then the output of DIAMOND was analysed by MEGAN6 (\textit{blast2rma} tool), which assigns read pairs to taxa through LCA algorithm. 
    Here the parameter \textit{-supp} was 0.1, which means a taxon is reported after being represented by at least 0.1\% of all assigned read pairs. 
    It was used in order to avoid false positive results.

    \subsubsection{Functional annotation}
    Functional annotation was conducted by EggNOG-mapper v.2.1.2 \citep{huerta2017fast}. 
    Sequences were searched against eggNOG database \citep{huerta2019eggnog} for best seed orthologs using DIAMOND and fine-grained orthology assignments were retrieved from pre-computed eggNOG phylogenetic trees. 
    Then functional descriptions of retrieved orthologs including Gene Ontology (GO) terms \citep{gene2004gene}, KOs, Enzyme Commission (EC) numbers \cite{webb1992enzyme}, Carbohydrate-Active Enzymes (CAZy) terms \cite{cantarel2009carbohydrate} and Clusters of Orthologous Groups (COG) functional categories \cite{tatusov2000cog} were transferred to query sequences.

  \subsection{Candidate models for fitting rarefaction curves}
  \begin{table}[H]
    \centering
    \caption{Candidate species accumulation models. 
    Dependent variable $D^{(q)}$ is Hill number of order $q$ and 
    independent variable $x$ is sequencing depth. 
    $a$, $b$, $c$, $d$ are fitted coefficients.}
    \label{candidate_models}
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{lllllll}
    \toprule
    Model & Parameter($k$) & Derivative & Asymptote & Reference \\ \midrule
    $D^{(q)} = \frac{ax}{bx+1}$ & 2 & $\frac{dD^{q}}{dx} = \frac{a}{(bx+1)^2}$ & $\frac{a}{b}$ & \cite{clench1979make}  \\
    $D^{(q)} = a(1-e^{-bx})$ & 2 & $\frac{dD^{q}}{dx} = abe^{-bx}$ & $a$ & \cite{miller1989documenting}  \\
    $D^{(q)} = a-bc^x$ & 3 & $\frac{dD^{q}}{dx} = -bc^{x}log(c)$ & $a$ & \cite{ratkowsky1983nonlinear}  \\
    $D^{(q)} = a(1-e^{-bx})^c$ & 3 & $\frac{dD^{q}}{dx} = abce^{-bx}(1-e^{-bx})^{c-1}$ & $a$ & \cite{ratkowsky1990handbook}  \\
    $D^{(q)} = a(1-(1+(\frac{x}{c})^d)^{-b})$ & 4 & $\frac{dD^{q}}{dx} = \frac{abd}{c}(\frac{x}{c})^{d-1}(1+(\frac{x}{c})^d)^{-b-1}$ & $a$ & \cite{mielke1974some}\\
    \bottomrule
    \end{tabular}
    }
    \end{table}

  \subsection{Exemplification of effect of quality control}
  \begin{figure}[H]
    \begin{subfigure}
      \centering
      \textbf{a}
    \end{subfigure}
    \hspace{0.32\linewidth}
    \begin{subfigure}
      \centering
      \textbf{b}
    \end{subfigure}
    \hspace{0.32\linewidth}
    \begin{subfigure}
      \centering
      \textbf{c}
    \end{subfigure}
    \newline
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2a_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2c_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2e_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \newline
    \begin{subfigure}
      \centering
      \textbf{d}
    \end{subfigure}
    \hspace{0.32\linewidth}
    \begin{subfigure}
      \centering
      \textbf{e}
    \end{subfigure}
    \hspace{0.32\linewidth}
    \begin{subfigure}
      \centering
      \textbf{f}
    \end{subfigure}
    \newline
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2b_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2d_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}
      \centering
      \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/Figure2f_PGcomcol4a_Bimp.png}
    \end{subfigure}
    \caption{Data quality report of forward reads from bumble bee sample \textit{Bee\_Bimpatiens\_hv4\_1}. 
    a, b and c shows low base quality in 3'-end, uneven base content in 5'-end and present of Nextera adaptors in raw data, respectively. 
    d, e and f shows the same results from clean data.}
    \label{QC}
    \end{figure}

  \subsection{Numbers of raw, clean and non-host read pairs}
  \begin{table}[H]
    \centering
    \caption{Basic statistics of sequenced read pairs. 
    Data in "Clean" considers as background the numbers of raw read pairs ("Raw"), while data in "Non-host" considers as background the numbers of clean read pairs ("Clean").}
    \label{data_statistics}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{@{}ccccc@{}}
    \toprule
    Sample                           &Host                     &Raw    &Clean (\%)&Non-host (\%) \\ \midrule
    \textit{Bee\_Amellifera\_hv13\_1}&\textit{Apis mellifera}  &1104861&842095 (76.22\%)&665507 (79.03\%) \\
    \textit{Bee\_Amellifera\_hv13\_2}&\textit{Apis mellifera}  &56836899&35282101 (62.08\%)&10413704 (29.52\%) \\
    \textit{Bee\_Amellifera\_hv15\_1}&\textit{Apis mellifera}  &63159968&45059211 (71.34\%)&38837759 (86.19\%) \\
    \textit{Bee\_Amellifera\_wild\_1}&\textit{Apis mellifera}  &58113227&44466776 (76.52\%)&17014144 (38.26\%) \\
    \textit{Bee\_Bimpatiens\_hv3\_1} &\textit{Bombus impatiens}&63973750&53612702 (83.80\%)&5300592 (9.89\%) \\
    \textit{Bee\_Bimpatiens\_hv4\_1} &\textit{Bombus impatiens}&58988182&48426748 (82.10\%)&3557052 (7.35\%) \\
    \textit{Bee\_Bimpatiens\_hv4\_2}&\textit{Bombus impatiens} &54955553&45805759 (83.35\%)&4618023 (10.08\%) \\
    \textit{Flower\_eDNA}           &None                      &1443107&882436 (61.15\%)&882436 (100\%) \\
    \bottomrule
    \end{tabular}}
    \end{table}

  \subsection{Species composition of arthropods, plants, fungi and viruses}
  \begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Arthropods.pdf}
    \caption{Heatmaps for arthropod species abundance distribution in all samples. 
    The relative abundance takes reads assigned to arthropod species as background. 
    Species with relative abundance smaller than 1\% in all samples are collapsed as "others". 
    It should be noted that for bee samples, host contamination was removed before taxon profiling. 
    As a result, the relative abundances of honey bees are extremely low in three honey bee samples, and the same for bumble bees in three bumble bee samples.}
    \label{ArthropodHeatmap}
    \end{figure}

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Plants.pdf}
    \caption{Heatmaps for plant species abundance distribution in all samples. 
    The relative abundance takes reads assigned to plant species as background. 
    Species with relative abundance smaller than 1\% in all samples are collapsed as "others".}
    \label{PlantHeatmap}
    \end{figure}

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Fungi.pdf}
    \caption{Heatmaps for fungal species abundance distribution in all samples. 
    The relative abundance takes reads assigned to fungal species as background. 
    Species with relative abundance smaller than 1\% in all samples are collapsed as "others".}
    \label{FungusHeatmap}
    \end{figure}

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Viruses.pdf}
    \caption{Heatmaps for viruse species abundance distribution in all samples. 
    The relative abundance takes reads assigned to viruse species as background. 
    Species with relative abundance smaller than 1\% in all samples are collapsed as "others".}
    \label{ViruseHeatmap}
    \end{figure}

  \subsection{Inferred carbohydrate metabolism pathways}
  \begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{../Figures/PathwayCov_Carbonhydrate.pdf}
    \caption{Heatmaps for pathways of carbohydrate metabolism.}
    \label{Carbohydrate}
    \end{figure}

  \newpage

  % \bibliographystyle{unsrt}
  % \bibliographystyle{plainnat}
  \bibliography{reference}

\end{document}

### 2021-08-19 SeminarDiary/SeminarDiary.tex
Added README file.

\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{floatrow}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{booktabs}

\title{Seminar Diary}

\author{Cong Liu\footnotemark[1]}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{Department of Life Sciences (Silwood Park), Imperial College of Science, Technology and Medicine}

\date{2021}

\linespread{1.5}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\begin{document}
  \maketitle
  \newpage

  \linenumbers
  \section{Sleeping in a society of honey bees: the tale of a sleep-deprived dancer and her unwitting followers, and the search of insect dreams}
  Lecturer: Barrett Klein, University of Wisconsin.
  \newline
  Date: 2020.10.15
  \newline
  Honey bee (\textit{Apis mellifer}) foragers share information on the destinations of resources (food, water, \textit{etc}) to nest mates via waggle dances. 
  In waggle dances, the direction one forager waggles relative to vertical direction indicates the direction of the food resource relative to the sun, while the time it waggles is closelty correlated with distance to the resource.
  \newline 
  With sleep deprivation, the preciseness of foragers' waggle dances is decreased. 
  Sleep-restricted bee dancers performed fewer dances compared with controls. 
  They also performed proportionally fewer precise dances, or precise dances with fewer waggle phases, either leads to decrease in information load of waggle dances. 
  As for nest mates following imprecise dances, they were more likely to switch dances rather than exit, following fewer waggling phases. 
  These findings indicate that sleep loss is likely to impact negatively on both delivery and receiving of information vai waggle dances of honey bees. 
  They are of consensus with previous studies revealing the role of sleep in communication and learning consolidation. 
  \newline
  Another interesting topic is whetehr honey bees dream during sleep. 
  In order to examine it, the first thing need to be seen is what is happening in the honey bee brain during sleep. 
  By imaging brain activity of sensing odors of honey bees while they sleep, disperse activities were found, indicating the possibility of dreaming.
  \newline
  In summary, sleep deprivation impacted the communication between honey bees negatively, and disperse activities during sleep were found in sensing odors of honey bees.

  \newpage
  \section{Thermal ecology of infectious disease}
  Lecturer: Martha Socket, University of Califormia Los Angeles
  \newline
  Date: 2020.10.22
  \newline
  Temperature is an important abiotic factor that influences ecological processes including infectious disease transmission, and research on it has been motivated by climate change. 
  Investigations in mosquito-borne viruses and a fungal parasite (\textit{Metschnikowia bicuspidata}) infecting freshwater zooplankton (\textit{Daphnia dentifera}) helped understand the thermal response of pathogen transmission, which is often nolinear and combining multipe mechanisms. 
  \newline 
  The analysis of 15 mosquito-pathogen system (10 pathogens and 9 vector species) showed unimodal response to temperature, while the effect of same temperature on transmission of different pathogens varies strongly. 
  Compared with tropical pathogens, temperate pathogens systematically have broader thermal ranges, lower thermal minima and optima. 
  This variation is determined by both vector and pathogen species, and restriction to transmission is provided by different traits.  
  Warming is expected to increase transmission under thermal optima, but decrease transmission above thermal optima. 
  \newline
  Investigation in \textit{D. dentifera} and fungal parasite \textit{M. bicuspidata} illustrated a novel mechanism through which temperature affects transmission. 
  Warm temperatures lead to high transmission via impacting host feeding rate and parasite spore development, shaping epidemic size and seasonality.
  \newline
  In summary, these investigations highlight the impact of temperature on transmission of infectious diseases.

  \newpage
  \section{Eco-evo dynamics of experimentally tractable microbial systems}
  Lecturer: Jose I. Jimenez, Imperial College London
  \newline
  Date: 2020.10.29
  \newline
  Predictable manipulation of microbial community is valuable for multiple applications, but hindered by the complexity of interactions between microorganisms, as well as by interactions between microbial community and the environment. 
  Experimental population dynamics under lab-controlled conditions can provide insight into these interactions and potentiality for artificial modification of microbial community.
  \newline
  Investigations in horizonal transmission of antimicrobial resistance genes, which is mediated by F plasmid conjugation in \textit{Escherichia coli}, highlighted the influence imposed by population structure.  
  In liquid culture, conjugation can be inhibited by suppression of the formation of mating pairs using filamentous phages or M13 minor coat protein g3p. 
  In surface-associated growth, conjugation can be suppressed by severe genetic drift, which leads to spatial isolation of donor and recipient cells and thus restricts conjugation. 
  These results provide evidence that spatial structure of population could impose impact on the horizonal transfer of antimicrobial resistance genes.
  \newline
  Beside spatial structure, interventions of biological traits might be sufficient to drive population dynamics. 
  In \textit{Pseudomas aeruginosa}, mutation in a secondary receptor leads to decrease in the production of siderophore. 
  The effect of this mutation is dependent on the interactions with the environment. 
  It brings increase in fitness compared with wild-type, when high cost is required for the production of siderophore.
  \newline
  In summary, experimental microbial populations illustrate the impact of spatial structure and traits on population dynamics.

  \newpage
  \section{The honeybee waggle dance: evolutionary marvel but modern-day relic?}
  Lecturer: Elli Leadbeater, Royal Holloway University
  \newline
  Date: 2020.11.26
  \newline
  Honey bees \textit{Apis mellifera} share information on spatial location of resources with nest mates via waggle dances. 
  In order to investigate when spatial information from waggle dances is actually used by honey bees, network-based diffusion analysis was used to quantify the information flow and assess the impact of dance communication and hive-based olfactory information transfer on honey bee recruitment events. 
  The results show that successful recruits to novel locations are dependent on information from dances instead of olfactory cues, although the latter can also guide honey bees to the same locations. 
  However, in recruits to known locations, the importance of dances is reduced. 
  \newline
  Honey bee foragers recruit nest mates to novel locations with resources like food and water. 
  How do foragers evaluate the value of locations to make decision on recruiting nest mates? 
  To investigate in this question, decoding dances were used to quantify the forage value of landscapes for social bees. 
  By studying behaviour of honey bees in urban and rural areas, it is found that bees in urban area evaluate different landscapes quite evenly, while bees in rural area evaluate landscapes with more variances, and high values are assigned to oilseed rape.

  \newpage
  \section{Contemporary evolution and adaptive divergence in open ocean environments: new insights and applications to fisheries mangement}
  lecturer: Nina Overgaard Therkildsen, Cornell University
  \newline
  Date: 2021.2.25
  \newline
  Pressures from human activities is increasingly threatenning the persistence of marine species, urging better understanding in how and how quick orginasms can genetically adapt to changing environmental conditions. 
  DNA sequencing methods enables effective genetic studies of non-model species at population level, providing possibility for investigations in local adaption of marine species and further applications on fishery management.
  \newline
  In Atlantic silverside \textit{Menidia menidia}, strong adaptive divergences were found despite high gene flow. 
  Dramatic genomic footprints of selection were found, corresponding to cryptic adaptive divergence. 
  Massive linkage disequilibrium blocks are fixed for opposite alleles despite of small divergence at genome level. 
  This may be caused by high selective pressure that overcomes gene flow between populations of different locations. 
  An alternative cause is chromosomal rearrangement, which potentially link locally adaptive alleles as "supergenes".
  \newline
  Such insight in marine population genetics can be important for fishery management. 
  It is found that size-selective fishing accerlates loss of genetic diversity. 
  Under selection, highly polygenic parallel allele frequency shifts. 
  Interestingly, under parallel phynotypic responses to selection, there can be idiosyncratic genomic responses.

  \newpage
  \section{Semi-automated modeling of COVID-19 in the United States}
  Lecturer: John Drake, University of Georgia
  \newline
  Date: 2021.3.4
  \newline
  Modeling the spread of COVID-19 is helpful for understanding the transmission of epidemic and public policy making. 
  Such models are often characterized by high complexity in model structure, requiring great care to ensure they are fitted intelligently with biologically realistic coefficients, since good fit does not necessarily result from plausible parameters. 
  Initializing parameter search with previous well-fitted parameters can be a helpful strategy.  
  Also, assumptions should be continuously questioned as new information is gathered.
  \newline
  By modeling the transmission of COVID-19 in United States, it is revealed that increased social distance and decreased human mobility could significantly reduce the impact of pandemic. 
  Many places in United States have returned to normal conditions, indicating there is still room for improvement in controlling pandemic. 
  The model also illustrates the importance of early intervention, which is critical to controlling the pandemic. 
  \newline 
  Accoding to the results of the model, it may be possible in some states to release travelling restrictions without risking a resurgence in the near term. 
  However, this may be contingent on continuing other measures that reduce transmission.

  \newpage
  \section{The evolution of human commensalism in Passer sparrows}
  Lecturer: Mark Ravinet, University of Nottingham
  \newline
  Date: 2021.3.11
  \newline
  Human commensalism is widespread. Many species benefit from human activities. 
  Passer sparrows are used to investigate what factors drive the evolution of human commensalism. 
  \newline
  Genomic analysis of house sparrows provides insight into the evolution of human commensalism. 
  The model shows that hoouse commensalism arose in Near East and divergented into two clades: one spreaded into south Europe and experienced extensive admixture events, leading to hybrid speciation of Italian sparrow; the other one spreaded further into Europe with agriculture. 
  \newline
  The evolution of human commensalism also causes phenotypic consequences, including sedentary, nesting in human structures and feeding on human resources. 
  It also impacts morphological traits including skull and beak shape, which are recognized as potential adaptive traits to clutivated cereals. 
  \newline 
  Human commensalism also leads to strong divergent selection between house and Bactrianus sparrows. 
  On chromosome 8, two genes are strongly selected. 
  One is \textit{COL11A1}, whose homologies in human are related with Marshall syndrome. 
  The other one is associated with starch digestion in humans and dogs. 
  These findings are likely to be helpful for understanding functional shifts accompanied with origin of human commensalism.

  \newpage
  \section{Eco-evolutionary dynamics of coronaviruses}
  Lecturer: Jessica Metcalf, Princeton University
  \newline
  Date: 2021.5.6
  \newline
  Coronaviruses represent a vast, diverse and zoonotic reservoir of viruses, although there are only four phylogenetically distant endemic coronaviruses discovered in human in past two decades. 
  The successful emergence of a endemic pathogen is dependent on success in threading the needle in terms of virulence and transmission, and in evading existing immunity in host populations. 
  Beyond ascertainment and change in recent conditions, the intersection between transmission, virulence and the existing immune protection is likely to be the answer for why there is only a small number of endemic coronaviruses.
  \newline
  Facing the imapct of SARS-CoV-2, vaccines show clear benefits vastly outweigh risks, although they may drive the evolution of viruses. 
  Vaccines have theoretical potentiality to select viruses with increased virulence if they fail to provide protection, which would likely to cause cost falling on people without access to vaccines. 
  The evoluton of virulence should be minotored in preparation for further impact on human society.
  \newline
  Still few understanding in reinfection of coronaviruses is available, although it is important for understanding the effect of vaccination. 
  Burden and timing of SARS-CoV-2 infections are shaped by immune responses and vaccine doses in both short and long term. 
  One-dose-strategy might be good in short term in order to increase the number of immunized people, but in longer term, two-dose-strategy could mitigate the possibility of antigenic evolution.

  \newpage
  \section{From 1 ul of DNA to ecosystem scale biodiversity in four easy steps: the fantastic world of eDNA analysis}
  Lecturer: Si Creer, Bangor University
  \newline
  Date: 2021.5.20
  \newline
  Environmental DNA (eDNA) refers to free DNA molucules in the environment, released from multiple species. 
  It provides potentiality for efficient and effective assessment of biodiversity. 
  Multiple methods can be used for manipulation of eDNA, including quantative polymerase chain reaction, metabarcoding and shotgun eDNA sequencing. 
  The following case studies illustrate the application of eDNA in investigations in biodiversity.
  \newline
  The first case study focuses on diversity of pollen in the air and its fluctuation in time and space. 
  The results show that aerial grass pollen communities shift in beta composition throughout the grass flowering season. 
  The second case studies look into soil samples. 
  It is found that land uses imposes impact on richness of different communities. 
  After sorting land usage types in the productivity gradient, the richness of bacterial, fungal and protist communities follow identical types of pattern, while archaea and animal communities behave in different ways. 
  Using the same dataset, the relationships between textural heterogeneity and other factors are illustrated. 
  Results show that bacterial community is related with textural heterogeneity, but fungal community is not. 
  The third case is analysis of freshwater samples from a lake ecosystem, assessing annual dynamics of community. 
  The last case assesses foraging of honey bee via analysis eDNA extracted from honey, revealing historical changes in floral resources.

  \newpage
  \section{Living together: cooperation in the sociable weaver}
  Lecturer: Rita Covas, University of Porto
  \newline
  Date: 2021.5.27
  \newline
  Cooperation is widespread in nature and diverse in fuctions. 
  It brings benefits to the group, but costly to the individual. 
  To understand the cooperation and conflict in groups of organisms, sociable weaver is a suitable study model. 
  They cooperate in four distinct behaviours: nest building, helping at the nest, predator mobbing and vigilance. 
  \newline
  In cooperation of breeding, helpers of sociable waevers do not reproduce, but help breed offsprings of other group members. 
  A possible reason for the delay of breeding in helper sociable waevers is that breeding under poor conditions is too costly. 
  This hypothesis is verified by increase in independent breeding and decrease in helping after artificial food supplementation. 
  \newline
  To understand the cost of helping, free radical activity was measured under experimental increase in the cost of helping. 
  As a result, in young individuals, probability of helping increases if they are in poor physiolohical conditions. 
  Experimental increase in the energy cost of helping leading to increase in free radical damage and decrease in feeding rate. 
  \newline
  In summary, there is a trade-off between investment in helping and self maintenance. Individuals may adjust their behaviour in order to minimise possible costs.
  \newline
  It is also found that most helpers are related to the breeders. 
  Cooperation in breeding is generally positive on its success and allows breeders to decrease their efforts in caring for brood. 
  It also improved the suvival of female breeders.

  \newpage
  \section{Tracing the evolutionary history of viruses from the Stone Age to the present using ancient DNA}
  Lecturer: Martin Sikora, University of Copenhagen
  \newline
  Date: 2021.6.10
  \newline
  The recovery of ancient pathogen DNA provides valuable insights into the origin epidemics in human history, especially those lacking reliable historical records. It also provides a direct window into the evolution of pathogens, generating understanding in the general principles of evolutionary biology.
  \newline 
  From ancient human remains, genomes of variola viruses (samllpox) were recovered, revealing that a previously unknown clade was widespread in Northern Europe during the Viking Age. This clade of variola viruses from Viking Age and the viruses spreaded in 19th century evolved from a common ancestor at approximate 1700 years ago, via distinct paths of gene inactivation.
  \newline
  Another case of investigation in the genomes of ancient pathogens looks into human adenovirus with a history of 3100 years. 
  It shows that adenovirus that causing common childhood infections today were already spreading in human communities in Upper Palaeolothic. The genome of this virus shows low rate of molecular evolution, indicating its long-term co-divergent with host. The identification of ancient intra-type divergences and recent within-type variations indicate that it is possible that adenovirus was capable of human transmission in ancient time.

  \newpage
  \section{UK's work on the global food system: how we use research to further our work with government and industry}
  Lecturer: Mollie Gupta, WWF
  \newline
  Date: 2021.5.13
  \newline
  Food is the greatest part in ecological foodprint of humanity. 
  The food system is one of major drivers of biodiversity loss and greenhouse gas emissions. 
  Although a huge amount of land has been used for food production, yet there are regions where indernourishment is still a challenge, while other regions where there is overconsumption.
  \newline
  There are several drivers making food system consuming a huge amount of resources, one of them is overconsumption of animal protein. 
  Besides, the production of animal protein is inefficient, and a third of agricultural production is wasted. 
  Under such conditions, there are things need to happen including cut food loss and waste, increase food productivity through nature positive approaches and adoption of sustainable diet choices. 
  Furthermore, improvenment in goverance, planning and use of landscapes, including restoration of degraded ecosystems, is needed. 
  \newline 
  Facing these on-going issues, UK government set up policies. 
  A mandatory due diligence obligation is introduced on companies that place commodities and derived products that contribute to deforestation. Actions are taken to ensure similar principles are applied to the finance industry.

%   \newpage
%   \section{Ecosystem feedbacks to climate change: when and where do microbes matter?}
%   Lecturer: Bonnie Waring, Grantham Institute on Climate Change/DoLS
%   Date: 2020.11.12
%   Carbon dioxide accumulation in the atomosphere causes climate change, and soil organic matter represnts the largest terrestrial carbon pool, whose dynamics leads to uncertaintity in predictions of feedback on climate change. 
%   The cycle of soil carbon is governed by microbial decomposers, which may have impact on ecosystem responses to climate change in multiple aspects.
%   \newline
%   Investigations in tropical dry forest highlight the role of soil fungal community in plant growth.

%   When the soil is nutritionally poor, the plant community growing on the soil has high values of nutrient response efficiency, \textit{i.e.} high productivity per unit soil nutrient. 
%   No correlation between nitrogen response efficiency and phosphorus response efficiency, indicating they are controlled by different traits. 
%   This is consistent with prior understanding in nutrition absorbing, which is mediated by fungal symbionts.

%   Decomposition rates were correlated with tree and soil fungal community composition as well as soil fertility, but these relationships differed among litter types. In low fertility soils dominated by ectomycorrhizal oak trees, bulk litter turnover rates were low, regardless of soil moisture. By contrast, in higher fertility soils that supported mostly arbuscular mycorrhizal trees, bulk litter decay rates were strongly dependent on seasonal water availability. Both measures of decomposition increased with forest age, as did the frequency of termite-mediated wood decay. Taken together, our results demonstrate that soils and forest age exert strong control over decomposition dynamics in these tropical dry forests, either directly through effects on microclimate and nutrients, or indirectly by affecting tree and microbial community composition and traits, such as litter quality.

%   No correlation between nitrogen response efficiency and phosphorus response efficiency, indicating they are controlled by different traits. 
%   Soil fungal communities respond to soil nutrients.

  \end{document}

### 2021-08-19 MResProject/Code/CompareSensitivity.R

@@ -1,0 +1,75 @@
+library(ggplot2)
+
+HillDiversity = read.table("Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
+HillDiversity = subset(HillDiversity,Group=="All")
+
+LF_F18 = subset(HillDiversity,HillDiversity$Sample=="LF_F18")
+PGcomcol3_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol3_Bimp")
+PGcomcol4a_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4a_Bimp")
+PGcomcol4b_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4b_Bimp")
+PGnos_high_hv13_1 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-1")
+PGnos_high_hv13_2 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-2")
+PGnos_inter_hv15 = subset(HillDiversity,HillDiversity$Sample=="PGnos_inter_hv15")
+PGpollen_fresh = subset(HillDiversity,HillDiversity$Sample=="PGpollen_fresh")
+
+pdf("ExtraSpecies_Bumble.pdf")
+p1 = ggplot()+
+  geom_point(size=2,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
+                         y=(PGcomcol3_Bimp$SpeciesRichness-PGcomcol3_Bimp$AssemblySpeciesRichness)/PGcomcol3_Bimp$AssemblySpeciesRichness,
+                         colour="PGcomcol3_Bimp")))+
+  geom_point(size=2,(aes(x=PGcomcol4a_Bimp$CleanRead*PGcomcol4a_Bimp$SubsamplePercent/1e+6,
+                         y=(PGcomcol4a_Bimp$SpeciesRichness-PGcomcol4a_Bimp$AssemblySpeciesRichness)/PGcomcol4a_Bimp$AssemblySpeciesRichness,
+                         colour="PGcomcol4a_Bimp")))+
+  geom_point(size=2,(aes(x=PGcomcol4b_Bimp$CleanRead*PGcomcol4b_Bimp$SubsamplePercent/1e+6,
[…]

### 2021-08-19 MResProject/Code/DiversityModel.R

@@ -1,0 +1,252 @@
+library(minpack.lm)
+
+ReadData = function(type){ # Taxon/Function
+    data = paste(type,"_HillDiversity.txt",sep="")
+    HillDiversity = read.table(data,sep="\t",header=TRUE)
+    return(HillDiversity)
+} 
+
+# Functions for multimodel inference
+RSS = function(x, y, predic_y){
+  # Sum of squares
+  # x: independent variable values
+  # y: dependent variable values
+  # predic_y: predicted dependent variable values
+  Rss = sum((y-predic_y)^2)
+  return(Rss)}
+likelihood = function(x, y, predic_y){
+  # Likelihood
+  # x: independent variable values
+  # y: dependent variable values
+  # predic_y: predicted dependent variable values
+  Rss = RSS(x,y,predic_y)
+  n = length(x)
+  L = -0.5*n*log(Rss/n)
+  return(L)}
+AICc = function(x, y, predic_y, k){
+  # corrected Akaike information criterion (AICc)
+  # x: independent variable values
+  # y: dependent variable values
+  # predic_y: predicted dependent variable values
+  # k: number of coefficients
+  L = likelihood(x,y,predic_y)
+  n = length(x)
+  AICc = -2*L+2*k+2*k*(k+1)/(n-k-1)
+  return(AICc)}
+AIC_weight = function(vector){
+  # Akaike weight
+  # vector: AIC values
+  detaAIC = vector-min(vector,na.rm=TRUE)
+  weight = exp(-0.5*detaAIC)/sum(exp(-0.5*detaAIC),na.rm=TRUE)
+  return(weight)}
+
+# Candidate species accumulation models:
+model1 = function(x,a,b){return( a*x/(b*x+1) )}
+model2 = function(x,a,b){return( a*(1-exp(-b*x)) )}
+model3 = function(x,a,b,c){return( a-b*c^x )}
+model4 = function(x,a,b,c){return( a*(1-exp(-b*x))^c )}
+model5 = function(x,a,b,c,d){return( a*(1-(1+(x/c)^d)^-b) )}
+
+# Derivations of candidate models
+d_model1 = function(x,a,b){return( a/((b*x+1)^2) )}
+d_model2 = function(x,a,b){return( a*b*exp(-b*x) )}
+d_model3 = function(x,a,b,c){return( -b*c^(x)*log(c) )}
[…]

### 2021-08-19 MResProject/Code/Figures_OriginalData.R

@@ -1,0 +1,406 @@
+library(ggplot2)
+library(ComplexHeatmap)
+library(circlize)
+library(proxy)
+library(ape)
+
+#########################################################################
+#########################################################################
+### NonHostRatio.pdf
+#########################################################################
+#########################################################################
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
+CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
+MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
+HostReadCount = CleanReadCount-MetagenomicReadCount
+
+data = rbind(
+  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
+  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
+)
+
+pdf("NonHostRatio.pdf")
+p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
+  geom_bar(stat = "identity")+
+  ylab("Read (million)")+
+  xlab(NULL)+
+  theme_classic()+
+  theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
+  scale_y_continuous(expand = c(0,0))
+print(p)
+dev.off()
+#########################################################################
+#########################################################################
+### Group abundance distribution
+#########################################################################
+#########################################################################
[…]

### 2021-08-19 MResProject/Code/FunctionAnnotation.py

@@ -1,0 +1,72 @@
+import os
+import sys
+import pandas as pd
+import numpy as np
+import re
+
+args = sys.argv
+
+sample = args[1]
+percent = args[2]
+print(sample)
+print(percent)
+
+dire = "/rds/general/user/cl3820/home/Annotations/"+sample+"/"+percent+"_1/FunctionAnnotation"
+
+#########################################################################
+#########################################################################
+### Taxon and Function annotation of each read/CDS
+#########################################################################
+#########################################################################
+read2txid = pd.read_table(dire+"/read_txid.txt",header=None,sep="\t") # readID, rank, txid
+CDS2txid = pd.read_table(dire+"/CDS_txid_quantify.txt",header=0,sep="\t")
+txid2path = pd.read_table(dire+"/TaxonQuantification.txt",header=0,sep="\t")
+
+def CDSName(series):
+    series["CDSname"] = str(series["SeqID"])+":"+str(series["start"])+"-"+str(series["end"])+"("+str(series["strand"])+")"
+    return series
+CDS2txid = CDS2txid.apply(func=CDSName,axis=1,raw=False)
+
+
+def IDConvert(series):
+    if series["SeqType"]=="forward":
+        series["SeqID"] = str(series["SeqID"])+"_forward"
+        return series
+    elif series["SeqType"]=="reverse":
+        series["SeqID"] = str(series["SeqID"])+"_reverse"
+        return series
+    else:
+        return series
+
+def MergeAnnotation(SeqType):
+
+    Annotations = pd.read_table(dire+"/"+SeqType+"_annotation.txt.emapper.annotations",header=0,sep="\t")
+
+    Seq2KEGG = pd.DataFrame({"SeqID":Annotations["#query"],"KEGG_KO":Annotations["KEGG_ko"]})
+    
+    if SeqType=="CDS":
+        Seq2Taxon = pd.DataFrame({"SeqID":CDS2txid["CDSname"],"txid":CDS2txid["txid"],"ReadCount":CDS2txid["ReadCount"]})
+    else:
+        Seq2Taxon = pd.DataFrame({"SeqID":read2txid[0],"txid":read2txid[2],"ReadCount":np.repeat(np.array([1]),read2txid[0].size)})
+    
[…]

### 2021-08-19 MResProject/Code/ModelTables.R

@@ -1,0 +1,479 @@
+library(ggplot2)
+library(minpack.lm)
+
+source("Diversity.R")
+
+q_values = c("0","1","2")
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
+            "PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh")
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2",
+             "Bee_Amellifera_hv13_1","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1")
+names(relabels)=Samples
+
+ConvertID = function(input){
+  output = rep(NA,length(input))
+  for (i in 1:length(input)){
+  if (input[i] %in% Samples){
+  output[i] = unname(relabels[input[i]])
+  }else{
+    output[i]=input[i]
+  }}
+  return(output)
+}
+
+Fitting = function(type){ # Taxon/Function
+    OutputTable = data.frame()
+
+    for (sample in Samples){
+    for (q in q_values){
+        run = run_ModelFitting(sample,q,type)
+
+        ret = c(sample,q,run$Asymptote,
+                
+                run$simu_x[length(run$simu_x)],run$y[length(run$y)],run$simu_y[length(run$simu_y)],
+                run$d_simu_y[length(run$d_simu_y)],run$simu_y[length(run$simu_y)]/run$Asymptote,
+                
+                run$OptDepth_0.5,run$OptDiversity_0.5,run$OptDiversity_0.5/run$Asymptote,
+                run$OptDepth_0.1,run$OptDiversity_0.1,run$OptDiversity_0.1/run$Asymptote,
+                run$OptDepth_0.05,run$OptDiversity_0.05,run$OptDiversity_0.05/run$Asymptote,
+                run$OptDepth_0.01,run$OptDiversity_0.01,run$OptDiversity_0.01/run$Asymptote,
+                
+                run$m1[1],run$m1[2],run$m1[3],run$weight[1],
[…]

### 2021-08-19 MResProject/Code/PathwayReconstruct.py

@@ -1,0 +1,45 @@
+import os
+import sys
+import numpy as np
+import pandas as pd
+
+args = sys.argv
+
+sample = args[1]
+percent = args[2]
+print(sample)
+print(percent)
+
+dire = "/rds/general/user/cl3820/home/Annotations/"+sample+"/"+percent+"_1/FunctionAnnotation"
+
+KO_abundance = pd.read_table(dire+"/KO_quantify.txt",sep="\t",header=0)
+KO_term = pd.read_table("/rds/general/user/cl3820/home/MinPath/data/KEGG-family.txt",sep="\t",header=None)
+KO_term.columns = ["KEGG_KO","Description"]
+
+KO_abundance_term = pd.merge(KO_abundance,KO_term,on="KEGG_KO",how="left")
+KO_abundance_term.to_csv(dire+"/KO_Abundance_Description.txt",header=True,sep="\t",index=False)
+
+Txid_KO = pd.read_table(dire+"/Txid_KO.txt",sep="\t",header=None)
+Txid_KO = Txid_KO.drop(index=0)
+Txid_KO.to_csv(dire+"/Txid_KO_NoHeader.txt",header=False,sep="\t",index=False)
+
+cmd = "python"+" "+"/rds/general/user/cl3820/home/MinPath/MinPath.py"+" "+"-ko"+" "+dire+"/Txid_KO_NoHeader.txt"+" "+"-report"+" "+dire+"/Pathway.txt"+" "+"-details"+" "+dire+"/PathwayDetails.txt"
+os.system(cmd)
+
+Pathway = pd.read_table(dire+"/Pathway.txt",sep="  ",header=None)
+
+def ConvertData(series):
+    PathwayID = "map"+series[0].split(" ")[1]
+    Naive = series[1].split(" ")[1]
+    MinPath = series[2].split(" ")[1]
+    TotalGene = series[4]
+    GeneFound = series[6]
+    Cov = GeneFound/TotalGene
+    Description = series[8]
+    dic = {"PathwayID":PathwayID,"Naive":Naive,"MinPath":MinPath,"TotalGene":TotalGene,"GeneFound":GeneFound,"Coverage":Cov,"Description":Description}
+    ret = pd.Series(dic)
+    return ret
+
+Pathway = Pathway.apply(func=ConvertData,axis=1).sort_values(by="Coverage",axis=0,ascending=False)
+
+Pathway.to_csv(dire+"/PathwaySummary.txt",header=True,sep="\t",index=False)

### 2021-08-19 MResProject/Code/QualityControl_HostRemove.py

@@ -1,0 +1,151 @@
+"""
+This script conducts quality filtering and host removing.
+Host removing can be ignored if argument 3 is "None".
+
+ARGUMENTS:
+1: rawData1 (file, raw fq file 1)
+2: rawData2 (file, raw fq file 2)
+3: HostIndex (file, base name of Bowtie2 index of host genome)
+4: outDir (directory, named after sample name)
+5: sample (string, sample name)
+6: threads (integer, number of threads)
+
+DEPENDENCIES:
+/rds/general/user/cl3820/home/anaconda3/bin/fastqc
+/rds/general/user/cl3820/home/NexteraPE-PE.fa (fasta file of adaptor)
+/rds/general/user/cl3820/home/anaconda3/bin/trimmomatic
+/rds/general/user/cl3820/home/anaconda3/bowtie2
+/rds/general/user/cl3820/home/anaconda3/bin/samtools
+
+INPUT:
+rawData1
+rawData2
+HostIndex
+
+OUTPUT:
+4 .html and 4 .zip files in outDir (Fastqc reports of raw and clean reads)
+outDir+"/"+sample+"_clean.1.fq", outDir+"/unpaired_"+sample+".1.fq" (clean and paired reads)
+outDir+"/"+sample+"_clean.2.fq", outDir+"/unpaired_"+sample+".2.fq" (clean and unpaired reads)
+outDir+"/"+sample+"_Host.sam"+".bam" (BAM file from mapping clean-paired reads to host genome)
+outDir+"/"+sample+"_Host.sam"+".bam_mapped" (BAM file of reads mapped to host genome)
+outDir+"/"+sample+"_Host.sam"+".bam_mapped.1.fq", outDir+"/"+sample+"_Host.sam"+".bam_mapped.2.fq" (host reads)
+outDir+"/"+sample+"_Host.sam"+".bam_unmapped" (BAM file of reads not mapped to host genome)
+outDir+"/"+sample+"_Host.sam"+".bam_unmapped.1.fq", outDir+"/"+sample+"_Host.sam"+".bam_unmapped.2.fq" (non-host reads)
+"""
+
+import os
+import sys
+
+args = sys.argv
+
+# Arguments
+rawData1 = args[1] # Path to raw data 1
+rawData2 = args[2] # Path to raw data 2
+HostIndex = args[3] # Path to Bowtie2 index of host genomes. If no host, set it "None"
[…]

### 2021-08-19 MResProject/Code/TaxonAnnotation.py

@@ -1,0 +1,146 @@
+import os
+import sys
+import numpy as np
+import pandas as pd
+sys.path.append('/rds/general/user/cl3820/home/taxomias')
+import taxomias as tx
+import re
+
+args = sys.argv
+
+sample = args[1]
+percent = args[2]
+print(sample)
+print(percent)
+
+dire = "/rds/general/user/cl3820/home/Annotations/"+sample+"/"+percent+"_1/FunctionAnnotation"
+
+#########################################################################
+#########################################################################
+### Merge taxon and abundance table of CDS
+#########################################################################
+#########################################################################
+CDS_quantify = pd.read_table(dire+"/CDSquantify.txt",sep="\t",header=None) #fileds: nucleotide ID, start, end, name, score, strand, read count, read length, seq length, coverage
+
+CDS_txid = pd.read_table(dire+"/CDS_info.txt",sep="\t",header=None) # fileds: nucleotide ID, start, end, name, score, strand, assembly ID, txid
+
+CDS_txid.columns = ["SeqID","start","end","CDSname","score","strand","AssemblyID","txid"]
+CDS_txid["ReadCount"] = CDS_quantify[6]
+CDS_txid["Coverage"] = CDS_quantify[9]
+
+CDS_txid = CDS_txid[CDS_txid["ReadCount"]!=0]
+CDS_txid.to_csv(dire+"/CDS_txid_quantify.txt",sep="\t",index=False,header=True) # header: "SeqID","start","end","CDSname","score","strand","AssemblyID","txid", "ReadCount", "Coverage"
+
+#########################################################################
+#########################################################################
+### Abundance of taxa identified
+#########################################################################
+#########################################################################
+CDS = pd.read_table(dire+"/CDS_txid_quantify.txt",sep="\t",header=0) # header: "SeqID","start","end","CDSname","score","strand","AssemblyID","txid", "ReadCount", "Coverage"
+read = pd.read_table(dire+"/../FirstRound/taxon_ID.txt",sep="\t",header=None) # fields: rank (S,G), txid, read count (pair)
+
+txid_CDSquantify = CDS["ReadCount"].groupby(CDS["txid"]).sum() # read count
+
[…]

### 2021-08-23 MResProject/Latex/Draft.tex
CMEECourseWork

@@
 \usepackage[toc,page]{appendix}
-
-\title{Metagenomic DNA discoveries after sequencing everything (bacteria, parasites, food, gut) inside a bee}
+\usepackage{makecell}
+
+% Metagenomic DNA discoveries after sequencing everything (bacteria, parasites, food, gut) inside a bee
+\title{Optimize sequencing depth required for reliable profiling of microbiome by rarefaction and multimodel inference, using shotgun metagenomic data from pollination system and a modular profiling pipeline}
 \author{Cong Liu}
@@
   \begin{center}
-    A thesis submitted in partial fulfilment of the requirements for the degree of Master
-of Science/Research at Imperial College London
-\newline
-Submitted for the MRes/MSc in Computational Methods in Ecology and Evolution
+    A thesis submitted in partial fulfilment of the requirements for the degree of Master of Research at Imperial College London
+\newline
+Submitted for the MRes in Computational Methods in Ecology and Evolution
   \end{center}
@@
   \newline
+  All datasets used in this project are provided by Dr. Peter Graystock and the project was conducted under his supervison. 
+  I am responsible for the development and conduction of the analyses presented.
 
@@
   \begin{abstract}
-    Bee-associated microbiome plays a crucial role in host health and relevant investigations have been boosted by shotgun metagenomics. 
-    However, bioinformatics for metagenomic data analysis is complex, and the results may be compromised by insufficient sequencing. 
-    Here, an integrated pipeline combining assembly-dependent and -independent methods was introduced for taxonomic and functional profiling of shotgun metagenomic data. 
-    It was used for profiling metagenomic datasets ($2 \times 150 bp$ read pairs) from honey bees, bumble bees and flower surface. 
-    Rarefaction and model fitting was conducted to compute expected species/function diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to determine minimal sequencing depth capable of estimating diversity sufficiently.
-    As a result, functional profiling was demanding about sequencing effort. 
-    None of datasets involved was sufficient for providing almost complete coverage of function diversity. 
-    As for species diversity, the average minimal sequencing depth for reliable estimation of Hill number of order 0, 1 and 2 for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; and for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million.
-    For flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
+    Bee-associated microbiome plays a crucial role in host health and relevant investigations have been boosted by shotgun metagenomics, which provides unique advantages by capturing diversity of multiple taxonomic clades and providing information on function potentiality.
+    However, utilization of shotgun metagenomics is hindered by complexity of data analysis and high cost of sequencing. 
+    % However, bioinformatics for metagenomic data analysis is complex, and the results may be compromised by insufficient sequencing depth. 
+    Here, an integrated pipeline combining assembly-dependent and -independent methods was introduced for taxonomic and functional profiling of shotgun metagenomic data, and a framework of rarefaction and multimodel inference was constructed for optimizing sequencing depth.
+    Both the pipeline and the framework were used for analysis of real metagenomic datasets ($2 \times 150 bp$ read pairs) from honey bees, bumble bees and flower washes. 
+    The integrated pipeline illustrated taxon composition and metabolic potentiality of metagenome, and provided improvement in species identification compared with an assembly-dependent procedure. 
+    Sequencing depth can be optimized for species diversity estimation especially when little emphasis is given to rare species, while functional profiling requires deeper sequencing than taxon profiling.
+    % Rarefaction and model fitting was conducted to compute expected species/function diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to optimize sequencing depth, balancing sequencing effort and capability of estimating diversity reliably.
+    % As a result, functional profiling was demanding about sequencing effort. 
+    % None of datasets involved was sufficient for providing almost complete coverage of function diversity. 
+    % As for species diversity, the average optimal sequencing depth for reliable estimation of Hill number of order 0, 1 and 2 for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; and for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million.
+    % For flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
     These results are helpful for cost-effective utilization of shotgun metagenomics in investigations of pollination system. 
-    The integrated pipeline and the framework for rarefaction analysis can also be applied for researches on other environments. 
+    % The integrated pipeline and the framework for rarefaction analysis can also be applied for researches on other environments. 
   \end{abstract}
@@
   \section{Introduction}
-  The health of bees is a crucial issue that has received increasing concern \citep{amiri2020using}. 
-  As pollinators of numerous plants, bees play an important role in the stability of natural and agricultural systems \citep{hristov2020significance,foldesi2021larger,bansch2021crop,khalifa2021overview}.
-  However, diverse pathogens and environmental factors impose threaten on bee health. 
-  The trend of bee decline has been widely observed at a global scale and attributed to multiple factors including pesticide exposure, invasive species, habitat loss, disease prevalence and climate change \citep{brown2009conservation,hristov2020factors,cheng2021ecology,zattara2021worldwide}.
+  Pollinators such as bees are crucial to maintain global food security and provide stability of natural systems \citep{hristov2020significance,bansch2021crop,khalifa2021overview} but their health is under increasing concern \citep{amiri2020using}.
+  % The health of bees is a crucial issue that has received increasing concern \citep{amiri2020using}. 
+  % As pollinators of numerous plants, bees play an important role in the stability of natural and agricultural systems \citep{hristov2020significance,bansch2021crop,khalifa2021overview}.
+  % foldesi2021larger 
+  Diverse pathogens and environmental factors threaten bee health and are contributing to their declines. 
+  % The trend of bee decline has been widely observed at a global scale and attributed to multiple factors including 
+  A combination of stressors including parasites, pesticide exposure, invasive species, habitat loss and climate change are all contributing to declines of bee populations.
+\citep{brown2009conservation,hristov2020factors,cheng2021ecology,zattara2021worldwide}.
   \newline
   Bees are associated with a community of microorganisms influencing host health \citep{engel2016bee,raymann2018role}. 
-  Bee-associated microbiome plays a role in food digestion and carbohydrate metabolism by mediating processes including breaking down 
-  % plant-produced polysaccharide including 
-  plant-produced pectin and hemicellulose \citep{zheng2019division}; hydrolysis of sucrose \citep{engel2012functional,lee2015saccharide}, a predominant component of nectar \citep{nicolson2007nectar} and metabolism of mannose \citep{engel2012functional,lee2015saccharide} which presents in nectar
-  % of \textit{Tilia} 
-  \citep{adler2000ecological} and is poisonous to honey bees \citep{de1986mechanism}. 
-  Besides, it is also involved in immunity against pathogens, providing protection against pathogens including \textit{Crithidia}, 
+  Within the gut of bees, stable microbial communities (microbiomes) play crucial roles in food digestion, parasite defence and chemical detoxification. 
+  They mediate food digestion processes including 
+  % plant-produced polysaccharide including pectin and hemicellulose \citep{zheng2019division}
+  polysaccharides breakdown \citep{zheng2019division}, sucrose hydrolysis \citep{engel2012functional,lee2015saccharide}, 
+  % a predominant component of nectar \citep{nicolson2007nectar} 
+  and mannose metabolism \citep{engel2012functional,lee2015saccharide}. 
+  % which presents in nectar of \textit{Tilia} \citep{adler2000ecological} and is poisonous to honey bees \citep{de1986mechanism}. 
+  They also provide protection against pathogens including \textit{Crithidia}, 
   % a protozoan genus exclusively parasitising arthropods 
@@
   % a bacteria causing lethal American foulbrood in honey bees 
-  \citep{ebeling2016biology,forsgren2010novel} and \textit{Nosema} 
+  \citep{ebeling2016biology,forsgren2010novel} and \textit{Nosema sp.} 
   % a genus of fungal pathogens 
   \citep{cariveau2014variation,maes2016diet}. 
-  \newline
-  Host-associated microbiome plays an important role in host homeostasis and metagenomics boosted by high throughput sequencing provides powerful tools for understanding its composition, function and dynamics.
-  For example, amplicon sequencing is a powerful tool and has revealed incredible understanding in microbiome \citep{eckburg2005diversity,galloway2020tools,new2020metagenomics}. 
-  However, it only focuses on a small part of the whole microbiome. 
-  Shotgun sequencing of microbiome, or metagenomics, unselectively captures DNA in a sample and is capable of providing comprehensive inventories of taxa and functional gene clusters (FGCs) with high resolution \citep{quince2017shotgun,new2020metagenomics}.
-  \newline
+  Besides, bee-associated symbionts can aid in detoxification. 
+  They are involved in resistance to both metal and metalloid toxins including cadmium \citep{rothman2019cadmium}, copper \citep{rothman2020direct} and selenate \citep{rothman2019bumble}. 
+  \newline
+  Amplicon sequencing, in which a species-specific barcode region is amplified and sequenced, is a powerful method for investigations of microbiome \citep{abdelfattah2018metabarcoding}.  
+  It is vastly used in bee microbiome investigations to illustrate the taxonomic diversity of bee-associated bacteria and fungi (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}).
+  However, bees visit numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including bacteria, fungi, plants, arthropods and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
+  It is difficult to explore this diversity via amplicon sequencing because it only captures a fraction of the whole community since analysis of different taxonomic groups is based on different barcode regions, \textit{e.g.} 16S ribosomal RNA (rRNA) for bacteria \citep{hayashi2002phylogenetic,eckburg2005diversity}, internal transcribed spacer (ITS) for fungi \citep{nilsson2008intraspecific}, cytochrome c oxidase subunit I (COI) for Animalia \citep{hebert2003barcoding}
+  and plastid genes for plants \citep{group2009dna}. 
+  As a result, amplicon sequencing only captures taxon diversity within a certain clade. 
+  Besides, it is difficult to illustrate function potentiality of bee-associated microbiome using amplicon sequencing since it does not provide information on content of functional gene clusters (FGCs), \textit{i.e.} aggregates of genes with same function.
+  As a result, functional capacity needs to be inferred based on reference genomes \citep{asshauer2015tax4fun,douglas2018predicting}. 
+  However, bee bacterial symbionts are diversified at strain level \citep{engel2012functional,powell2016strain,ellegaard2020vast} and bacterial strains are often highly variable in gene content \citep{cordero2014explaining,brockhurst2019ecology}.
+  As a result, amplicon sequencing-based inference of functional capacity of bee microbiome may not be reliable.
+  % Host-associated microbiome plays an important role in host homeostasis and metagenomics boosted by high throughput sequencing provides powerful tools for understanding its composition, function and dynamics.
+  % For example, amplicon sequencing is a powerful tool and has revealed incredible understanding in microbiome \citep{eckburg2005diversity,galloway2020tools,new2020metagenomics}. 
+  % However, it only focuses on a small part of the whole microbiome. 
+  % Shotgun sequencing of microbiome, or metagenomics, unselectively captures DNA in a sample and is capable of providing comprehensive inventories of taxa and functional gene clusters (FGCs) with high resolution \citep{quince2017shotgun,new2020metagenomics}.
+  \newline
+  Shotgun metagenomics provides an alternative for microbiome investigations to overcome drawbacks of amplicon sequencing. 
+  By capturing and sequencing DNA fragments unselectively, shotgun metagenomics is capable of providing comprehensive inventories of taxa and FGCs \citep{quince2017shotgun,new2020metagenomics,galloway2020tools}.
   However, utilization of shotgun metagenomics is hindered by challenges in bioinformatics. 
-  Typical goal of metagenomics is to provide taxonomic and functional profile of the community, and there is not a golden standard for bioinformatics of metagenome. 
-  Generaly, one of the first steps in metagenomic analysis is assembling short reads into long contigs, which can help improve accuracy of metagenomic annotation \citep{tran2020assembling} and is necessary for
+  Typical goal of metagenomics is to provide taxonomic and functional profile of microbiome, and there is not a golden standard for bioinformatics of metagenome. 
+  Generally, one of the first steps in metagenomic analysis is assembling short reads into long contigs, which can help improve accuracy of metagenomic annotation \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling} and is necessary for
   % tasks including recovery of uncultured genomes \citep{garza2015cultured,chen2020accurate} and 
   discovery of novel taxa and genes \citep{culligan2014metagenomics,youngblut2020large}. 
-  However, metagenome assembly is complex, compromised by fragmental assembly, chimeras \citep{mikheenko2016metaquast} and loss of taxon/function diversity due to unassembled reads \citep{vollmers2017comparing,ayling2020new}.
-  Probably because of these shortcomings, assembly is skipped in some researches and short reads are directly proceeded for annotation \citep{tringe2005comparative,huson2007megan,abubucker2012metabolic,vermote2018amplicon,bovo2018shotgun}, although the accuracy may be compromised due to low information load of short reads \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling}.
-  A combination of both assembly-dependent and -free method might be helpful for overcoming the complexity of metagenomic assembly and inaccuracy of short read annotation \citep{becker2020modular}. 
-  \newline
-  Another challenge of metagenomics is the determination of sequencing depth. 
-  It is recommended to retrieve as many reads as possible \citep{quince2017shotgun}, since insufficient sequencing causes imprecise estimation of taxon/FGC diversity \citep{cattonaro2018you,zaheer2018impact,pereira2019impact,gweon2019impact}.
-  However, deep sequencing is expensive, which hinders its utilization, especially in large-scale projects. 
-  Currently, there is hardly any published guideline for the sufficient sequencing depth of a given environment or study type in order to reach a trade-off between sequencing effort and reliable output.
-  \newline
-  The determination of sequencing depth can be conducted by rarefaction analysis, a method originated from traditional ecology \citep{sanders1968marine,hurlbert1971nonconcept,heck1975explicit,moreno2000assessing,hortal2005ed,gomez2014using,hughes2021sampling}.
-  In field based surveys, a random sample of individuals is drawn from a community and assigned to species. 
-  Then a rarefaction curve illustrating expected biodiversity represented by given sampling effort (often measured by number of captured individuals) is generated by random subsampling the original sample without replacement, and quantified by model fitting \citep{hughes2005application,gotelli2011estimating}.
-  The slope of the rarefaction curve represents the expected rise of the curve if one more individual is captured. 
-  The sample is nearly complete if and only if the final slope is small, and the point at which the slope of rarefaction curve falls to a cut-off value represents the minimal sampling effort required for assessment of biodiversity \citep{heck1975explicit,moreno2000assessing,hortal2004butterfly,hortal2005ed,chao2012coverage,gomez2014using,roswell2021conceptual}.
-  This framework for determination of sampling effort can be used in shotgun metagenomics, since a metagenomic dataset can be viewed as a random sample of an assemblage of genomic sequences, and 
-  profiling is the process by which reads are assigned to taxa or FGCs. 
-  The concept corresponding to sampling effort is sequencing depth in metagenomics, which is measured by read number.
-  \newline 
-  In macroecology, comprehensive analytical frameworks are available for computing expected biodiversity returned by given sample sizes using a reference sample \citep{heck1975explicit,chao2012coverage,chao2014rarefaction}.
-  % However, analytical approaches derived for computing rarefaction curve in macroecology \citep{heck1975explicit,chao2012coverage,chao2014rarefaction} 
-  However, they are not suitable for metagenomics because 
-  % they are based on 
-  of the assumptions that every captured individual can be assuredly assigned to a species, and the present of rare species is as reliable as that of abundant species. 
-  In shotgun metagenomics, reads may be unannotated or annotated incorrectly due to low sequencing quality, host contamination, similar structures in genomes of different species, non-coding regions in genomes and limited sensitivity of profiling pipeline.
-  As a result, taxa or FGCs of low relative abundance are more likely to be false positive than that of high abundance.
-  \newline
-  In this project, I aimed to (1) construct an integrated pipeline combining assembly-dependent and -independent methods for metagenomic profiling and (2) estimate minimal sequencing depth sufficient for covering species and FGC diversity of metagenome from three environmental types: honey bees, bumble bees and surface of flowers.
-  In the integrated pipeline (Figure \ref{Pipeline}), assembly-dependent taxon profiling is conducted after quality filtering and removing host contamination. 
+  However, metagenome assembly is complex, compromised by fragmental assembly, chimaeras \citep{mikheenko2016metaquast} and loss of taxon/function diversity due to unassembled reads \citep{vollmers2017comparing,ayling2020new}.
+  Probably because of these shortcomings, assembly is skipped in some researches and short reads are directly proceeded for annotation \citep{tringe2005comparative,abubucker2012metabolic,vermote2018amplicon,bovo2018shotgun}, although the accuracy can be compromised due to low information load of short reads \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling}.
+  A combination of both assembly-dependent and -free methods could overcome the complexity and improving accuracy of metagenomic profiling \citep{becker2020modular}.
+  % complexity of metagenomic assembly and inaccuracy of short read annotation \citep{becker2020modular}. 
+  \newline
+  A remaining challenge of metagenomics is the determination of a sequencing depth that provides reliable estimation of taxon/FGC diversity without overspending. 
+  It is recommended to retrieve as many reads as possible \citep{quince2017shotgun} since insufficient sequencing causes compromise in metagenome profiling \citep{cattonaro2018you,zaheer2018impact,pereira2019impact,gweon2019impact}.
+  However, deep metagenomic sequencing is expensive, which hinders its utilization, especially in large-scale projects. 
+  Currently, there are few published guidelines for the sufficient sequencing depth of a given environment or study type in order to reach a trade-off between sequencing effort and reliable output. 
+  \newline
+  In order to balance sequencing cost and reliable estimation of taxon/FGC diversity, expected diversity represented by given sequencing depth need to be computed. 
+  Since a metagenomic dataset can be viewed as a random sample of an assemblage of genomic sequences, and profiling is the process by which reads are assigned to taxa or FGCs, the relationship between sequencing depth and diversity can be illustrated by rarefaction (randomly subsampling the original dataset without replacement) and quantified by model fitting, if the original dataset can provide an almost complete inventory of taxa/FGCs \citep{heck1975explicit,hortal2005ed,gomez2014using,hughes2021sampling}.
+  The sequencing depth is sufficient for reliable estimation of taxon/FGC diversity if and only if the slope of the model is small \citep{hortal2005ed,chao2012coverage,roswell2021conceptual}. 
+  % The determination of sequencing depth can be conducted by rarefaction analysis, a method widely used in traditional ecology \citep{heck1975explicit,hortal2005ed,gomez2014using,hughes2021sampling}.
+  % In field based surveys, a random sample of individuals is drawn from a community and assigned to species. 
+  % Then a rarefaction curve illustrating expected biodiversity represented by given sampling effort (often measured by number of captured individuals) is generated by random subsampling the original sample without replacement, and quantified by model fitting \citep{hughes2005application,gotelli2011estimating}.
+  % The slope of the rarefaction curve represents the expected rise of the curve if one more individual is captured. 
+  % The sample is nearly complete if and only if the final slope is small, and the point at which the slope of rarefaction curve falls to a cut-off value represents the minimal sampling effort required for assessment of biodiversity \citep{hortal2005ed,chao2012coverage,gomez2014using,roswell2021conceptual}.
+  % This framework for determination of sampling effort can be used in shotgun metagenomics, since a metagenomic dataset can be viewed as a random sample of an assemblage of genomic sequences, and 
+  % profiling is the process by which reads are assigned to taxa or FGCs. 
+  % The concept corresponding to sampling effort is sequencing depth in metagenomics, which is measured by read number.
+  % \newline 
+  % In macroecology, comprehensive analytical frameworks are available for computing expected biodiversity returned by given sample sizes using a reference sample \citep{heck1975explicit,chao2012coverage,chao2014rarefaction}.
+  % % However, analytical approaches derived for computing rarefaction curve in macroecology \citep{heck1975explicit,chao2012coverage,chao2014rarefaction} 
+  % However, they are not suitable for metagenomics because 
+  % % they are based on 
+  % of the assumptions that every captured individual can be assuredly assigned to a species, and the present of rare species is as reliable as that of abundant species. 
+  % In shotgun metagenomics, reads may be unannotated or annotated incorrectly due to low sequencing quality, host contamination, similar structures in genomes of different species, non-coding regions in genomes and limited sensitivity of profiling pipeline.
+  % As a result, taxa or FGCs of low relative abundance are more likely to be false positive than that of high abundance.
+  \newline
+  In this project, I utilised metagenomes from three environmental types: the gut of a honey bee (\textit{Apis mellifera}), the gut of a common North American bumble bee (\textit{Bombus impatiens}) and the surface of a flower (\textit{Erigeron annuus}).
+  I aimed to (1) develop an integrated pipeline combining assembly-dependent and -independent methods to deliver improved taxon annotation of sequencing data and (2) optimize sequencing depth to balance sequencing cost and requirement for reliable analysis of microbial species diversity, or the description of their functional diversity.
+  In the integrated pipeline (Figure \ref{Pipeline}), 
+  assembly-dependent taxon profiling is conducted after quality filtering and removing host contamination. 
   To address high negative rate of assembly-dependent search, a reference database of genomes from species present in the assembly is constructed and used for filtering non-host reads. 
   Reads not recruited by the reference database are subjected to assembly-free taxonomic search. 
-  This integrated pipeline was used to profile metagenomic datasets from honey bees, bumble bees and environmental DNA (eDNA) washed from a flower (\textit{Erigeron annuus}). 
-  It was shown that the construction of reference database and assembly-free search helped identified species not represented by the assembly. 
-  Then I simulated different sequencing depth by rarefaction and profiled subsampled datasets using the integrated pipeline, generating inventories of species and Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}.
-  Each KO represents one FGC, \textit{i.e.} an aggregate of genes with same function. 
+  This integrated pipeline was used to profile metagenomic datasets involved in this project. 
+  % It was shown that the construction of reference database and assembly-free search helped identified species not represented by the assembly. 
+  Then in order to estimate optimal sequencing depth for reliable representing taxonomic/functional diversity of metagenomes, I simulated different sequencing depth by rarefaction and profiled subsampled datasets using the integrated pipeline, generating inventories of species and FGCs represented by Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}.
   Diversity of species and KOs was measured by Hill numbers of order 0, 1 and 2. 
@@
   % The higher the order is, the more sensitive to relative abundances Hill number is. 
-  The relationship between Hill numbers and sequencing depth (number of 150 bp pair-end reads) was quantified by fitting and averaging asymptotic species accumulation models, and estimation of minimal sequencing depth was given by the point where the slope of rarefaction curve drops to cut-off values.
-  Sample would be excluded from estimation of minimal sequencing depth if the original dataset was not sufficient for providing an almost complete inventory of species or KOs, which was characterized by small final slope of rarefaction curve for species or KO richness (Hill number of order 0).
-  As a result, when measuring species diversity by Hill number of order 0, 1 and 2, the average minimal sequencing depth for honey bee samples are 40.33 million, 18.57 million and 17.45 million; for bumble bee samples, the averages are 42.49 million, 40.33 million and 24.77 million; and for flower surface, 0.88 million sequencing depth is not sufficient for providing an almost complete inventory of species, indicating higher sequencing depth is needed.
-  As for functional diversity, no datasets involved in this project is big enough for providing an almost complete inventory of KOs, indicating the sequencing depth need to be higher than the maximum of each sample type, \textit{i.e.} 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
+  The relationship between Hill numbers and sequencing depth was quantified by fitting and averaging asymptotic species accumulation models, and estimation of optimal sequencing depth was given by the point where the slope of rarefaction curve drops to cut-off values.
+  % Sample would be excluded from optimization of sequencing depth if the original dataset was not sufficient for providing an almost complete inventory of species or KOs, which was characterized by small final slope of rarefaction curve for species or KO richness (Hill number of order 0).
+  % As a result, when measuring species diversity by Hill number of order 0, 1 and 2, the average optimal sequencing depth for honey bee samples are 40.33 million, 18.57 million and 17.45 million; for bumble bee samples, the averages are 42.49 million, 40.33 million and 24.77 million; and for flower surface, 0.88 million sequencing depth is not sufficient for providing an almost complete inventory of species, indicating higher sequencing depth is needed.
+  % As for functional diversity, no datasets involved in this project is big enough for providing an almost complete inventory of KOs, indicating the sequencing depth need to be higher than the maximum of each sample type, \textit{i.e.} 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
+  % The integrated pipeline and the framework for rarefaction analysis can also be applied for investigations of microbiomes from other environments, and the estimations of optimal sequencing depth provide guidelines for cost-effective utilization of shotgun metagenomics in investigations of pollination system.
 
@@
     \subsection{Samples, DNA extraction and sequencing}
+    Samples include four honey bees (two from the same hive (hive 13), one from a hive in the same apiary (hive 15) and one caught foraging), three bumble bees from commercially supplied (Biobest) bumblebee colonies (two from the same colony), and one buffer wash of a wild flower (\textit{Erigeron annuus}).
+    \newline
+    DNA extraction was performed as in \cite{graystock2020dominant}, followed by library preparation using a template protocol with Illumina Nextera Library Prep kits.
+Briefly, this involved tagmentation into fragments of 300 bases before eight samples of 10ng were pooled together and sent to Beijing Genomics Institute for further quality control and sequencing using a full lane in the X-ten platform.
 
@@
       \subsubsection{Integrated pipeline}
-      The integrated pipeline was designed for shotgun metagenomic profiling (assigning reads to taxa or FGCs). 
+      The integrated pipeline was designed for shotgun metagenomic profiling, \textit{i.e.} assigning reads to taxa or FGCs. 
       It is separated into five modules (Figure \ref{Pipeline}).
       \newline
-      In the module of quality control and host removing, sequencing data quality is checked using FastQC v.0.11.5 \citep{andrews2010fastqc} and quality control is conducted by Trimmomatic v.0.39 \citep{bolger2014trimmomatic}.
+      In quality control and host removing, raw sequencing data quality is checked using FastQC v.0.11.5 \citep{andrews2010fastqc} and filtered by Trimmomatic v.0.39 \citep{bolger2014trimmomatic}. 
       Then clean reads are mapped to host genome using Bowtie2 v.2.4.2 \citep{langmead2012fast} and non-host reads are extracted by SAMtools v.1.11 \citep{li2009sequence}. 
@@
       Then fragment recruitment is conducted. 
-      A reference database comprising reference genome dataset, \textit{i.e.} genomic sequences in FASTA format and corresponding genome annotation in general feature format (gff), was constructed. 
+      A reference database is constructed and it comprises reference genome dataset, \textit{i.e.} genomic sequences in FASTA format and corresponding genome annotation in general feature format (gff).
       For each species represented by assembly, its reference genome dataset, if available, is downloaded from NCBI using its \textit{datasets} command-line tool and added to the reference database. 
@@
 
-    \subsection{Estimation of minimal sequencing depth required for metagenomic profiling}
-    The impact of sequencing depth on taxon/function diversity of metagenome was simulated by rarefaction. 
-    Diversity was measured by Hill numbers, which are calculated from inventory of relative abundances. 
-    For taxon diversity, the inventory was generated by assigning reads to species; while for function diversity, it was obtained by assigning reads to KOs. 
-    Then the rarefaction curve plotting Hill number against sequencing depth was computed, and minimal sequencing depth required for reliable extimation of diversity were given by the point where the slope of rarefaction curve drops to a cut-off value.
+    \subsection{Estimation of optimal sequencing depth required for metagenomic profiling}
+    % The impact of sequencing depth on taxon/function diversity of metagenome was simulated by rarefaction. 
+    % Diversity was measured by Hill numbers, which are calculated from inventory of relative abundances. 
+    % For taxon diversity, the inventory was generated by assigning reads to species; while for function diversity, it was obtained by assigning reads to KOs. 
+    % Then the rarefaction curve plotting Hill number against sequencing depth was computed, and optimal sequencing depth required for reliable estimation of diversity were given by the point where the slope of rarefaction curve drops to a cut-off value.
 
@@
       The asymptote of rarefaction curve as sequencing depth tends to infinity is given by Equation \ref{asymptote}. 
-      It provides an estimation of the total diversity and is comparable among metagenomic DNA samples with different sequencing depth \citep{lamas1991preliminary,soberonm1993use,hortal2004butterfly,jimenez2005determining,hortal2006evaluating}.
-      However, the accuracy of asymptotic estimators is controversial in macroecology \citep{soberonm1993use,colwell1994estimating,chazdon1998statistical,jimenez2006comparing,hortal2006evaluating}, and their performance in shotgun metagenomics is seldom evaluated.
+      It provides an estimation of the total diversity and is comparable among metagenomic DNA samples with different sequencing depth. 
+      % \citep{lamas1991preliminary,soberonm1993use,hortal2004butterfly,jimenez2005determining,hortal2006evaluating}. 
+      However, the accuracy of asymptotic estimators is controversial \citep{colwell1994estimating,chazdon1998statistical,jimenez2006comparing,hortal2006evaluating}.
       \begin{equation}
@@
 
-      \subsubsection{Estimating minimal sequencing depth using rarefaction curves} 
-      Minimal sequencing depth is defined as the point at which diversity starts to level off as sequencing depth increases, and its precise estimation via rarefaction is based on the assumption that the original dataset is sufficient for detection of almost all species/KOs present.
+      \subsubsection{Estimating optimal sequencing depth using rarefaction curves} 
+      Optimal sequencing depth is defined as the point at which diversity starts to level off as sequencing depth increases, and its precise estimation via rarefaction is based on the assumption that the original dataset is sufficient for detection of almost all species/KOs present.
       % providing a reliable inventory of species/KOs present, \textit{i.e.} almost all species/KOs present in the DNA sample are detected. 
       This assumption can be verified by looking at the rarefaction curve that plots species/KO richness (Hill number of order 0) against sequencing depth. 
-      The original dataset is sufficient for providing a reliable inventory if and only if the rarefaction curve of richness is characterized by a small final slope \citep{heck1975explicit,moreno2000assessing,hortal2004butterfly,hortal2005ed,gomez2014using}.
-      Then an estimation of minimal sequencing depth is provided by the point at which the slope of rarefaction curve decreases to a given cut-off value \citep{hortal2005ed}. 
+      The original dataset is sufficient for providing a reliable inventory if and only if the rarefaction curve of richness is characterized by a small final slope \citep{heck1975explicit,hortal2005ed,chao2012coverage}.
+      Then an estimation of optimal sequencing depth is provided by the point at which the slope of rarefaction curve decreases to a given cut-off value \citep{hortal2005ed,gomez2014using}. 
       % \newline 
@@
 
-    \subsection{Sequence reads and pipeline evaluation}
+    \subsection{Sequence reads}
     Eight samples (four honey bees, three bumble bees and one flower eDNA) were sequenced. 
@@
     Table \ref{data_statistics} reports numbers of raw, clean and non-host read pairs. 
-    Honey bee sample \textit{Bee\_Amellifera\_13\_1} was dropped for further analysis since its raw read pair number (1.10 million) is significantly lower than three other samples (about 59 million). 
+    Honey bee sample \textit{Bee\_Amellifera\_13\_1} was filtered from further analysis since its low raw read pair number (1.10 million compared to the other samples at ~59 million) is suggestive of a poor quality sample.
     After quality control, 62.08\%-76.52\% of raw read pairs were retained for these three honey bee samples. 
@@
     For flower eDNA sample, 1.44 million raw read pairs were obtained and 61.15\% of them were retained.
-    \newline
-    In integrated pipeline (Figure \ref{Pipeline}), clean non-host reads are first assembled to into contigs and assigned to taxa. 
-    To address false negative results in assembly-dependent taxon search \citep{sharon2015accurate,vollmers2017comparing}, a reference database composed of genomes of species represented by contigs is constructed.
-    Reads not aligned to the reference database are subjected to assembly-independent taxon search. 
-    The reference database and assembly-independent search helped improve species identification in all three sample types, especially in simulations of low sequencing depth (Figure \ref{CompareSensitivity}).
+
+    % \subsection{Characterization of species composition}
+    \subsection{Application of integrated pipeline}
+    The integrated pipeline was used to profile metagenomic datasets from pollination system, illustrating its capacity in presenting taxon composition and functional potentiality of microbiome. 
+    Although samples are different in proportion of host contamination (Table \ref{data_statistics}, Figure \ref{GroupAbundance}a), diverse communities composed of multiple taxonomic clades were identified (Figure \ref{GroupAbundance}b), and most species identified are common in pollination system.
+    % All seven samples were dominated by bacterial and/or arthropod species (Figure \ref{GroupAbundance}b). 
+    % Honey bee samples \textit{Bee\_Amellifers\_hv13\_2} and \textit{Bee\_Amellifera\_wild\_1} were dominated by bacteria (approximate 90\% relative abundance), while in \textit{Bee\_Amellifera\_hv15\_1}, arthropods, bacteria and viruses accounted for most annotated reads.
+    % As for bumble bee samples, they were all dominated by bacteria and arthropods. 
+    % For the flower eDNA sample, arthropods were the most dominant and bacteria were the second.
 
@@
         \end{subfigure}
-        \hspace{0.32\linewidth}
-        \begin{subfigure}
-          \centering
+        \hspace{0.5\linewidth}
+        \begin{subfigure}
           \textbf{b}
         \end{subfigure}
-        \hspace{0.32\linewidth}
-        \begin{subfigure}
-          \centering
-          \textbf{c}
-        \end{subfigure}
-        \newline
-        \hfill
-        \begin{subfigure}
-          \centering
-          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Honey.pdf}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}
-          \centering
-          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Bumble.pdf}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}
-          \centering
-          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Flower.pdf}
-        \end{subfigure}
-        \caption{Integrated pipeline improves the detection of species richness. 
-        The horizonal axis represents sequencing depth, and the vertical axis represents the ratio between number of species only detected by assembly-independent search and number of species detected by assembly-dependent search.
-        Sample type is shown in the top left of each subfigure.}
-        \label{CompareSensitivity}
-        \end{figure}
-
-    \subsection{Characterization of species composition}
-    All seven samples were dominated by bacterial and/or arthropod species (Figure \ref{GroupAbundance}b). 
-    Honey bee samples \textit{Bee\_Amellifers\_hv13\_2} and \textit{Bee\_Amellifera\_wild\_1} were dominated by bacteria (approximate 90\% relative abundance), while in \textit{Bee\_Amellifera\_hv15\_1}, arthropods, bacteria and viruses accounted for most annotated reads.
-    As for bumble bee samples, they were all dominated by bacteria and arthropods. 
-    For the flower eDNA sample, arthropods were the most dominant and bacteria were the second.
-
-      \begin{figure}[H]
-        \centering
-        \begin{subfigure}
-          \centering
-          \textbf{a}
-        \end{subfigure}
-        \newline
-        \begin{subfigure}
-          \centering
-          \includegraphics[width=0.5\textwidth]{../Figures/NonHostRatio.pdf}
-        \end{subfigure}
-        \vfill
-        \newline
-        \begin{subfigure}
-          \centering
-          \textbf{b}
-        \end{subfigure}
-        \newline
-        \begin{subfigure}
-          \centering
-          \includegraphics[width=0.5\textwidth]{../Figures/1_species_RelAbundance_GroupAbundance.pdf}
-        \end{subfigure}
-        \vfill
+        \newline
+        \hfill
+        \begin{subfigure}
+          \centering
+          \includegraphics[width=0.48\linewidth,height=0.48\linewidth]{../Figures/NonHostRatio.pdf}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}
+          \centering
+          \includegraphics[width=0.48\linewidth,height=0.48\linewidth]{../Figures/1_species_RelAbundance_GroupAbundance.pdf}
+        \end{subfigure}
+
+        % \begin{subfigure}
+        %   \centering
+        %   \textbf{a}
+        % \end{subfigure}
+        % \newline
+        % \begin{subfigure}
+        %   \centering
+        %   \includegraphics[width=0.5\textwidth]{../Figures/NonHostRatio.pdf}
+        % \end{subfigure}
+        % \vfill
+        % \newline
+        % \begin{subfigure}
+        %   \centering
+        %   \textbf{b}
+        % \end{subfigure}
+        % \newline
+        % \begin{subfigure}
+        %   \centering
+        %   \includegraphics[width=0.5\textwidth]{../Figures/1_species_RelAbundance_GroupAbundance.pdf}
+        % \end{subfigure}
+        % \vfill
         \caption{a. The number of host and non-host reads in each sample. 
@@
 
-    Figure \ref{BacteriaHeatmap} illustrates composition of bacteria, most of which are common bee-associated species within \textit{Bifidobacterium}, \textit{Frischella}, \textit{Gilliamella}, \textit{Snodgrassella} and \textit{Lactobacillus} \citep{koch2011bacterial,moran2015genomics,kwong2017dynamic}.
-    \textit{Apilactobacillus} and \textit{Bombilactobacillus} are genera separated from \textit{Lactobacillus} recently \citep{zheng2020taxonomic}. 
-    \textit{Fructobacillus} is often found in fructose-rich environments like flowers \citep{endo2014genus}. 
-    \textit{Bartonella apis} is related to animal pathogens \citep{kevsnerova2016bartonella} and is widespread in honey bee workers \citep{raymann2018role}. 
+    The present of core members of bee-associated bacterial community including species within \textit{Bifidobacterium}, \textit{Frischella}, \textit{Gilliamella}, \textit{Snodgrassella}, \textit{Lactobacillus}, \textit{Apilactobacillus} and \textit{Bombilactobacillus} (Figure \ref{BacteriaHeatmap}) \citep{koch2011bacterial,moran2015genomics,kwong2017dynamic,zheng2020taxonomic} suggests good sample quality.
+    As for other abundant bacteria, \textit{Fructobacillus sp.} are often found in fructose-rich environments like flowers \citep{endo2014genus}; \textit{Bartonella apis} is related to animal pathogens \citep{kevsnerova2016bartonella} and is widespread in honey bee workers \citep{raymann2018role}; \textit{Candidatus Schmidhempelia bombi} is a known uncultured symbiont of \textit{Bombus impatiens} \citep{martinson2014genomic}.
+    It should be noted that some typical bee-associated bacteria were also found on the flower, including \textit{Bartonella apis}, \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}.
+    % \textit{Apilactobacillus} and \textit{Bombilactobacillus} are genera separated from \textit{Lactobacillus} recently \citep{zheng2020taxonomic}.  
     % \textit{Bombiscardovia coagulans} is a member of Bifidobacteriaceae isolated from \textit{Bombus lapidarius} \citep{killer2010bombiscardovia}. 
-    % \textit{Candidatus Schmidhempelia bombi} is an uncultured symbiont of \textit{Bombus impatiens} \citep{martinson2014genomic}. 
-    % It should be noted that some typical bee-associated bacteria were found on the flower, including \textit{Bartonella apis}, \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}.
     % \newline
@@
     \newline
-    Figure \ref{ArthropodHeatmap} shows composition of arthropods, and most of them are pollinators within \textit{Apis} and \textit{Bombus}. 
+    Composition of arthropods and plants indicating interactions within pollination networks. 
+    Most arthropods identified are pollinators within \textit{Apis} and \textit{Bombus} (Figure \ref{ArthropodHeatmap}). 
     However, some of them might be considered as false positive. 
@@
     % As a result, in honey bee samples, \textit{Apis} species were rare and \textit{Bombus} species were abundant, while in bumble bee samples, \textit{Bombus} species were rare and \textit{Apis} species are abundant.
-    \newline
-    Figure \ref{PlantHeatmap} illustrates plant species, indicating foraging area of bees. 
-    Most samples were dominanted by one or two plant species, except \textit{Bee\_Amellifera\_hv13\_2}. 
-    Some crops were identified, including \textit{Brassica napus} (rape), \textit{Brassica oleracea}, \textit{Cicer arietinum} (chickpea), \textit{Glycine max} (soybean), \textit{Helianthus annuus} (sunflower), \textit{Nicotiana sylvestris} (flowering tabacco) and \textit{Raphanus sativus} (radish).
-    \newline
-    Figure \ref{FungusHeatmap} shows compositions of fungal species. 
-    \textit{Nosema ceranae}, a widespread bee pathogen, was the dominant fungal species in most samples including the flower eDNA. 
-    Three yeast species (\textit{Clavispora lusitaniae}, \textit{Saprochaete ingens} and \textit{Wickerhamiella sorbophila}) were found in bees. 
-    % Other fungal species include three yeasts (\textit{Clavispora lusitaniae}, \textit{Saprochaete ingens} and \textit{Wickerhamiella sorbophila}) 
+    As for plant species (Figure \ref{PlantHeatmap}), they indicate foraging areas of bees.
+Several crop species were identified, including \textit{Brassica napus} (rape), \textit{Brassica oleracea}, \textit{Cicer arietinum} (chickpea), \textit{Glycine max} (soybean), \textit{Helianthus annuus} (sunflower), \textit{Nicotiana sylvestris} (flowering tabacco) and \textit{Raphanus sativus} (radish).
+    \newline
+    Fungal and viruse species were identified. 
+    In fungal communities of most samples, \textit{Nosema ceranae}, a widespread bee pathogen, was the dominant species. (Figure \ref{FungusHeatmap}). 
+    Besides, three yeast species (\textit{Clavispora lusitaniae}, \textit{Saprochaete ingens} and \textit{Wickerhamiella sorbophila}) were also found in bees.  
     % and one opportunistic pathogen (\textit{Malassezia restricta}). 
-    \newline
-    Figure \ref{ViruseHeatmap} illustrates viruses identified. 
-    Several phages were identified, including \textit{Bifidobacterium phage BitterVaud1} that infects bee-commensal bacterium \textit{Bifidobacterium asteroides} \citep{bonilla2020honey}, \textit{Bacteriophage sp.} that infects \textit{Pseudomonas aeruginosa} \citep{essoh2015investigation}, an opportunistic pathogen that might contaminate bees \citep{bailey1968honey,papadopoulou1992experimental,papadopoulou1993haemocyte}, and species in Myoviridae and Siphoviridae.
-    % family Myoviridae and Siphoviridae
-    Most of the others are arthropod-associated viruses. 
-    \textit{Apis mellifera filamentous virus} and \textit{Bombus cryptarum densovirus} are bee-infecting viruses \citep{clark1978filamentous,bailey1981properties,schoonvaere2018study}. 
-    Several arthropod-infecting parvoviruses were found, including \textit{Blattodean pefuambidensovirus 1}, \textit{Hemipteran scindoambidensovirus 1}, \textit{Hymenopteran scindoambidensovirus 1} and \textit{Orthopteran scindoambidensovirus 1} \citep{penzes2020reorganizing}.
+    As for viruses, most of them are phages or arthropod-infecting species (Figure \ref{ViruseHeatmap}). 
+    Phage species include \textit{Bifidobacterium phage BitterVaud1} infecting bee-commensal bacterium \textit{Bifidobacterium asteroides} \citep{bonilla2020honey}; \textit{Bacteriophage sp.} infecting \textit{Pseudomonas aeruginosa} \citep{essoh2015investigation}, an opportunistic pathogen that might contaminate bees \citep{bailey1968honey,papadopoulou1992experimental,papadopoulou1993haemocyte}; and unclassified species within Myoviridae and Siphoviridae.
+    Listed arthropod-infecting viruses including \textit{Apis mellifera filamentous virus} and \textit{Bombus cryptarum densovirus} that infect bees; and several parvoviruses (\textit{Blattodean pefuambidensovirus 1}, \textit{Hemipteran scindoambidensovirus 1}, \textit{Hymenopteran scindoambidensovirus 1} and \textit{Orthopteran scindoambidensovirus 1}) \citep{penzes2020reorganizing}.
+    % % family Myoviridae and Siphoviridae
+    % Most of the others are arthropod-associated viruses. 
+    % \textit{Apis mellifera filamentous virus} and \textit{Bombus cryptarum densovirus} are bee-infecting viruses \citep{clark1978filamentous,bailey1981properties,schoonvaere2018study}. 
+    % Several arthropod-infecting parvoviruses were found, including \textit{Blattodean pefuambidensovirus 1}, \textit{Hemipteran scindoambidensovirus 1}, \textit{Hymenopteran scindoambidensovirus 1} and \textit{Orthopteran scindoambidensovirus 1} \citep{penzes2020reorganizing}.
 
@@
 
-    \subsection{Characterization of functional profiling}
-    In order to illustrate metabolic potentially of metagenomic samples, KEGG pathways were inferred using a parsimony approach. 
-    Reads assigned to plant and arthropod species were not involved in pathway inference. 
+    The integrated pipeline also provides information on FGC content, which shows function potentiality of metagenome. 
+    Here FGC content was represented by identified KOs, which were used for KEGG pathway inference in order to illustrate metabolic potentially of metagenomic samples. 
+    Reads assigned to plants and arthropods were not involved in pathway inference since they are unlikely to represent living organisms. 
     The coverage of a pathway was calculated by the ratio between number of annotated KOs and total number of KOs involved in that pathway. 
@@
     Here concern is given to metabolism pathways of carbonhydrates and amino acids, which are crucial for bee health. 
-    Inferred pathways indicate potential capability of metabolism of sugars including fructose, sucrose, mannose and galactose (Figure \ref{Carbohydrate}), and all essential amino acids for honey bees (Figure \ref{AminoAcid})\citep{groot1953protein}.
+    Inferred pathways indicate potential capability of metabolism of sugars including fructose, sucrose, mannose and galactose (Figure \ref{Carbohydrate}), and all ten essential amino acids for honey bees (\textit{i.e.} arginine, histidine, isoleucine, leucine, lysine, methionine, phenylalanine, threonine, tryptophan and valine) (Figure \ref{AminoAcid}) \citep{groot1953protein}.
+
+    \subsection{Evaluation of performance of integrated pipeline in species identification}
+    The performance of integrated pipeline in species identification was evaluated by comparing it with assembly-dependent method, using rarefied datasets. 
+    In integrated pipeline (Figure \ref{Pipeline}), clean non-host reads are first assembled to into contigs and assigned to taxa. 
+    % To address false negative results in assembly-dependent taxon search \citep{sharon2015accurate,vollmers2017comparing}, 
+    Then a reference database composed of genomes of assembly-represented species is constructed. 
+    Reads not aligned to the reference database are subjected to assembly-independent taxon search. 
+    The reference database and assembly-independent search helped improve species identification in all three sample types, especially in simulations of low sequencing depth (Figure \ref{CompareSensitivity}).
 
       \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.8\textwidth]{../Figures/PathwayCov_AminoAcid.pdf}
-        \caption{Heatmaps for pathways of amino acid metabolism.}
-        \label{AminoAcid}
+        \begin{subfigure}
+          \centering
+          \textbf{a}
+        \end{subfigure}
+        \hspace{0.32\linewidth}
+        \begin{subfigure}
+          \centering
+          \textbf{b}
+        \end{subfigure}
+        \hspace{0.32\linewidth}
+        \begin{subfigure}
+          \centering
+          \textbf{c}
+        \end{subfigure}
+        \newline
+        \hfill
+        \begin{subfigure}
+          \centering
+          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Honey.pdf}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}
+          \centering
+          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Bumble.pdf}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}
+          \centering
+          \includegraphics[width=0.3\linewidth,height=0.3\linewidth]{../Figures/ExtraSpecies_Flower.pdf}
+        \end{subfigure}
+        \caption{Integrated pipeline improves the detection of species richness. 
+        The horizonal axis represents sequencing depth, and the vertical axis represents growth rate of detected species richness comparing the integrated pipeline and assembly-dependent species identification.
+        Different sequencing depth was simulated by rarefaction.
+        % the ratio between number of novel species detected by assembly-independent search and number of species detected by assembly-dependent search. 
+        Sample type is shown in the top left of each subfigure.}
+        \label{CompareSensitivity}
         \end{figure}
 
-    \subsection{Minimal sequencing depth required for detection of species and function diversity}
-    In order to estimate minimal sequencing depth for combinations of sample type (honey bee, bumble bee and flower eDNA) and study type (species profiling and function profiling), shallow sequencing was simulated by rarefaction.
-    The relationship between sequencing depth (clean read pairs) and species/KO diversity (Hill numbers of order 0, 1, 2) was quantified by fitting and averaging asymptotic species accumulation models.
-    The asymptote of the model provides an estimation of total diversity and its slope reflects the increase rate of diversity. 
-    Minimal sequencing depth was estimated by the point at wich the slope of the rarefaction curve drops to a cut-off value.
+    \subsection{Optimal sequencing depth required for detection of species and function diversity}
+    In order to determine the influence of sequencing depth and thus optimize sequencing depth for 
+    analysing taxonomic and functional diversity, rarefactiona anlysis was conducted. 
+    Different sequencing depth was simulated by randomly subsampling original datasets at proportions from 10\% to 90\% at an interval of 10\%. 
+    The relationship between sequencing depth (clean read pair number) and species/KO diversity (Hill numbers of order 0, 1, 2) was quantified by fitting and averaging asymptotic species accumulation models.
+    The slope of the model reflects the increase rate of diversity. 
+    The point at which it drops to a cut-off value provides an estimation of optimal sequencing depth. 
+    Besides, the asymptote of the model as sequencing depth tends to infinity provides an estimation of total diversity. 
     \newline
@@
     As for function diversity rarefaction, the final slopes of all KO richness rarefaction curves are higher than 15, indicating no dataset can providing an almost complete inventory of KOs. 
-    Thus, estimation of minimal sequencing depth was conducted for the combinations of two sample types (honey bee and bumble bee) and one study type (species profiling), based on five datasets (two honey bees and three bumble bees).
+    Thus, estimation of optimal sequencing depth was conducted for the combinations of two sample types (honey bee and bumble bee) and one study type (species profiling), based on five datasets (two honey bees and three bumble bees).
     \begin{figure}[H]
@@
 
-    Minimal sequencing depth is estimated by the point at which the slope of rarefaction curve drops to a cut-off value. 
-    Table \ref{MinDepth} summarizes estimations of minimal sequencing depth for detection of species diversity, using 0.5, 0.1, 0.05 and 0.01 as cut-off values.  
+    Optimal sequencing depth is estimated by the point at which the slope of rarefaction curve drops to a cut-off value. 
+    Table \ref{MinDepth} summarizes estimations of optimal sequencing depth for detection of species diversity, using 0.5, 0.1, 0.05 and 0.01 as cut-off values.  
     When order $q$ of Hill number equals 0, \textit{i.e.} species abundances are not considered, cut-off value of 0.1 for slope of rarefaction curve is sufficient for providing completeness $> 97\%$ in all samples.
-    The average minimal sequencing depth are 40.33 million for honey bees and 42.49 million for bumble bees. 
+    The average optimal sequencing depth are 40.33 million for honey bees and 42.49 million for bumble bees. 
     When species abundances are considered (order $q$ equals 1 or 2), cut-off value of 0.01 can provide completeness $> 95\%$ in most pairs of sample and $q$ value. 
-    For honey bees, the average minimal sequencing depth are 18.57 million ($q = 1$) and 17.45 million ($q = 2$). 
-    For bumble bee samples, the average minimal sequencing depth are 40.33 million ($q = 1$) and 24.77 million ($q = 2$). 
+    For honey bees, the average optimal sequencing depth are 18.57 million ($q = 1$) and 17.45 million ($q = 2$). 
+    For bumble bee samples, the average optimal sequencing depth are 40.33 million ($q = 1$) and 24.77 million ($q = 2$). 
       \begin{table}[H]
@@
 \section{Discussion}
-Shotgun metagenomics provides powerful tools for microbiome investigations, yet its utilization is hindered by bioinformatical challenges and high cost of deep sequencing. 
-Here, I constructed an integrated pipeline, which combines assembly-dependent and -independent profiling methods to help detect species richness and profiled real metagenomic datasets from honey bees, bumble bees and flower surface.
-Then I simulated the relationship between species/KO diversity measured by Hill numbers (order $q = 0, 1, 2$) and sequencing depth measured by clean read pair ($2 \times 150$ bp) number. 
-It is showed that to detect species diversity, the average minimal sequencing depth for honey bee samples are 40.33 million ($q = 0$), 18.57 million ($q = 1$) and 17.45 million ($q = 2$); for bumble bee samples, the averages are 42.49 million ($q = 0$), 40.33 million ($q = 1$) and 24.77 million ($q = 2$); and for flower surface, more than 0.88 million sequencing depth is needed.
-As for function diversity, no datasets in this project is sufficient for providing an almost complete inventory of KOs, indicating deeper sequencing is needed, \textit{i.e.} sequencing depth need to be higher than 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
-Additionally, bee symbionts and pathogens were found on the flower eDNA sample, and pathway inference indicates that bee-associated microbiome may have capability of metabolizing amino acids that are essential for host.
-\newline
-% High throughput sequencing provides approaches including amplicon sequencing and shotgun metagenomics for investigations of bee-associated microbiome, which imposes significant impact on bee health \citep{engel2016bee,raymann2018role,bonilla2018functional}.
-% a crucial issue receiving increasing concern \citep{breeze2011pollination,hristov2020significance}. 
-Shotgun metagenomics provides unique advantages over amplicon sequencing, which is vastly used in bee microbiome investigations (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}).
-In amplicon sequencing, a species-specific barcode region is amplified and sequenced \citep{abdelfattah2018metabarcoding}. 
-Since it captures a small region of the whole genome, amplicon sequencing dataset is relatively small in size, which makes it low-cost both economically and computationally. 
-Besides, comprehensive and streamlined softwares for amplicon sequencing analysis are available, including QIIME \citep{bolyen2019reproducible}, Mothur \citep{schloss2020reintroducing} and VSEARCH \citep{rognes2016vsearch}.
-However, a single amplicon sequencing dataset does not represent all taxa in the community since different barcode region is used for identification of different taxonomic group, \textit{e.g.} 
-16S ribosomal RNA (rRNA) for bacteria \citep{hayashi2002phylogenetic,eckburg2005diversity}, 
-internal transcribed spacer (ITS) for fungi \citep{nilsson2008intraspecific}, 
-cytochrome c oxidase subunit I (COI) for Animalia \citep{hebert2003barcoding} 
-and plastid genes for plants \citep{group2009dna}. 
-Besides, it does not provide information on FGCs. 
-Metabolic capacity of microbiome need to be inferred based on reference genomes \Citep{asshauer2015tax4fun,douglas2018predicting}. 
-Shotgun metagenomics provides an alternative to overcome these drawbacks by capturing and sequencing DNA in a sample unselectively. 
-It is capable of representing all taxonomic groups and providing information on FGC composition. 
-\newline
-The advantages of shotgun metagenomics over amplicon sequencing are valuable for investigations in bee-associated microbiome for two reasons. 
-First, bees vist numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including plants, arthropods, bacteria and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
-These materials represent a diverse assemblage which is difficult to be profiled comprehensively via amplicon sequencing. 
-Besides, bee bacterial symbionts are diversified at strain level \citep{engel2012functional,powell2016strain,ellegaard2020vast}. 
-Bacterial strains are often highly variable in gene content \citep{cordero2014explaining,brockhurst2019ecology}, and thus different in metabolic capacity. 
-However, resolving strain-level diversity by species-specific region is difficult \citep{rodriguez2018much,ciufo2018using,olm2020consistent}, and no information on gene content is provided by amplicon sequencing.
-Based on these considerations, shotgun metagenomics provides valuable tools for bee microbiome investigations. 
-However, utilization of shotgun metagenomics is hindered by unique challenges. 
-First, there is not a golden standard for bioinformatics of metagenomic annotation pipeline to provide abundances of taxa and FGCs. 
-Second, shotgun metagenomics is often associated with high cost since it captures a big proportion of microbial genomes. 
-\newline
-The integrated pipeline for taxonomic and functional profiling of metagenomic dataset provides several advantages. 
+% Shotgun metagenomics provides powerful tools for microbiome investigations, yet its utilization is hindered by bioinformatical challenges and high cost of deep sequencing. 
+Here, I constructed an integrated pipeline combining assembly-dependent and -independent methods for taxonomic and functional profiling of shotgun metagenomics, and applied it to analysis of metagenomes from honey bees, bumble bees and flower washes.
+The profiling results showed that the integrated pipeline is able to capture taxonomic diversity by identifying species from multiple clades and infer metabolic potentiality of metagenome by providing information on FGC content.
+It can be more sensitive in species identification compared with standard assembly-dependent methods. 
+Then I computed expected species/FGC diversity represented by given sequencing depth through rarefaction analysis, in order to optimize sequencing depth to balance cost and reliability of analysis results.
+Optimal sequencing depth differs by types of samples and investigations. 
+For estimation of species diversity, sequencing depth can be optimized especially when low leverage is given to rare species. 
+As for functional profiling, deeper sequencing depth is required.  
+% Then I simulated the relationship between species/KO diversity measured by Hill numbers (order $q = 0, 1, 2$) and sequencing depth measured by clean read pair ($2 \times 150$ bp) number. 
+% It is showed that to detect species diversity, the average minimal sequencing depth for honey bee samples are 40.33 million ($q = 0$), 18.57 million ($q = 1$) and 17.45 million ($q = 2$); for bumble bee samples, the averages are 42.49 million ($q = 0$), 40.33 million ($q = 1$) and 24.77 million ($q = 2$); and for flower surface, more than 0.88 million sequencing depth is needed.
+% As for function diversity, no datasets in this project is sufficient for providing an almost complete inventory of KOs, indicating deeper sequencing is needed, \textit{i.e.} sequencing depth need to be higher than 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
+% Additionally, bee symbionts and pathogens were found on the flower eDNA sample, and pathway inference indicates that bee-associated microbiome may have capability of metabolizing amino acids that are essential for host.
+\newline
+The integrated pipeline (Figure \ref{Pipeline}) for taxonomic and functional profiling of metagenome provides several advantages. 
 First, through combination with assembly-free taxon search, it helps solve high false negative rate associated with assembly-dependent species identification, which is caused by reads left unassembled.
@@
 For example, BWA aligner \citep{li2009fast} serves as an alternative for Bowtie2, and SPAdes can be replaced by other metagenomic assemblers such as Megahit \citep{li2015megahit} and IDBA-UD \citep{peng2012idba}.
-Third, the output files generated by each step are recorded and can be inspected easily, which is important for troubleshooting. 
-\newline
-Determination of sequencing depth is important for shotgun metagenomics since insufficient sequencing causes underestimation of taxonomic/functional diversity \citep{cattonaro2018you,zaheer2018impact,gweon2019impact,pereira2019impact}, while deep sequencing is of high cost.
-Here, expected species/KO diversity provided by given sequencing depth was estimated by rarefaction and model fitting, using datasets from honey bees, bumble bees and flower surface. 
+Third, the output files generated by each step are recorded and can be inspected easily, which provides transparence for troubleshooting. 
+However, the performance of integrated pipeline need to be evaluated more comprehensively by analysis of mock datasets and comparison with other profiling strategies. 
+Standardized mock dataset can be used to benchmark sensitivity and accuracy of integrated pipeline since it is an artificial metagenome with predefined diversity, generated by combining known sequences from different species \citep{vollmers2017comparing,sczyrba2017critical,becker2020modular}.
+Besides, the performance of integrated pipeline need to be compared with other widely used analysis strategies, such as MG-RAST \citep{meyer2008metagenomics}, SqueezeMeta \citep{tamames2019squeezemeta} and Kraken \citep{wood2014kraken}.
+% High throughput sequencing provides approaches including amplicon sequencing and shotgun metagenomics for investigations of bee-associated microbiome, which imposes significant impact on bee health \citep{engel2016bee,raymann2018role,bonilla2018functional}.
+% a crucial issue receiving increasing concern \citep{breeze2011pollination,hristov2020significance}. 
+% Shotgun metagenomics provides unique advantages over amplicon sequencing, which is vastly used in bee microbiome investigations (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}).
+% In amplicon sequencing, a species-specific barcode region is amplified and sequenced \citep{abdelfattah2018metabarcoding}. 
+% Since it captures a small region of the whole genome, amplicon sequencing dataset is relatively small in size, which makes it low-cost both economically and computationally. 
+% Besides, comprehensive and streamlined softwares for amplicon sequencing analysis are available, including QIIME \citep{bolyen2019reproducible}, Mothur \citep{schloss2020reintroducing} and VSEARCH \citep{rognes2016vsearch}.
+% However, a single amplicon sequencing dataset does not represent all taxa in the community since different barcode region is used for identification of different taxonomic group, \textit{e.g.} 
+% 16S ribosomal RNA (rRNA) for bacteria \citep{hayashi2002phylogenetic,eckburg2005diversity}, 
+% internal transcribed spacer (ITS) for fungi \citep{nilsson2008intraspecific}, 
+% cytochrome c oxidase subunit I (COI) for Animalia \citep{hebert2003barcoding} 
+% and plastid genes for plants \citep{group2009dna}. 
+% Besides, it does not provide information on FGCs. 
+% Metabolic capacity of microbiome need to be inferred based on reference genomes \Citep{asshauer2015tax4fun,douglas2018predicting}. 
+% Shotgun metagenomics provides an alternative to overcome these drawbacks by capturing and sequencing DNA in a sample unselectively. 
+% It is capable of representing all taxonomic groups and providing information on FGC composition. 
+% \newline
+% The advantages of shotgun metagenomics over amplicon sequencing are valuable for investigations in bee-associated microbiome for two reasons. 
+% First, bees vist numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including plants, arthropods, bacteria and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
+% These materials represent a diverse assemblage which is difficult to be profiled comprehensively via amplicon sequencing. 
+% Besides, bee bacterial symbionts are diversified at strain level \citep{engel2012functional,powell2016strain,ellegaard2020vast}. 
+% Bacterial strains are often highly variable in gene content \citep{cordero2014explaining,brockhurst2019ecology}, and thus different in metabolic capacity. 
+% However, resolving strain-level diversity by species-specific region is difficult \citep{rodriguez2018much,ciufo2018using,olm2020consistent}, and no information on gene content is provided by amplicon sequencing.
+% Based on these considerations, shotgun metagenomics provides valuable tools for bee microbiome investigations. 
+% However, utilization of shotgun metagenomics is hindered by unique challenges. 
+% First, there is not a golden standard for bioinformatics of metagenomic annotation pipeline to provide abundances of taxa and FGCs. 
+% Second, shotgun metagenomics is often associated with high cost since it captures a big proportion of microbial genomes. 
+\newline
+The integrated pipeline was used to analyze metagenomes of bees and flower washes, illustrating their taxon composition and metabolic potentiality. 
+Bee-associated microorganisms were identified in flower washes, including both pathogens (\textit{e.g.} \textit{Nosema ceranae} and \textit{Apis mellifera filamentous virus}) and symbionts (\textit{e.g.} \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}) (Figure \ref{BacteriaHeatmap}, \ref{FungusHeatmap} and \ref{ViruseHeatmap}).
+Flowers have been indicated as hubs for transmission of bee pathogens \cite{durrer1994shared,koch2017role}. 
+Through shared flower use, multiple pathogens transmit between pollinators, including \textit{Nosema ceranae} \citep{furst2014disease} and \textit{Crithidia bombi} \citep{figueroa2019bee}. 
+There is also growing evidence for present of bee symbionts on flower \citep{mcfrederick2012environment,mcfrederick2017flowers,keller2020more,vannette2020floral}.
+However, its role in bee microbiome assembly and functional importance in pollination remains an open question \citep{keller2020more,vannette2020floral}. 
+As for function profiling, it is indicated that bee-associated microbiome is capable of metabolizing carbohydrates such as glucose, fructose, sucrose and mannose (Figure \ref{Carbohydrate}). 
+Carbohydrates are main component of bee diet and microbiome-mediated carbohydrate-processing have been vastly investigated \citep{engel2012functional,lee2015saccharide,lee2018differential,taylor2019effect}.
+Besides, pathways for metabolism of all ten essential amino acids for honey bees \citep{groot1953protein} were inferred (Figure \ref{AminoAcid}). 
+Essential amino acids are crucial for bee health \citep{simcock2014single,paoli2014dietary,stabler2015nutrient,hendriksma2019effects} and influence feeding preference due to their potential deficiency in single pollen source \citep{cook2003honey,hendriksma2014amino,hendriksma2016honey}.
+Whether bee-associated microbiome influences host health by providing amino acids need to be further investigated. 
+% deficiency of arginine in dandelion \citep{herbert1970brood} and histidine in corn \citep{hocherl2012evaluation}.
+\newline
+Optimization of sequencing depth is important for shotgun metagenomics since insufficient sequencing causes underestimation of taxonomic/functional diversity \citep{cattonaro2018you,zaheer2018impact,gweon2019impact,pereira2019impact}, while deep sequencing is of high cost.
+Here, expected species/KO diversity provided by given sequencing depth was estimated by rarefaction and model fitting, using datasets from honey bees, bumble bees and flower washes. 
 It was shown that increasing sequencing depth boosted identification of species/KO (Figure \ref{RichnessAccumulation}, Table \ref{RichnessModelSlope}), highlighting value of deep metagenomic sequencing.
@@
 Therefore, when dealing with function potentiality of microbiome associated with bees or flowers, retrieving as many reads as possible would be recommended. 
-As for species profiling, although deep sequencing is still valuable, optimization of sequencing depth can be made when the budget is limited (Table \ref{MinDepth}). 
-For honey bees, approximate 40 million sequencing depth can be sufficient for representing species richness. 
-When assessing biodiversity by Hill numbers of order 1 (Equation \ref{HillShannon}) or 2 (Equation \ref{HillSimpson}), 17-19 million sequencing depth can provide robust estimation. 
-As for bumble bees, about 40-43 million sequencing depth can provide reliable estimation for Hill numbers of order 0 (richness) or 1, and about 25 million sequencing depth can be sufficient for representing biodiversity measured by Hill number of order 2.
-\newline
-Additionally, the results of metagenomic profiling indicate overlap between microbiome of bees and flowers, and provide evidence on potentiality of bee microbiome in metabolism of carbonhydrates and amino acids.
-In the flower eDNA sample, bee-associated microorganisms were identified, including both pathogens (\textit{e.g.} \textit{Nosema ceranae} and \textit{Apis mellifera filamentous virus}) and typical bee symbionts (\textit{e.g.} \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}) (Figure \ref{BacteriaHeatmap}, \ref{FungusHeatmap} and \ref{ViruseHeatmap}).
-Shared microbiome between bees and flowers is revealed by growing evidence, although its role in pollination system remains an open question \citep{keller2020more,vannette2020floral}. 
-As for function profiling, it is indicated that bee-associated microbiome is capable of metabolizing carbohydrates such as glucose, fructose, sucrose and mannose (Figure \ref{Carbohydrate}). 
-Carbohydrates are main component of bee diet and microbiome-mediated carbohydrate-processing have been vastly investigated \citep{engel2012functional,lee2015saccharide,lee2018differential,taylor2019effect}.
-Besides, pathways for metabolism of all ten essential amino acids for honey bees (arginine, histidine, isoleucine, leucine, lysine, methionine, phenylalanine, threonine, tryptophan and valine) \citep{groot1953protein} were inferred (Figure \ref{AminoAcid}).
-Essential amino acids are crucial for bee health \citep{simcock2014single,paoli2014dietary,stabler2015nutrient,hendriksma2019effects} and influence feeding preference due to their potential deficiency in single pollen source \citep{cook2003honey,hendriksma2014amino,hendriksma2016honey}.
-Whether bee-associated microbiome influences host health by providing amino acids need to be further investigated. 
-% deficiency of arginine in dandelion \citep{herbert1970brood} and histidine in corn \citep{hocherl2012evaluation}.
-\newline
-There are several limitations of this project. 
-First, the integrated pipeline need to be evaluated more comprehensively. 
-Mock metagenomic datasets of different diversity can be used to evaluate sensitivity and accuracy of integrated pipeline and its performance need to be compared with other profiling methods. 
-Second, the efficacy of estimation of minimal sequencing depth required for different environmental types is reduced by limited number of samples. 
+As for species profiling, although deep sequencing is still valuable, sequencing depth can be optimized when the budget is limited (Table \ref{MinDepth}), especially when low leverage is given to rare species.
+For honey bees, approximate 40 million sequencing depth (12 Gbp) can be sufficient for representing species richness. 
+When assessing biodiversity with reduced emphasis on rare species, 17-19 million sequencing depth (5.1-5.7 Gbp) can provide robust estimation. 
+As for bumble bees, about 40-43 million sequencing depth (12-12.9 Gbp) can provide reliable estimation for species richness and diversity index with emphasis on species of general abundance, and about 25 (7.5 Gbp) million sequencing depth can be sufficient for estimation of biodiversity with high leverage on abundant species.
+It should be noted that the efficacy of optimal sequencing depth estimation is reduced by limited number of samples. 
 Here, honey bee and bumble bee associated microbiome was represented by only three samples, and there was only one sample of flower eDNA. 
 However, microbiomes of pollination system are highly dynamic and variable in diversity. 
-To generate reliable guideline for sufficient sequencing depth, more samples need to be evolved. 
-Third, there is a lack of repeat in sequencing depth subsampling. 
-Repeated subsampling boosts precise computation of rarefaction curve and increases accuracy of estimation of minimal sequencing depth. 
-\newline
-Oerall, I constructed an integrated pipeline, combining assembly-dependent and -free methods for metagenomic profiling. 
-The pipeline was used for profiling metagenomic datasets ($2 \times 150 bp$ read pairs) from pollination system. 
-Then I conducted rarefaction analysis, computing expected species/KO diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to determine minimal sequencing depth capable of reliably estimating diversity.
-It was shown that functional profiling is demanding about sequencing effort. 
-Sequencing depth of 45.06 million (13.52 Gbp) for honey bees, 53.61 million (16.08 Gbp) for bumble bees and 0.88 million (0.26 Gbp) for flower surface were not sufficient for providing almost complete inventories of KOs.
-For species diversity of order 0, 1 and 2, the average minimal sequencing depth for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million.
-As for species profiling of flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
-These results are helpful for applying shotgun metagenomics to pollination system investigations in an cost-effective way. 
-The integrated pipeline and the framework for rarefaction analysis can be used for researches on other environments.
+To generate reliable guideline for sequencing depth optimization, more samples need to be evolved. 
+Besides, there is a lack of repeat in sequencing depth subsampling. 
+Repeated subsampling boosts precise computation of rarefaction curve and increases accuracy of estimation of optimal sequencing depth.
+
+\section{Conclusion}
+Shotgun metagenomics is capable of illustrating diversity of multiple taxonomic clades and gene content, and thus provides unique advantages over vastly used amplicon sequencing, particularly for investigations of highly diverse microbial communities.
+However, utilization of shotgun metagenomics is hindered by challenges in data analysis and high cost of sequencing. 
+Here, I constructed an integrated pipeline for analysis of shotgun metagenomic data. 
+It provides benefits in terms of results, flexibility and transparence. 
+% The pipeline was used for profiling metagenomic datasets from pollination system. 
+I also constructed a framework for optimizing depth of shotgun metagenomic sequencing in order to balance high cost of sequencing and reliability of analysis results. 
+The pipeline and the framework were used for analysis of real datasets from pollination system, providing guidelines for cost-effective metagenomic investigations of bee- and flower-associated microbiomes.
+% Then I conducted rarefaction analysis, computing expected species/KO diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to optimize sequencing depth for balancing cost and reliable estimation of diversity.
+% It was shown that functional profiling is demanding about sequencing effort and obtaining as many sequencing reads as possible would be recommended. 
+% For taxonomic profiling, deep sequencing is still valuable but sequencing depth can be optimized, especially when little emphasis is given to rare taxa. 
+% Sequencing depth of 45.06 million (13.52 Gbp) for honey bees, 53.61 million (16.08 Gbp) for bumble bees and 0.88 million (0.26 Gbp) for flower surface were not sufficient for providing almost complete inventories of KOs.
+% For species diversity of order 0, 1 and 2, the average minimal sequencing depth for honey bee samples are 40.33 million (12.10 Gbp), 18.57 million (5.57 Gbp) and 17.45 million (5.24 Gbp), respectively; for bumble bee samples, the averages are 42.49 million (12.75 Gbp), 40.33 million (12.10 Gbp) and 24.77 (7.43 Gbp) million.
+% As for species profiling of flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
+% These results are helpful for applying shotgun metagenomics to pollination system investigations in an cost-effective way. 
+% The integrated pipeline and the framework for rarefaction analysis can be used for researches on other environments.
 
@@
 \section{Data and Code Availability}
+% Personal access token:
+% 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
+Scripts used for the analyses are available at \href{https://github.com/CongLiu37/CMEECourseWork/tree/main/MResProject}{github}. 
+Metagenomic datasets involved in this project cannot be made available publicly since they are yet to be formally published.
 
@@
     \label{HostRemove}
-    Quality control was conducted to reduce compromise from low quality reads.
-    Data quality was checked using FastQC v.0.11.5 \citep{andrews2010fastqc} before filtering. 
+    Raw data quality control was conducted to reduce compromise from low quality reads.
+    Raw data quality was checked using FastQC v.0.11.5 \citep{andrews2010fastqc} before filtering. 
     FastQC reports of raw reads showed the following aspects need to be covered in quality control: (1) low base quality in 3'-end (Figure \ref{QC}a); (2) uneven base content in 5'-end (Figure \ref{QC}c) and (3) the present of Nextera adaptors (Figure \ref{QC}e).
-    Therefore, quality control was conducted using Trimmomatic v.0.39 \citep{bolger2014trimmomatic}, which (1) trimmed adaptors; (2) cutted 15 bases from the 5'-ends of reads; (3) cutted bases off from 3'-ends of reads if Phred-33 quality is below 20; (4) dropped reads shorter than 50 bp; (5) dropped reads if average Phred-33 quality is below 20.
+    Therefore, raw reads were filtered using Trimmomatic v.0.39 \citep{bolger2014trimmomatic}, which (1) trimmed adaptors; (2) cutted 15 bases from the 5'-ends of reads; (3) cutted bases off from 3'-ends of reads if Phred-33 quality is below 20; (4) dropped reads shorter than 50 bp; (5) dropped reads if average Phred-33 quality is below 20.
     Then unpaired reads were removed and quality of clean data was checked using FastQC (Figure \ref{QC}d, \ref{QC}e, \ref{QC}f).
@@
     Sequences were searched against eggNOG database \citep{huerta2019eggnog} for best seed orthologs using DIAMOND and fine-grained orthology assignments were retrieved from pre-computed eggNOG phylogenetic trees.
-    Then functional descriptions of retrieved orthologs including Gene Ontology (GO) terms \citep{gene2004gene}, KOs, Enzyme Commission (EC) numbers \cite{webb1992enzyme}, Carbohydrate-Active Enzymes (CAZy) terms \cite{cantarel2009carbohydrate} and Clusters of Orthologous Groups (COG) functional categories \cite{tatusov2000cog} were transferred to query sequences.
+    Then functional descriptions of retrieved orthologs including Gene Ontology (GO) terms \citep{gene2004gene}, KOs, Enzyme Commission (EC) numbers \citep{webb1992enzyme}, Carbohydrate-Active Enzymes (CAZy) terms \citep{cantarel2009carbohydrate} and Clusters of Orthologous Groups (COG) functional categories \citep{tatusov2000cog} were transferred to query sequences.
 
@@
     \centering
-    \caption{Basic statistics of sequenced read pairs. 
-    Data in "Clean" considers as background the numbers of raw read pairs ("Raw"), while data in "Non-host" considers as background the numbers of clean read pairs ("Clean").}
+    \caption{Statistics of sequenced read pairs.}
     \label{data_statistics}
@@
     \toprule
-    Sample                           &Host                     &Raw    &Clean (\%)&Non-host (\%) \\ \midrule
-    \textit{Bee\_Amellifera\_hv13\_1}&\textit{Apis mellifera}  &1104861&842095 (76.22\%)&665507 (79.03\%) \\
-    \textit{Bee\_Amellifera\_hv13\_2}&\textit{Apis mellifera}  &56836899&35282101 (62.08\%)&10413704 (29.52\%) \\
-    \textit{Bee\_Amellifera\_hv15\_1}&\textit{Apis mellifera}  &63159968&45059211 (71.34\%)&38837759 (86.19\%) \\
-    \textit{Bee\_Amellifera\_wild\_1}&\textit{Apis mellifera}  &58113227&44466776 (76.52\%)&17014144 (38.26\%) \\
-    \textit{Bee\_Bimpatiens\_hv3\_1} &\textit{Bombus impatiens}&63973750&53612702 (83.80\%)&5300592 (9.89\%) \\
-    \textit{Bee\_Bimpatiens\_hv4\_1} &\textit{Bombus impatiens}&58988182&48426748 (82.10\%)&3557052 (7.35\%) \\
-    \textit{Bee\_Bimpatiens\_hv4\_2}&\textit{Bombus impatiens} &54955553&45805759 (83.35\%)&4618023 (10.08\%) \\
-    \textit{Flower\_eDNA}           &None                      &1443107&882436 (61.15\%)&882436 (100\%) \\
+    Sample                           &Host                     &Raw read pair   &\makecell[c]{Clean read pair\\\left[percentage\ of\ raw\ read\ pair\right]}&\makecell[c]{Non-host read pair\\\left[percentage\ of\ clean\ read\ pair]} \\ \midrule
+    \textit{Bee\_Amellifera\_hv15\_1}&\textit{Apis mellifera}  &63159968&45059211 \left[71.34\%\right]&38837759 \left[86.19\%\right] \\
+    \textit{Bee\_Amellifera\_wild\_1}&\textit{Apis mellifera}  &58113227&44466776 \left[76.52\%\right]&17014144 \left[38.26\%\right] \\
+    \textit{Bee\_Amellifera\_hv13\_2}&\textit{Apis mellifera}  &56836899&35282101 \left[62.08\%\right]&10413704 \left[29.52\%\right] \\
+    \textit{Bee\_Amellifera\_hv13\_1}&\textit{Apis mellifera}  &1104861&842095 \left[76.22\%\right]&665507 \left[79.03\%\right] \\
+    \textit{Bee\_Bimpatiens\_hv3\_1} &\textit{Bombus impatiens}&63973750&53612702 \left[83.80\%\right]&5300592 \left[9.89\%\right] \\
+    \textit{Bee\_Bimpatiens\_hv4\_1} &\textit{Bombus impatiens}&58988182&48426748 \left[82.10\%\right]&3557052 \left[7.35\%\right] \\
+    \textit{Bee\_Bimpatiens\_hv4\_2}&\textit{Bombus impatiens} &54955553&45805759 \left[83.35\%\right]&4618023 \left[10.08\%\right] \\
+    \textit{Flower\_eDNA}           &None                      &1443107&882436 \left[61.15\%\right]&882436 \left[100\%\right] \\
     \bottomrule
@@
 
-  \subsection{Inferred carbohydrate metabolism pathways}
+  \subsection{Inferred pathways of carbohydrate and amino acid metabolism}
   \begin{figure}[H]
@@
 
+    \begin{figure}[H]
+      \centering
+      \includegraphics[width=0.8\textwidth]{../Figures/PathwayCov_AminoAcid.pdf}
+      \caption{Heatmaps for pathways of amino acid metabolism.}
+      \label{AminoAcid}
+      \end{figure}
+
   \newpage

### 2021-08-23 Code/CompareSensitivity.R

@@ -1,0 +1,89 @@
+library(ggplot2)
+
+HillDiversity = read.table("Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
+
+LF_F18 = subset(HillDiversity,HillDiversity$Sample=="LF_F18")
+PGcomcol3_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol3_Bimp")
+PGcomcol4a_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4a_Bimp")
+PGcomcol4b_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4b_Bimp")
+PGnos_high_hv13_1 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-1")
+PGnos_high_hv13_2 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-2")
+PGnos_inter_hv15 = subset(HillDiversity,HillDiversity$Sample=="PGnos_inter_hv15")
+PGpollen_fresh = subset(HillDiversity,HillDiversity$Sample=="PGpollen_fresh")
+
+pdf("ExtraSpecies_Bumble.pdf")
+p1 = ggplot()+
+  geom_point(size=4,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
+                         y=(PGcomcol3_Bimp$SpeciesRichness-PGcomcol3_Bimp$AssemblySpeciesRichness)/PGcomcol3_Bimp$AssemblySpeciesRichness,
+                         colour="PGcomcol3_Bimp")))+
+  geom_point(size=4,(aes(x=PGcomcol4a_Bimp$CleanRead*PGcomcol4a_Bimp$SubsamplePercent/1e+6,
+                         y=(PGcomcol4a_Bimp$SpeciesRichness-PGcomcol4a_Bimp$AssemblySpeciesRichness)/PGcomcol4a_Bimp$AssemblySpeciesRichness,
+                         colour="PGcomcol4a_Bimp")))+
+  geom_point(size=4,(aes(x=PGcomcol4b_Bimp$CleanRead*PGcomcol4b_Bimp$SubsamplePercent/1e+6,
[…]

### 2021-08-23 Code/ComputeDiversity.py

@@ -1,0 +1,116 @@
+import os
+import re
+import sys
+import pandas as pd
+import numpy as np
+import math
+e = math.e
+
+Type = sys.argv[1] # Taxon/Function
+# Sample names
+samples = ["LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh"]
+
+# Rarefaction percentage
+percent = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1]
+
+# Sample name to raw read number
+RawReadCount = {"LF_F18":1443107,"PGcomcol3_Bimp":63973750,"PGcomcol4a_Bimp":58988182,"PGcomcol4b_Bimp":54955553,"PGnos_high_hv13-1":1104861,"PGnos_high_hv13-2":56836899,"PGnos_inter_hv15":63159968,"PGpollen_fresh":58113227}
+
+# Sample name to clean read number
+CleanReadCount = {"LF_F18":882436,"PGcomcol3_Bimp":53612702,"PGcomcol4a_Bimp":48426748,"PGcomcol4b_Bimp":45805759,"PGnos_high_hv13-1":842095,"PGnos_high_hv13-2":35282101,"PGnos_inter_hv15":45059211,"PGpollen_fresh":44466776}
+
+# Sample name to metagenomic (non-host) read number
+MetagenomicReadCount = {"LF_F18":882436,"PGcomcol3_Bimp":5300592,"PGcomcol4a_Bimp":3557052,"PGcomcol4b_Bimp":4618023,"PGnos_high_hv13-1":665507,"PGnos_high_hv13-2":10413704,"PGnos_inter_hv15":38837759,"PGpollen_fresh":17014144}
+
+def HillDiversity(vector,q):
+    """
+    Compute Hill number.
+
+    INPUT:
+    q: order of Hill number
+    vector: iterative and numeric subject represents relative abundances of species
+    """
+    if q == 1:
+        ShannonIndex = 0
+        for p in vector:
+            ShannonIndex = ShannonIndex-p*math.log(p)
+        D = math.exp(ShannonIndex)
+    else:
+        index = 0
+        for p in vector:
+            index = index+math.pow(p,q)
+        D = math.pow(index,1.0/(1.0-q))
+    return(D)
+
[…]

### 2021-08-23 Code/Figures_OriginalData.R

@@ -1,0 +1,401 @@
+library(ggplot2)
+library(ComplexHeatmap)
+library(circlize)
+library(proxy)
+library(ape)
+
+#########################################################################
+#########################################################################
+### NonHostRatio.pdf
+#########################################################################
+#########################################################################
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
+CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
+MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
+HostReadCount = CleanReadCount-MetagenomicReadCount
+
+data = rbind(
+  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
+  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
+)
+
+pdf("NonHostRatio.pdf")
+p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
+  geom_bar(stat = "identity")+
+  ylab("Read (million)")+
+  xlab(NULL)+
+  theme_classic()+
+  theme(axis.title.y=element_text(size=12,face="bold"),
+        axis.text.y=element_text(size=12,face="bold"),
+        axis.text.x=element_text(size=12,face="bold",angle=-62,hjust=0,vjust=0),
+        legend.text=element_text(size=12,face="bold"),
+        legend.title=element_text(size=12,face="bold"),
+        legend.position="top")+
+  #theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
+  scale_y_continuous(expand = c(0,0))
+print(p)
+dev.off()
+#########################################################################
+#########################################################################
[…]

### 2021-08-23 Code/HeatMap.R

@@ -1,0 +1,130 @@
+library(ggplot2)
+
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
+CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
+MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
+HostReadCount = CleanReadCount-MetagenomicReadCount
+
+data = rbind(
+  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
+  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
+)
+
+pdf("NonHostRatio.pdf")
+p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
+  geom_bar(stat = "identity")+
+  ylab("Read (million)")+
+  xlab(NULL)+
+  theme_classic()+
+  theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
+  scale_y_continuous(expand = c(0,0))
+print(p)
+dev.off()
+
+#########################################################################
+#########################################################################
+### Subsampling
+#########################################################################
+#########################################################################
+names(relabels) = Samples
+relabels = sort(relabels)
+ranks = c("phylum","class","order","family","genus","species")
+
+ReadData = function(sample,rank,percent,rep){
+    # Read quantification file
+    # Return data frame with taxon names and relative abundances
+    data = paste(sample,"/",percent,"_",rep,"/FunctionAnnotation/",rank,"Quantify.txt",sep="")
+    data = read.table(data,header=TRUE,sep="\t")
+
+    d = data.frame(Name = data$Name,Group=data$Group,quantify = data$TotalCount)
+    
+    colnames(d) = c("Name","Group",relabels[sample])
[…]

### 2021-08-23 Code/KO_quantification.R

@@ -1,0 +1,61 @@
+library(stringr)
+library(dplyr)
+
+args = commandArgs(TRUE)
+
+sample = args[1]
+percent = args[2]
+
+dire = paste("/rds/general/user/cl3820/home/Annotations/",sample,"/",percent,"_1/FunctionAnnotation",sep="")
+
+#########################################################################
+#########################################################################
+### 
+#########################################################################
+#########################################################################
+
+data = paste(dire,"/SeqAnnotations.txt",sep="")
+data = read.table(data,sep="\t",header=TRUE)
+data$ReadCount[is.na(data$ReadCount)] = 1
+
+annotations = str_split(data$KEGG_KO,",")
+time = sapply(annotations,length)
+data = data.frame(SeqID=rep(data$SeqID,time),
+                  KEGG_KO=unlist(annotations),
+                  txid=rep(data$txid,time),
+                  ReadCount=rep(data$ReadCount,time),
+                  TxPath=rep(data$TxPath,time),
+                  TxGroup=rep(data$TxGroup,time),
+                  SeqType=rep(data$SeqType,time))
+
+annotations = str_split(data$KEGG_KO,":")
+time = sapply(annotations,length)
+data = data.frame(SeqID=rep(data$SeqID,time),
+                  KEGG_KO=unlist(annotations),
+                  txid=rep(data$txid,time),
+                  ReadCount=rep(data$ReadCount,time),
+                  TxPath=rep(data$TxPath,time),
+                  TxGroup=rep(data$TxGroup,time),
+                  SeqType=rep(data$SeqType,time))
+data = subset(data,data$KEGG_KO!="ko")
+write.table(data,paste(dire,"/SeqAnnotations_complete.txt",sep=""),sep="\t",row.names=FALSE,quote=FALSE)
+
+data = subset(data,data$TxGroup!="Plants")
+data = subset(data,data$TxGroup!="Arthropods")
+data = subset(data,data$KEGG_KO!="-")
+data = subset(data,data$KEGG_KO!="")
+data[is.na(data)] = "None"
+
[…]

### 2021-08-23 Code/ModelTables.R

@@ -1,0 +1,569 @@
+library(ggplot2)
+library(minpack.lm)
+
+source("Diversity.R")
+
+q_values = c("0","1","2")
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
+            "PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh")
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2",
+             "Bee_Amellifera_hv13_1","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1")
+names(relabels)=Samples
+
+ConvertID = function(input){
+  output = rep(NA,length(input))
+  for (i in 1:length(input)){
+  if (input[i] %in% Samples){
+  output[i] = unname(relabels[input[i]])
+  }else{
+    output[i]=input[i]
+  }}
+  return(output)
+}
+
+Fitting = function(type){ # Taxon/Function
+    OutputTable = data.frame()
+
+    for (sample in Samples){
+    for (q in q_values){
+        run = run_ModelFitting(sample,q,type)
+
+        ret = c(sample,q,run$Asymptote,
+                
+                run$simu_x[length(run$simu_x)],run$y[length(run$y)],run$simu_y[length(run$simu_y)],
+                run$d_simu_y[length(run$d_simu_y)],run$simu_y[length(run$simu_y)]/run$Asymptote,
+                
+                run$OptDepth_0.5,run$OptDiversity_0.5,run$OptDiversity_0.5/run$Asymptote,
+                run$OptDepth_0.1,run$OptDiversity_0.1,run$OptDiversity_0.1/run$Asymptote,
+                run$OptDepth_0.05,run$OptDiversity_0.05,run$OptDiversity_0.05/run$Asymptote,
+                run$OptDepth_0.01,run$OptDiversity_0.01,run$OptDiversity_0.01/run$Asymptote,
+                
+                run$m1[1],run$m1[2],run$m1[3],run$weight[1],
+                run$m2[1],run$m2[2],run$m2[3],run$weight[2],
[…]

### 2021-08-23 Code/CompareSensitivity.R
CMEECourseWork

@@ -1,89 +1,0 @@
-library(ggplot2)
-
-HillDiversity = read.table("Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
-
-LF_F18 = subset(HillDiversity,HillDiversity$Sample=="LF_F18")
-PGcomcol3_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol3_Bimp")
-PGcomcol4a_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4a_Bimp")
-PGcomcol4b_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol4b_Bimp")
-PGnos_high_hv13_1 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-1")
-PGnos_high_hv13_2 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-2")
-PGnos_inter_hv15 = subset(HillDiversity,HillDiversity$Sample=="PGnos_inter_hv15")
-PGpollen_fresh = subset(HillDiversity,HillDiversity$Sample=="PGpollen_fresh")
-
-pdf("ExtraSpecies_Bumble.pdf")
-p1 = ggplot()+
-  geom_point(size=4,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
-                         y=(PGcomcol3_Bimp$SpeciesRichness-PGcomcol3_Bimp$AssemblySpeciesRichness)/PGcomcol3_Bimp$AssemblySpeciesRichness,
-                         colour="PGcomcol3_Bimp")))+
-  geom_point(size=4,(aes(x=PGcomcol4a_Bimp$CleanRead*PGcomcol4a_Bimp$SubsamplePercent/1e+6,
-                         y=(PGcomcol4a_Bimp$SpeciesRichness-PGcomcol4a_Bimp$AssemblySpeciesRichness)/PGcomcol4a_Bimp$AssemblySpeciesRichness,
-                         colour="PGcomcol4a_Bimp")))+
-  geom_point(size=4,(aes(x=PGcomcol4b_Bimp$CleanRead*PGcomcol4b_Bimp$SubsamplePercent/1e+6,
[…]

### 2021-08-23 Code/ComputeDiversity.py

@@ -1,116 +1,0 @@
-import os
-import re
-import sys
-import pandas as pd
-import numpy as np
-import math
-e = math.e
-
-Type = sys.argv[1] # Taxon/Function
-# Sample names
-samples = ["LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh"]
-
-# Rarefaction percentage
-percent = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1]
-
-# Sample name to raw read number
-RawReadCount = {"LF_F18":1443107,"PGcomcol3_Bimp":63973750,"PGcomcol4a_Bimp":58988182,"PGcomcol4b_Bimp":54955553,"PGnos_high_hv13-1":1104861,"PGnos_high_hv13-2":56836899,"PGnos_inter_hv15":63159968,"PGpollen_fresh":58113227}
-
-# Sample name to clean read number
-CleanReadCount = {"LF_F18":882436,"PGcomcol3_Bimp":53612702,"PGcomcol4a_Bimp":48426748,"PGcomcol4b_Bimp":45805759,"PGnos_high_hv13-1":842095,"PGnos_high_hv13-2":35282101,"PGnos_inter_hv15":45059211,"PGpollen_fresh":44466776}
-
-# Sample name to metagenomic (non-host) read number
-MetagenomicReadCount = {"LF_F18":882436,"PGcomcol3_Bimp":5300592,"PGcomcol4a_Bimp":3557052,"PGcomcol4b_Bimp":4618023,"PGnos_high_hv13-1":665507,"PGnos_high_hv13-2":10413704,"PGnos_inter_hv15":38837759,"PGpollen_fresh":17014144}
-
-def HillDiversity(vector,q):
-    """
-    Compute Hill number.
-
-    INPUT:
-    q: order of Hill number
-    vector: iterative and numeric subject represents relative abundances of species
-    """
-    if q == 1:
-        ShannonIndex = 0
-        for p in vector:
-            ShannonIndex = ShannonIndex-p*math.log(p)
-        D = math.exp(ShannonIndex)
-    else:
-        index = 0
-        for p in vector:
-            index = index+math.pow(p,q)
-        D = math.pow(index,1.0/(1.0-q))
-    return(D)
-
[…]

### 2021-08-23 Code/DiversityModel.R

@@ -1,252 +1,0 @@
-library(minpack.lm)
-
-ReadData = function(type){ # Taxon/Function
-    data = paste(type,"_HillDiversity.txt",sep="")
-    HillDiversity = read.table(data,sep="\t",header=TRUE)
-    return(HillDiversity)
-} 
-
-# Functions for multimodel inference
-RSS = function(x, y, predic_y){
-  # Sum of squares
-  # x: independent variable values
-  # y: dependent variable values
-  # predic_y: predicted dependent variable values
-  Rss = sum((y-predic_y)^2)
-  return(Rss)}
-likelihood = function(x, y, predic_y){
-  # Likelihood
-  # x: independent variable values
-  # y: dependent variable values
-  # predic_y: predicted dependent variable values
-  Rss = RSS(x,y,predic_y)
-  n = length(x)
-  L = -0.5*n*log(Rss/n)
-  return(L)}
-AICc = function(x, y, predic_y, k){
-  # corrected Akaike information criterion (AICc)
-  # x: independent variable values
-  # y: dependent variable values
-  # predic_y: predicted dependent variable values
-  # k: number of coefficients
-  L = likelihood(x,y,predic_y)
-  n = length(x)
-  AICc = -2*L+2*k+2*k*(k+1)/(n-k-1)
-  return(AICc)}
-AIC_weight = function(vector){
-  # Akaike weight
-  # vector: AIC values
-  detaAIC = vector-min(vector,na.rm=TRUE)
-  weight = exp(-0.5*detaAIC)/sum(exp(-0.5*detaAIC),na.rm=TRUE)
-  return(weight)}
-
-# Candidate species accumulation models:
-model1 = function(x,a,b){return( a*x/(b*x+1) )}
-model2 = function(x,a,b){return( a*(1-exp(-b*x)) )}
-model3 = function(x,a,b,c){return( a-b*c^x )}
-model4 = function(x,a,b,c){return( a*(1-exp(-b*x))^c )}
-model5 = function(x,a,b,c,d){return( a*(1-(1+(x/c)^d)^-b) )}
-
-# Derivations of candidate models
-d_model1 = function(x,a,b){return( a/((b*x+1)^2) )}
-d_model2 = function(x,a,b){return( a*b*exp(-b*x) )}
-d_model3 = function(x,a,b,c){return( -b*c^(x)*log(c) )}
[…]

### 2021-08-23 Code/Figures_OriginalData.R

@@ -1,401 +1,0 @@
-library(ggplot2)
-library(ComplexHeatmap)
-library(circlize)
-library(proxy)
-library(ape)
-
-#########################################################################
-#########################################################################
-### NonHostRatio.pdf
-#########################################################################
-#########################################################################
-Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
-relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
-CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
-MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
-HostReadCount = CleanReadCount-MetagenomicReadCount
-
-data = rbind(
-  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
-  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
-)
-
-pdf("NonHostRatio.pdf")
-p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
-  geom_bar(stat = "identity")+
-  ylab("Read (million)")+
-  xlab(NULL)+
-  theme_classic()+
-  theme(axis.title.y=element_text(size=12,face="bold"),
-        axis.text.y=element_text(size=12,face="bold"),
-        axis.text.x=element_text(size=12,face="bold",angle=-62,hjust=0,vjust=0),
-        legend.text=element_text(size=12,face="bold"),
-        legend.title=element_text(size=12,face="bold"),
-        legend.position="top")+
-  #theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
-  scale_y_continuous(expand = c(0,0))
-print(p)
-dev.off()
-#########################################################################
-#########################################################################
[…]

### 2021-08-23 Code/FunctionAnnotation.py

@@ -1,72 +1,0 @@
-import os
-import sys
-import pandas as pd
-import numpy as np
-import re
-
-args = sys.argv
-
-sample = args[1]
-percent = args[2]
-print(sample)
-print(percent)
-
-dire = "/rds/general/user/cl3820/home/Annotations/"+sample+"/"+percent+"_1/FunctionAnnotation"
-
-#########################################################################
-#########################################################################
-### Taxon and Function annotation of each read/CDS
-#########################################################################
-#########################################################################
-read2txid = pd.read_table(dire+"/read_txid.txt",header=None,sep="\t") # readID, rank, txid
-CDS2txid = pd.read_table(dire+"/CDS_txid_quantify.txt",header=0,sep="\t")
-txid2path = pd.read_table(dire+"/TaxonQuantification.txt",header=0,sep="\t")
-
-def CDSName(series):
-    series["CDSname"] = str(series["SeqID"])+":"+str(series["start"])+"-"+str(series["end"])+"("+str(series["strand"])+")"
-    return series
-CDS2txid = CDS2txid.apply(func=CDSName,axis=1,raw=False)
-
-
-def IDConvert(series):
-    if series["SeqType"]=="forward":
-        series["SeqID"] = str(series["SeqID"])+"_forward"
-        return series
-    elif series["SeqType"]=="reverse":
-        series["SeqID"] = str(series["SeqID"])+"_reverse"
-        return series
-    else:
-        return series
-
-def MergeAnnotation(SeqType):
-
-    Annotations = pd.read_table(dire+"/"+SeqType+"_annotation.txt.emapper.annotations",header=0,sep="\t")
-
-    Seq2KEGG = pd.DataFrame({"SeqID":Annotations["#query"],"KEGG_KO":Annotations["KEGG_ko"]})
-    
-    if SeqType=="CDS":
-        Seq2Taxon = pd.DataFrame({"SeqID":CDS2txid["CDSname"],"txid":CDS2txid["txid"],"ReadCount":CDS2txid["ReadCount"]})
-    else:
-        Seq2Taxon = pd.DataFrame({"SeqID":read2txid[0],"txid":read2txid[2],"ReadCount":np.repeat(np.array([1]),read2txid[0].size)})
-    
[…]

### 2021-08-23 Code/HeatMap.R

@@ -1,130 +1,0 @@
-library(ggplot2)
-
-Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
-relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
-CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
-MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
-HostReadCount = CleanReadCount-MetagenomicReadCount
-
-data = rbind(
-  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
-  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
-)
-
-pdf("NonHostRatio.pdf")
-p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
-  geom_bar(stat = "identity")+
-  ylab("Read (million)")+
-  xlab(NULL)+
-  theme_classic()+
-  theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
-  scale_y_continuous(expand = c(0,0))
-print(p)
-dev.off()
-
-#########################################################################
-#########################################################################
-### Subsampling
-#########################################################################
-#########################################################################
-names(relabels) = Samples
-relabels = sort(relabels)
-ranks = c("phylum","class","order","family","genus","species")
-
-ReadData = function(sample,rank,percent,rep){
-    # Read quantification file
-    # Return data frame with taxon names and relative abundances
-    data = paste(sample,"/",percent,"_",rep,"/FunctionAnnotation/",rank,"Quantify.txt",sep="")
-    data = read.table(data,header=TRUE,sep="\t")
-
-    d = data.frame(Name = data$Name,Group=data$Group,quantify = data$TotalCount)
-    
-    colnames(d) = c("Name","Group",relabels[sample])
[…]

### 2021-08-23 Code/IntegratedPipeline.py

@@ -1,469 +1,0 @@
-import os
-import sys
-import pandas as pd
-import numpy as np
-
-args = sys.argv
-
-# Absolute path to non-host data
-# /rds/general/user/cl3820/home/Non_Host_data/<SampleName>*
-rawData1 = args[1] 
-rawData2 = args[2]
-
-# Absolute path to output directory, named after sample
-# e.g. /rds/general/user/cl3820/ephemeral/Rarefaction/PGcomcol3_Bimp
-outDir = args[3]
-
-sample = args[4] # Sample Name
-threads = str(args[5]) # 32
-sample_percent = str(args[6]) # What percent of the original dataset is subsampled
-repeat = str(args[7]) # int
-
-sample_percent = sample_percent+"_"+repeat # e.g. 0.1_1 (0.1: subsampling percent; 1: repeat 1)
-
-print("#########################################################################")
-print("#########################################################################")
-print(args)
-#########################################################################
-#########################################################################
-### Subsampling
-#########################################################################
-#########################################################################
-if not os.path.exists(outDir):
-    print("Make directory: "+outDir)
-    os.system("mkdir "+outDir)
-if not os.path.exists(outDir+"/"+sample_percent):
-    print("Make directory: "+outDir+"/"+sample_percent)
-    os.system("mkdir "+outDir+"/"+sample_percent)
-
-if sample_percent.split("_")[0] != "1":
-    Data1 = outDir+"/"+sample_percent+"/"+sample+"_"+sample_percent.split("_")[0]+"_1.fq"
-    Data2 = outDir+"/"+sample_percent+"/"+sample+"_"+sample_percent.split("_")[0]+"_2.fq"
-    if not os.path.exists(Data1) or not os.path.exists(Data2):
-        # BBmap: Subsample metagenomic mate pairs
-        # INPUT: rawData1
-        #        rawData2
-        # OUTPUT: Data1 = outDir+"/"+sample_percent+"/"+sample+"_"+sample_percent.split("_")[0]+"_1.fq"
-        #         Data2 = outDir+"/"+sample_percent+"/"+sample+"_"+sample_percent.split("_")[0]+"_2.fq"
[…]

### 2021-08-23 Code/ModelTables.R

@@ -1,569 +1,0 @@
-library(ggplot2)
-library(minpack.lm)
-
-source("Diversity.R")
-
-q_values = c("0","1","2")
-Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
-            "PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh")
-relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2",
-             "Bee_Amellifera_hv13_1","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1")
-names(relabels)=Samples
-
-ConvertID = function(input){
-  output = rep(NA,length(input))
-  for (i in 1:length(input)){
-  if (input[i] %in% Samples){
-  output[i] = unname(relabels[input[i]])
-  }else{
-    output[i]=input[i]
-  }}
-  return(output)
-}
-
-Fitting = function(type){ # Taxon/Function
-    OutputTable = data.frame()
-
-    for (sample in Samples){
-    for (q in q_values){
-        run = run_ModelFitting(sample,q,type)
-
-        ret = c(sample,q,run$Asymptote,
-                
-                run$simu_x[length(run$simu_x)],run$y[length(run$y)],run$simu_y[length(run$simu_y)],
-                run$d_simu_y[length(run$d_simu_y)],run$simu_y[length(run$simu_y)]/run$Asymptote,
-                
-                run$OptDepth_0.5,run$OptDiversity_0.5,run$OptDiversity_0.5/run$Asymptote,
-                run$OptDepth_0.1,run$OptDiversity_0.1,run$OptDiversity_0.1/run$Asymptote,
-                run$OptDepth_0.05,run$OptDiversity_0.05,run$OptDiversity_0.05/run$Asymptote,
-                run$OptDepth_0.01,run$OptDiversity_0.01,run$OptDiversity_0.01/run$Asymptote,
-                
-                run$m1[1],run$m1[2],run$m1[3],run$weight[1],
-                run$m2[1],run$m2[2],run$m2[3],run$weight[2],
[…]

### 2021-08-23 Code/QualityControl_HostRemove.py

@@ -1,151 +1,0 @@
-"""
-This script conducts quality filtering and host removing.
-Host removing can be ignored if argument 3 is "None".
-
-ARGUMENTS:
-1: rawData1 (file, raw fq file 1)
-2: rawData2 (file, raw fq file 2)
-3: HostIndex (file, base name of Bowtie2 index of host genome)
-4: outDir (directory, named after sample name)
-5: sample (string, sample name)
-6: threads (integer, number of threads)
-
-DEPENDENCIES:
-/rds/general/user/cl3820/home/anaconda3/bin/fastqc
-/rds/general/user/cl3820/home/NexteraPE-PE.fa (fasta file of adaptor)
-/rds/general/user/cl3820/home/anaconda3/bin/trimmomatic
-/rds/general/user/cl3820/home/anaconda3/bowtie2
-/rds/general/user/cl3820/home/anaconda3/bin/samtools
-
-INPUT:
-rawData1
-rawData2
-HostIndex
-
-OUTPUT:
-4 .html and 4 .zip files in outDir (Fastqc reports of raw and clean reads)
-outDir+"/"+sample+"_clean.1.fq", outDir+"/unpaired_"+sample+".1.fq" (clean and paired reads)
-outDir+"/"+sample+"_clean.2.fq", outDir+"/unpaired_"+sample+".2.fq" (clean and unpaired reads)
-outDir+"/"+sample+"_Host.sam"+".bam" (BAM file from mapping clean-paired reads to host genome)
-outDir+"/"+sample+"_Host.sam"+".bam_mapped" (BAM file of reads mapped to host genome)
-outDir+"/"+sample+"_Host.sam"+".bam_mapped.1.fq", outDir+"/"+sample+"_Host.sam"+".bam_mapped.2.fq" (host reads)
-outDir+"/"+sample+"_Host.sam"+".bam_unmapped" (BAM file of reads not mapped to host genome)
-outDir+"/"+sample+"_Host.sam"+".bam_unmapped.1.fq", outDir+"/"+sample+"_Host.sam"+".bam_unmapped.2.fq" (non-host reads)
-"""
-
-import os
-import sys
-
-args = sys.argv
-
-# Arguments
-rawData1 = args[1] # Path to raw data 1
-rawData2 = args[2] # Path to raw data 2
-HostIndex = args[3] # Path to Bowtie2 index of host genomes. If no host, set it "None"
[…]

### 2021-08-23 MResProject/Code/CompareSensitivity.R

@@ -1,7 +1,20 @@
+# DESCRIPTION:
+# This script compares performance of integrated pipeline and assembly-dependent methods in terms of species identification.
+
+# DEPENDENCIES:
+# ggplot2
+
+# ARGUMENTS:
+
+# OUTPUT:
+# Seen in annotations
+
+# Note:
+# Take output of ComputeDiversity.py as input
+
 library(ggplot2)
 
 HillDiversity = read.table("Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
-HillDiversity = subset(HillDiversity,Group=="All")
 
 LF_F18 = subset(HillDiversity,HillDiversity$Sample=="LF_F18")
 PGcomcol3_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol3_Bimp")
@@ -14,21 +27,26 @@ PGpollen_fresh = subset(HillDiversity,HillDiversity$Sample=="PGpollen_fresh")
 
 pdf("ExtraSpecies_Bumble.pdf")
 p1 = ggplot()+
-  geom_point(size=2,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
+  geom_point(size=4,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
                          y=(PGcomcol3_Bimp$SpeciesRichness-PGcomcol3_Bimp$AssemblySpeciesRichness)/PGcomcol3_Bimp$AssemblySpeciesRichness,
                          colour="PGcomcol3_Bimp")))+
-  geom_point(size=2,(aes(x=PGcomcol4a_Bimp$CleanRead*PGcomcol4a_Bimp$SubsamplePercent/1e+6,
+  geom_point(size=4,(aes(x=PGcomcol4a_Bimp$CleanRead*PGcomcol4a_Bimp$SubsamplePercent/1e+6,
                          y=(PGcomcol4a_Bimp$SpeciesRichness-PGcomcol4a_Bimp$AssemblySpeciesRichness)/PGcomcol4a_Bimp$AssemblySpeciesRichness,
                          colour="PGcomcol4a_Bimp")))+
-  geom_point(size=2,(aes(x=PGcomcol4b_Bimp$CleanRead*PGcomcol4b_Bimp$SubsamplePercent/1e+6,
[…]

### 2021-08-23 MResProject/Code/ComputeDiversity.py

@@ -1,3 +1,19 @@
+"""
+DESCRIPTION:
+This script computes Hill numbers of order 0, 1, 2 for inventories of species/KOs
+
+DEPENDENCIES:
+Python modules: os, re, sys, pandas, numpy, math
+
+ARGUMENTS:
+
+OUTPUT:
+Seen in annotations
+
+Note:
+Take output of IntegratedPipeline.py as input
+"""
+
 import os
 import re
 import sys

### 2021-08-23 MResProject/Code/DiversityModel.R

@@ -1,3 +1,16 @@
+# DESCRIPTION:
+# Functions used for rarefaction model fitting.
+
+# DEPENDENCIES:
+# minpack.lm
+
+# ARGUMENTS:
+
+# OUTPUT:
+
+# Note:
+# Take output of ComputeDiversity.py as input
+
 library(minpack.lm)
 
 ReadData = function(type){ # Taxon/Function

### 2021-08-23 MResProject/Code/FiguresFromOriginalData.R

@@ -1,0 +1,374 @@
+# DESCRIPTION:
+# This script visualize profiling results of original datasets.
+
+# DEPENDENCIES:
+# ggplot2, ComplexHeatmap, circlize, proxy, ape
+
+# ARGUMENTS:
+
+# OUTPUT:
+# Seen in annotations
+
+# Note:
+# Take output of IntegratedPipeline.py, UncollapseKO.R and PathwayInference.py as input
+
+
+library(ggplot2)
+library(ComplexHeatmap)
+library(circlize)
+library(proxy)
+library(ape)
+
+#########################################################################
+# Proportions of host contamination
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
+CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
+MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
+HostReadCount = CleanReadCount-MetagenomicReadCount
+
+data = rbind(
+  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
+  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
+)
+
+pdf("NonHostRatio.pdf")
+p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
+  geom_bar(stat = "identity")+
+  ylab("Read (million)")+
+  xlab(NULL)+
+  theme_classic()+
+  theme(axis.title.y=element_text(size=12,face="bold"),
+        axis.text.y=element_text(size=12,face="bold"),
+        axis.text.x=element_text(size=12,face="bold",angle=-62,hjust=0,vjust=0),
+        legend.text=element_text(size=12,face="bold"),
+        legend.title=element_text(size=12,face="bold"),
+        legend.position="top")+
[…]

### 2021-08-23 MResProject/Code/Figures_OriginalData.R

@@ -1,406 +1,0 @@
-library(ggplot2)
-library(ComplexHeatmap)
-library(circlize)
-library(proxy)
-library(ape)
-
-#########################################################################
-#########################################################################
-### NonHostRatio.pdf
-#########################################################################
-#########################################################################
-Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh") # "PGnos_high_hv13-1"
-relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1") # "Bee_Amellifera_hv13_1"
-CleanReadCount = c(882436,53612702,48426748,45805759,35282101,45059211,44466776) # 842095
-MetagenomicReadCount = c(882436,5300592,3557052,4618023,10413704,38837759,17014144) # 665507
-HostReadCount = CleanReadCount-MetagenomicReadCount
-
-data = rbind(
-  data.frame(relabel=relabels,ReadCount=MetagenomicReadCount,Type=rep("Non-host",length(MetagenomicReadCount))),
-  data.frame(relabel=relabels,ReadCount=HostReadCount,Type=rep("Host",length(MetagenomicReadCount)))
-)
-
-pdf("NonHostRatio.pdf")
-p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
-  geom_bar(stat = "identity")+
-  ylab("Read (million)")+
-  xlab(NULL)+
-  theme_classic()+
-  theme(axis.text.x=element_text(angle=90,hjust=0.5,vjust=0.5))+
-  scale_y_continuous(expand = c(0,0))
-print(p)
-dev.off()
-#########################################################################
-#########################################################################
-### Group abundance distribution
-#########################################################################
-#########################################################################
[…]

### 2021-08-23 MResProject/Code/IntegratedPipeline.py

@@ -1,151 +1,262 @@
+"""
+DESCRIPTION:
+This is the script for the integrated pipeline. 
+It is composed of header lines and modules indicated by a line of "#". 
+The header lines and each module can be combined together as another script. 
+Modules include (1) quality control and host removing; (2) subsampling; (3) assembly-dependent species identification; (4) reference database construction; (5) fragment recruitment; (6) assembly-independent species identification; (7) functional annotation; (8) annotation integration.
+
+DEPENDENCIES:
+Python modules: os, sys, pandas, numpy, Biopython, re, taxomias (https://github.com/wegnerce/taxomias)
+Conda-managed softwares: Fastqc, Trimmomatic, Bowtie2, SAMtools, BBmap, DIAMOND
+Other softwares: SPAdes, MEGAN6, dataset (command-line tool of NCBI), EggNOG-mapper
+Databases: nr.dmnd (DIAMOND database of nr), megan-map-Jul2020-2.db (MEGAN6 database)
+
+ARGUMENTS:
+args[1]: <file> raw fastq file 1
+args[2]: <file> raw fastq file 2
+args[3]: <directory> output directory
+args[4]: <string> sample identifier
+args[5]: <integer> threads
+args[6]: <float> subsampling proportion
+args[7]: <integer> indicate time of repeatedly subsampling
+args[8]: <string> base name of Bowtie2 index of host genome. If None, host removing is skipped.
+
+OUTPUT:
+Seen in annotations of each module.
+"""
+
 import os
 import sys
 import pandas as pd
 import numpy as np
+# sys.path.append('/rds/general/user/cl3820/home/taxomias')
+import taxomias as tx
+import re
 
 args = sys.argv
 
-# Absolute path to non-host data
-# /rds/general/user/cl3820/home/Non_Host_data/<SampleName>*
+# Arguments
 rawData1 = args[1] 
 rawData2 = args[2]
-
-# Absolute path to output directory, named after sample
-# e.g. /rds/general/user/cl3820/ephemeral/Rarefaction/PGcomcol3_Bimp
 outDir = args[3]
+sample = args[4]
+threads = str(args[5]) 
[…]

### 2021-08-23 MResProject/Code/KO_quantification.R

@@ -1,61 +1,0 @@
-library(stringr)
-library(dplyr)
-
-args = commandArgs(TRUE)
-
-sample = args[1]
-percent = args[2]
-
-dire = paste("/rds/general/user/cl3820/home/Annotations/",sample,"/",percent,"_1/FunctionAnnotation",sep="")
-
-#########################################################################
-#########################################################################
-### 
-#########################################################################
-#########################################################################
-
-data = paste(dire,"/SeqAnnotations.txt",sep="")
-data = read.table(data,sep="\t",header=TRUE)
-data$ReadCount[is.na(data$ReadCount)] = 1
-
-annotations = str_split(data$KEGG_KO,",")
-time = sapply(annotations,length)
-data = data.frame(SeqID=rep(data$SeqID,time),
-                  KEGG_KO=unlist(annotations),
-                  txid=rep(data$txid,time),
-                  ReadCount=rep(data$ReadCount,time),
-                  TxPath=rep(data$TxPath,time),
-                  TxGroup=rep(data$TxGroup,time),
-                  SeqType=rep(data$SeqType,time))
-
-annotations = str_split(data$KEGG_KO,":")
-time = sapply(annotations,length)
-data = data.frame(SeqID=rep(data$SeqID,time),
-                  KEGG_KO=unlist(annotations),
-                  txid=rep(data$txid,time),
-                  ReadCount=rep(data$ReadCount,time),
-                  TxPath=rep(data$TxPath,time),
-                  TxGroup=rep(data$TxGroup,time),
-                  SeqType=rep(data$SeqType,time))
-data = subset(data,data$KEGG_KO!="ko")
-write.table(data,paste(dire,"/SeqAnnotations_complete.txt",sep=""),sep="\t",row.names=FALSE,quote=FALSE)
-
-data = subset(data,data$TxGroup!="Plants")
-data = subset(data,data$TxGroup!="Arthropods")
-data = subset(data,data$KEGG_KO!="-")
-data = subset(data,data$KEGG_KO!="")
-data[is.na(data)] = "None"
-
[…]

### 2021-08-23 MResProject/Code/ModelTables.R

@@ -1,479 +1,0 @@
-library(ggplot2)
-library(minpack.lm)
-
-source("Diversity.R")
-
-q_values = c("0","1","2")
-Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
-            "PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh")
-relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2",
-             "Bee_Amellifera_hv13_1","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1")
-names(relabels)=Samples
-
-ConvertID = function(input){
-  output = rep(NA,length(input))
-  for (i in 1:length(input)){
-  if (input[i] %in% Samples){
-  output[i] = unname(relabels[input[i]])
-  }else{
-    output[i]=input[i]
-  }}
-  return(output)
-}
-
-Fitting = function(type){ # Taxon/Function
-    OutputTable = data.frame()
-
-    for (sample in Samples){
-    for (q in q_values){
-        run = run_ModelFitting(sample,q,type)
-
-        ret = c(sample,q,run$Asymptote,
-                
-                run$simu_x[length(run$simu_x)],run$y[length(run$y)],run$simu_y[length(run$simu_y)],
-                run$d_simu_y[length(run$d_simu_y)],run$simu_y[length(run$simu_y)]/run$Asymptote,
-                
-                run$OptDepth_0.5,run$OptDiversity_0.5,run$OptDiversity_0.5/run$Asymptote,
-                run$OptDepth_0.1,run$OptDiversity_0.1,run$OptDiversity_0.1/run$Asymptote,
-                run$OptDepth_0.05,run$OptDiversity_0.05,run$OptDiversity_0.05/run$Asymptote,
-                run$OptDepth_0.01,run$OptDiversity_0.01,run$OptDiversity_0.01/run$Asymptote,
-                
-                run$m1[1],run$m1[2],run$m1[3],run$weight[1],
[…]

### 2021-08-23 MResProject/Code/PathwayInference.py

@@ -1,0 +1,69 @@
+"""
+DESCRIPTION:
+This script conducts pathway inference.
+
+DEPENDENCIES:
+Python modules: os, sys, numpy, pandas
+Other softwares: MinPath
+
+ARGUMENTS:
+args[1]:  <directory> output directory
+args[2]: <float> subsampling proportion
+
+OUTPUT:
+Seen in annotations
+
+Note:
+Take output of IntegratedPipeline.py as input
+"""
+
+import os
+import sys
+import numpy as np
+import pandas as pd
+
+args = sys.argv
+
+sample = args[1]
+percent = args[2]
+
+dire = sample+"/"+percent+"_1/FunctionAnnotation"
+
+KO_abundance = pd.read_table(dire+"/KO_quantify.txt",sep="\t",header=0)
+KO_term = pd.read_table("MinPath/data/KEGG-family.txt",sep="\t",header=None)
+KO_term.columns = ["KEGG_KO","Description"]
+
+KO_abundance_term = pd.merge(KO_abundance,KO_term,on="KEGG_KO",how="left")
+# output
+KO_abundance_term.to_csv(dire+"/KO_Abundance_Description.txt",header=True,sep="\t",index=False)
+
+Txid_KO = pd.read_table(dire+"/Txid_KO.txt",sep="\t",header=None)
+Txid_KO = Txid_KO.drop(index=0)
+#output
+Txid_KO.to_csv(dire+"/Txid_KO_NoHeader.txt",header=False,sep="\t",index=False)
+
+# pathway inference
+cmd = "python"+" "+"/rds/general/user/cl3820/home/MinPath/MinPath.py"+" "+"-ko"+" "+dire+"/Txid_KO_NoHeader.txt"+" "+"-report"+" "+dire+"/Pathway.txt"+" "+"-details"+" "+dire+"/PathwayDetails.txt"
+os.system(cmd)
+
+Pathway = pd.read_table(dire+"/Pathway.txt",sep="  ",header=None)
+
+def ConvertData(series):
+    """
+    Wrangle output of MinPath
+    """
+    PathwayID = "map"+series[0].split(" ")[1]
+    Naive = series[1].split(" ")[1]
+    MinPath = series[2].split(" ")[1]
+    TotalGene = series[4]
+    GeneFound = series[6]
+    Cov = GeneFound/TotalGene
+    Description = series[8]
[…]

### 2021-08-23 MResProject/Code/PathwayReconstruct.py

@@ -1,45 +1,0 @@
-import os
-import sys
-import numpy as np
-import pandas as pd
-
-args = sys.argv
-
-sample = args[1]
-percent = args[2]
-print(sample)
-print(percent)
-
-dire = "/rds/general/user/cl3820/home/Annotations/"+sample+"/"+percent+"_1/FunctionAnnotation"
-
-KO_abundance = pd.read_table(dire+"/KO_quantify.txt",sep="\t",header=0)
-KO_term = pd.read_table("/rds/general/user/cl3820/home/MinPath/data/KEGG-family.txt",sep="\t",header=None)
-KO_term.columns = ["KEGG_KO","Description"]
-
-KO_abundance_term = pd.merge(KO_abundance,KO_term,on="KEGG_KO",how="left")
-KO_abundance_term.to_csv(dire+"/KO_Abundance_Description.txt",header=True,sep="\t",index=False)
-
-Txid_KO = pd.read_table(dire+"/Txid_KO.txt",sep="\t",header=None)
-Txid_KO = Txid_KO.drop(index=0)
-Txid_KO.to_csv(dire+"/Txid_KO_NoHeader.txt",header=False,sep="\t",index=False)
-
-cmd = "python"+" "+"/rds/general/user/cl3820/home/MinPath/MinPath.py"+" "+"-ko"+" "+dire+"/Txid_KO_NoHeader.txt"+" "+"-report"+" "+dire+"/Pathway.txt"+" "+"-details"+" "+dire+"/PathwayDetails.txt"
-os.system(cmd)
-
-Pathway = pd.read_table(dire+"/Pathway.txt",sep="  ",header=None)
-
-def ConvertData(series):
-    PathwayID = "map"+series[0].split(" ")[1]
-    Naive = series[1].split(" ")[1]
-    MinPath = series[2].split(" ")[1]
-    TotalGene = series[4]
-    GeneFound = series[6]
-    Cov = GeneFound/TotalGene
-    Description = series[8]
-    dic = {"PathwayID":PathwayID,"Naive":Naive,"MinPath":MinPath,"TotalGene":TotalGene,"GeneFound":GeneFound,"Coverage":Cov,"Description":Description}
-    ret = pd.Series(dic)
-    return ret
-
-Pathway = Pathway.apply(func=ConvertData,axis=1).sort_values(by="Coverage",axis=0,ascending=False)
-
-Pathway.to_csv(dire+"/PathwaySummary.txt",header=True,sep="\t",index=False)

### 2021-08-23 MResProject/Code/Read2Taxon2KO.py

@@ -1,0 +1,141 @@
+import os
+import sys
+import numpy as np
+import pandas as pd
+# sys.path.append('/rds/general/user/cl3820/home/taxomias')
+import taxomias as tx
+import re
+
+args = sys.argv
+
+sample = args[1]
+percent = args[2]
+print(args)
+
+dire = sample+"/"+percent+"_1/FunctionAnnotation"
+
+# Merge taxon and abundance table of CDS
+CDS_quantify = pd.read_table(dire+"/CDSquantify.txt",sep="\t",header=None) #fileds: nucleotide ID, start, end, name, score, strand, read count, read length, seq length, coverage
+
+CDS_txid = pd.read_table(dire+"/CDS_info.txt",sep="\t",header=None) # fileds: nucleotide ID, start, end, name, score, strand, assembly ID, txid
+
+CDS_txid.columns = ["SeqID","start","end","CDSname","score","strand","AssemblyID","txid"]
+CDS_txid["ReadCount"] = CDS_quantify[6]
+CDS_txid["Coverage"] = CDS_quantify[9]
+
+CDS_txid = CDS_txid[CDS_txid["ReadCount"]!=0]
+CDS_txid.to_csv(dire+"/CDS_txid_quantify.txt",sep="\t",index=False,header=True) # header: "SeqID","start","end","CDSname","score","strand","AssemblyID","txid", "ReadCount", "Coverage"
+
+#########################################################################
+#########################################################################
+### Abundance of taxa identified
+#########################################################################
+#########################################################################
+CDS = pd.read_table(dire+"/CDS_txid_quantify.txt",sep="\t",header=0) # header: "SeqID","start","end","CDSname","score","strand","AssemblyID","txid", "ReadCount", "Coverage"
+read = pd.read_table(dire+"/../FirstRound/taxon_ID.txt",sep="\t",header=None) # fields: rank (S,G), txid, read count (pair)
+
+txid_CDSquantify = CDS["ReadCount"].groupby(CDS["txid"]).sum() # read count
+
+txid = CDS["txid"].values.tolist()+read[1].values.tolist()
+txid = list(set(txid))
+
+path = []
+rank = []
+for i in txid:
+    rank.append(tx.RankByTaxid(i))
+    path_id = tx.PathByTaxid(i)
+    path_name = ""
+    for j in path_id:
[…]

### 2021-08-23 MResProject/Code/UncollapseKO.R

@@ -1,0 +1,74 @@
+# DESCRIPTION:
+# This script uncollapse KO annotations.
+
+# DEPENDENCIES:
+# stringr, dplyr
+
+# ARGUMENTS:
+# args[1]:  <directory> output directory
+# args[2]: <float> subsampling proportion
+
+# OUTPUT:
+# Seen in annotations
+
+# Note:
+# Take output of IntegratedPipeline.py as input
+
+library(stringr)
+library(dplyr)
+
+args = commandArgs(TRUE)
+
+sample = args[1]
+percent = args[2]
+
+dire = paste("/rds/general/user/cl3820/home/Annotations/",sample,"/",percent,"_1/FunctionAnnotation",sep="")
+
+data = paste(dire,"/SeqAnnotations.txt",sep="")
+data = read.table(data,sep="\t",header=TRUE)
+data$ReadCount[is.na(data$ReadCount)] = 1
+
+annotations = str_split(data$KEGG_KO,",")
+time = sapply(annotations,length)
+data = data.frame(SeqID=rep(data$SeqID,time),
+                  KEGG_KO=unlist(annotations),
+                  txid=rep(data$txid,time),
+                  ReadCount=rep(data$ReadCount,time),
+                  TxPath=rep(data$TxPath,time),
+                  TxGroup=rep(data$TxGroup,time),
+                  SeqType=rep(data$SeqType,time))
+
+annotations = str_split(data$KEGG_KO,":")
+time = sapply(annotations,length)
+data = data.frame(SeqID=rep(data$SeqID,time),
+                  KEGG_KO=unlist(annotations),
+                  txid=rep(data$txid,time),
+                  ReadCount=rep(data$ReadCount,time),
+                  TxPath=rep(data$TxPath,time),
+                  TxGroup=rep(data$TxGroup,time),
+                  SeqType=rep(data$SeqType,time))
+data = subset(data,data$KEGG_KO!="ko")
+# Output: SeqID to taxon to KO
+write.table(data,paste(dire,"/SeqAnnotations_complete.txt",sep=""),sep="\t",row.names=FALSE,quote=FALSE)
+
+data = subset(data,data$TxGroup!="Plants")
+data = subset(data,data$TxGroup!="Arthropods")
[…]

### 2021-08-23 MResProject/Code/run_ModelFitting.R

@@ -1,0 +1,585 @@
+# DESCRIPTION:
+# Run model fitting. 
+# Generate tables summarizing coefficients, model final slopes, optimal sequencing depth.
+# Visualize models.
+
+# DEPENDENCIES:
+# minpack.lm, ggplot2
+# R script DiversityModel.R
+
+# ARGUMENTS:
+
+# OUTPUT:
+
+# Note:
+# Take output of ComputeDiversity.py as input
+
+library(ggplot2)
+library(minpack.lm)
+
+source("Diversity.R")
+
+q_values = c("0","1","2")
+Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
+            "PGnos_high_hv13-1","PGnos_high_hv13-2","PGnos_inter_hv15","PGpollen_fresh")
+relabels = c("Flower_eDNA","Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2",
+             "Bee_Amellifera_hv13_1","Bee_Amellifera_hv13_2","Bee_Amellifera_hv15_1","Bee_Amellifera_wild_1")
+names(relabels)=Samples
+
+ConvertID = function(input){
+  output = rep(NA,length(input))
+  for (i in 1:length(input)){
+  if (input[i] %in% Samples){
+  output[i] = unname(relabels[input[i]])
+  }else{
+    output[i]=input[i]
+  }}
+  return(output)
+}
+
+Fitting = function(type){ # Taxon/Function
+    OutputTable = data.frame()
+
+    for (sample in Samples){
+    for (q in q_values){
+        run = run_ModelFitting(sample,q,type)
+
+        ret = c(sample,q,run$Asymptote,
+                
+                run$simu_x[length(run$simu_x)],run$y[length(run$y)],run$simu_y[length(run$simu_y)],
+                run$d_simu_y[length(run$d_simu_y)],run$simu_y[length(run$simu_y)]/run$Asymptote,
+                
+                run$OptDepth_0.5,run$OptDiversity_0.5,run$OptDiversity_0.5/run$Asymptote,
+                run$OptDepth_0.1,run$OptDiversity_0.1,run$OptDiversity_0.1/run$Asymptote,
[…]

### 2021-08-25 MResProject/Latex/Draft.tex
CMEECourseWork

@@
 % Metagenomic DNA discoveries after sequencing everything (bacteria, parasites, food, gut) inside a bee
-\title{Optimize sequencing depth required for reliable profiling of microbiome by rarefaction and multimodel inference, using shotgun metagenomic data from pollination system and a modular profiling pipeline}
+\title{Optimize sequencing depth for shotgun metagenomics of pollination system by rarefaction, using a modular profiling pipeline}
 \author{Cong Liu}
@@
   \newline
-  All datasets used in this project are provided by Dr. Peter Graystock and the project was conducted under his supervison. 
+  All datasets used in this project are provided by Dr. Peter Graystock and the project was conducted under his supervision. 
   I am responsible for the development and conduction of the analyses presented.
@@
   \begin{abstract}
-    Bee-associated microbiome plays a crucial role in host health and relevant investigations have been boosted by shotgun metagenomics, which provides unique advantages by capturing diversity of multiple taxonomic clades and providing information on function potentiality.
+    Bee gut microbiome plays a crucial role in host health, involving in food digestion, pathogen defence and chemical detoxification. 
+    Vast relevant investigations use amplicon sequencing to explore bacterial diversity, while emergence of shotgun metagenomics offers unique advantages by capturing diversity of multiple taxonomic clades and providing information on function potentiality.
     However, utilization of shotgun metagenomics is hindered by complexity of data analysis and high cost of sequencing. 
@@
     Here, an integrated pipeline combining assembly-dependent and -independent methods was introduced for taxonomic and functional profiling of shotgun metagenomic data, and a framework of rarefaction and multimodel inference was constructed for optimizing sequencing depth.
-    Both the pipeline and the framework were used for analysis of real metagenomic datasets ($2 \times 150 bp$ read pairs) from honey bees, bumble bees and flower washes. 
-    The integrated pipeline illustrated taxon composition and metabolic potentiality of metagenome, and provided improvement in species identification compared with an assembly-dependent procedure. 
-    Sequencing depth can be optimized for species diversity estimation especially when little emphasis is given to rare species, while functional profiling requires deeper sequencing than taxon profiling.
+    Both the pipeline and the framework were used for analysis of deep-sequencing datasets ($2 \times 150 $bp read pairs) from of honey bees, bumble bees and flower washes. 
+    The integrated pipeline illustrated taxon composition and metabolic potentiality of the metagenomes, and provided significant improvements in species identification. 
+    For species diversity estimation, about 40 and 43 million read pairs would be sufficient for metagenomic datasets from honey bees and bumble bees, respectively. 
+    If low leverage is given to rare species, shallower sequencing can be adopted. 
+    Function profiling is much less stable to sequencing depth than species content. 
+    Additional functional gene clusters (FGCs) were still being discovered at original sequencing depth of all samples. 
+    % Sequencing depth can be optimized for species diversity estimation especially when little emphasis is given to rare species, while functional profiling requires deeper sequencing than taxon profiling.
     % Rarefaction and model fitting was conducted to compute expected species/function diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to optimize sequencing depth, balancing sequencing effort and capability of estimating diversity reliably.
@@
     % For flower surface, more than 0.88 million (0.26 Gbp) sequencing depth is needed. 
-    These results are helpful for cost-effective utilization of shotgun metagenomics in investigations of pollination system. 
+    Overall, this project provides guidelines for defining a balance between sequencing cost and acquirement of reliable results for investigations of pollination system. 
+    Similar studies for other host species are recommended before undertaking metagenomic projects involving a large number of samples. 
     % The integrated pipeline and the framework for rarefaction analysis can also be applied for researches on other environments. 
@@
   \section{Introduction}
-  Pollinators such as bees are crucial to maintain global food security and provide stability of natural systems \citep{hristov2020significance,bansch2021crop,khalifa2021overview} but their health is under increasing concern \citep{amiri2020using}.
+  Pollinators such as bees are crucial to maintain global food security and provide stability of natural systems \citep{hristov2020significance,bansch2021crop,khalifa2021overview} but their populations are facing declines \citep{brown2009conservation,hristov2020factors,cheng2021ecology,zattara2021worldwide}.
   % The health of bees is a crucial issue that has received increasing concern \citep{amiri2020using}. 
@@
   % foldesi2021larger 
-  Diverse pathogens and environmental factors threaten bee health and are contributing to their declines. 
+  % Diverse pathogens and environmental factors threaten bee health and are contributing to their declines. 
   % The trend of bee decline has been widely observed at a global scale and attributed to multiple factors including 
-  A combination of stressors including parasites, pesticide exposure, invasive species, habitat loss and climate change are all contributing to declines of bee populations.
+  A combination of stressors including parasites, pesticide exposure, invasive species, habitat loss and climate change is contributing to declines of bee populations.
 \citep{brown2009conservation,hristov2020factors,cheng2021ecology,zattara2021worldwide}.
   \newline
-  Bees are associated with a community of microorganisms influencing host health \citep{engel2016bee,raymann2018role}. 
-  Within the gut of bees, stable microbial communities (microbiomes) play crucial roles in food digestion, parasite defence and chemical detoxification. 
-  They mediate food digestion processes including 
+  % Bees are associated with a community of microorganisms influencing host health \citep{engel2016bee,raymann2018role}. 
+  Within the gut of bees, stable microbial communities (microbiomes) play crucial roles in food digestion, parasite defence and chemical detoxification \citep{moran2015genomics,engel2016bee,raymann2018role}.
+  They help mediate food digestion processes including 
   % plant-produced polysaccharide including pectin and hemicellulose \citep{zheng2019division}
@@
   % which presents in nectar of \textit{Tilia} \citep{adler2000ecological} and is poisonous to honey bees \citep{de1986mechanism}. 
-  They also provide protection against pathogens including \textit{Crithidia}, 
+  Bee microbiomes also provide protection against pathogens including \textit{Crithidia}, 
   % a protozoan genus exclusively parasitising arthropods 
@@
   % a genus of fungal pathogens 
-  \citep{cariveau2014variation,maes2016diet}. 
-  Besides, bee-associated symbionts can aid in detoxification. 
-  They are involved in resistance to both metal and metalloid toxins including cadmium \citep{rothman2019cadmium}, copper \citep{rothman2020direct} and selenate \citep{rothman2019bumble}. 
-  \newline
-  Amplicon sequencing, in which a species-specific barcode region is amplified and sequenced, is a powerful method for investigations of microbiome \citep{abdelfattah2018metabarcoding}.  
-  It is vastly used in bee microbiome investigations to illustrate the taxonomic diversity of bee-associated bacteria and fungi (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}).
-  However, bees visit numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including bacteria, fungi, plants, arthropods and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
+  \citep{cariveau2014variation,maes2016diet}, 
+  and are involved in resistance to both metal and metalloid toxins including cadmium \citep{rothman2019cadmium}, copper \citep{rothman2020direct} and selenate \citep{rothman2019bumble}. 
+  \newline
+  Amplicon sequencing, in which a species-specific barcode region is amplified and sequenced, is a powerful and vastly used method for investigations of microbiome compositions \citep{abdelfattah2018metabarcoding}.
+  In bee microbiome investigations, it is used to illustrate the taxonomic diversity of bee-associated bacteria and fungi (\textit{e.g.} \cite{geldert2021dietary,wang2021gut,powell9field,kapheim2021composition}).
+  However, bees visit numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into pollinator ecology by reflecting interactions between bees and other organisms including bacteria, fungi, plants, arthropods and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
   It is difficult to explore this diversity via amplicon sequencing because it only captures a fraction of the whole community since analysis of different taxonomic groups is based on different barcode regions, \textit{e.g.} 16S ribosomal RNA (rRNA) for bacteria \citep{hayashi2002phylogenetic,eckburg2005diversity}, internal transcribed spacer (ITS) for fungi \citep{nilsson2008intraspecific}, cytochrome c oxidase subunit I (COI) for Animalia \citep{hebert2003barcoding}
@@
   Besides, it is difficult to illustrate function potentiality of bee-associated microbiome using amplicon sequencing since it does not provide information on content of functional gene clusters (FGCs), \textit{i.e.} aggregates of genes with same function.
-  As a result, functional capacity needs to be inferred based on reference genomes \citep{asshauer2015tax4fun,douglas2018predicting}. 
+  As a result, functional capacity needs to be inferred based on taxon composition. 
+  Amplicon-based function predictors such as Tax4Fun \citep{asshauer2015tax4fun} and PICRUSt \citep{douglas2018predicting} predict functional capacity based on pre-sequenced genomes without taking gene content variation within taxa.
   However, bee bacterial symbionts are diversified at strain level \citep{engel2012functional,powell2016strain,ellegaard2020vast} and bacterial strains are often highly variable in gene content \citep{cordero2014explaining,brockhurst2019ecology}.
-  As a result, amplicon sequencing-based inference of functional capacity of bee microbiome may not be reliable.
+  As a result, amplicon-based inference of functional capacity of bee microbiome may not be reliable.
   % Host-associated microbiome plays an important role in host homeostasis and metagenomics boosted by high throughput sequencing provides powerful tools for understanding its composition, function and dynamics.
@@
   \newline
-  Shotgun metagenomics provides an alternative for microbiome investigations to overcome drawbacks of amplicon sequencing. 
+  Shotgun metagenomics provides a solution for microbiome investigations to overcome drawbacks of amplicon sequencing. 
   By capturing and sequencing DNA fragments unselectively, shotgun metagenomics is capable of providing comprehensive inventories of taxa and FGCs \citep{quince2017shotgun,new2020metagenomics,galloway2020tools}.
   However, utilization of shotgun metagenomics is hindered by challenges in bioinformatics. 
-  Typical goal of metagenomics is to provide taxonomic and functional profile of microbiome, and there is not a golden standard for bioinformatics of metagenome. 
+  The goal of metagenomics is typically to provide a taxonomic and functional profile of the microbiome, and there is not a gold standard for performing metagenomic data analysis. 
+  % bioinformatics of metagenome. 
   Generally, one of the first steps in metagenomic analysis is assembling short reads into long contigs, which can help improve accuracy of metagenomic annotation \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling} and is necessary for
@@
   However, metagenome assembly is complex, compromised by fragmental assembly, chimaeras \citep{mikheenko2016metaquast} and loss of taxon/function diversity due to unassembled reads \citep{vollmers2017comparing,ayling2020new}.
-  Probably because of these shortcomings, assembly is skipped in some researches and short reads are directly proceeded for annotation \citep{tringe2005comparative,abubucker2012metabolic,vermote2018amplicon,bovo2018shotgun}, although the accuracy can be compromised due to low information load of short reads \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling}.
+  Probably because of these shortcomings, assembly is sometimes skipped and short reads are directly proceeded for annotation \citep{tringe2005comparative,abubucker2012metabolic,vermote2018amplicon,bovo2018shotgun}, although the accuracy can be compromised due to low information load of short reads \citep{wommack2008metagenomics,carr2014comparative,tran2020assembling}.
   A combination of both assembly-dependent and -free methods could overcome the complexity and improving accuracy of metagenomic profiling \citep{becker2020modular}.
@@
   Since a metagenomic dataset can be viewed as a random sample of an assemblage of genomic sequences, and profiling is the process by which reads are assigned to taxa or FGCs, the relationship between sequencing depth and diversity can be illustrated by rarefaction (randomly subsampling the original dataset without replacement) and quantified by model fitting, if the original dataset can provide an almost complete inventory of taxa/FGCs \citep{heck1975explicit,hortal2005ed,gomez2014using,hughes2021sampling}.
-  The sequencing depth is sufficient for reliable estimation of taxon/FGC diversity if and only if the slope of the model is small \citep{hortal2005ed,chao2012coverage,roswell2021conceptual}. 
+  The sequencing depth is sufficient for reliable estimation of taxon/FGC diversity if and only if the slope of the rarefaction curve is small \citep{hortal2005ed,chao2012coverage,roswell2021conceptual}.
   % The determination of sequencing depth can be conducted by rarefaction analysis, a method widely used in traditional ecology \citep{heck1975explicit,hortal2005ed,gomez2014using,hughes2021sampling}.
@@
   \newline
-  In this project, I utilised metagenomes from three environmental types: the gut of a honey bee (\textit{Apis mellifera}), the gut of a common North American bumble bee (\textit{Bombus impatiens}) and the surface of a flower (\textit{Erigeron annuus}).
+  In this project, I utilised metagenomic datasets ($2 \times 150 $bp) from three environmental types: the gut of honey bees (\textit{Apis mellifera}), the gut of common North American bumble bees (\textit{Bombus impatiens}) and the surface of a wild flower (\textit{Erigeron annuus}).
   I aimed to (1) develop an integrated pipeline combining assembly-dependent and -independent methods to deliver improved taxon annotation of sequencing data and (2) optimize sequencing depth to balance sequencing cost and requirement for reliable analysis of microbial species diversity, or the description of their functional diversity.
-  In the integrated pipeline (Figure \ref{Pipeline}), 
-  assembly-dependent taxon profiling is conducted after quality filtering and removing host contamination. 
-  To address high negative rate of assembly-dependent search, a reference database of genomes from species present in the assembly is constructed and used for filtering non-host reads. 
-  Reads not recruited by the reference database are subjected to assembly-free taxonomic search. 
-  This integrated pipeline was used to profile metagenomic datasets involved in this project. 
-  % It was shown that the construction of reference database and assembly-free search helped identified species not represented by the assembly. 
-  Then in order to estimate optimal sequencing depth for reliable representing taxonomic/functional diversity of metagenomes, I simulated different sequencing depth by rarefaction and profiled subsampled datasets using the integrated pipeline, generating inventories of species and FGCs represented by Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}.
-  Diversity of species and KOs was measured by Hill numbers of order 0, 1 and 2. 
-  Sequencing depth was measured by number of clean read pairs (150 bp read length). 
-  % The higher the order is, the more sensitive to relative abundances Hill number is. 
-  The relationship between Hill numbers and sequencing depth was quantified by fitting and averaging asymptotic species accumulation models, and estimation of optimal sequencing depth was given by the point where the slope of rarefaction curve drops to cut-off values.
-  % Sample would be excluded from optimization of sequencing depth if the original dataset was not sufficient for providing an almost complete inventory of species or KOs, which was characterized by small final slope of rarefaction curve for species or KO richness (Hill number of order 0).
-  % As a result, when measuring species diversity by Hill number of order 0, 1 and 2, the average optimal sequencing depth for honey bee samples are 40.33 million, 18.57 million and 17.45 million; for bumble bee samples, the averages are 42.49 million, 40.33 million and 24.77 million; and for flower surface, 0.88 million sequencing depth is not sufficient for providing an almost complete inventory of species, indicating higher sequencing depth is needed.
-  % As for functional diversity, no datasets involved in this project is big enough for providing an almost complete inventory of KOs, indicating the sequencing depth need to be higher than the maximum of each sample type, \textit{i.e.} 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
-  % The integrated pipeline and the framework for rarefaction analysis can also be applied for investigations of microbiomes from other environments, and the estimations of optimal sequencing depth provide guidelines for cost-effective utilization of shotgun metagenomics in investigations of pollination system.
+  The integrated pipeline provided improvement in species identification compared with the assembly-dependent method. 
+  Rarefaction analysis showed that about 40/43 million clean read pairs would be a suitable compromise for sequencing honey/bumble bee samples and species diversity detection. 
+  Shallower sequencing can be adopted with reduced emphasis on rare species. 
+  Functional profiling is more demanding about sequencing depth than species profiling. 
+  Significant accumulation of FGCs was observed at final points of rarefaction curves from all samples.  
+  These results provide guidelines for defining a balance between sequencing cost and obtaining reliable taxonomic/functional profiles for metagenomic investigations of pollination system. 
+  Similar studies for other host species are recommended before undertaking metagenomic projects with big sample size. 
+  % In the integrated pipeline (Figure \ref{Pipeline}), 
+  % assembly-dependent taxon profiling is conducted after quality filtering and removing host contamination. 
+  % To address high negative rate of assembly-dependent search, a reference database of genomes from species present in the assembly is constructed and used for filtering non-host reads. 
+  % Reads not recruited by the reference database are subjected to assembly-free taxonomic search. 
+  % This integrated pipeline was used to profile metagenomic datasets involved in this project. 
+  % % It was shown that the construction of reference database and assembly-free search helped identified species not represented by the assembly. 
+  % Then in order to estimate optimal sequencing depth for reliable representing taxonomic/functional diversity of metagenomes, I simulated different sequencing depth by rarefaction and profiled subsampled datasets using the integrated pipeline, generating inventories of species and FGCs represented by Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}.
+  % Diversity of species and KOs was measured by Hill numbers of order 0, 1 and 2. 
+  % Sequencing depth was measured by number of clean read pairs (150 bp read length). 
+  % % The higher the order is, the more sensitive to relative abundances Hill number is. 
+  % The relationship between Hill numbers and sequencing depth was quantified by fitting and averaging asymptotic species accumulation models, and estimation of optimal sequencing depth was given by the point where the slope of rarefaction curve drops to cut-off values.
+  % % Sample would be excluded from optimization of sequencing depth if the original dataset was not sufficient for providing an almost complete inventory of species or KOs, which was characterized by small final slope of rarefaction curve for species or KO richness (Hill number of order 0).
+  % % As a result, when measuring species diversity by Hill number of order 0, 1 and 2, the average optimal sequencing depth for honey bee samples are 40.33 million, 18.57 million and 17.45 million; for bumble bee samples, the averages are 42.49 million, 40.33 million and 24.77 million; and for flower surface, 0.88 million sequencing depth is not sufficient for providing an almost complete inventory of species, indicating higher sequencing depth is needed.
+  % % As for functional diversity, no datasets involved in this project is big enough for providing an almost complete inventory of KOs, indicating the sequencing depth need to be higher than the maximum of each sample type, \textit{i.e.} 45.06 million for honey bees, 53.61 million for bumble bees and 0.88 million for flower surface.
+  % % The integrated pipeline and the framework for rarefaction analysis can also be applied for investigations of microbiomes from other environments, and the estimations of optimal sequencing depth provide guidelines for cost-effective utilization of shotgun metagenomics in investigations of pollination system.
+
+  \section{Materials and Methods}
+    \subsection{Samples, DNA extraction and sequencing}
+    Samples include four honey bees (two from the same hive (hive 13), one from a hive in the same apiary (hive 15) and one caught foraging), three bumble bees from commercially supplied (Biobest) bumblebee colonies (two from the same colony), and one buffer wash of a wild flower (\textit{Erigeron annuus}).
+    \newline
+    DNA extraction was performed as in \cite{graystock2020dominant}, followed by library preparation using a low template protocol with Illumina Nextera Library Prep kits.
+Briefly, this involved tagmentation into fragments of 300 bases before eight samples of 10ng were pooled together and sent to Beijing Genomics Institute (BGI) for further quality control and sequencing using a full lane in the X-ten platform.
+
+    \subsection{Metagenomic profiling using integrated pipeline}
+      \subsubsection{Integrated pipeline}
 
@@
 
-  \section{Materials and Methods}
-    \subsection{Samples, DNA extraction and sequencing}
-    Samples include four honey bees (two from the same hive (hive 13), one from a hive in the same apiary (hive 15) and one caught foraging), three bumble bees from commercially supplied (Biobest) bumblebee colonies (two from the same colony), and one buffer wash of a wild flower (\textit{Erigeron annuus}).
-    \newline
-    DNA extraction was performed as in \cite{graystock2020dominant}, followed by library preparation using a template protocol with Illumina Nextera Library Prep kits.
-Briefly, this involved tagmentation into fragments of 300 bases before eight samples of 10ng were pooled together and sent to Beijing Genomics Institute for further quality control and sequencing using a full lane in the X-ten platform.
-
-    \subsection{Metagenomic profiling using integrated pipeline}
-      \subsubsection{Integrated pipeline}
-      The integrated pipeline was designed for shotgun metagenomic profiling, \textit{i.e.} assigning reads to taxa or FGCs. 
+      I designed an integrated pipeline for shotgun metagenomic profiling, \textit{i.e.} assigning reads to taxa or FGCs. 
       It is separated into five modules (Figure \ref{Pipeline}).
@@
       \newline
-      Then fragment recruitment is conducted. 
+      Then fragment recruitment is conducted to filter reads mapped to species represented by the assembly. 
       A reference database is constructed and it comprises reference genome dataset, \textit{i.e.} genomic sequences in FASTA format and corresponding genome annotation in general feature format (gff).
@@
       Finally, functional annotation is conducted by EggNOG-mapper v.2.1.2 \citep{huerta2017fast}. 
-      It takes coding sequences (CDSs) of genomes in the reference database and reads subject to assembly-independent species identification as input and assigns them to KOs.
-      \newline
-      The integrated pipeline was used for analyzing metagenomic datasets involved in this study and details in parameter settings of each module are described in Supplementary \ref{ParameterSetting}.
+      It takes coding sequences (CDSs) of genomes in the reference database and reads subject to assembly-independent species identification as input and assigns them to Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) \citep{kanehisa2000kegg}.
+      \newline
+      The integrated pipeline was used for analysing metagenomic datasets involved in this study. 
+      Details in the pipeline and parameter settings of each module are described in Supplementary \ref{ParameterSetting}.
 
@@
       Reads mapped to non-coding regions were not taken into consideration in order to avoid overestimation since the assembly-independent search was based on aligning reads to nr database, which is composed of proteins.
-      As for KO quantification, CDSs with zero-coverage were excluded. 
+      As for KO quantification, CDSs with zero coverage were excluded. 
       Abundances of KOs were calculated by summating number of reads that (1) mapped to CDSs assigned to KOs and (2) assigned to KOs directly. 
@@
 
-      \subsubsection{Simulating different sequencing depth by subsampling and measuring diversity by Hill numbers}
+      \subsubsection{Simulating different sequencing depth by subsampling and diversity measured using Hill numbers}
       Species/KO inventories obtained from different sequencing depth was simulated by rarefaction. 
@@
       \newline
-      After profiling subsampled datasets, species/KO diversity was measured by Hill numbers of order $q$, defined as Equation \ref{HillNumbers} \citep{hill1973diversity}.
+      After profiling subsampled datasets, species/KO diversity was measured by Hill number, a parametric family of diversity indexes differing by order $q$ \citep{hill1973diversity,ma2018measuring,roswell2021conceptual}.
+      Hill numbers provide unique advantages over other diversity indexes \citep{chao2014unifying,chao2014rarefaction,alberdi2019guide,roswell2021conceptual}. 
+      First, Hill numbers follow a replication principle: if a proportion of categories in an inventory was removed randomly, all Hill numbers are expected to decrease by that proportion. 
+      Second, the sensitivity of Hill numbers to relative abundances can be modulated by order $q$. 
+      % Third, all Hill numbers are pressed in the units of effective numbers of species: the number of equally abundant species in an imaginary inventory with the same diversity. 
+      Third, widely used diversity indexes including species richness, Shannon index and Simpson index, can be converted to Hill numbers through algebraic transformations. 
+      \newline
+      Hill number of order $q$ is defined as Equation \ref{HillNumbers} \citep{hill1973diversity}.
       \begin{equation}
@@
       \end{equation}
-      $p_i$ represents the relative abundance of $i$th species/KO, and $q$ determines sensitivity to relative abundances. 
+      $p_i$ represents the relative abundance of $i$th species/KO. 
       When $q = 0$, abundances are not taken into consideration and $D^{(0)}$ equals species/KO richness. 
-      When $q = 1$, Hill number is defined as the limit of Equation \ref{HillNumbers} as $q$ tends to 1 (\ref{HillShannon}) and emphasis is given to species/KOs with general abundances.
+      When $q = 1$, emphasis is given to species/KOs with general abundances. 
+      Hill number is defined as the limit of Equation \ref{HillNumbers} as $q$ tends to 1 and equals the exponential of Shannon index (\ref{HillShannon}).  
       \begin{equation}
@@
       Order $q$ determines leverage given to abundant categories. 
-      All Hill numbers behave in the following way: if a proportion of categories in an inventory was removed randomly, all Hill numbers would decrease by that proportion \citep{roswell2021conceptual}.
+      All Hill numbers behave in the following way: removing a proportion of categories in an inventory randomly is expected to cause decrease of Hill numbers in that proportion \citep{roswell2021conceptual}.
       Thus, it can be hypothesized that as sequencing depth (number of clean read pairs) increases, the detection of novel species/KOs leads to increase of Hill numbers, and when sequencing depth is so big that all species/KOs present in the metagenomic DNA sample have been detected, Hill numbers level off.
@@
     After quality control, 62.08\%-76.52\% of raw read pairs were retained for these three honey bee samples. 
-    Then a different proportion of non-host read pairs (29.52\%-86.19\%) were retained. 
+    Then a different proportion of non-host read pairs (29.52\%-86.19\%) were retained from each sample. 
     As for bumble bee samples, about 58 million raw read pairs were obtained for each sample and 82.1\%-83.8\% were retained after quality control. 
@@
     For flower eDNA sample, 1.44 million raw read pairs were obtained and 61.15\% of them were retained. 
+    Host removing was not conducted because it is a sample of eDNA washed from flower surface.
 
@@
     The integrated pipeline was used to profile metagenomic datasets from pollination system, illustrating its capacity in presenting taxon composition and functional potentiality of microbiome. 
-    Although samples are different in proportion of host contamination (Table \ref{data_statistics}, Figure \ref{GroupAbundance}a), diverse communities composed of multiple taxonomic clades were identified (Figure \ref{GroupAbundance}b), and most species identified are common in pollination system.
+    Although samples are different in proportion of host contamination (Table \ref{data_statistics}, Figure \ref{GroupAbundance}a), diverse communities composed of multiple taxonomic clades were identified (Figure \ref{GroupAbundance}b).
+    Most species identified are common in pollination system. 
+    Their present indicate that samples were of good quality and representative for microbiomes from pollination system. 
     % All seven samples were dominated by bacterial and/or arthropod species (Figure \ref{GroupAbundance}b). 
@@
         \begin{subfigure}
+          \centering
           \textbf{b}
@@
         % \vfill
-        \caption{a. The number of host and non-host reads in each sample. 
-        b.
-The relative abundance of species under six taxonomic groups: superkingdom Viruses, superkingdom Bacteria, kingdom Viridiplantae (plants), kingdom Fungi, phylum Arthropoda and others (species that are not in the other five groups).}
+        \caption{The number of host and non-host reads in each sample (a) and the relative abundance of species under six taxonomic groups (b): superkingdom Viruses, superkingdom Bacteria, kingdom Viridiplantae (plants), kingdom Fungi, phylum Arthropoda and others (species that are not in the other five groups).}
         \label{GroupAbundance}
@@
 
-    The present of core members of bee-associated bacterial community including species within \textit{Bifidobacterium}, \textit{Frischella}, \textit{Gilliamella}, \textit{Snodgrassella}, \textit{Lactobacillus}, \textit{Apilactobacillus} and \textit{Bombilactobacillus} (Figure \ref{BacteriaHeatmap}) \citep{koch2011bacterial,moran2015genomics,kwong2017dynamic,zheng2020taxonomic} suggests good sample quality.
+    The presence of known core members of bee-associated bacterial community including species within \textit{Bifidobacterium}, \textit{Frischella}, \textit{Gilliamella}, \textit{Snodgrassella}, \textit{Lactobacillus}, \textit{Apilactobacillus} and \textit{Bombilactobacillus} (Figure \ref{BacteriaHeatmap}) \citep{koch2011bacterial,moran2015genomics,kwong2017dynamic,zheng2020taxonomic} suggests good sample quality.
     As for other abundant bacteria, \textit{Fructobacillus sp.} are often found in fructose-rich environments like flowers \citep{endo2014genus}; \textit{Bartonella apis} is related to animal pathogens \citep{kevsnerova2016bartonella} and is widespread in honey bee workers \citep{raymann2018role}; \textit{Candidatus Schmidhempelia bombi} is a known uncultured symbiont of \textit{Bombus impatiens} \citep{martinson2014genomic}.
@@
     \newline
-    Fungal and viruse species were identified. 
+    Fungal and virus species were identified. 
     In fungal communities of most samples, \textit{Nosema ceranae}, a widespread bee pathogen, was the dominant species. (Figure \ref{FungusHeatmap}). 
@@
         \begin{subfigure}
-          \centering
+
           \textbf{b}
@@
         \begin{subfigure}
-          \centering
+
           \textbf{c}
@@
         \caption{Integrated pipeline improves the detection of species richness. 
-        The horizonal axis represents sequencing depth, and the vertical axis represents growth rate of detected species richness comparing the integrated pipeline and assembly-dependent species identification.
+        The horizontal axis represents sequencing depth, and the vertical axis represents growth rate of detected species richness comparing the integrated pipeline and assembly-dependent species identification.
         Different sequencing depth was simulated by rarefaction.
@@
     In order to determine the influence of sequencing depth and thus optimize sequencing depth for 
-    analysing taxonomic and functional diversity, rarefactiona anlysis was conducted. 
+    analysing taxonomic and functional diversity, rarefaction analysis was conducted. 
     Different sequencing depth was simulated by randomly subsampling original datasets at proportions from 10\% to 90\% at an interval of 10\%. 
@@
       \end{subfigure}
-      \caption{Rarefaction curves for species (a, b, c) or KO (d, e, f) richness (Hill number of order 0). 
-      The horizonal axis represents sequencing depth, and the vertical axis represents richness. 
+      \caption{Rarefaction curves for species (a, b, c) or Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs) (d, e, f) richness (Hill number of order 0). 
+      The horizontal axis represents sequencing depth, and the vertical axis represents richness. 
       Sample type is shown in the top left of each subfigure. 
-      Note that the scale of horizonal axis in subfigure c and f is much smaller than that in other subfigures.}
+      Note that the scale of horizontal axis in subfigure c and f is much smaller than that in other subfigures.}
       \label{RichnessAccumulation}
@@
         \centering
-        \caption{Summary of final point of rarefaction curve for species/KO richness (Hill number of order 0). 
+        \caption{Summary of final point of rarefaction curve for richness (Hill number of order 0) of species or Kyoto Encyclopedia of Genes and Genomes (KEGG) orthologies (KOs). 
       Type: indicates whether this row reports rarefaction curve for species or KO richness. 
       Depth: sequencing depth taking million read pairs as unit. 
-      OR: observed species/KO richness. 
-      ER: expected species/KO richness predicted by modeling rarefaction curve. 
-      FS: final slope of rarefaction curve. 
-      Asym: asymptote calculated by modeling rarefaction curve. 
-      Comp: completeness, represented by ratio between ER and Asym.}
+      Observed richness: observed species/KO richness. 
+      Expected richness: expected species/KO richness predicted by modelling rarefaction curve. 
+      Final slope: final slope of rarefaction curve. 
+      Asymptote: asymptote as sequencing depth tends to infinity, calculated by modelling rarefaction curve. 
+      Completeness: ratio between expected richness and asymptote.}
       \label{RichnessModelSlope}
-      \resizebox{\textwidth}{!}{%
+      \resizebox{500pt}{!}{%
       \begin{tabular}{cccccccc} %ccccccc
       \toprule
-Sample                           &Type   &Depth &OR  & ER          & FS      & Asym    & Comp \\ \midrule
+Sample                           &Type   &Depth &Observed richness  & Expected richness          & Final slope      & Asymptote    & Completeness \\ \midrule
 \textit{Bee\_Amellifera\_hv13\_2}&species&35.28 &144 & 146.69      & 1.0958  & 184.94  & 0.7931 \\
@@
       % \caption{Rarefaction curves for species richness (Hill number of order 0). 
-      % The horizonal axis represents sequencing depth, and the vertical axis represents species richness. 
+      % The horizontal axis represents sequencing depth, and the vertical axis represents species richness. 
       % Sample type is shown in the top left of each subfigure.}
@@
         % \caption{Rarefaction curves for KO richness (Hill number of order 0). 
-        % The horizonal axis represents sequencing depth, and the vertical axis represents KO richness. 
+        % The horizontal axis represents sequencing depth, and the vertical axis represents KO richness. 
         % Sample type is shown in the top left of each subfigure.}
@@
     For bumble bee samples, the average optimal sequencing depth are 40.33 million ($q = 1$) and 24.77 million ($q = 2$).
+
     \begin{table}[H]
       \centering
-        \caption{Summary of minimal sequencing depth estimated from different cut-off values of slope. 
-        Minimal sequencing depth was estimated by the point at which the slope of rarefaction curve drops to a cut-off value (0.5, 0.1, 0.05 or 0.01), which is indicated in names of columns. 
-        For example, MinD\_0.5 represents estimated minimal sequencing depth taking 0.5 as cut-off value, and ED\_0.5 is expected Hill number from MinD\_0.5.
-Comp\_0.5 is the ratio between OptDiv\_0.5 and the asymptote (represented by Asym).
-        Unit of sequencing depth is million read pairs. 
-        $q$ refers to order of Hill number determining sensitivity to species abundance distribution.}
+      \caption{Summary of optimal sequencing depth estimated from different cut-off values of slope. 
+      Optimal sequencing depth was estimated by the point at which the slope of rarefaction curve drops to a cut-off value (0.5, 0.1, 0.05 or 0.01). 
+      $q$: order of Hill number that determines sensitivity to species abundances. 
+      Asymptote: asymptote as sequencing depth tends to infinity, calculated by modelling rarefaction curve. 
+      Depth: optimal sequencing depth taking million read pairs as unit.  
+      Expected diversity: expected Hill number provided by the optimal sequencing depth.   
+      Completeness: ratio between expected diversity and asymptote.}
       \label{MinDepth}
-        \resizebox{\textwidth}{!}{%
-        \begin{tabular}{ccccccccccccccc} % lllllllllllllll
-        \toprule
-Sample&$q$&Asym  &MinD\_0.5&ED\_0.5&Comp\_0.5  &MinD\_0.1&ED\_0.1&Comp\_0.1  &MinD\_0.05&ED\_0.05&Comp\_0.05  &MinD\_0.01&ED\_0.01&Comp\_0.01 \\ \midrule
-% \textit{Bee\_Amellifera\_hv13\_1}&0&4262.21 &1373.18&4022.37&0.9437 &2142.41&4213.53&0.9886 &2473.90&4237.44&0.9942 &3244.93&4256.60&0.9987\\
-% \textit{Bee\_Amellifera\_hv13\_2}&0&184.94  &59.87&165.10&0.8927  &120.88&179.94&0.9730  &149.83&182.02&0.9842&226.97&183.88&0.9942\\
+      \resizebox{500pt}{!}{%
+      \begin{tabular}{ccccccccccccccc}
+      \hline
+      \multirow{2}{*}{Sample} & \multirow{2}{*}{\textit{q}} & \multirow{2}{*}{Asymptote} & \multicolumn{3}{c}{Slope $ < 0.5$} & \multicolumn{3}{c}{Slope $< 0.1$} & \multicolumn{3}{c}{Slope $< 0.05$}  & \multicolumn{3}{c}{Slope $< 0.01$}  \\ \cline{4-15} & & & Depth & \makecell[c]{Expected\\diversity} &Completeness & Depth & \makecell[c]{Expected\\diversity} & Completeness & Depth & \makecell[c]{Expected\\diversity} & Completeness & Depth & \makecell[c]{Expected\\diversity} & Completeness \\ \hline
       \textit{Bee\_Amellifera\_hv15\_1}&0&88.84  &23.54&84.85 &0.9551  &36.27&87.99 &0.9905  &41.95&88.40 &0.9951  &55.75&88.74 &0.9989\\
       \textit{Bee\_Amellifera\_wild\_1}&0&176.84 &30.53&172.46&0.9752  &44.39&175.88&0.9946  &50.57&176.33&0.9971  &65.86&176.70&0.9992\\
-
-% \textit{Bee\_Amellifera\_hv13\_1}&1&7.06  &0.06&6.56&0.9296  &0.63&6.66&0.9434  &1.30&6.71&0.9501  &3.41&6.76&0.9571\\
-% \textit{Bee\_Amellifera\_hv13\_2}&1&16.01 &5.55&15.03&0.9385 &8.70&15.81&0.9872 &10.08&15.91&0.9934  &13.34&15.99&0.9984\\
       \textit{Bee\_Amellifera\_hv15\_1}&1&12.28  &3.18 &10.67 &0.8699  &5.83 &11.33 &0.9224  &7.21 &11.43 &0.9304  &15.21&11.58 &0.9429\\
       \textit{Bee\_Amellifera\_wild\_1}&1&14.77  &0.69 &13.49 &0.9137  &3.30 &14.03 &0.9498  &6.20 &14.23 &0.9635  &21.93&14.58 &0.9868\\  
-
-% \textit{Bee\_Amellifera\_hv13\_1}&2&4.85   &0.02 &4.26  &0.8789  &0.20 &4.29 &0.8848  &0.94&4.34 &0.8950  &4.27 &4.42 &0.9115\\
-% \textit{Bee\_Amellifera\_hv13\_2}&2&11.00  &4.47 &10.15 &0.9232  &7.20 &10.83&0.9845  &8.38&10.91&0.9922  &11.14&10.98&0.9984\\
-\textit{Bee\_Amellifera\_hv15\_1}&2&8.40   &3.10 &6.35  &0.7561  &8.17 &7.49  &0.8909  &11.97&7.75  &0.9229  &27.99&8.11 &0.9655\\
-\textit{Bee\_Amellifera\_wild\_1}&2&9.88   &0.18 &9.49  &0.9602  &0.90 &9.63  &0.9747  &1.73 &9.69  &0.9805  &6.91 &9.80  &0.9916\\
-
       \textit{Bee\_Bimpatiens\_hv3\_1}&0&90.79  &30.80&83.69&0.9218  &52.03&88.85&0.9786  &62.56&89.61&0.9870  &92.35&90.32&0.9948\\
@@
       \textit{Bee\_Bimpatiens\_hv4\_2}&2&7.12   &2.90 &5.34 &0.7493  &7.47 &6.38 &0.8961  &10.58&6.60 &0.9270  &23.73&6.90 &0.9683\\          
-
-% \textit{Flower\_eDNA}&0&3034.88 &922.36&2870.43&0.9458  &1428.16&2996.00&0.9872  &1648.07&3011.86&0.9924  &2173.39&3024.82& 0.9967\\
-% \textit{Flower\_eDNA}&1&6.46    &0.74  &5.59   &0.8656  &2.89   &6.07   &0.9399  &4.50   &6.19   &0.9575  &11.30  &6.34   & 0.9810\\
-% \textit{Flower\_eDNA}&2&4.40    &0.55  &3.50   &0.7940  &2.47   &3.92   &0.8910  &3.93   &4.03   &0.9145  &10.24  &4.17   & 0.9463\\
-        \bottomrule
+      \hline
       \end{tabular}%
@@
 
+%       \begin{table}[H]
+%         \centering
+%         \caption{Summary of minimal sequencing depth estimated from different cut-off values of slope. 
+%         Minimal sequencing depth was estimated by the point at which the slope of rarefaction curve drops to a cut-off value (0.5, 0.1, 0.05 or 0.01), which is indicated in names of columns. 
+%         For example, MinD\_0.5 represents estimated minimal sequencing depth taking 0.5 as cut-off value, and ED\_0.5 is expected Hill number from MinD\_0.5.
+Comp\_0.5 is the ratio between OptDiv\_0.5 and the asymptote (represented by Asym).
+%         Unit of sequencing depth is million read pairs. 
+%         $q$ refers to order of Hill number determining sensitivity to species abundance distribution.}
+%         \label{MinDepth}
+%         \resizebox{500pt}{!}{%
+%         \begin{tabular}{ccccccccccccccc} % lllllllllllllll
+%         \toprule
+% Sample&$q$&Asym  &MinD\_0.5&ED\_0.5&Comp\_0.5  &MinD\_0.1&ED\_0.1&Comp\_0.1  &MinD\_0.05&ED\_0.05&Comp\_0.05  &MinD\_0.01&ED\_0.01&Comp\_0.01 \\ \midrule
+% % \textit{Bee\_Amellifera\_hv13\_1}&0&4262.21 &1373.18&4022.37&0.9437 &2142.41&4213.53&0.9886 &2473.90&4237.44&0.9942 &3244.93&4256.60&0.9987\\
+% % \textit{Bee\_Amellifera\_hv13\_2}&0&184.94  &59.87&165.10&0.8927  &120.88&179.94&0.9730  &149.83&182.02&0.9842&226.97&183.88&0.9942\\
+% \textit{Bee\_Amellifera\_hv15\_1}&0&88.84  &23.54&84.85 &0.9551  &36.27&87.99 &0.9905  &41.95&88.40 &0.9951  &55.75&88.74 &0.9989\\
+% \textit{Bee\_Amellifera\_wild\_1}&0&176.84 &30.53&172.46&0.9752  &44.39&175.88&0.9946  &50.57&176.33&0.9971  &65.86&176.70&0.9992\\
+
+% % \textit{Bee\_Amellifera\_hv13\_1}&1&7.06  &0.06&6.56&0.9296  &0.63&6.66&0.9434  &1.30&6.71&0.9501  &3.41&6.76&0.9571\\
+% % \textit{Bee\_Amellifera\_hv13\_2}&1&16.01 &5.55&15.03&0.9385 &8.70&15.81&0.9872 &10.08&15.91&0.9934  &13.34&15.99&0.9984\\
+% \textit{Bee\_Amellifera\_hv15\_1}&1&12.28  &3.18 &10.67 &0.8699  &5.83 &11.33 &0.9224  &7.21 &11.43 &0.9304  &15.21&11.58 &0.9429\\
+% \textit{Bee\_Amellifera\_wild\_1}&1&14.77  &0.69 &13.49 &0.9137  &3.30 &14.03 &0.9498  &6.20 &14.23 &0.9635  &21.93&14.58 &0.9868\\
+
+% % \textit{Bee\_Amellifera\_hv13\_1}&2&4.85   &0.02 &4.26  &0.8789  &0.20 &4.29 &0.8848  &0.94&4.34 &0.8950  &4.27 &4.42 &0.9115\\
+% % \textit{Bee\_Amellifera\_hv13\_2}&2&11.00  &4.47 &10.15 &0.9232  &7.20 &10.83&0.9845  &8.38&10.91&0.9922  &11.14&10.98&0.9984\\
+% \textit{Bee\_Amellifera\_hv15\_1}&2&8.40   &3.10 &6.35  &0.7561  &8.17 &7.49  &0.8909  &11.97&7.75  &0.9229  &27.99&8.11 &0.9655\\
+% \textit{Bee\_Amellifera\_wild\_1}&2&9.88   &0.18 &9.49  &0.9602  &0.90 &9.63  &0.9747  &1.73 &9.69  &0.9805  &6.91 &9.80  &0.9916\\
+
+% \textit{Bee\_Bimpatiens\_hv3\_1}&0&90.79  &30.80&83.69&0.9218  &52.03&88.85&0.9786  &62.56&89.61&0.9870  &92.35&90.32&0.9948\\
+% \textit{Bee\_Bimpatiens\_hv4\_1}&0&62.92  &24.83&57.22&0.9093  &42.76&61.61&0.9791  &51.24&62.22&0.9887  &73.55&62.76&0.9973\\
+% \textit{Bee\_Bimpatiens\_hv4\_2}&0&85.69  &21.75&82.30&0.9604  &32.67&85.01&0.9920  &37.39&85.35&0.9960  &48.40&85.62&0.9992\\
+
+% \textit{Bee\_Bimpatiens\_hv3\_1}&1&21.59  &3.63 &10.50&0.4862  &9.47 &11.76&0.5449  &15.37&12.18&0.5639  &58.09&13.04&0.6040\\
+% \textit{Bee\_Bimpatiens\_hv4\_1}&1&11.85  &3.80 &9.45 &0.7973  &10.15&10.87&0.9174  &14.68&11.19&0.9445  &31.22&11.57&0.9766\\
+% \textit{Bee\_Bimpatiens\_hv4\_2}&1&12.66  &4.17 &10.24&0.8087  &10.47&11.67&0.9213  &14.85&11.98&0.9458  &31.68&12.36&0.9760\\
+
+% \textit{Bee\_Bimpatiens\_hv3\_1}&2&8.73   &2.20 &6.16 &0.7051  &6.28 &7.06 &0.8088  &9.45 &7.28 &0.8344  &23.89&7.60 &0.8708\\
+% \textit{Bee\_Bimpatiens\_hv4\_1}&2&8.33   &3.12 &6.28 &0.7540  &8.52 &7.50 &0.9002  &12.30&7.76 &0.9323  &26.68&8.09 &0.9718\\
+% \textit{Bee\_Bimpatiens\_hv4\_2}&2&7.12   &2.90 &5.34 &0.7493  &7.47 &6.38 &0.8961  &10.58&6.60 &0.9270  &23.73&6.90 &0.9683\\
+
+% % \textit{Flower\_eDNA}&0&3034.88 &922.36&2870.43&0.9458  &1428.16&2996.00&0.9872  &1648.07&3011.86&0.9924  &2173.39&3024.82& 0.9967\\
+% % \textit{Flower\_eDNA}&1&6.46    &0.74  &5.59   &0.8656  &2.89   &6.07   &0.9399  &4.50   &6.19   &0.9575  &11.30  &6.34   & 0.9810\\
+% % \textit{Flower\_eDNA}&2&4.40    &0.55  &3.50   &0.7940  &2.47   &3.92   &0.8910  &3.93   &4.03   &0.9145  &10.24  &4.17   & 0.9463\\
+%         \bottomrule
+%         \end{tabular}%
+%         }
+%         \end{table}
+
 \section{Discussion}
@@
 Here, I constructed an integrated pipeline combining assembly-dependent and -independent methods for taxonomic and functional profiling of shotgun metagenomics, and applied it to analysis of metagenomes from honey bees, bumble bees and flower washes.
-The profiling results showed that the integrated pipeline is able to capture taxonomic diversity by identifying species from multiple clades and infer metabolic potentiality of metagenome by providing information on FGC content.
-It can be more sensitive in species identification compared with standard assembly-dependent methods. 
+The profiling results showed that the integrated pipeline is able to determine a comprehensive view of the taxonomic diversity (across multiple clades) and infer functional potentiality of metagenome by providing information on FGC content.
+The developed method is more sensitive to species identification compared with standard assembly-dependent methods. 
 Then I computed expected species/FGC diversity represented by given sequencing depth through rarefaction analysis, in order to optimize sequencing depth to balance cost and reliability of analysis results.
@@
 \newline
-The integrated pipeline (Figure \ref{Pipeline}) for taxonomic and functional profiling of metagenome provides several advantages. 
+The integrated pipeline for taxonomic and functional profiling of metagenome provides several advantages. 
 First, through combination with assembly-free taxon search, it helps solve high false negative rate associated with assembly-dependent species identification, which is caused by reads left unassembled.
-This was shown by analyzing real metagenomic datasets from pollination system and simulating different sequencing depth by rarefaction (Figure \ref{CompareSensitivity}). 
+This was shown by analysing real metagenomic datasets from pollination system and simulating different sequencing depth by rarefaction. 
 Second, the modularity of integrated pipeline provides flexibility for incorporation of alternative tools. 
 For example, BWA aligner \citep{li2009fast} serves as an alternative for Bowtie2, and SPAdes can be replaced by other metagenomic assemblers such as Megahit \citep{li2015megahit} and IDBA-UD \citep{peng2012idba}.
-Third, the output files generated by each step are recorded and can be inspected easily, which provides transparence for troubleshooting. 
-However, the performance of integrated pipeline need to be evaluated more comprehensively by analysis of mock datasets and comparison with other profiling strategies. 
-Standardized mock dataset can be used to benchmark sensitivity and accuracy of integrated pipeline since it is an artificial metagenome with predefined diversity, generated by combining known sequences from different species \citep{vollmers2017comparing,sczyrba2017critical,becker2020modular}.
-Besides, the performance of integrated pipeline need to be compared with other widely used analysis strategies, such as MG-RAST \citep{meyer2008metagenomics}, SqueezeMeta \citep{tamames2019squeezemeta} and Kraken \citep{wood2014kraken}.
+Third, the output files generated by each step are recorded and can be inspected easily, which provides transparency for troubleshooting. 
+However, the performance of integrated pipeline would to be evaluated more comprehensively by further analysis of different datasets and comparison with other profiling strategies. 
+Metagenomes from other host species could be used to illustrate the performance of integrated pipeline. 
+Standardized mock metagenomes, even though they are less complex than real ones, could also be used to benchmark sensitivity and accuracy of integrated pipeline since it is an artificial metagenome with predefined diversity, generated by combining known sequences from different species \citep{vollmers2017comparing,sczyrba2017critical,becker2020modular}.
+Further, the performance of integrated pipeline in metagenome profiling could be further benchmarked against other analysis strategies, such as MG-RAST \citep{meyer2008metagenomics}, SqueezeMeta \citep{tamames2019squeezemeta} and Kraken \citep{wood2014kraken}.
 % High throughput sequencing provides approaches including amplicon sequencing and shotgun metagenomics for investigations of bee-associated microbiome, which imposes significant impact on bee health \citep{engel2016bee,raymann2018role,bonilla2018functional}.
@@
 % The advantages of shotgun metagenomics over amplicon sequencing are valuable for investigations in bee-associated microbiome for two reasons. 
-% First, bees vist numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including plants, arthropods, bacteria and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
+% First, bees visit numerous niches during environment exploration and foraging activities, and can get contact with diverse eDNA signatures, which provide insight into bee ecology by reflecting interactions between bees and other organisms including plants, arthropods, bacteria and viruses \citep{bovo2018shotgun,ribani2020honey,bovo2020shotgun,matsuzawa2020application}.
 % These materials represent a diverse assemblage which is difficult to be profiled comprehensively via amplicon sequencing. 
@@
 \newline
-The integrated pipeline was used to analyze metagenomes of bees and flower washes, illustrating their taxon composition and metabolic potentiality. 
-Bee-associated microorganisms were identified in flower washes, including both pathogens (\textit{e.g.} \textit{Nosema ceranae} and \textit{Apis mellifera filamentous virus}) and symbionts (\textit{e.g.} \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}) (Figure \ref{BacteriaHeatmap}, \ref{FungusHeatmap} and \ref{ViruseHeatmap}).
-Flowers have been indicated as hubs for transmission of bee pathogens \cite{durrer1994shared,koch2017role}. 
-Through shared flower use, multiple pathogens transmit between pollinators, including \textit{Nosema ceranae} \citep{furst2014disease} and \textit{Crithidia bombi} \citep{figueroa2019bee}. 
+The integrated pipeline was used to analyse metagenomes of bees and flower washes, illustrating their taxon composition and metabolic potentiality. 
+Bee-associated microorganisms were identified in flower washes, including both pathogens (\textit{e.g.} \textit{Nosema ceranae} and \textit{Apis mellifera filamentous virus}) and symbionts (\textit{e.g.} \textit{Bifidobacterium asteroides}, \textit{Bombilactobacillus mellis} and \textit{Gilliamella apicola}).
+Flowers have been indicated as hubs for transmission of bee pathogens \cite{durrer1994shared,koch2017role,graystock2020dominant}. 
+Through shared flower use, multiple pathogens transmit between pollinators, including \textit{Nosema ceranae} \citep{graystock2015parasites} 
+% furst2014disease
+and \textit{Crithidia bombi} \citep{figueroa2019bee}. 
 There is also growing evidence for present of bee symbionts on flower \citep{mcfrederick2012environment,mcfrederick2017flowers,keller2020more,vannette2020floral}.
 However, its role in bee microbiome assembly and functional importance in pollination remains an open question \citep{keller2020more,vannette2020floral}. 
-As for function profiling, it is indicated that bee-associated microbiome is capable of metabolizing carbohydrates such as glucose, fructose, sucrose and mannose (Figure \ref{Carbohydrate}). 
+As for function profiling, it is indicated that bee-associated microbiome is capable of metabolizing carbohydrates such as glucose, fructose, sucrose and mannose. 
 Carbohydrates are main component of bee diet and microbiome-mediated carbohydrate-processing have been vastly investigated \citep{engel2012functional,lee2015saccharide,lee2018differential,taylor2019effect}.
-Besides, pathways for metabolism of all ten essential amino acids for honey bees \citep{groot1953protein} were inferred (Figure \ref{AminoAcid}). 
+Besides, pathways for metabolism of all ten essential amino acids for honey bees \citep{groot1953protein} were inferred. 
 Essential amino acids are crucial for bee health \citep{simcock2014single,paoli2014dietary,stabler2015nutrient,hendriksma2019effects} and influence feeding preference due to their potential deficiency in single pollen source \citep{cook2003honey,hendriksma2014amino,hendriksma2016honey}.
@@
 Here, expected species/KO diversity provided by given sequencing depth was estimated by rarefaction and model fitting, using datasets from honey bees, bumble bees and flower washes. 
-It was shown that increasing sequencing depth boosted identification of species/KO (Figure \ref{RichnessAccumulation}, Table \ref{RichnessModelSlope}), highlighting value of deep metagenomic sequencing.
-For function profiling, no dataset involved here is big enough to provide an almost complete inventory of KOs (Table \ref{RichnessModelSlope}) even though most samples were deeply sequenced (Table \ref{QC}), indicating such task is demanding about sequencing depth.
+It was shown that increasing sequencing depth boosted identification of species/KO, highlighting value of deep metagenomic sequencing. 
+For function profiling, no dataset involved here is big enough to provide an almost complete inventory of KOs even though most samples were deeply sequenced, indicating such task is demanding about sequencing depth.
 Therefore, when dealing with function potentiality of microbiome associated with bees or flowers, retrieving as many reads as possible would be recommended. 
-As for species profiling, although deep sequencing is still valuable, sequencing depth can be optimized when the budget is limited (Table \ref{MinDepth}), especially when low leverage is given to rare species.
+As for species profiling, although deep sequencing is still valuable, sequencing depth can be optimized when the budget is limited, especially when low leverage is given to rare species. 
 For honey bees, approximate 40 million sequencing depth (12 Gbp) can be sufficient for representing species richness. 
@@
 Here, I constructed an integrated pipeline for analysis of shotgun metagenomic data. 
-It provides benefits in terms of results, flexibility and transparence. 
+It provides benefits in terms of results, flexibility and transparency. 
 % The pipeline was used for profiling metagenomic datasets from pollination system. 
 I also constructed a framework for optimizing depth of shotgun metagenomic sequencing in order to balance high cost of sequencing and reliability of analysis results. 
-The pipeline and the framework were used for analysis of real datasets from pollination system, providing guidelines for cost-effective metagenomic investigations of bee- and flower-associated microbiomes.
+The pipeline and the framework were used for analysis of real datasets from pollination system. 
+For species diversity detection, about 40 million clean $2 \times 150$ bp read pairs would be sufficient honey bee samples to balance sequencing cost and reliable output; and 43 million would be sufficient for sequencing bumble bee samples.
+Shallower sequencing can be adopted with reduced emphasis on rare species. 
+As for functional profiling, obtaining as many reads as possible would be the recommendation. 
+These results provide guidelines for cost-effective metagenomic investigations of bee microbiomes. 
+Methods used in this project can be adopted to similar studies for other host species, which are recommended before undertaking metagenomic projects with big sample size.
+
 % Then I conducted rarefaction analysis, computing expected species/KO diversity (Hill numbers of order 0, 1, 2) returned by given sequencing effort in order to optimize sequencing depth for balancing cost and reliable estimation of diversity.
@@
 \section{Data and Code Availability}
-% Personal access token:
-% 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
 Scripts used for the analyses are available at \href{https://github.com/CongLiu37/CMEECourseWork/tree/main/MResProject}{github}. 
@@
 
-% \appendix
-% \appendixpage
-% \addappheadtotoc
+\newpage
+
+  % \bibliographystyle{unsrt}
+  % \bibliographystyle{plainnat}
+  \bibliography{reference}
+
+\newpage
+
 \newcommand{\beginsupplement}{%
@@
     \label{HostRemove}
-    Raw data quality control was conducted to reduce compromise from low quality reads.
+    Raw data quality control was conducted to reduce compromise from low-quality reads.
     Raw data quality was checked using FastQC v.0.11.5 \citep{andrews2010fastqc} before filtering. 
     FastQC reports of raw reads showed the following aspects need to be covered in quality control: (1) low base quality in 3'-end (Figure \ref{QC}a); (2) uneven base content in 5'-end (Figure \ref{QC}c) and (3) the present of Nextera adaptors (Figure \ref{QC}e).
-    Therefore, raw reads were filtered using Trimmomatic v.0.39 \citep{bolger2014trimmomatic}, which (1) trimmed adaptors; (2) cutted 15 bases from the 5'-ends of reads; (3) cutted bases off from 3'-ends of reads if Phred-33 quality is below 20; (4) dropped reads shorter than 50 bp; (5) dropped reads if average Phred-33 quality is below 20.
+    Therefore, raw reads were filtered using Trimmomatic v.0.39 \citep{bolger2014trimmomatic}, which (1) trimmed adaptors; (2) cutted 15 bases from the 5'-ends of reads; (3) cut bases off from 3'-ends of reads if Phred-33 quality is below 20; (4) dropped reads shorter than 50 bp; (5) dropped reads if average Phred-33 quality is below 20.
     Then unpaired reads were removed and quality of clean data was checked using FastQC (Figure \ref{QC}d, \ref{QC}e, \ref{QC}f).
@@
     Besides, alignments with an E-value $< 1e-5$ or identity $< 50\%$ were removed, and for each contig, only alignments above 10\% of the best local bit score were retained. 
-    The output of DIAMOND was analysized by the \textit{blast2rma} tool of MEGAN6 with \textit{-lg} flag, which runs lowest-common-ancestor (LCA)-based algorithm developed for long contigs and assigns each contig to a taxon \citep{huson2018megan}.
+    The output of DIAMOND was analysed by the \textit{blast2rma} tool of MEGAN6 with \textit{-lg} flag, which runs lowest-common-ancestor (LCA)-based algorithm developed for long contigs and assigns each contig to a taxon \citep{huson2018megan}.
     The parameter \textit{-supp} was 0, which means the present of a taxon would be identified as long as at least one contig was assigned. 
@@
     \label{candidate_models}
-    \resizebox{\textwidth}{!}{%
+    \resizebox{500pt}{!}{%
     \begin{tabular}{lllllll}
@@
     \label{data_statistics}
-    \resizebox{\textwidth}{!}{
+    \resizebox{500pt}{!}{
     \begin{tabular}{@{}ccccc@{}}
@@
     \includegraphics[width=0.8\textwidth]{../Figures/RelativeAbundance_0_01_species_Viruses.pdf}
-    \caption{Heatmaps for viruse species abundance distribution in all samples. 
-    The relative abundance takes reads assigned to viruse species as background. 
+    \caption{Heatmaps for virus species abundance distribution in all samples. 
+    The relative abundance takes reads assigned to virus species as background. 
     Species with relative abundance smaller than 1\% in all samples are collapsed as "others".}
@@
 
-  \newpage
-
-  % \bibliographystyle{unsrt}
-  % \bibliographystyle{plainnat}
-  \bibliography{reference}
-
 \end{document}

### 2021-08-25 MResProject/Code/CompareSensitivity.R

@@ -14,7 +14,7 @@
 
 library(ggplot2)
 
-HillDiversity = read.table("Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
+HillDiversity = read.table("/home/cong/CMEECourseWork/MResProject/Tables/Taxon_HillDiversity.txt",sep="\t",header=TRUE,row.names = NULL)
 
 LF_F18 = subset(HillDiversity,HillDiversity$Sample=="LF_F18")
 PGcomcol3_Bimp = subset(HillDiversity,HillDiversity$Sample=="PGcomcol3_Bimp")
@@ -25,7 +25,7 @@ PGnos_high_hv13_2 = subset(HillDiversity,HillDiversity$Sample=="PGnos_high_hv13-
 PGnos_inter_hv15 = subset(HillDiversity,HillDiversity$Sample=="PGnos_inter_hv15")
 PGpollen_fresh = subset(HillDiversity,HillDiversity$Sample=="PGpollen_fresh")
 
-pdf("ExtraSpecies_Bumble.pdf")
+pdf("/home/cong/CMEECourseWork/MResProject/Figures/ExtraSpecies_Bumble.pdf")
 p1 = ggplot()+
   geom_point(size=4,(aes(x=PGcomcol3_Bimp$CleanRead*PGcomcol3_Bimp$SubsamplePercent/1e+6,
                          y=(PGcomcol3_Bimp$SpeciesRichness-PGcomcol3_Bimp$AssemblySpeciesRichness)/PGcomcol3_Bimp$AssemblySpeciesRichness,
@@ -48,7 +48,8 @@ p1 = ggplot()+
   scale_x_continuous(expand = c(0,0),limits = c(0,65))+
   scale_y_continuous(expand = c(0,0),limits = c(-1,1))+
   scale_color_manual(values=c("#FF3399","#FF3300","#990000"),
-                     labels=c("Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2"))
+                     labels=c("Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2"))+
+  geom_hline(aes(yintercept = 0,linetype="dashed",size=10))
 print(p1)
 dev.off()
 #
@@ -82,9 +83,9 @@ p2 = ggplot()+
 print(p2)
[…]

### 2021-08-25 MResProject/Code/FiguresFromOriginalData.R

@@ -35,12 +35,12 @@ data = rbind(
 pdf("NonHostRatio.pdf")
 p = ggplot(data,aes(fill=Type,x=relabel,y=ReadCount/1e+6))+
   geom_bar(stat = "identity")+
-  ylab("Read (million)")+
+  ylab("Reads (million)")+
   xlab(NULL)+
   theme_classic()+
   theme(axis.title.y=element_text(size=12,face="bold"),
         axis.text.y=element_text(size=12,face="bold"),
-        axis.text.x=element_text(size=12,face="bold",angle=-62,hjust=0,vjust=0),
+        axis.text.x=element_text(size=12,face="bold",angle=90,hjust=0,vjust=0), # 
         legend.text=element_text(size=12,face="bold"),
         legend.title=element_text(size=12,face="bold"),
         legend.position="top")+
@@ -98,7 +98,7 @@ Plot = function(rank){
     theme_classic()+
     theme(axis.title.y=element_text(size=12,face="bold"),
           axis.text.y=element_text(size=12,face="bold"),
-          axis.text.x=element_text(size=12,face="bold",angle=-62,hjust=0,vjust=0),
+          axis.text.x=element_text(size=12,face="bold",angle=90,hjust=0,vjust=0),
           legend.text=element_text(size=12,face="bold"),
           legend.title=element_text(size=12,face="bold"),
           legend.position="top")+
@@ -239,8 +239,8 @@ Matrix2Heatmap = function(rank,dominance,group,width,height){
   
   pdf(figure,width=width,height=height)
   p = Heatmap(data,
-              name="Relative Abundance",
-              heatmap_legend_param = list(title_position="topleft",
+              heatmap_legend_param = list(title = "Relative Abundance",
+                                          title_position="topleft",
                                           title_gp=gpar(fontsize=5, fontface="bold"),
                                           labels_gp = gpar(fontsize = 5)),
               # column_title=FALSE,
@@ -249,7 +249,8 @@ Matrix2Heatmap = function(rank,dominance,group,width,height){
               row_title_gp=gpar(fontface = "bold",fontsize=8),
               column_names_gp=gpar(fontface ="bold",fontsize=5),
               column_title_gp=gpar(fontface="bold",fontsize=8),
-              column_names_side = "top",
+              column_names_side = "bottom",
+              column_names_rot = 90,
               cluster_rows=FALSE,
[…]

### 2021-08-31 MResProject/Latex/CompileLatex.sh
CMEECourseWork

@@ -12,3 +12,6 @@ rm $1.blg
 rm $1.synctex.gz
 rm $1.fdb_latexmk
 rm $1.fls
+rm $1.nav
+rm $1.snm
+rm $1.toc

### 2021-09-08 MResProject/Latex/Draft.tex
CMEECourseWork

@@
 
+\newpage
+\subsection{Presentation}
+As pollinators, bees play crucial role in agriculture and provide huge economic benefit
+\newline
+but their populations are facing challenges from factors like invasive species, parasites, pesticide exposure, habitat loss and climate change. 
+Together, these make bee health a crucial issue.
+\newline
+Like other animals, bees are associated with diverse gut microbial communities impacting host health. 
+It includes bacteria, fungi and viruses. 
+It also provides materials of environmental DNA, indicating interactions with other organisms.
+\newline
+This microbiome influences bee health significantly by mediating processes including food digestion, parasite defence and chemical detoxification. 
+\newline
+Exploration of bee microbiome has been boosted by high throughput methods such as amplicon sequencing and shotgun metagenomics.
+Amplicon sequencing captures species-specific region to reveal composition of microbial communities. 
+It is cost-effective and is vastly used. 
+However, it does not cover all taxa and does not provide information on gene content, making unreliable function inference. (strain diversity)
+(Strains of Gilliamella apicola variant in metabolizing mannose, xylose, arabinose, and rhamnose, all of which are toxic to bees)
+(Strains of lactobacilli and bifidobacteria are highly variant in carbohydrate metabolism)
+Shotgun metagenomics provides a solution to overcome these drawbacks by capturing DNA fragments unselectively.
+\newline
+However, shotgun metagenomics is of complex data analysis and high cost.   
+Generally, one of the first steps of data analysis is assembling short reads into long contigs, which enable accurate taxonomic/functional annotation. 
+But assembly is of high false negative rate since there are always reads left unassembled. 
+Alternatively, short reads can also be processed directly by mapping to a reference database, but the output might be inaccurate due to limited mappability.
+Besides, shotgun metagenomics is high cost. 
+A shallow 6 Gbp metagenomic dataset may cost 120 pounds per sample, while a standard 15 Mbp amplicon sequencing only costs about 20 pounds per sample. 
+\newline
+Here, I aimed to address data analysis pipeline and high cost shotgun metagenomics. 
+\newline
+I developed an integrated pipeline combining assembly-dependent and assembly-free methods. 
+Raw reads are first filtered to remove low quality data and host contamination. 
+Then clean reads are assembled for species identification. 
+To resolve species not represent by the assembly, I mapped reads to genomes of identified species. 
+Unmapped reads are processed directly for species identification. 
+\newline
+Using this pipeline, I processed datasets from hony bees, bumble bees and flower washes.
+\newline
+Although these datasets are different in proportion of host contamination, they all represent a multi-kingdom community.
+\newline
+Bees possess a highly conserved and specialized core gut microbiome, which consists of bacteria including Bifidobacterium, Lactobacillus, Gilliamella, Frischella and Snodgrassella. 
+This heatmap shows the composition of bacterial communities and as expected, a complete set of core bacterial were found. 
+It indicates these samples were of good quality and representivity.
+\newline
+As for other species, there were insect pollinators and crops. Fungal communities were dominated by Nosema, a widespread bee pathogen and some yeast species. 
+\newline
+Then I compared integrated pipeline with a standard assembly-dependent methods. 
+These points above zero means the integrated pipeline resolved species not represented by assembly
+\newline
+A brief summary: I developed a pipeline analyzing metagenomic data. 
+It is capable of finding more species than assembly-dependent methods. 
+Besides, it is easy to incorporate alternative tools into each module and is easy for troubleshooting since all output files are well documented. 
+\newline
+Then I optimized sequencing depth for metagenomics of different host species, in order to define a trade-off between sequencing effort and reliable species/function diversity analysis.
+\newline
+First, I measured species/function diversity. 
+There are several diversity indexes used in ecology and among them, I picked Hill numbers. 
+Hill number is a family of parametric diversity indexes and it provides several unique advantages. 
+First, it obeys replication principle: 
+Assume there are two equally diverse assemblages with no shared species, the diversity of pooled assemblage is twice the single assemblages. 
+It indicates that as sequencing depth increase, discovery of novel species would lead to increase in Hill numbers. 
+When the sequencing depth is so big that almost all species have been found, Hill numbers would level off. 
+Second, its sensitivity to relative abundances can be modulated by values of order. 
+Big order value means little emphasis on rare species. 
+This is useful for metagenomics because rare species are more likely to be false positives than abundant species.
+Finally, it can be transformed to other diversity indexes like richness, shannon index and simpson index through simple algebraic transformation.
+\newline
+So I simulated shallow sequencing by randomly subsampling the original datasets and fitted the relationship between Hill numbers and sequencing depth. 
+The slope of the curve reflects extra diversity brought by additional sequencing effort. 
+So I looked the point at which the curve slope is small enough and defined it as the optimal sequencing depth, a trade-off between sequencing cost and obtaining meaningful information on species/function diversity.
+\newline
+This analysis assumes that the original dataset is almost complete, namely almost all species or function category are represented by the original dataset. 
+So I first looked at relationship between richness, or Hill number of order zero, and sequencing depth. 
+If the original dataset is complete, the model should level off at the final point. 
+Figures in first row are for species richness. 
+One honey bee sample and the flower sample were dropped because of incompleteness. 
+Figures in second row are for function diversity and no curve levels off.
+\newline
+As a result, 
+for species diversity estimation, 12.10 Gbp for honey bees and 12.75 Gbp for bumble bees would be sufficient. 
+Sequencing depth can be further reduced if there is little emphasis on rare species. 
+As for functional diversity, no datasets were complete.
+\newline
+So I estimated optimal sequencing depth for species diversity estimation of honey bee and bumble bee samples. 
+For function diversity, even the deepest dataset was not sufficient, indicating more sequencing effort is needed.
+\newline
+Finally some take-home message. 
+I developed a pipeline for metagenomic data analysis and it provides improvement in species identification. 
+Then I found that about 12 Gbp would be sufficient for species diversity estimation of honey bee and bumble bee samples, and that would be about 200 pounds per sample. 
+This sequencing depth can be further reduced if little weight is given to rare species. 
+As for function diversity, deep sequencing is valuable. 
+Similar experiments can be performed as pilot study of large scale projects and are helpful for budget management.
+
 \end{document}

### 2021-09-08 MResProject/Code/CompareSensitivity.R

@@ -49,22 +49,22 @@ p1 = ggplot()+
   scale_y_continuous(expand = c(0,0),limits = c(-1,1))+
   scale_color_manual(values=c("#FF3399","#FF3300","#990000"),
                      labels=c("Bee_Bimpatiens_hv3_1","Bee_Bimpatiens_hv4_1","Bee_Bimpatiens_hv4_2"))+
-  geom_hline(aes(yintercept = 0,linetype="dashed",size=10))
+  geom_hline(yintercept = 0,linetype="dotted",size=2)
 print(p1)
 dev.off()
 #
-pdf("ExtraSpecies_Honey.pdf")
+pdf("/home/cong/CMEECourseWork/MResProject/Figures/ExtraSpecies_Honey.pdf")
 p2 = ggplot()+
   # geom_point(size=2,(aes(x=PGnos_high_hv13_1$CleanRead*PGnos_high_hv13_1$SubsamplePercent/1e+6,
   #                        y=(PGnos_high_hv13_1$SpeciesRichness-PGnos_high_hv13_1$AssemblySpeciesRichness)/PGnos_high_hv13_1$AssemblySpeciesRichness,
   #                        colour="PGnos_high_hv13_1")))+
-  geom_point(size=2,(aes(x=PGnos_high_hv13_2$CleanRead*PGnos_high_hv13_2$SubsamplePercent/1e+6,
+  geom_point(size=4,(aes(x=PGnos_high_hv13_2$CleanRead*PGnos_high_hv13_2$SubsamplePercent/1e+6,
                          y=(PGnos_high_hv13_2$SpeciesRichness-PGnos_high_hv13_2$AssemblySpeciesRichness)/PGnos_high_hv13_2$AssemblySpeciesRichness,
                          colour="PGnos_high_hv13_2")))+
-  geom_point(size=2,(aes(x=PGnos_inter_hv15$CleanRead*PGnos_inter_hv15$SubsamplePercent/1e+6,
+  geom_point(size=4,(aes(x=PGnos_inter_hv15$CleanRead*PGnos_inter_hv15$SubsamplePercent/1e+6,
                          y=(PGnos_inter_hv15$SpeciesRichness-PGnos_inter_hv15$AssemblySpeciesRichness)/PGnos_inter_hv15$AssemblySpeciesRichness,
                          colour="PGnos_inter_hv15")))+
-  geom_point(size=2,(aes(x=PGpollen_fresh$CleanRead*PGpollen_fresh$SubsamplePercent/1e+6,
[…]

### 2021-09-08 MResProject/Code/run_ModelFitting.R

@@ -17,7 +17,7 @@
 library(ggplot2)
 library(minpack.lm)
 
-source("Diversity.R")
+source("DiversityModel.R")
 
 q_values = c("0","1","2")
 Samples = c("LF_F18","PGcomcol3_Bimp","PGcomcol4a_Bimp","PGcomcol4b_Bimp",
@@ -304,8 +304,10 @@ p7 = ggplot()+
   theme_classic()+
   theme(axis.title=element_text(size=20,face="bold"),
         axis.text=element_text(size=20,face="bold"),
-        legend.text=element_text(size=15,face="bold"),
-        legend.title=element_text(size=15,face="bold"),
+        #legend.text=element_text(size=15,face="bold"),
+        #legend.title=element_text(size=15,face="bold"),
+        legend.position="none",
+        plot.margin=unit(c(5.5, 230, 5.5, 5.5),"points"),
         title=element_text(size=20,face="bold"))+
   scale_x_continuous(expand = c(0,0),limits = c(0,1))+
   scale_y_continuous(expand = c(0,0),limits = c(0,180))+
@@ -325,8 +327,10 @@ p8 = ggplot()+
   theme_classic()+
   theme(axis.title=element_text(size=20,face="bold"),
         axis.text=element_text(size=20,face="bold"),
-        legend.text=element_text(size=15,face="bold"),
-        legend.title=element_text(size=15,face="bold"),
+        # legend.text=element_text(size=15,face="bold"),
+        # legend.title=element_text(size=15,face="bold"),
+        legend.position="none",
+        plot.margin=unit(c(5.5, 230, 5.5, 5.5),"points"),
         title=element_text(size=20,face="bold"))+
   scale_x_continuous(expand = c(0,0),limits = c(0,1))+
   scale_y_continuous(expand = c(0,0),limits = c(0,22))+
@@ -346,8 +350,10 @@ p9 = ggplot()+
   theme_classic()+
   theme(axis.title=element_text(size=20,face="bold"),
         axis.text=element_text(size=20,face="bold"),
-        legend.text=element_text(size=15,face="bold"),
-        legend.title=element_text(size=15,face="bold"),
+        # legend.text=element_text(size=15,face="bold"),
+        # legend.title=element_text(size=15,face="bold"),
+        legend.position="none",
+        plot.margin=unit(c(5.5, 230, 5.5, 5.5),"points"),
         title=element_text(size=20,face="bold"))+
[…]
